### 2014-10-17 EducProposal.Rmd
Created .bib files and updated README

---
title: "Source1"
author: "Sam"
date: "October 17, 2014"
output: html_document
bibliography
  - Main.bib
---

Education and Entrepreurship
Thierry Racuad and Sam Dundon
Introduction to Collaborative Social Science Data Analysis

```{r, echo=FALSE, include=FALSE}
# Install rempis from Christpher Gandrud's website
devtools::install_github('christophergandrud/repmis')
library(repmis)
# Load citation package
pkgs <- c('dplyr','ggplot2')
repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')

summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2014-10-17 EducProposal.Rmd
Updated Markdown file and linked with .bib file

@@
 ---
-title: "Source1"
-author: "Sam"
+title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
 date: "October 17, 2014"
+author: "Sam Dundon and Thierry Racaud"
 output: html_document
-bibliography
+bibliography:
   - Main.bib
@@
 
-Education and Entrepreurship
-Thierry Racuad and Sam Dundon
-Introduction to Collaborative Social Science Data Analysis
+*Introduction to Collaborative Social Science Data Analysis*
+
+###Research Question  
+Drawing a comparison between three different welfare systems, id est Sweden, France and Britain, to what extent do the behavioural characteristics of a given education system - more or less individualistic, more or less group focused, more or less reinforcing self-confidence - affect the rate of entrepreneurship in that country?!
+
+###Research design
+My thesis [@Scott1996] research project consists in a comparative study of educations policies in at least two or three EU countries and their specific economic impact, or its absence, on GDP through a detailed causal chain.
+Too often, at least in France, when it comes to public budgeting and allocating funds for education policies, the decision process does not seem to be very rational.
+Very often, it does not seem to take into account the return on investment that should be expected in the long run.
+Perhaps because many policy makers have no inside knowledge from the field, thus it could be that they do not have all the tools or do not know how to assess the potential impact, therefore, they just do not take this into their decision-making process.
+
+###Analytical Method
+The causal chain would be the following:
+
+More positive feedback and more self-confidence reinforcement, either within the organisation or directly between teachers and students should impact positively both the entrepreneurship rate and the career-change rate of the given country.
+
+More group-oriented and team-building practices, either within the organisation or as the staff strategy/policy towards strudents should lead to more of the same supportive approach to management in businesses throughout the given country.
+
+Should these three indicators indeed be impacted, then there could be some positive impact on GDP at large, of course controlling for more favourable environments, similar business perspectives, etc.
+
+The specific variables to trace this potential causal chain still need to be determined.
+
+###Concepts that I may need for my research
+
+####Return on Investment
+Self-confidence: It is difficult to obtain a credible measurement of self confidence, how should I measure this?
+
+Positive reinforcement is more easily defined but is also culture-dependent
+Individual-focused systems vs group-oriented ones, how do you delimitate?
+Types of management
+
+Return on Investment, how do you evaluate euros of tomorrow or value for money rate, perhaps using the social discount rate for some part, but also considering the potential GDP that could result from another education system management and culture vs what you would get carrying on like now.
 
@@
 
-summary(cars)
 ```
-
-You can also embed plots, for example:
-
-```{r, echo=FALSE}
-plot(cars)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2014-10-17 EducProposal.Rmd
Updates with references and estimate strategy

@@
 
-###Research design
-My thesis [@Scott1996] research project consists in a comparative study of educations policies in at least two or three EU countries and their specific economic impact, or its absence, on GDP through a detailed causal chain.
+###Research Justification
 Too often, at least in France, when it comes to public budgeting and allocating funds for education policies, the decision process does not seem to be very rational.
@@
 ###Analytical Method
-The causal chain would be the following:
+####Causal Chain
 
@@
 
+####Estimation Strategy  
+The estimation strategy will consist of using cross-sectional data about Sweden, France and Britain in different points in time regarding the sense of belonging to a group, the self-confidence patterns and the entrepreneurship features of each country.
+
+The dependent variable would be the rate of entrepreneurship with its related activities or attitudes as defined by the Global Entrepreneurship Monitor, or GEM [link](http://www.gemconsortium.org).  
+- Established Business Ownership Rate   
+- Entrepreneurial intention  
+- Entrepreneurship as desirable career choice
+
+The explanatory variables would be the sense of belonging to the group as defined by OECD PISA (Data from 2012), the sense of individuality as an index constructed from World Value Survey items (Data from 2005 /2006), the degree of self confidence as an index again gathered from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
+
+We will obviously need to control for the economic outlook at the time of data collection about entrepreneurship characteristics.
+But we will also need to control for nine key entrepreneurship conditions as defined in the National Experts Survey (NES) that may affect the rate of entrepreneurship.
+
+These nine conditions are the following:
+- Finance   
+- Government policies  
+- Government programmes  
+- Entrepreneurial Education and Training  
+- Research and Development Transfer (R & D)  
+- Commercial and professional infrastructure  
+- Internal Market openness  
+- Physical infrastructure and services  
+- Cultural and social norms
+
+The first step will be to see what the different behavioural and cultural patterns are in each country as observed among students.
+The differences observed may require some cultural explanations, including explanations regarding the type of welfare state in the given country.
+
+Then, should indeed different patterns be observed, we will need to proceed to an Ordinary Least Square (OLS) Regression in order to check to what extent these characteristics affect the rate of entrepreneurship in the country.
+
+Our main hypothesis would be that the more culturally group-oriented and the more self-confident a population is, the higher should entrepreneurship in that country be.
+
+Aside the sense of belonging as defined by OECD PISA study, here are some of the items from the World Value Survey 2005-2009 wave I could use to build the indexes about “sense of belonging to a group“, “sense of individuality” and “degree of self confidence”.
+
 ###Concepts that I may need for my research
@@
 
-Positive reinforcement is more easily defined but is also culture-dependent
-Individual-focused systems vs group-oriented ones, how do you delimitate?
+Positive reinforcement is more easily defined but is also culture-dependent. Individual-focused systems vs group-oriented ones, how do you delimitate?
+
 Types of management
@@
 ```
+
+###Literature Review
+
+###References

### 2014-10-17 EducProposal.Rmd
Added hyperlinks to proposal markdown file

@@
 
-The dependent variable would be the rate of entrepreneurship with its related activities or attitudes as defined by the Global Entrepreneurship Monitor, or GEM [link](http://www.gemconsortium.org).  
+The dependent variable would be the rate of entrepreneurship with its related activities or attitudes as defined by the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org).
+
 - Established Business Ownership Rate   
@@
 
-The explanatory variables would be the sense of belonging to the group as defined by OECD PISA (Data from 2012), the sense of individuality as an index constructed from World Value Survey items (Data from 2005 /2006), the degree of self confidence as an index again gathered from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
+The explanatory variables would be the sense of belonging to the group as defined by OECD [Program for International Student Assessment (PISA)](http://www.oecd.org/pisa/) (Data from 2012), the sense of individuality as an index constructed from [World Value Survey](http://www.worldvaluessurvey.org/wvs.jsp) items (Data from 2005 /2006), the degree of self confidence as an index again gathered from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
 
 We will obviously need to control for the economic outlook at the time of data collection about entrepreneurship characteristics.
-But we will also need to control for nine key entrepreneurship conditions as defined in the National Experts Survey (NES) that may affect the rate of entrepreneurship.
+But we will also need to control for nine key entrepreneurship conditions as defined in the [National Experts Survey (NES)](http://www.gemiran.ir/sec/gem/?@=28) that may affect the rate of entrepreneurship.
 

### 2014-10-18 EducProposal.Rmd
Created maps to add to Assignment 2, updated README and edited text

--- 2014-10-17 EducProposal.Rmd
@@
 ---
+* * * 
+```{r echo=FALSE,cache=TRUE}
+# Install necessary packages
+library(maps)
+library(mapdata)
+```
 
@@
 ###Research Question  
-Drawing a comparison between three different welfare systems, id est Sweden, France and Britain, to what extent do the behavioural characteristics of a given education system - more or less individualistic, more or less group focused, more or less reinforcing self-confidence - affect the rate of entrepreneurship in that country?!
+Drawing a comparison between Sweden, France, and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-focused, or focused on positive reinforcement - affect the rate of entrepreneurship in each country?
 
-###Research design
-My thesis [@Scott1996] research project consists in a comparative study of educations policies in at least two or three EU countries and their specific economic impact, or its absence, on GDP through a detailed causal chain.
-Too often, at least in France, when it comes to public budgeting and allocating funds for education policies, the decision process does not seem to be very rational.
+```{r echo=FALSE,cache=TRUE}
+map('worldHires', 'sweden', col="gray90", fill=TRUE)
+
+map('worldHires',
+    c('UK', 'Ireland', 'Isle of Man','Isle of Wight','Wales:Anglesey'),
+    xlim=c(-11,3), ylim=c(49,60.9),
+    col="gray90", fill=TRUE)
+
+map('worldHires','France', xlim=c(-8.2,8.5), ylim=c(42.2,51.1),
+    col="gray90", fill=TRUE)
+
+```
+
+###Research Justification
+Often, when it comes to public budgeting for education policies, the decision process does not appear to be rational.
 Very often, it does not seem to take into account the return on investment that should be expected in the long run.
-Perhaps because many policy makers have no inside knowledge from the field, thus it could be that they do not have all the tools or do not know how to assess the potential impact, therefore, they just do not take this into their decision-making process.
+Perhaps this is because many policy makers have no inside knowledge of the field.
+Thus, it may be that they do not have all of the neccesary tools or do not know how to assess the potential impact of their funding decisions, leading to the exclusion of this consideration from their decision-making process.
 
 ###Analytical Method
-The causal chain would be the following:
+####Causal Chain
 
-More positive feedback and more self-confidence reinforcement, either within the organisation or directly between teachers and students should impact positively both the entrepreneurship rate and the career-change rate of the given country.
+A higher degree of positive feedback and self-confidence reinforcement, either within organisations or directly between teachers and students is expected to positively impact both the  entrepreneurship rate and the rate of career-change within a given country.
 
-More group-oriented and team-building practices, either within the organisation or as the staff strategy/policy towards strudents should lead to more of the same supportive approach to management in businesses throughout the given country.
+More group-oriented and team-building practices, either within organisations or as a staff strategy/policy towards students is expected to lead to more of the same supportive approach in a team member-manager context within a given country.
 
-Should these three indicators indeed be impacted, then there could be some positive impact on GDP at large, of course controlling for more favourable environments, similar business perspectives, etc.
+If these assumptions are correct, the positive impact of these practices may increase productivity and country GDP.
+This project will identify variables that may be used to conduct this analysis and appropriate control variables to account for other business conditions and social conditions.
+The specific variables to trace this potential causal chain still need to be determined.
 
-The specific variables to trace this potential causal chain still need to be determined.
+####Estimation Strategy  
+The estimation strategy will consist of using cross-sectional data about Sweden, France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.
+
+The dependent variable will be the rate of entrepreneurship with its related activities or attitudes as defined by the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org):
+
+- Established Business Ownership Rate;   
+- Entrepreneurial intention; and  
+- Entrepreneurship as desirable career choice.
+
+The explanatory variables will be the sense of belonging to the group as defined by OECD [Program for International Student Assessment (PISA)](http://www.oecd.org/pisa/) (Data from 2012), the sense of individuality as an index constructed from [World Value Survey](http://www.worldvaluessurvey.org/wvs.jsp) items (Data from 2005 /2006), the degree of self confidence as an index again gathered from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
+
+As mentioned above, we will need to control for the economic outlook at the time of data collection about entrepreneurship characteristics.
+We will also need to control for nine key entrepreneurship conditions as defined in the [National Experts Survey (NES)](http://www.gemiran.ir/sec/gem/?@=28) that may affect the rate of entrepreneurship.
+These nine conditions are the following:
+
+1. Finance  
+2. Government policies  
+3. Government programmes  
+4. Entrepreneurial Education and Training  
+5. Research and Development Transfer (R & D)  
+6. Commercial and professional infrastructure  
+7. Internal Market openness  
+8. Physical infrastructure and services  
+9. Cultural and social norms
+
+The first step will be to see what the different behavioural and cultural patterns are in each country as observed among students.
+The differences observed may require some cultural explanations, including explanations regarding the type of welfare state in the given country.
+
+Then, should indeed different patterns be observed, we will need to proceed to an Ordinary Least Square (OLS) Regression in order to check to what extent these characteristics affect the rate of entrepreneurship in the country.
+
+Our main hypothesis would be that the more culturally group-oriented and the more self-confident a population is, the higher should entrepreneurship in that country be.
+
+Aside the sense of belonging as defined by OECD PISA study, here are some of the items from the World Value Survey 2005-2009 wave I could use to build the indexes about “sense of belonging to a group“, “sense of individuality” and “degree of self confidence”.
 
@@
 
-```{r, echo=FALSE, include=FALSE}
+```{r, echo=FALSE, include=FALSE, cache=TRUE}
 # Install rempis from Christpher Gandrud's website

### 2014-10-18 EducProposal.Rmd
Deleted unncessary files and edited proposal accordingly

@@
 * * * 
-```{r echo=FALSE,cache=TRUE}
+```{r echo=FALSE,cache=TRUE,include=FALSE}
+# Set working directory
+setwd('~/DataAnalysis/')
+
 # Install necessary packages
-library(maps)
-library(mapdata)
+# Install rempis from Christpher Gandrud's website
+devtools::install_github('christophergandrud/repmis')
+library(repmis)
+# Load citation package
+pkgs <- c('dplyr','ggplot2')
+repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')
+
 ```
@@
 Drawing a comparison between Sweden, France, and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-focused, or focused on positive reinforcement - affect the rate of entrepreneurship in each country?
-
-```{r echo=FALSE,cache=TRUE}
-map('worldHires', 'sweden', col="gray90", fill=TRUE)
-
-map('worldHires',
-    c('UK', 'Ireland', 'Isle of Man','Isle of Wight','Wales:Anglesey'),
-    xlim=c(-11,3), ylim=c(49,60.9),
-    col="gray90", fill=TRUE)
-
-map('worldHires','France', xlim=c(-8.2,8.5), ylim=c(42.2,51.1),
-    col="gray90", fill=TRUE)
-
-```
 
@@
 
-```{r, echo=FALSE, include=FALSE, cache=TRUE}
-# Install rempis from Christpher Gandrud's website
-devtools::install_github('christophergandrud/repmis')
-library(repmis)
-# Load citation package
-pkgs <- c('dplyr','ggplot2')
-repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')
-
-```
-
 ###Literature Review

### 2014-10-18 TrialFile.Rmd
Deleted unncessary files and edited proposal accordingly

---
title: "Untitled"
author: "Sam"
date: "October 18, 2014"
output: html_document
---

This is an extra file for trying out features including making maps for the proposal.

```{r echo=FALSE, cache=TRUE}
install.packages('maptools')
library(maptools)
install.packages('maps')
library(maps)
install.packages('mapproj')
library(mapproj)
install.packages('ggmap')
library(ggmap)
install.packages('mapdata')
library(mapdata)

library(sp)
library(lattice)
install.packages('latticeExtra')
library(latticeExtra)
library(colorspace)

# Create maps of Sweden, France, and the UK using maps and mapdata packages
map('worldHires', 'sweden', col="gray90", fill=TRUE)

map('worldHires',
    c('UK', 'Ireland', 'Isle of Man','Isle of Wight','Wales:Anglesey'),
    xlim=c(-11,3), ylim=c(49,60.9),
    col="gray90", fill=TRUE)

map('worldHires','France', xlim=c(-8.2,8.5), ylim=c(42.2,51.1),
    col="gray90", fill=TRUE)
```

### 2014-10-18 EducProposal.Rmd
Re-arranged and tried to simplify code chunks in proposal

@@
 # Load citation package
-pkgs <- c('dplyr','ggplot2')
+pkgs <- c('dplyr','ggplot2','repmis')
 repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')
@@
 
-Our main hypothesis would be that the more culturally group-oriented and the more self-confident a population is, the higher should entrepreneurship in that country be.
+Our main hypothesis is that the more culturally group-oriented and the more self-confident a population is, the higher entrepreneurship in that country will be.
 
-Aside the sense of belonging as defined by OECD PISA study, here are some of the items from the World Value Survey 2005-2009 wave I could use to build the indexes about “sense of belonging to a group“, “sense of individuality” and “degree of self confidence”.
+###Neccesary Concepts  
+1.
+Return on Investment: Assigning a future Euro value to a present-day investment.
+This may require the use of a social deiscout rate, but will also need to consider the potential GDP increase brought about by improved education policies.
 
-###Concepts that I may need for my research
+2.
+Self-confidence: It is difficult to obtain a credible measurement of self confidence, but the study considers how this increased self-confidence positively affects GDP and the rate of entrepeurship in a given country.
+It will therefore need to include some quantiative approach to measuring this factor.
 
-####Return on Investment
-Self-confidence: It is difficult to obtain a credible measurement of self confidence, how should I measure this?
+3.
+Positive reinforcement: This is easier to define than self-confience, but it is also culture-dependent (individual-focused systems vs group-oriented ones).
+This will also need to be quantified for the qualitative portion of this project.
 
-Positive reinforcement is more easily defined but is also culture-dependent. Individual-focused systems vs group-oriented ones, how do you delimitate?
-
-Types of management
-
-Return on Investment, how do you evaluate euros of tomorrow or value for money rate, perhaps using the social discount rate for some part, but also considering the potential GDP that could result from another education system management and culture vs what you would get carrying on like now.
+4.
+Types of management: This study focuses on social issues and how these factors affect entrepreneurship, but management styles can transcend social norms.
+Control variables will need to be identified to address this.
 

### 2014-10-18 EducProposal.Rmd
Tried making a table for the proposal document

@@
 * * * 
-```{r echo=FALSE,cache=TRUE,include=FALSE}
+```{r echo=FALSE, cache=TRUE, include=FALSE}
 # Set working directory

### 2014-10-18 TrialFile.Rmd
Tried making a table for the proposal document

@@
 ```
+
+<table>
+<tr class="header">
+<th align="left"> </th>
+<th align="left"> </th>
+</tr>
+<tr class="odd">
+<td align="left">Finance</td>
+<td align="left">Government Policy</td>
+<td align="left">Entrepreneurial Education and Training</td>
+<td align="left">Research and Development Transfer (R & D)</td>
+
+</tr>
+<tr class="even">
+<td align="left">Commercial and professional infrastructure</td>
+<td align="left">Internal Market openness</td>
+<td align="left">Physical infrastructure and services</td>
+<td align="left">Cultural and social norms </td>
+</tr>
+</table>

### 2014-10-19 TrialFile.Rmd
Reverted to bullets for proposal document

@@
     col="gray90", fill=TRUE)
+
+### Need a map of 3 kinds of welfare states
+### Scandanavian
+### Market oriented (UK)
+### France/Germany - state established historical welfare state
+
 ```

### 2014-10-21 EducProposal.Rmd
Reverted to bullets for proposal document
Update EducProposal.Rmd

@@
 ###Research Question  
-Drawing a comparison between Sweden, France, and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-focused, or focused on positive reinforcement - affect the rate of entrepreneurship in each country?
+Drawing a comparison between Portugal, Sweden, France, and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, or focused on positive reinforcement - affect the rate of entrepreneurship in each country?
 
@@
 Very often, it does not seem to take into account the return on investment that should be expected in the long run.
-Perhaps this is because many policy makers have no inside knowledge of the field.
-Thus, it may be that they do not have all of the neccesary tools or do not know how to assess the potential impact of their funding decisions, leading to the exclusion of this consideration from their decision-making process.
+Still many claimns have been made in the literature that start-up and entrepreneurship activities at a country-level are affected by factors other than structural and economic, that is cultural or educational.
+However only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, almost none explored how cultural patterns affected these dispositions.
 

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

@@
 ####Estimation Strategy  
-The estimation strategy will consist of using cross-sectional data about Sweden, France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.
+The estimation strategy will consist of using cross-sectional data about Portugal, Sweden, France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.
 

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

@@
 ###Research Justification
-Often, when it comes to public budgeting for education policies, the decision process does not appear to be rational.
-Very often, it does not seem to take into account the return on investment that should be expected in the long run.
-Still many claimns have been made in the literature that start-up and entrepreneurship activities at a country-level are affected by factors other than structural and economic, that is cultural or educational.
+Often, when it comes to public budgeting for education policies, the decision process does not appear to be rational, it does not seem to take into account the return on investment that should be expected in the long run.
+Still many claims have been made in the literature that start-up and entrepreneurship activities at a country-level are affected by factors other than structural and economic, that is cultural or educational.
 However only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, almost none explored how cultural patterns affected these dispositions.

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

@@
 However only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, almost none explored how cultural patterns affected these dispositions.
+
+When cultural factors are looked at, they are considered as a given feature that can hardly be traced.
+By having a closer look at education systems, we intend to look at the processes through which some of these cultural patterns are enhanced and passed from one generation to the next.
+Aside of parental education, schools are indeed the very place where children are taught how to fit in the society.
+This research is an attempt at looking at one trait in particular
 

### 2014-10-21 EducProposal.Rmd
Trial with picture
Removed unnecessary picture
Another unnecessary picture removed
Update EducProposal.Rmd

@@
 Aside of parental education, schools are indeed the very place where children are taught how to fit in the society.
-This research is an attempt at looking at one trait in particular
+This research is an attempt at looking at one trait in particular that is self-confidence.
+
+Chart about factors that affect entrepreneurship.
+Source: OECD Local Entrepreneurship Reviews
+Strentghening Entrepreneurship and economic development in East Germany: Lessons from local approaches.
+![here](https://github.com/SamDund/Assign2Education/blob/master/Untitled.png)
 

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

--- 2014-10-21 EducProposal.Rmd
@@
 ###Research Justification
-Often, when it comes to public budgeting for education policies, the decision process does not appear to be rational, it does not seem to take into account the return on investment that should be expected in the long run.
-Still many claims have been made in the literature that start-up and entrepreneurship activities at a country-level are affected by factors other than structural and economic, that is cultural or educational.
-However only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, almost none explored how cultural patterns affected these dispositions.
+When it comes to public budgeting for education policies, the decision process often does not appear to be rational.
+That is, it does not seem to take into account the return on investment that should be expected in the long run.
+Despite this, many claims have been made in the entrepreneurship literature that start-up activities at a country-level are affected by factors other than structural and economic, including cultural and educational.
+However only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, while almost none explored how cultural patterns affected these dispositions.
+
+When cultural factors are examined, they are considered as a given feature that can hardly be traced.
+By having a closer look at education systems, we intend to explore the processes through which some of these cultural patterns are enhanced and passed from one generation to the next.
+Aside from parental education, schools are indeed the very place where children are taught how to fit into society.
+This research is an attempt at looking at one trait in particular, self-confidence.
+
+Chart about factors that affect entrepreneurship.
+Source: OECD Local Entrepreneurship Reviews
+Strentghening Entrepreneurship and economic development in East Germany: Lessons from local approaches.
+![here](https://github.com/SamDund/Assign2Education/blob/master/Untitled.png)
 

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

@@
 ###Research Question  
-Drawing a comparison between Portugal, Sweden, France, and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, or focused on positive reinforcement - affect the rate of entrepreneurship in each country?
+Drawing a comparison between Portugal, Sweden, France, and Britain, to what extent do the behavioural characteristics of the education system - the degree of reliance on positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
 
@@
 
-A higher degree of positive feedback and self-confidence reinforcement, either within organisations or directly between teachers and students is expected to positively impact both the  entrepreneurship rate and the rate of career-change within a given country.
+A higher degree of positive feedback and self-confidence reinforcement, either within organisations or directly between teachers and students is expected to positively impact the rate of entrepreneurship within the country.
 

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

@@
 
-A higher degree of positive feedback and self-confidence reinforcement, either within organisations or directly between teachers and students is expected to positively impact the rate of entrepreneurship within the country.
+Stronger culture of positive reinforcement ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level
 
-More group-oriented and team-building practices, either within organisations or as a staff strategy/policy towards students is expected to lead to more of the same supportive approach in a team member-manager context within a given country.
-
-If these assumptions are correct, the positive impact of these practices may increase productivity and country GDP.
-This project will identify variables that may be used to conduct this analysis and appropriate control variables to account for other business conditions and social conditions.
 The specific variables to trace this potential causal chain still need to be determined.

### 2014-10-21 TrialFile.Rmd
Re-knitted proposal

--- 2014-10-18 TrialFile.Rmd
@@
     col="gray90", fill=TRUE)
+
+### Need a map of 3 kinds of welfare states
+### Scandanavian
+### Market oriented (UK)
+### France/Germany - state established historical welfare state
+
 ```
+
+![Untitled.png](~/DataAnalysis)

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

@@
 ###Research Question  
-Drawing a comparison between Portugal, Sweden, France, and Britain, to what extent do the behavioural characteristics of the education system - the degree of reliance on positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
+Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - the degree of reliance on positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
 
@@
 
-The specific variables to trace this potential causal chain still need to be determined.
-
 ####Estimation Strategy  
-The estimation strategy will consist of using cross-sectional data about Portugal, Sweden, France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.
+The estimation strategy will consist of using cross-sectional data about France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.
 
@@
 
-The explanatory variables will be the sense of belonging to the group as defined by OECD [Program for International Student Assessment (PISA)](http://www.oecd.org/pisa/) (Data from 2012), the sense of individuality as an index constructed from [World Value Survey](http://www.worldvaluessurvey.org/wvs.jsp) items (Data from 2005 /2006), the degree of self confidence as an index again gathered from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
+The key explanatory variable will be the degree of self confidence as an index that we will compute from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
 
@@
 
-The first step will be to see what the different behavioural and cultural patterns are in each country as observed among students.
-The differences observed may require some cultural explanations, including explanations regarding the type of welfare state in the given country.
+The first step will be to see if, regarding self-confidence, different patterns can be observed in each country. In which case, we may need to call on cultural explanations.
 
@@
 
-Our main hypothesis is that the more culturally group-oriented and the more self-confident a population is, the higher entrepreneurship in that country will be.
+Our main hypothesis is that the more self-confident a population is on average, the higher entrepreneurship in that country will be.
 

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

@@
 Return on Investment: Assigning a future Euro value to a present-day investment.
-This may require the use of a social deiscout rate, but will also need to consider the potential GDP increase brought about by improved education policies.
+This may require the use of a social discount rate, but will also need to consider the potential GDP increase brought about by improved education policies.
 
-2.
-Self-confidence: It is difficult to obtain a credible measurement of self confidence, but the study considers how this increased self-confidence positively affects GDP and the rate of entrepeurship in a given country.
-It will therefore need to include some quantiative approach to measuring this factor.
+2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach to measuring this factor.
 
@@
 
-4.
-Types of management: This study focuses on social issues and how these factors affect entrepreneurship, but management styles can transcend social norms.
-Control variables will need to be identified to address this.
-
 ###Literature Review

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

@@
 
-###Neccesary Concepts  
+###Necessary Concepts  
 1.
@@
 
-3.
-Positive reinforcement: This is easier to define than self-confience, but it is also culture-dependent (individual-focused systems vs group-oriented ones).
-This will also need to be quantified for the qualitative portion of this project.
+3. Positive reinforcement: This can possibly be computed as an index and characterized on a scale even if this is not easy to quantify.
 

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

@@
 
+What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
+However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” (Freytag Andreas, Thurik Roy, 2007).
+Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
+
+Over a hundred years have passed since Max Weber tried to explicit how religious-ethical motivations affect entrepreneurship (Max Weber, 1905), and religion may be less effective in justifying why some are more likely to start businesses than others.
+Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” (OECD Report 2009).
+
+Despite various claims of the existence of a cultural effect, few empirical studies have actually been carried out.
+It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund (Davidsson and Wiklund study 1997), at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors.
+As they compared two Swedish regions similar in terms of structure, and observed different outcomes, they concluded on the possibility of a small cultural effect.
+
+This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities.
+
 ###References

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

@@
 Source: OECD Local Entrepreneurship Reviews
-Strentghening Entrepreneurship and economic development in East Germany: Lessons from local approaches.
+Strengthening entrepreneurship and economic development in East Germany: Lessons from local approaches.
 ![here](https://github.com/SamDund/Assign2Education/blob/master/Untitled.png)
@@
 
+"Self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).
+
 ###References

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

@@
 
-"Self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).
+We intend to look at self-esteem as partially the product of an education pattern, which would result into a higher self-confidence on average, even if so far, "self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).
 

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

--- 2014-10-21 EducProposal.Rmd
@@
 
-"Self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).
+We intend to look at self-esteem as partially the product of an education pattern, which would affect the whole population, even if so far, "self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).
 

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

--- 2014-10-21 EducProposal.Rmd
@@
 This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities.
-
-"Self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).
+More specifically, we intend to look at self-esteem as partially the product of an education pattern, which would affect the whole population, even if so far, "self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).
 

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 
-The key explanatory variable will be the degree of self confidence as an index that we will compute from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
+The key explanatory variable will be the degree of self confidence.
+We will compute an index from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
 

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities.
-More specifically, we intend to look at self-esteem as partially the product of an education pattern, which would affect the whole population, even if so far, "self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).
+Indeed, like many in the education literature tend to assert, we believe there is an effect of school personnel on student self-esteem (Scott, Dustin, Mertens, Murray, 1996).
+We will explore further the way this mechanism works.
+Now, entrepreneurship literature generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” (OECD Report 2009).
+We intend to show that these individual characteristics are partly shaped at an institutional collective level through the education systems and their staff attitudes.
+
+Of course, King and Sobel (2008), among others, have already tried to show how school choice can increase the rate of youth entrepreneurship but their perspective was slightly different.
+They  asserted that more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
+We believe there is a more widely spread systematic effect of cultural and educational patterns.
+David Watkins (2010) cross-cultural perspective on teaching and learning shall be useful in that respect.
+Kai-Ming Cheng and Kam-Cheung Wong’s study about school effectiveness in East Asia (2006) could also be of help.
+
+Also, as self-confidence is considered to rely partly on one’s integration within social networks (OECD Report 2009), we will also refer to cross-cultural studies such as that of Green, Deschamps and Páez (2005) about individualism and collectivism, or what Freeman (1997) called idiocentrism and allocentrism.
+Raeff, Greenfield and Quiroz (2000) have also conceptualised interpersonal relationships in both cultural contexts.
+More school-focused, Yamauchi (1998) as well as Davies and Aurini (2003) have looked at individualism and collectivism in the classroom and in pedagogy respectively.
+All these will be precious on the way.
+
+Besides direct or indirect school effects, we will necessarily look into entrepreneurship and its determinants at large.
+Thus we will refer to Grilo and Thurik’s research (2005 and 2006) about what determines entrepreneurship engagement levels throughout the European Union, and also to Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries (2002).
+Eventtually, with Gartner (1990) we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper (2008), we will asks ourselves what “entrepreneurship” data really shows.
 

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 
-2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach to measuring this factor.
+2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach in measuring this factor.
 
-3. Positive reinforcement: This can possibly be computed as an index and characterized on a scale even if this is not easy to quantify.
+3. Positive reinforcement: Again even if this is not easy to quantify, we will attempt to compute as an index and characterize it on a scale.
 

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 ###Research Question  
-Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - the degree of reliance on positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
+Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
 

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
-However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” (Freytag Andreas, Thurik Roy, 2007).
+However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [(Freytag Andreas, Thurik Roy, 2007)](Freytag2007).
 Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.

### 2014-10-22 EducProposal.Rmd
No message

--- 2014-10-22 EducProposal.Rmd
@@
 
-The key explanatory variable will be the degree of self confidence.
-We will compute an index from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
+The key explanatory variable will be the degree of self confidence as an index that we will compute from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
 
@@
 
-2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach in measuring this factor.
+2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach to measuring this factor.
 
-3. Positive reinforcement: Again even if this is not easy to quantify, we will attempt to compute as an index and characterize it on a scale.
+3. Positive reinforcement: This can possibly be computed as an index and characterized on a scale even if this is not easy to quantify.
 
@@
 What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
-However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” (Freytag Andreas, Thurik Roy, 2007).
+However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [@Freytag2007].
 Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
@@
 This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities.
-Indeed, like many in the education literature tend to assert, we believe there is an effect of school personnel on student self-esteem (Scott, Dustin, Mertens, Murray, 1996).
-We will explore further the way this mechanism works.
-Now, entrepreneurship literature generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” (OECD Report 2009).
-We intend to show that these individual characteristics are partly shaped at an institutional collective level through the education systems and their staff attitudes.
-
-Of course, King and Sobel (2008), among others, have already tried to show how school choice can increase the rate of youth entrepreneurship but their perspective was slightly different.
-They  asserted that more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
-We believe there is a more widely spread systematic effect of cultural and educational patterns.
-David Watkins (2010) cross-cultural perspective on teaching and learning shall be useful in that respect.
-Kai-Ming Cheng and Kam-Cheung Wong’s study about school effectiveness in East Asia (2006) could also be of help.
-
-Also, as self-confidence is considered to rely partly on one’s integration within social networks (OECD Report 2009), we will also refer to cross-cultural studies such as that of Green, Deschamps and Páez (2005) about individualism and collectivism, or what Freeman (1997) called idiocentrism and allocentrism.
-Raeff, Greenfield and Quiroz (2000) have also conceptualised interpersonal relationships in both cultural contexts.
-More school-focused, Yamauchi (1998) as well as Davies and Aurini (2003) have looked at individualism and collectivism in the classroom and in pedagogy respectively.
-All these will be precious on the way.
-
-Besides direct or indirect school effects, we will necessarily look into entrepreneurship and its determinants at large.
-Thus we will refer to Grilo and Thurik’s research (2005 and 2006) about what determines entrepreneurship engagement levels throughout the European Union, and also to Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries (2002).
-Eventtually, with Gartner (1990) we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper (2008), we will asks ourselves what “entrepreneurship” data really shows.
+More specifically, we intend to look at self-esteem as partially the product of an education pattern, which would affect the whole population, even if so far, "self-confidence in one's own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" (OECD Report 2009).
 

### 2014-10-22 EducProposal.Rmd
Edited unnecessary tags

--- 2014-10-22 EducProposal.Rmd
@@
 title: "The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship"
+author: "Sam Dundon and Thierry Racaud"
 date: "October 17, 2014"
-author: "Sam Dundon and Thierry Racaud"
-output: html_document
-bibliography:
-  - Main.bib
+output: pdf_document
+bibliography: Main.bib
 ---
@@
 Strengthening entrepreneurship and economic development in East Germany: Lessons from local approaches.
-![here](https://github.com/SamDund/Assign2Education/blob/master/Untitled.png)
 
-###Analytical Method
-####Causal Chain
+### Analytical Method
+
+#### Causal Chain
 
@@
 What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
+However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [@Freytag2007].
+Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
+
+What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
 However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [(Freytag Andreas, Thurik Roy, 2007)](Freytag2007).

### 2014-10-22 EducProposal.Rmd
Changing Date

@@
 author: "Sam Dundon and Thierry Racaud"
-date: "October 17, 2014"
-output: pdf_document
+date: "October 24, 2014"
+output: html_document
 bibliography: Main.bib
@@
 Strengthening entrepreneurship and economic development in East Germany: Lessons from local approaches.
+
+###Literature Review
+
+What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
+However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [@Freytag2007].
+Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
+
+Over a hundred years have passed since Max Weber tried to explicit how religious-ethical motivations affect entrepreneurship (Max Weber, 1905), and religion may be less effective in justifying why some are more likely to start businesses than others.
+Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” (OECD Report 2009).
+
+Despite various claims of the existence of a cultural effect, few empirical studies have actually been carried out.
+It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund (Davidsson and Wiklund study 1997), at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors.
+As they compared two Swedish regions similar in terms of structure, and observed different outcomes, they concluded on the possibility of a small cultural effect.
+
+This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities.
+Indeed, like many in the education literature tend to assert, we believe there is an effect of school personnel on student self-esteem (Scott, Dustin, Mertens, Murray, 1996).
+We will explore further the way this mechanism works.
+Now, entrepreneurship literature generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” (OECD Report 2009).
+We intend to show that these individual characteristics are partly shaped at an institutional collective level through the education systems and their staff attitudes.
+
+Of course, King and Sobel (2008), among others, have already tried to show how school choice can increase the rate of youth entrepreneurship but their perspective was slightly different.
+They  asserted that more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
+We believe there is a more widely spread systematic effect of cultural and educational patterns.
+David Watkins (2010) cross-cultural perspective on teaching and learning shall be useful in that respect.
+Kai-Ming Cheng and Kam-Cheung Wong’s study about school effectiveness in East Asia (2006) could also be of help.
+
+Also, as self-confidence is considered to rely partly on one’s integration within social networks (OECD Report 2009), we will also refer to cross-cultural studies such as that of Green, Deschamps and Páez (2005) about individualism and collectivism, or what Freeman (1997) called idiocentrism and allocentrism.
+Raeff, Greenfield and Quiroz (2000) have also conceptualised interpersonal relationships in both cultural contexts.
+More school-focused, Yamauchi (1998) as well as Davies and Aurini (2003) have looked at individualism and collectivism in the classroom and in pedagogy respectively.
+All these will be precious on the way.
+
+Besides direct or indirect school effects, we will necessarily look into entrepreneurship and its determinants at large.
+Thus we will refer to Grilo and Thurik’s research (2005 and 2006) about what determines entrepreneurship engagement levels throughout the European Union, and also to Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries (2002).
+Eventtually, with Gartner (1990) we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper (2008), we will asks ourselves what “entrepreneurship” data really shows.
 
@@
 
-###Literature Review
-
-What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
-However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [@Freytag2007].
-Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
-
-What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
-However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [(Freytag Andreas, Thurik Roy, 2007)](Freytag2007).
-Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
-
-Over a hundred years have passed since Max Weber tried to explicit how religious-ethical motivations affect entrepreneurship (Max Weber, 1905), and religion may be less effective in justifying why some are more likely to start businesses than others.
-Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” (OECD Report 2009).
-
-Despite various claims of the existence of a cultural effect, few empirical studies have actually been carried out.
-It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund (Davidsson and Wiklund study 1997), at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors.
-As they compared two Swedish regions similar in terms of structure, and observed different outcomes, they concluded on the possibility of a small cultural effect.
-
-This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities.
-Indeed, like many in the education literature tend to assert, we believe there is an effect of school personnel on student self-esteem (Scott, Dustin, Mertens, Murray, 1996).
-We will explore further the way this mechanism works.
-Now, entrepreneurship literature generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” (OECD Report 2009).
-We intend to show that these individual characteristics are partly shaped at an institutional collective level through the education systems and their staff attitudes.
-
-Of course, King and Sobel (2008), among others, have already tried to show how school choice can increase the rate of youth entrepreneurship but their perspective was slightly different.
-They  asserted that more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
-We believe there is a more widely spread systematic effect of cultural and educational patterns.
-David Watkins (2010) cross-cultural perspective on teaching and learning shall be useful in that respect.
-Kai-Ming Cheng and Kam-Cheung Wong’s study about school effectiveness in East Asia (2006) could also be of help.
-
-Also, as self-confidence is considered to rely partly on one’s integration within social networks (OECD Report 2009), we will also refer to cross-cultural studies such as that of Green, Deschamps and Páez (2005) about individualism and collectivism, or what Freeman (1997) called idiocentrism and allocentrism.
-Raeff, Greenfield and Quiroz (2000) have also conceptualised interpersonal relationships in both cultural contexts.
-More school-focused, Yamauchi (1998) as well as Davies and Aurini (2003) have looked at individualism and collectivism in the classroom and in pedagogy respectively.
-All these will be precious on the way.
-
-Besides direct or indirect school effects, we will necessarily look into entrepreneurship and its determinants at large.
-Thus we will refer to Grilo and Thurik’s research (2005 and 2006) about what determines entrepreneurship engagement levels throughout the European Union, and also to Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries (2002).
-Eventtually, with Gartner (1990) we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper (2008), we will asks ourselves what “entrepreneurship” data really shows.
-
 ###References

### 2014-10-22 EducProposal.Rmd
Spaces for Headings

@@
 
-###Research Question  
+### Research Question  
 Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
 
-###Research Justification
+### Research Justification
 When it comes to public budgeting for education policies, the decision process often does not appear to be rational.
@@
 
-###Literature Review
+### Literature Review
 
@@
 
-####Estimation Strategy  
+#### Estimation Strategy  
 The estimation strategy will consist of using cross-sectional data about France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.
@@
 
-###Necessary Concepts  
+### Necessary Concepts  
 1.
@@
 
-###References
+### References

### 2014-10-22 EducProposal.Rmd
Adding OECD image
Image try
Added image from OECD publication

@@
 Chart about factors that affect entrepreneurship.
-Source: OECD Local Entrepreneurship Reviews
 Strengthening entrepreneurship and economic development in East Germany: Lessons from local approaches.
@@
 ### Necessary Concepts
+
 1.
@@
 
+<br>
+<p align="center">
+[<img align="center" src="img/OECDChart.png" alt="Factors Affecting Entrepreneurship" height=350 width=450 />](img/OECDChart.png)</br>
+Source: OECD Local Entrepreneurship Reviews [@OECD2009]
+</p>
+
 ### References

### 2014-10-22 EducProposal.Rmd
Minor edits to chart formatting

@@
 [<img align="center" src="img/OECDChart.png" alt="Factors Affecting Entrepreneurship" height=350 width=450 />](img/OECDChart.png)</br>
+</p>
+<p align="center">
 Source: OECD Local Entrepreneurship Reviews [@OECD2009]
 </p>
-
 ### References

### 2014-10-22 EducProposal.Rmd
Edited working directory for consistency

@@
 # Set working directory
-setwd('~/DataAnalysis/')
+setwd('~/Assign2Education/')
 

### 2014-10-22 EducProposal.Rmd
Re-edited chart formatting

@@
 
-<br>
 <p align="center">
@@
 </p>
+
 ### References

### 2014-10-22 EducProposal.Rmd
Removed chart
Bibtex edits

@@
 output: html_document
-bibliography: Main.bib
+bibliography: 
+  - Main.bib
 ---
@@
 
-<p align="center">
-[<img align="center" src="img/OECDChart.png" alt="Factors Affecting Entrepreneurship" height=350 width=450 />](img/OECDChart.png)</br>
-</p>
-<p align="center">
-Source: OECD Local Entrepreneurship Reviews [@OECD2009]
-</p>
-
 ### References

### 2014-10-22 EducProposal.Rmd
Proposal with chart
Update EducProposal.Rmd

@@
 
-### Research Question  
-Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
-
-### Research Justification
+### Research Design
 When it comes to public budgeting for education policies, the decision process often does not appear to be rational.
@@
 
-Chart about factors that affect entrepreneurship.
-Strengthening entrepreneurship and economic development in East Germany: Lessons from local approaches.
+### Research Question  
+Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
 
@@
 
+Chart about factors that affect entrepreneurship.
+Strengthening entrepreneurship and economic development in East Germany: Lessons from local approaches.
+
+<p align="center">
+[<img align="center" src="img/OECDChart.png" alt="Factors Affecting Entrepreneurship" height=350 width=450 />](img/OECDChart.png)</br>
+</p>
+<p align="center">
+Source: OECD Local Entrepreneurship Reviews [@OECD2009]
+</p>
+
 ### References

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 That is, it does not seem to take into account the return on investment that should be expected in the long run.
-Despite this, many claims have been made in the entrepreneurship literature that start-up activities at a country-level are affected by factors other than structural and economic, including cultural and educational.
+Although many claims have been made in the entrepreneurship literature that start-up activities at a country-level are affected by factors other than structural and economic, including cultural and educational.
 However only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, while almost none explored how cultural patterns affected these dispositions.
@@
 We will explore further the way this mechanism works.
-Now, entrepreneurship literature generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” (OECD Report 2009).
+As for entrepreneurship literature, it generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” (OECD Report 2009).
 We intend to show that these individual characteristics are partly shaped at an institutional collective level through the education systems and their staff attitudes.

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 As for entrepreneurship literature, it generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” (OECD Report 2009).
-We intend to show that these individual characteristics are partly shaped at an institutional collective level through the education systems and their staff attitudes.
+We intend to show that these individual characteristics are partly shaped at an institutional and collective level through the education systems and staff attitudes.
 

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 
-Also, as self-confidence is considered to rely partly on one’s integration within social networks (OECD Report 2009), we will also refer to cross-cultural studies such as that of Green, Deschamps and Páez (2005) about individualism and collectivism, or what Freeman (1997) called idiocentrism and allocentrism.
-Raeff, Greenfield and Quiroz (2000) have also conceptualised interpersonal relationships in both cultural contexts.
+Also, as self-confidence is considered to rely partly on one’s integration within social networks (OECD Report 2009), we will refer to cross-cultural studies such as that of Green, Deschamps and Páez (2005) about individualism and collectivism, what Freeman (1997) called idiocentrism and allocentrism.
+Raeff, Greenfield and Quiroz (2000) have also conceptualised interpersonal relationships in both contexts.
 More school-focused, Yamauchi (1998) as well as Davies and Aurini (2003) have looked at individualism and collectivism in the classroom and in pedagogy respectively.
@@
 Besides direct or indirect school effects, we will necessarily look into entrepreneurship and its determinants at large.
-Thus we will refer to Grilo and Thurik’s research (2005 and 2006) about what determines entrepreneurship engagement levels throughout the European Union, and also to Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries (2002).
-Eventtually, with Gartner (1990) we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper (2008), we will asks ourselves what “entrepreneurship” data really shows.
+Thus we will quote Grilo and Thurik’s research (2005 and 2006) about what determines entrepreneurship engagement levels throughout the European Union, and also Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries (2002).
+Eventually, with Gartner (1990) we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper (2008), we will ask ourselves what “entrepreneurship” data really shows.
 

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 
-### Research Design
+### Research Interest
 When it comes to public budgeting for education policies, the decision process often does not appear to be rational.
@@
 What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
-However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [@Freytag2007].
+However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [@Freytag2007] .
 Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [@Freytag2007] .
-Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
+Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report, Strengthening entrepreneurship and economic development in East Germany, 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
 
 Over a hundred years have passed since Max Weber tried to explicit how religious-ethical motivations affect entrepreneurship (Max Weber, 1905), and religion may be less effective in justifying why some are more likely to start businesses than others.
-Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” (OECD Report 2009).
+Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” (OECD Report, Strengthening entrepreneurship and economic development in East Germany, 2009).
 

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

--- 2014-10-22 EducProposal.Rmd
@@
 ### Research Interest
+
 When it comes to public budgeting for education policies, the decision process often does not appear to be rational.
@@
 ### Research Question
+
 Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
@@
 However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [@Freytag2007] .
-Even if “in recent years research has increasingly devoted itself to the subject” (OECD Report 2009), a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
+Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
 
 Over a hundred years have passed since Max Weber tried to explicit how religious-ethical motivations affect entrepreneurship (Max Weber, 1905), and religion may be less effective in justifying why some are more likely to start businesses than others.
-Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” (OECD Report 2009).
+Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” [@OECD2009].
 
 Despite various claims of the existence of a cultural effect, few empirical studies have actually been carried out.
-It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund (Davidsson and Wiklund study 1997), at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors.
+It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors.
 As they compared two Swedish regions similar in terms of structure, and observed different outcomes, they concluded on the possibility of a small cultural effect.
@@
 This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities.
-Indeed, like many in the education literature tend to assert, we believe there is an effect of school personnel on student self-esteem (Scott, Dustin, Mertens, Murray, 1996).
+Indeed, like many in the education literature tend to assert, we believe there is an effect of school personnel on student self-esteem [@Scott1996].
 We will explore further the way this mechanism works.
-As for entrepreneurship literature, it generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” (OECD Report 2009).
+As for entrepreneurship literature, it generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” [@OECD2009].
 We intend to show that these individual characteristics are partly shaped at an institutional and collective level through the education systems and staff attitudes.
 
-Of course, King and Sobel (2008), among others, have already tried to show how school choice can increase the rate of youth entrepreneurship but their perspective was slightly different.
+Of course, King and Sobel [@Kerry2008], among others, have already tried to show how school choice can increase the rate of youth entrepreneurship but their perspective was slightly different.
 They  asserted that more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
 We believe there is a more widely spread systematic effect of cultural and educational patterns.
-David Watkins (2010) cross-cultural perspective on teaching and learning shall be useful in that respect.
-Kai-Ming Cheng and Kam-Cheung Wong’s study about school effectiveness in East Asia (2006) could also be of help.
+David Watkins [@Watkins2010] cross-cultural perspective on teaching and learning shall be useful in that respect.
+Kai-Ming Cheng and Kam-Cheung Wong’s study about school effectiveness in East Asia [@Cheng2006] could also be of help.
 
-Also, as self-confidence is considered to rely partly on one’s integration within social networks (OECD Report 2009), we will refer to cross-cultural studies such as that of Green, Deschamps and Páez (2005) about individualism and collectivism, what Freeman (1997) called idiocentrism and allocentrism.
-Raeff, Greenfield and Quiroz (2000) have also conceptualised interpersonal relationships in both contexts.
-More school-focused, Yamauchi (1998) as well as Davies and Aurini (2003) have looked at individualism and collectivism in the classroom and in pedagogy respectively.
+Also, as self-confidence is considered to rely partly on one’s integration within social networks [@OECD2009], we will refer to cross-cultural studies such as that of Green, Deschamps and Páez [@green2005variation] about individualism and collectivism, what Freeman [@freeman1997demographic] called idiocentrism and allocentrism.
+Raeff, Greenfield and Quiroz [@raeff2000conceptualizing] have also conceptualised interpersonal relationships in both contexts.
+More school-focused, Yamauchi [@yamauchi1998individualism] as well as Davies and Aurini [@davies2003homeschooling] have looked at individualism and collectivism in the classroom and in pedagogy respectively.
 All these will be precious on the way.
@@
 Besides direct or indirect school effects, we will necessarily look into entrepreneurship and its determinants at large.
-Thus we will quote Grilo and Thurik’s research (2005 and 2006) about what determines entrepreneurship engagement levels throughout the European Union, and also Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries (2002).
-Eventually, with Gartner (1990) we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper (2008), we will ask ourselves what “entrepreneurship” data really shows.
+Thus we will quote Grilo and Thurik’s research [@Grilo2005b] about what determines entrepreneurship engagement levels throughout the European Union, and also Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries [@Wennekers2002].
+Eventually, with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.
 

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 The key explanatory variable will be the degree of self confidence.
-We will compute an index from both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
+As we did not find so far any satisfactory proxy for self-confidence in the way we intend to define it, we will need to compute an index.
+In order to do so, we will rely on both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
+
+V86   How important are adventure and taking risks to the person surveyed?
+V119 How good is competition?
+
+Please note that data was collected at different dates in Britain (2005) and in France (2006), but in both cases before the economic crisis, which may have affected people’s prospects and values.
+
+As we mentioned that self-confidence also depends on the integration in social networks, we will rely on the sense of belonging as defined by OECD PISA study.
+Again we will need to compute an index.
+In order to do so, we will also rely on the following items from the World Value Survey 2005-2009 wave about “sense of belonging to a group“ and “sense of individuality” and “degree of self confidence”.
+
+V65   I seek to be myself rather than to follow others
+V66   I live up to what my friends expect
+V67   I decide my goals in life by myself
+V78   How good / bad is greater respect for authority to the person surveyed?
+V186 How often do you attend religious services?
+V198 How justifiable can claiming government benefits be?
+V199 How justifiable can avoiding a fare on public transport be?
+V200 How justifiable can cheating on taxes be?
 

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 V86   How important are adventure and taking risks to the person surveyed?
+
 V119 How good is competition?
@@
 V65   I seek to be myself rather than to follow others
+
 V66   I live up to what my friends expect
+
 V67   I decide my goals in life by myself
+
 V78   How good / bad is greater respect for authority to the person surveyed?
+
 V186 How often do you attend religious services?
+
 V198 How justifiable can claiming government benefits be?
+
 V199 How justifiable can avoiding a fare on public transport be?
+
 V200 How justifiable can cheating on taxes be?

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

--- 2014-10-22 EducProposal.Rmd
@@
 Although many claims have been made in the entrepreneurship literature that start-up activities at a country-level are affected by factors other than structural and economic, including cultural and educational.
-However only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, while almost none explored how cultural patterns affected these dispositions.
+As a matter of fact, only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, while almost none explored how cultural patterns affected these dispositions.
 
@@
 #### Estimation Strategy
+
 The estimation strategy will consist of using cross-sectional data about France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.
@@
 
+GEM measure of entrepreneurship is often used or refered to in OECD studies.
+
 The key explanatory variable will be the degree of self confidence.
 As we did not find so far any satisfactory proxy for self-confidence in the way we intend to define it, we will need to compute an index.
-In order to do so, we will rely on both OECD PISA, World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
+In order to do so, we will rely on both [OECD PISA](http://www.oecd.org/pisa/keyfindings/pisa-2012-results.htm), World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
 

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

@@
 As we did not find so far any satisfactory proxy for self-confidence in the way we intend to define it, we will need to compute an index.
-In order to do so, we will rely on both [OECD PISA](http://www.oecd.org/pisa/keyfindings/pisa-2012-results.htm), World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
+In order to do so, we will rely on both [OECD PISA 2012](http://www.oecd.org/pisa/keyfindings/pisa-2012-results.htm), [World Value Survey 2005-2006](http://www.worldvaluessurvey.org/WVSOnline.jsp) and [GEM](http://www.gemconsortium.org) (Fear of failure rate, perceived capabilities).
 

### 2014-10-22 EducProposal.Rmd
Update EducProposal.Rmd

--- 2014-10-22 EducProposal.Rmd
@@
 As we did not find so far any satisfactory proxy for self-confidence in the way we intend to define it, we will need to compute an index.
-In order to do so, we will rely on both [OECD PISA](http://www.oecd.org/pisa/keyfindings/pisa-2012-results.htm), World Value Survey (Data from 2012 and 2005/2006 respectively) and GEM (Fear of failure rate, perceived capabilities).
+In order to do so, we will rely on both [OECD PISA 2012](http://www.oecd.org/pisa/keyfindings/pisa-2012-results.htm), [World Value Survey 2005-2009](http://www.worldvaluessurvey.org/WVSOnline.jsp) and [GEM](http://www.gemconsortium.org)
 
+From PISA 2012, we will use the items regarding engagement, drive and self-beliefs (Table III.2.3.a).
+More specifically we will compute data regarding the sense of belonging to measure the strength of inclusion in social networks.
+We also process measures of self-perception.
+They all come as a percentage of the country-representative student population.
+
+From World Value Survey, we will use the last data available, that of the fifth wave (2005-2009).
+Our main issue is that data was collected at different points in time in Britain (2005) and in France (2006), but in both cases before the economic crisis, which might have affected people’s prospects and values differently.
+We will specifically look at the following items:
 V86   How important are adventure and taking risks to the person surveyed?  
@@
 
-Please note that data was collected at different dates in Britain (2005) and in France (2006), but in both cases before the economic crisis, which may have affected people’s prospects and values.
+From GEM, we will use the most recent data available regarding the fear of failure rate and perceived capabilities).
+
+To compute these data together is quite a challenge and we are not yet fully sure on how to proceed.
+But at least, these multiple reliable measures from well-recognised sources should give us a composite but also comprehensive indicator about the average degree of self-confidence of individuals in each country.
 

### 2014-10-23 EducProposal.Rmd
Update EducProposal.Rmd

@@
 
+#### Hypothesis
+
+Our main hypothesis is that the more self-confident a population is on average, the higher entrepreneurship in that country will be.
+
 #### Causal Chain
@@
 
+##### Entrepreneurship as a dependent variable
+
 The dependent variable will be the rate of entrepreneurship with its related activities or attitudes as defined by the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org):
@@
 GEM measure of entrepreneurship is often used or refered to in OECD studies.
+
+##### Self-confidence as the key explanatory variable
 
@@
 
+##### Social inclusion as a complementary explanatory variable
+
 As we mentioned that self-confidence also depends on the integration in social networks, we will rely on the sense of belonging as defined by OECD PISA study.
@@
 
-As mentioned above, we will need to control for the economic outlook at the time of data collection about entrepreneurship characteristics.
+##### Other classic determinants of entrepreneurship as control variables
+
+We will obviously need to control for the economic outlook at the time of data collection about entrepreneurship characteristics.
 We will also need to control for nine key entrepreneurship conditions as defined in the [National Experts Survey (NES)](http://www.gemiran.ir/sec/gem/?@=28) that may affect the rate of entrepreneurship.
@@
 
+##### Process
+
 The first step will be to see if, regarding self-confidence, different patterns can be observed in each country. In which case, we may need to call on cultural explanations.
@@
 
-Our main hypothesis is that the more self-confident a population is on average, the higher entrepreneurship in that country will be.
-
 ### Necessary Concepts
 
-1.
+1. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach in measuring this factor.
+
+2. Positive reinforcement: Again even if this is not easy to quantify, we will attempt to compute an index and characterize it on a scale.
+
+3. Culture: Key concept broadly understood here as the ensemble of beliefs, values, norms and practices of a given society.
+
+4.
+Education: Here education is understood as the process of apprenticeship that takes place in schools throughout compulsory years (from the age of 6 to 16).
+Thus we examine the average potential effect of these years of "shaping" on individuals throughout the entire population of a country.
+
+5.
 Return on Investment: Assigning a future Euro value to a present-day investment.
 This may require the use of a social discount rate, but will also need to consider the potential GDP increase brought about by improved education policies.
-
-2. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index  to include some quantiative approach in measuring this factor.
-
-3. Positive reinforcement: Again even if this is not easy to quantify, we will attempt to compute as an index and characterize it on a scale.
 

### 2014-10-23 EducProposal.Rmd
Cleaned repository and checked references

@@
 output: html_document
-bibliography: 
-  - Main.bib
+bibliography: Main.bib
 ---

### 2014-10-23 EducProposal.Rmd
Minor changes

@@
 More specifically we will compute data regarding the sense of belonging to measure the strength of inclusion in social networks.
-We also process measures of self-perception.
+We will also process measures of self-perception.
 They all come as a percentage of the country-representative student population.
@@
 We will specifically look at the following items:
+
 V86   How important are adventure and taking risks to the person surveyed?
+
 V119 How good is competition?
@@
 
-As we mentioned that self-confidence also depends on the integration in social networks, we will rely on the sense of belonging as defined by OECD PISA study.
-Again we will need to compute an index.
-In order to do so, we will also rely on the following items from the World Value Survey 2005-2009 wave about “sense of belonging to a group“ and “sense of individuality” and “degree of self confidence”.
+As we mentioned that self-confidence also depends on the integration in social networks, we will partly rely on the sense of belonging as defined by OECD PISA study but again we will need to compute an index.
+In order to do so, we will also rely on the following items from the World Value Survey 2005-2009 wave about “sense of belonging to a group“ and “sense of individuality”.
 
@@
 
+We are not yet fully sure on how to control for all these though.
+
 ##### Process
@@
 
-2. Positive reinforcement: Again even if this is not easy to quantify, we will attempt to compute an index and characterize it on a scale.
+2.
+Positive reinforcement: Again even if this is not easy to characterize quantify, we will attempt to compute an index and characterize it on a scale.
+Should we eventually consider there is a lot of positive reinforcement in one country and very little in another, perhaps we could go as far as using a dummy variable.
 
-3. Culture: Key concept broadly understood here as the ensemble of beliefs, values, norms and practices of a given society.
+3. Culture: Key concept broadly understood here as the set of beliefs, values, norms and practices of a given society.
 
 4.
-Education: Here education is understood as the process of apprenticeship that takes place in schools throughout compulsory years (from the age of 6 to 16).
-Thus we examine the average potential effect of these years of "shaping" on individuals throughout the entire population of a country.
+Education: Here education is understood as the process of apprenticeship that takes place in school throughout compulsory years (from the age of 6 to 16).
+Thus we examine the average potential effect of these years of "shaping" on individuals for the entire population of a country.
 
 5.
-Return on Investment: Assigning a future Euro value to a present-day investment.
-This may require the use of a social discount rate, but will also need to consider the potential GDP increase brought about by improved education policies.
+Return on Investment: Future benefits of a euro spent at present.
+Here return on investment would only start to be visible after some time, once most of a generation has got into active life which may take up to five to ten years.
+But even then, not all the expected propensity to start a business will be palpable.
+When you add ot it the mechanism of the social discount rate, that huge distance in time as of now seem to prevent any calculations of return on investment when it comes to public budgeting for education policies.
 

### 2014-10-24 EducProposal.Rmd
Update EducProposal.Rmd
Minor formatting and bib edits

@@
 # Load citation package
-pkgs <- c('dplyr','ggplot2','repmis')
+pkgs <- c('repmis')
 repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')
@@
 
-When it comes to public budgeting for education policies, the decision process often does not appear to be rational.
-That is, it does not seem to take into account the return on investment that should be expected in the long run.
-Although many claims have been made in the entrepreneurship literature that start-up activities at a country-level are affected by factors other than structural and economic, including cultural and educational.
-As a matter of fact, only a few empirical studies have actually been carried out and most of them focused on which attitudes were favourable to starting a business, while almost none explored how cultural patterns affected these dispositions.
+The process of allocating public funds for education is an opportunity to make calculated long-term investments in a nation's populace.
+The rationale for decisions made during this process, however, is often difficult to understand.
+For example, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors -- not just structural and economic factors -- in determining individual and societal tendencies to start a business, these factors are often not included in the decisionmaking process.
+As a matter of fact, only a few empirical studies have actually been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored how cultural patterns affected these dispositions.
 
 When cultural factors are examined, they are considered as a given feature that can hardly be traced.
-By having a closer look at education systems, we intend to explore the processes through which some of these cultural patterns are enhanced and passed from one generation to the next.
+By having a closer look at education systems, however, we intend to explore the processes through which some of these cultural patterns are enhanced and passed from one generation to the next.
 Aside from parental education, schools are indeed the very place where children are taught how to fit into society.
-This research is an attempt at looking at one trait in particular, self-confidence.
+This research is an attempt to analyze  one trait in particular, self-confidence.
 
@@
 
-Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
+Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, and more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
 
@@
 What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
-However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that other than economic factors are at play” [@Freytag2007] .
-Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
+However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] .
+Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done, as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
 
-Over a hundred years have passed since Max Weber tried to explicit how religious-ethical motivations affect entrepreneurship (Max Weber, 1905), and religion may be less effective in justifying why some are more likely to start businesses than others.
+Over a hundred years have passed since Max Weber tried to explain how religious-ethical motivations affect entrepreneurship [@weberprotestant], and religion may be less effective in justifying why some are more likely to start businesses than others.
 Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” [@OECD2009].
@@
 This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities.
-Indeed, like many in the education literature tend to assert, we believe there is an effect of school personnel on student self-esteem [@Scott1996].
+Indeed, like many in the education literature tend to assert, we believe there is an effect by school personnel on student self-esteem [@Scott1996].
 We will explore further the way this mechanism works.
@@
 
-Of course, King and Sobel [@Kerry2008], among others, have already tried to show how school choice can increase the rate of youth entrepreneurship but their perspective was slightly different.
-They  asserted that more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
+Of course, King and Sobel [@Kerry2008], among others, have already tried to show how school choice can increase the rate of youth entrepreneurship, but their perspective was slightly different.
+They  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
 We believe there is a more widely spread systematic effect of cultural and educational patterns.
@@
 More school-focused, Yamauchi [@yamauchi1998individualism] as well as Davies and Aurini [@davies2003homeschooling] have looked at individualism and collectivism in the classroom and in pedagogy respectively.
-All these will be precious on the way.
+All these will be important on the way.
 
@@
 
-From GEM, we will use the most recent data available regarding the fear of failure rate and perceived capabilities).
+From GEM, we will use the most recent data available regarding the fear of failure rate and perceived capabilities.
 
@@
 But even then, not all the expected propensity to start a business will be palpable.
-When you add ot it the mechanism of the social discount rate, that huge distance in time as of now seem to prevent any calculations of return on investment when it comes to public budgeting for education policies.
+When you add it to the mechanism of the social discount rate, that huge distance in time as of now seem to prevent any calculations of return on investment when it comes to public budgeting for education policies.
 

### 2014-10-24 EducProposal.Rmd
Minor edits to proposal and revised README

@@
 For example, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors -- not just structural and economic factors -- in determining individual and societal tendencies to start a business, these factors are often not included in the decisionmaking process.
-As a matter of fact, only a few empirical studies have actually been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored how cultural patterns affected these dispositions.
+As a matter of fact, only a few empirical studies have actually been carried out on this topic and most of them focused on which attitudes were favorable to starting a business, while almost none explored how cultural patterns affected these dispositions.
 
@@
 
-Drawing a comparison between France and Britain, to what extent do the behavioural characteristics of the education system - individualistic, group-oriented, and more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
+Drawing a comparison between France and Britain, to what extent do the behavioral characteristics of the education system - individualistic, group-oriented, and more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
 
@@
 
-Over a hundred years have passed since Max Weber tried to explain how religious-ethical motivations affect entrepreneurship [@weberprotestant], and religion may be less effective in justifying why some are more likely to start businesses than others.
+Over a hundred years has passed since Max Weber tried to explain how religious-ethical motivations affect entrepreneurship [@weberprotestant], and religion may be less effective in justifying why some are more likely to start businesses than others.
 Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” [@OECD2009].
@@
 Despite various claims of the existence of a cultural effect, few empirical studies have actually been carried out.
-It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors.
-As they compared two Swedish regions similar in terms of structure, and observed different outcomes, they concluded on the possibility of a small cultural effect.
+It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), and then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors -- mainly economic, and cultural factors.
+As they compared two Swedish regions similar in terms of structure and observed different outcomes, they concluded there may be a small cultural effect in attitudes toward start-up activities.
 
-This thesis is an attempt at finding out if different patterns in education lead to different outcomes in terms of start-up activities.
-Indeed, like many in the education literature tend to assert, we believe there is an effect by school personnel on student self-esteem [@Scott1996].
-We will explore further the way this mechanism works.
-As for entrepreneurship literature, it generally acknowledges the influence of self-confidence on start-up activities although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” [@OECD2009].
+This thesis is an attempt at finding out whether different patterns in education lead to different outcomes in terms of start-up activities.
+Indeed, like many in the education literature tend to assert, we believe school personnel have an affect on student self-esteem [@Scott1996].
+We will further explore how this mechanism works.
+As for entrepreneurship literature, it generally acknowledges the influence of self-confidence on start-up activities, although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” [@OECD2009].
 We intend to show that these individual characteristics are partly shaped at an institutional and collective level through the education systems and staff attitudes.
@@
 Of course, King and Sobel [@Kerry2008], among others, have already tried to show how school choice can increase the rate of youth entrepreneurship, but their perspective was slightly different.
-They  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
+They  asserted that a more business-like environment in K-12 education was the key, which was favored by voucher programs.
 We believe there is a more widely spread systematic effect of cultural and educational patterns.
@@
 Also, as self-confidence is considered to rely partly on one’s integration within social networks [@OECD2009], we will refer to cross-cultural studies such as that of Green, Deschamps and Páez [@green2005variation] about individualism and collectivism, what Freeman [@freeman1997demographic] called idiocentrism and allocentrism.
-Raeff, Greenfield and Quiroz [@raeff2000conceptualizing] have also conceptualised interpersonal relationships in both contexts.
+Raeff, Greenfield and Quiroz [@raeff2000conceptualizing] have also conceptualized interpersonal relationships in both contexts.
 More school-focused, Yamauchi [@yamauchi1998individualism] as well as Davies and Aurini [@davies2003homeschooling] have looked at individualism and collectivism in the classroom and in pedagogy respectively.
@@
 
-Stronger culture of positive reinforcement ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level
+Stronger culture of positive reinforcement ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
 
@@
 
-GEM measure of entrepreneurship is often used or refered to in OECD studies.
+Note: The GEM measure of entrepreneurship is often used or referred to in OECD studies.
 
@@
 From PISA 2012, we will use the items regarding engagement, drive and self-beliefs (Table III.2.3.a).
-More specifically we will compute data regarding the sense of belonging to measure the strength of inclusion in social networks.
+This data is available in Excel format from the OECD.
+More specifically, we will compute data regarding the sense of belonging to measure the strength of inclusion in social networks.
 We will also process measures of self-perception.
@@
 
-From World Value Survey, we will use the last data available, that of the fifth wave (2005-2009).
+From World Value Survey, we will use the latest data available, that of the fifth wave (2005-2009).
 Our main issue is that data was collected at different points in time in Britain (2005) and in France (2006), but in both cases before the economic crisis, which might have affected people’s prospects and values differently.
@@
 V86   How important are adventure and taking risks to the person surveyed?  
-
 V119 How good is competition?
@@
 To compute these data together is quite a challenge and we are not yet fully sure on how to proceed.
-But at least, these multiple reliable measures from well-recognised sources should give us a composite but also comprehensive indicator about the average degree of self-confidence of individuals in each country.
+But at least, these multiple reliable measures from well-recognized sources should give us a composite but also comprehensive indicator about the average degree of self-confidence of individuals in each country.
 
@@
 
-As we mentioned that self-confidence also depends on the integration in social networks, we will partly rely on the sense of belonging as defined by OECD PISA study but again we will need to compute an index.
+As we mentioned that self-confidence also depends on the integration in social networks, we will partly rely on the sense of belonging as defined by OECD PISA study, but again we will need to compute an index.
 In order to do so, we will also rely on the following items from the World Value Survey 2005-2009 wave about “sense of belonging to a group“ and “sense of individuality”.
@@
 2. Government policies  
-3. Government programmes  
+3. Government programs  
 4. Entrepreneurial Education and Training  
@@
 
-We are not yet fully sure on how to control for all these though.
+We are not yet fully sure on how to best control for all these variables though and will work on this in the coming weeks.
 
@@
 
-Then, should indeed different patterns be observed, we will need to proceed to an Ordinary Least Square (OLS) Regression in order to check to what extent these characteristics affect the rate of entrepreneurship in the country.
+Then, should indeed different patterns be observed, we will proceed to an Ordinary Least Square (OLS) Regression to determine the extent of the affect of these characteristics on the rate of entrepreneurship in each country.
 
@@
 
-1. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index to include some quantiative approach in measuring this factor.
+1. Self-confidence: It is difficult to obtain a credible measurement of self confidence, but we will compute an index to include a quantitative approach in measuring this factor.
 
 2.
-Positive reinforcement: Again even if this is not easy to characterize quantify, we will attempt to compute an index and characterize it on a scale.
-Should we eventually consider there is a lot of positive reinforcement in one country and very little in another, perhaps we could go as far as using a dummy variable.
+Positive reinforcement: Again, even if this is not easy to characterize quantitatively, we will attempt to compute an index and characterize it on a scale.
+Should we eventually consider there is considerable positive reinforcement in one country and very little in another, perhaps we could go as far as using a dummy variable.
 
@@
 Return on Investment: Future benefits of a euro spent at present.
-Here return on investment would only start to be visible after some time, once most of a generation has got into active life which may take up to five to ten years.
+Here, return on investment would only start to be visible after some time, once most of a generation has got into active life which may take up to five to ten years.
 But even then, not all the expected propensity to start a business will be palpable.
@@
 
-Chart about factors that affect entrepreneurship.
+6. Individual vs. societal factors: The below chart identifies several of the individual and societal factors impacting the decision to become an entrepreneur.
+
 Strengthening entrepreneurship and economic development in East Germany: Lessons from local approaches.
@@
 
+### Conclusion  
+The impact of cultural factors in education on the rate of entrepreneurship in a given country is an important and under-researched topic that should be considered by policymakers constructing public education budgets.
+Through this project, we hope to encourage the consideration of these cultural factors by providing a qualitative and quantitative method for understanding the impact of these factors.
+Although several challenges remain to compiling the indexes discussed in this report, we are confident we can produce a helpful framework for examining and understanding these factors.
+
 ### References

### 2014-10-27 EducProposal.Rmd
Revised README and made small edits missed in the previous commit
Final edits to proposal
Reviewed pull req and knit new pdf and html

@@
 date: "October 24, 2014"
-output: html_document
+output: pdf_document
 bibliography: Main.bib
@@
 Also, as self-confidence is considered to rely partly on one’s integration within social networks [@OECD2009], we will refer to cross-cultural studies such as that of Green, Deschamps and Páez [@green2005variation] about individualism and collectivism, what Freeman [@freeman1997demographic] called idiocentrism and allocentrism.
-Raeff, Greenfield and Quiroz [@raeff2000conceptualizing] have also conceptualized interpersonal relationships in both contexts.
+Raeff, Greenfield and Quiroz [-@raeff2000conceptualizing] have also conceptualized interpersonal relationships in both contexts.
 More school-focused, Yamauchi [@yamauchi1998individualism] as well as Davies and Aurini [@davies2003homeschooling] have looked at individualism and collectivism in the classroom and in pedagogy respectively.
@@
 
-Strengthening entrepreneurship and economic development in East Germany: Lessons from local approaches.
-
 <p align="center">

### 2014-10-28 WebScraping1.Rmd
Code for webscraping GEM

---
title: "WebScraping1"
author: "Sam"
date: "October 27, 2014"
output: html_document
---

```{r}

library(httr)
library(dplyr)
install.packages("XML")
library(XML)

URL <- 'http://www.bbc.com/sport/winter-olympics/2014/medals/countries'

# Get and parse all tables on page
tables <- URL %>% GET() %>%
  content(as = 'parsed') %>%
  readHTMLTable()

# Gather content and parse all tables (only one on this page)
names(tables)
medals <- as.data.frame(tables)

### Clean ###
# Drop unwanted variables
medals

MedalsTable <- tables[]

head(MedalsTable)
summary(MedalsTable)
arrange <- arrange()
```

```{r}

# Install Foreign for accessing STATA file
install.packages("foreign")
library(foreign)
library(help=foreign)

# Load data locally
dataSPSS<-read.spss("/Users/samdundon/Desktop/2010GEMNES.sav", to.data.frame=TRUE)

### Clean ###

head(dataSPSS)
head(dataSPSS)[1,1:387]

```

### 2014-11-10 Proposal/EducProposal.Rmd
Reorganized repository

--- 2014-10-27 EducProposal.Rmd
@@
 date: "October 24, 2014"
-output: pdf_document
+output: word_document
 bibliography: Main.bib

### 2014-11-10 WebScraping1.Rmd
Reorganized repository

@@
 
+##### GEM Database #####
+
 # Install Foreign for accessing STATA file
@@
 
-# Load data locally
-dataSPSS<-read.spss("/Users/samdundon/Desktop/2010GEMNES.sav", to.data.frame=TRUE)
+# Loading NES data locally
+dataSPSS<-read.spss("/Users/samdundon/Desktop/2010GEMNES.sav", use.value.labels=TRUE, to.data.frame=TRUE)
+
+# Ordering data by country
+dataSPSS2 <- dataSPSS2[order(dataSPSS$)]
 
@@
 
+##### OECD PISA 2012 ####
+
+# Load data locally from
+
+# Convert Excel document into CSV  - with Numbers
+# Import CSV fileq
+
+# Mutate- run a function on all variables
+
+# Loading APS data locally
+dataSPSS2<-read.spss("/Users/samdundon/Desktop/GEM2010APS.sav", use.value.labels=TRUE, to.data.frame=TRUE)
+
+# Ordering data by country
+dataSPSS2 <- dataSPSS2[order(dataSPSS2$Country_Name),]
+
 ```
+
+```{r}
+install.packages("car")
+library(car)
+data(Prestige)
+car::scatterplotMatrix(Prestige)
+
+# Run an OLS log regression
+M1 <- lm(prestige ~ education, data = Prestige)
+
+# Obtain simple statistics
+summary(M1)
+
+# Find confidence interval for sample
+confint(M1)
+
+# Estimating model with categorial (factor) variable
+# Check variable class to see when you have a categorial or continuous variable
+M2 <- lm(prestige ~ education + type, data = Prestige)
+
+# Summary statistics
+summary(M2)
+
+# Using cut to create a categorial (factor) variable
+
+# Plot M2
+plot(M2, which = 2)
+
+# Load data
+URL <- 'http://www.ats.ucla.edu/stat/data/binary.csv'
+Admission <- read.csv(URL)
+car::scatterplotMatrix(Admission)
+
+# Create contingency table
+xtabs(~admit + rank, data = Admission)
+
+# Logistic regression with GLM
+Logit1 <- glm(admit ~ gre + gpa + as.factor(rank), data = Admission, family = 'binomial')
+
+# Obtain confidence intervals
+confint(Logit1)
+exp(cbind(OddsRatio = coef(Logit1), confint(Logit1)))
+
+```

### 2014-11-10 GEMDataSource.Rmd
revised data set

---
title: "DataGatheringandAnalysis"
author: "Sam"
date: "November 10, 2014"
output: html_document
---

```{r}
# Set working directory
setwd('~/Assign2Education/')

### Import data from GEM Survey ###

# Import fear of failure data
FearFail <- repmiss::source_data("", 
```

### 2014-11-10 Proposal/EducProposal.Rmd
revised data set

--- 2014-10-27 EducProposal.Rmd
@@
 # Set working directory
-setwd('~/Assign2Education/')
+setwd('~/Assign2Education/Proposal')
 

### 2014-11-10 GEMDataSource.Rmd
Deleted unecessary header
Imported, cleaned, and merged GEM data

@@
 
-### Import data from GEM Survey ###
+# Library Repmis, Tidy, Reshape2, and plyr packages
+library(repmis)
+library(tidyr)
+library(reshape2)
+library(plyr)
+
+#### Import data from GEM Survey ####
 
 # Import fear of failure data
-FearFail <- repmiss::source_data("", 
+FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = TRUE)
+
+# Import current owner data
+CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = TRUE)
+
+# Import entrepreneurial intention data
+EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = TRUE)
+
+# Import nascent entrepreneur data
+NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = TRUE)
+
+# Import perceived capabilities data
+PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = TRUE)
+
+#### Clean data using tidy ####
+
+### Clean FearFail ###
+
+# Remove X's in FearFail year columns
+names(FearFail) <- gsub("X", "", names(FearFail))
+
+# Change years from columns to rows and create CFearFail
+CFearFail <- melt(data = FearFail,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010", "2011", "2012",
+                                   "2013"))
+
+# Rename columns
+CFearFail <- plyr::rename(x = CFearFail, 
+                                      replace = c("variable" = "Year",
+                                                  "value" = "Percent Fear"))
+
+### Clean CurrentOwner ###
+# Remove X's in CurrentOwner year columns
+names(CurrentOwner) <- gsub("X", "", names(CurrentOwner))
+
+# Change years from columns to rows and create CCurrentOwner
+CCurrentOwner <- melt(data = CurrentOwner,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010", "2011", "2012",
+                                   "2013"))
+
+# Rename columns
+CCurrentOwner <- plyr::rename(x = CCurrentOwner, 
+                                      replace = c("variable" = "Year",
+                                                  "value" = "Percent Owner"))
+
+### Clean EntreIntention ###
+# Remove X's in EntreIntention year columns
+names(EntreIntention) <- gsub("X", "", names(EntreIntention))
+
+# Change years from columns to rows and create CEntreIntention (No 2001 data available)
+CEntreIntention <- melt(data = EntreIntention,
+                  id.vars = c("Country"),
+                  measure.vars = c("2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010", "2011", "2012",
+                                   "2013"))
+
+# Rename columns
+CEntreIntention <- plyr::rename(x = CEntreIntention, 
+                                      replace = c("variable" = "Year",
+                                                  "value" = "Percent Intention"))
+
+### Clean NascentEntre ###
+# Remove X's in NascentEntre year columns
+names(NascentEntre) <- gsub("X", "", names(NascentEntre))
+
+# Change years from columns to rows and create CNascentEntre
+CNascentEntre <- melt(data = NascentEntre,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010", "2011", "2012",
+                                   "2013"))
+
+# Rename columns
+CNascentEntre <- plyr::rename(x = CNascentEntre, 
+                                      replace = c("variable" = "Year",
+                                                  "value" = "Percent Nascent"))
+
+### Clean PerceivedCapabilities ###
+# Remove X's in PerceivedCapabilities year columns
+names(PerceivedCapabilities) <- gsub("X", "", names(PerceivedCapabilities))
+
+# Change years from columns to rows and create CPreceivedCapabilities
+CPerceivedCapabilities<- melt(data = PerceivedCapabilities,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010", "2011", "2012",
+                                   "2013"))
+
+# Rename columns
+CPerceivedCapabilities <- plyr::rename(x = CPerceivedCapabilities, 
+                                      replace = c("variable" = "Year",
+                                                  "value" = "Percent Perceived"))
+
+# Merge the data
+MergedGEM <- merge(CCurrentOwner, CEntreIntention,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+MergedGem2 <- merge(CFearFail, CNascentEntre,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+MergedGem3 <- merge(CPerceivedCapabilities, MergedGEM,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+FinalMerge <- merge(MergedGem2, MergedGem3,
+                   union("Country", "Year"),
+                   all = TRUE)
+
 ```

### 2014-11-11 GEMDataSource.Rmd
Small edits - need to get rid of hyphens in data

@@
 
-```{r}
+```{r echo =FALSE, cache=TRUE, include=FALSE}
 # Set working directory
@@
                                       replace = c("variable" = "Year",
-                                                  "value" = "Percent Fear"))
+                                                  "value" = "PercentFear"))
 
@@
                                       replace = c("variable" = "Year",
-                                                  "value" = "Percent Owner"))
+                                                  "value" = "PercentOwner"))
 
@@
                                       replace = c("variable" = "Year",
-                                                  "value" = "Percent Intention"))
+                                                  "value" = "PercentIntention"))
 
@@
                                       replace = c("variable" = "Year",
-                                                  "value" = "Percent Nascent"))
+                                                  "value" = "PercentNascent"))
 
@@
                                       replace = c("variable" = "Year",
-                                                  "value" = "Percent Perceived"))
+                                                  "value" = "PercentPerceived"))
 
-# Merge the data
+#### Merge the data ####
 MergedGEM <- merge(CCurrentOwner, CEntreIntention,
@@
 
+# Convert year columns to numeric
+FinalMerge[,2001:2012] <- as.numeric(FinalMerge[,2001:2012])
+
+# Need to figure out how to get rid of "-" in data
+
+summary(FinalMerge)
+# Run a regression
+R1 <- lm(PercentNascent ~ PercentPerceived + PercentIntention, data = FinalMerge)
+R1
+
 ```

### 2014-11-11 GEMDataSource.Rmd
Changed percent columns to numeric and ran basic regression

@@
 
-# Convert year columns to numeric
-FinalMerge[,2001:2012] <- as.numeric(FinalMerge[,2001:2012])
+# Convert percent columns from character to numeric
+FinalMerge[,"PercentPerceived"] <- as.numeric(FinalMerge[,"PercentPerceived"])
+FinalMerge[,"PercentFear"] <- as.numeric(FinalMerge[,"PercentFear"])
+FinalMerge[,"PercentNascent"] <- as.numeric(FinalMerge[,"PercentNascent"])
+FinalMerge[,"PercentOwner"] <- as.numeric(FinalMerge[,"PercentOwner"])
+FinalMerge[,"PercentIntention"] <- as.numeric(FinalMerge[,"PercentIntention"])
 
-# Need to figure out how to get rid of "-" in data
+# Check data to confirm change
+summary(FinalMerge)
 
-summary(FinalMerge)
-# Run a regression
+# Run a linear regression
 R1 <- lm(PercentNascent ~ PercentPerceived + PercentIntention, data = FinalMerge)
-R1
+summary(R1)
+
+# Calculate confidence intervals
+confint(R1)
 

### 2014-11-11 GEMDataSource.Rmd
Added cache = false for repository data

@@
 # Import fear of failure data
-FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = TRUE)
+FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE)
 
 # Import current owner data
-CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = TRUE)
+CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = FALSE)
 
 # Import entrepreneurial intention data
-EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = TRUE)
+EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = FALSE)
 
 # Import nascent entrepreneur data
-NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = TRUE)
+NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = FALSE)
 
 # Import perceived capabilities data
-PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = TRUE)
+PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE)
 

### 2014-11-11 GEMDataSource.Rmd
Update 11/11

@@
 setwd('~/Assign2Education/')
+
+# Install rempis from Christpher Gandrud's website
 
@@
 # Run a linear regression
-R1 <- lm(PercentNascent ~ PercentPerceived + PercentIntention, data = FinalMerge)
+R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear, data = FinalMerge)
 summary(R1)
@@
 
+# Run a linear regression
+R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear, data = FinalMerge)
+summary(R2)
+
+# Calculate confidence intervals
+confint(R2)
+
+# Run a linear regression
+R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear, data = FinalMerge)
+summary(R3)
+
+# Calculate confidence intervals
+confint(R3)
+
+# Plot graph
+car::scatterplotMatrix(FinalMerge)
 ```

### 2014-11-13 GEMDataSource.Rmd
Added scatterplotmatrix
Adding control variable

@@
 
-# Install rempis from Christpher Gandrud's website
-
 # Library Repmis, Tidy, Reshape2, and plyr packages
@@
 library(plyr)
+library(WDI)
 
@@
 ### Clean FearFail ###
+# Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from seeting up a business.
 
@@
 ### Clean CurrentOwner ###
+# Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid sallaries, wages, or any other payments to the owners for more than 42 months
+
 # Remove X's in CurrentOwner year columns
@@
 ### Clean EntreIntention ###
+# Percentage of 18-64 population (individuals involved in any stage of entrepenerurial activity excluded) who intend to start a business within three years.
+
 # Remove X's in EntreIntention year columns
@@
 ### Clean PerceivedCapabilities ###
+# Percentage of 18-64 population who believe to have the required skills and knowledge to start a business
+
 # Remove X's in PerceivedCapabilities year columns
@@
 car::scatterplotMatrix(FinalMerge)
+
+#### Import WDI Annual GDP Growth Data ####
+WDIsearch('gdp')
+dat = WDI(indicator='GDP growth (annual %)', country=c('MX','CA','US',), start=2001, end=2013)
+
 ```

### 2014-11-13 GEMDataSource.Rmd
Cleaning Perceived Opportunities Data Set

@@
 
-# Import fear of failure data
+# Import GEM fear of failure data
 FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE)
 
-# Import current owner data
+# Import GEM estblished entrepreneurship - current owner data
 CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = FALSE)
 
-# Import entrepreneurial intention data
+# Import GEM entrepreneurial intention data
 EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = FALSE)
 
-# Import nascent entrepreneur data
+# Import GEM nascent entrepreneur data
 NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = FALSE)
 
-# Import perceived capabilities data
+# Import GEM perceived capabilities data
 PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE)
+
+# Import GEM perceived opportunities data as a proxy for potential control variables
+PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedOpportunities.csv", header = TRUE, cache = FALSE)
 
@@
 
+### Clean PerceivedOpportunities ###
+# Percentage of 18-64 population who see good opportunities to start a firm in the area where they live
+
+# Remove X's in PerceivedOpportunities year columns
+names(PerceivedOpportunities) <- gsub("X", "", names(PerceivedOpportunities))
+
+# Change years from columns to rows and create CPreceivedCapabilities
+CPerceivedOpportunities<- melt(data = PerceivedOpportunities,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010", "2011", "2012",
+                                   "2013"))
+
+# Rename columns
+CPerceivedCapabilities <- plyr::rename(x = CPerceivedCapabilities, 
+                                      replace = c("variable" = "Year",
+                                                  "value" = "PercentOpportunities"))
+
 #### Merge the data ####

### 2014-11-13 GEMDataSource.Rmd
Imported WDI data

--- 2014-11-13 GEMDataSource.Rmd
@@
 library(WDI)
+
+# Load citation package
+pkgs <- c('repmis', 'tidyr', 'reshape2', 'plyr', 'WDI')
+repmis::LoadandCite(pkgs, file= 'DataRpackageCitations.bib')
 
@@
 WDIsearch('gdp')
-dat = WDI(indicator='GDP growth (annual %)', country=c('MX','CA','US',), start=2001, end=2013)
+GDPGrowth = WDI(indicator='NY.GDP.MKTP.KD.ZG', country=c('MX','CA','US','FR','AU','AT','BE',
+                                                         'CL','CZ','DK','EE','FI','DE','HU', 
+                                                         'IS','IE','IL','IT','JP','KR','LU',
+                                                         'NL','NZ','NO','PL','PT','SK','SI',
+                                                         'ES','SE','CH','TR','GB','US','GR'), 
+                start=2001, end=2013)
+# Rename columns
+GDPGrowth <- plyr::rename(x = GDPGrowth, 
+                                      replace = c("year" = "Year",
+                                                  "NY.GDP.MKTP.KD.ZG" = "AnnualGDPGrowth",
+                                                  "country" = "Country"))
+
+# Recode country == "United States" to "United States of America" and Korea, Rep. to Korea (South)
+GDPGrowth$Country[GDPGrowth$Country == "United States"] <- "United States of America"
+
+# Recode country == "Korea, Rep."" to "Korea (South)"
+GDPGrowth$Country[GDPGrowth$Country == "Korea, Rep."] <- "Korea (South)"
+
+# Remove iso2c data to ease merge with FinalMerge data
+GDPGrowth$iso2c <- NULL
+
+# Merge GDPGrowth and FinalMerge
+CompeteDataset <- merge(FinalMerge, GDPGrowth,
+                   union("Country", "Year"),
+                   all = TRUE)
 

### 2014-11-13 GEMDataSource.Rmd
Label mistakes

@@
 # Rename columns
-CPerceivedCapabilities <- plyr::rename(x = CPerceivedCapabilities, 
+CPerceivedOpportunities <- plyr::rename(x = CPerceivedOpportunities, 
                                       replace = c("variable" = "Year",

### 2014-11-13 GEMDataSource.Rmd
Accept edit
Merge of Perceived Capabilities into FinalGEM

@@
 
-# Change years from columns to rows and create CPreceivedCapabilities
+# Change years from columns to rows and create CPreceivedOpportunities
 CPerceivedOpportunities<- melt(data = PerceivedOpportunities,
@@
 
-FinalMerge <- merge(MergedGem2, MergedGem3,
+MergedGem4 <- merge(MergedGem2, MergedGem3,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+FinalGEM <- merge(MergedGem4, CPerceivedOpportunities,
                    union("Country", "Year"),
@@
 # Convert percent columns from character to numeric
-FinalMerge[,"PercentPerceived"] <- as.numeric(FinalMerge[,"PercentPerceived"])
-FinalMerge[,"PercentFear"] <- as.numeric(FinalMerge[,"PercentFear"])
-FinalMerge[,"PercentNascent"] <- as.numeric(FinalMerge[,"PercentNascent"])
-FinalMerge[,"PercentOwner"] <- as.numeric(FinalMerge[,"PercentOwner"])
-FinalMerge[,"PercentIntention"] <- as.numeric(FinalMerge[,"PercentIntention"])
+FinalGEM[,"PercentPerceived"] <- as.numeric(FinalGEM[,"PercentPerceived"])
+FinalGEM[,"PercentFear"] <- as.numeric(FinalGEM[,"PercentFear"])
+FinalGEM[,"PercentNascent"] <- as.numeric(FinalGEM[,"PercentNascent"])
+FinalGEM[,"PercentOwner"] <- as.numeric(FinalGEM[,"PercentOwner"])
+FinalGEM[,"PercentIntention"] <- as.numeric(FinalGEM[,"PercentIntention"])
+FinalGEM[,"PercentOpportunities"] <- as.numeric(FinalGEM[,"PercentOpportunities"])
 
 # Check data to confirm change
-summary(FinalMerge)
+summary(FinalGEM)
 
 # Run a linear regression
-R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear, data = FinalMerge)
+R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear, data = FinalGEM)
 summary(R1)
@@
 # Run a linear regression
-R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear, data = FinalMerge)
+R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear, data = FinalGEM)
 summary(R2)
@@
 # Run a linear regression
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear, data = FinalMerge)
+R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear, data = FinalGEM)
 summary(R3)
@@
 # Plot graph
-car::scatterplotMatrix(FinalMerge)
+car::scatterplotMatrix(FinalGEM)
 
@@
 # Merge GDPGrowth and FinalMerge
-CompeteDataset <- merge(FinalMerge, GDPGrowth,
+CompeteDataset <- merge(FinalGEM, GDPGrowth,
                    union("Country", "Year"),

### 2014-11-13 GEMDataSource.Rmd
New data for opportunities
Updated environment and regression eq

@@
 # Import GEM perceived opportunities data as a proxy for potential control variables
-PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedOpportunities.csv", header = TRUE, cache = FALSE)
+PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE)
 
@@
 
-# Check data to confirm change
-summary(FinalGEM)
-
-# Run a linear regression
-R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear, data = FinalGEM)
-summary(R1)
-
-# Calculate confidence intervals
-confint(R1)
-
-# Run a linear regression
-R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear, data = FinalGEM)
-summary(R2)
-
-# Calculate confidence intervals
-confint(R2)
-
-# Run a linear regression
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear, data = FinalGEM)
-summary(R3)
-
-# Calculate confidence intervals
-confint(R3)
-
-# Plot graph
-car::scatterplotMatrix(FinalGEM)
-
 #### Import WDI Annual GDP Growth Data ####
@@
 
-# Merge GDPGrowth and FinalMerge
-CompeteDataset <- merge(FinalGEM, GDPGrowth,
+# Merge GDPGrowth and FinalGEM
+CompleteDataset <- merge(FinalGEM, GDPGrowth,
                    union("Country", "Year"),
@@
 
+# Remove unncessary data from environment
+remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre)
+
+# Check data to confirm change
+summary(CompleteDataset)
+
+# Run a linear regression
+R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
+           PercentOpportunities, data = CompleteDataset)
+summary(R1)
+
+# Calculate confidence intervals
+confint(R1)
+
+# Run a linear regression
+R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear, data = FinalGEM)
+summary(R2)
+
+# Calculate confidence intervals
+confint(R2)
+
+# Run a linear regression
+R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear, data = FinalGEM)
+summary(R3)
+
+# Calculate confidence intervals
+confint(R3)
+
+# Plot graph
+car::scatterplotMatrix(CompleteDataset)
+
 ```

### 2014-11-13 GEMDataSource.Rmd
Regressions Nascent Entrepreneurship, Established Owner

@@
 # Run a linear regression
-R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear, data = FinalGEM)
+R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
+           PercentOpportunities, data = CompleteDataset)
 summary(R2)
@@
 # Run a linear regression
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear, data = FinalGEM)
+R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
+           PercentOpportunities, data = CompleteDataset)
 summary(R3)

### 2014-11-13 GEMDataSource.Rmd
Start of Data Description

@@
 ---
-title: "DataGatheringandAnalysis"
-author: "Sam"
-date: "November 10, 2014"
+title: "The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis"
+author: "Samuel Dundon and Thierry Racaud"
+date: "November 14, 2014"
 output: html_document
@@
 ```
+
+*Introduction to Collaborative Social Science Data Analysis*
+
+### Research Question
+
+To what extent do the behavioural characteristics of the education system - individualistic, group-oriented, self-esteem reinforcing - affect the rate of entrepreneurship in OECD countries?
+
+### Estimation Strategy
+
+### Causal Chain
+
+Stronger culture of positive reinforcement ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
+
+### Data
+
+To find out, we need to gather quantitative data about entrepreneurship on the one hand, and some measures of these behavioural characteristics on the other hand.
+
+Regarding entrepreneurship, we intend to look into three dimensions.
+We intend to look at established entrepreneurship in the country, whether it is successful or not, nascent entrepreneurship (less than three months), again whether it is successful or not, and entrepreneurial intention.
+We may well observe different effects, studying them successively.

### 2014-11-13 GEMDataSource.Rmd
Added stargaze chart

--- 2014-11-13 GEMDataSource.Rmd
@@
 
-```{r echo =FALSE, cache=TRUE, include=FALSE}
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+
 # Set working directory
@@
 library(WDI)
+library(stargazer)
 
@@
 ### Clean FearFail ###
-# Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from seeting up a business.
+# Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
 
@@
 ### Clean NascentEntre ###
+# Percentage of 18-64 population who are currently a nascent entrepreneur, i.e., actively involved in setting up a business they will own or co-own; this business has not paid salaries, wages, or any other payments to the owners for more than three months.
+
 # Remove X's in NascentEntre year columns
@@
 #### Import WDI Annual GDP Growth Data ####
-WDIsearch('gdp')
 GDPGrowth = WDI(indicator='NY.GDP.MKTP.KD.ZG', country=c('MX','CA','US','FR','AU','AT','BE',
@@
 # Run a linear regression
-R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear, data = FinalGEM)
+R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear + AnnualGDPGrowth, data = CompleteDataset)
 summary(R2)
@@
 # Run a linear regression
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear, data = FinalGEM)
+R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear + AnnualGDPGrowth, data = CompleteDataset)
 summary(R3)
@@
 car::scatterplotMatrix(CompleteDataset)
+```
+
+```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'} 
+# Create regression output table
+labels <- c('(Intercept)', 'Percent Perceived', 'Percent Fear',
+            'Annual GDP Growth', 'Percent Opportunities')
+
+stargazer::stargazer(R1, R2, R3, covariate.lables = labels, title = 'Linear Regression Estimates', digits = 2, type = 'html')
 

### 2014-11-13 GEMDataSource.Rmd
Fixed regression output table

@@
 R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear + AnnualGDPGrowth, data = CompleteDataset)
+
+R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
+           PercentOpportunities, data = CompleteDataset)
+
 summary(R2)
@@
 R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear + AnnualGDPGrowth, data = CompleteDataset)
+
+R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
+           PercentOpportunities, data = CompleteDataset)
+
 summary(R3)
@@
 # Create regression output table
-labels <- c('(Intercept)', 'Percent Perceived', 'Percent Fear',
-            'Annual GDP Growth', 'Percent Opportunities')
+labels <- c('Percent Perceived', 'Percent Fear',
+            'Annual GDP Growth', 'Percent Opportunities', '(Intercept)')
 
-stargazer::stargazer(R1, R2, R3, covariate.lables = labels, title = 'Linear Regression Estimates', digits = 2, type = 'html')
+stargazer::stargazer(R1, R2, R3, covariate.labels = labels, 
+                     title = 'Linear Regression Estimates', digits = 2, type = 'html')
 
 ```
+
+*Introduction to Collaborative Social Science Data Analysis*
+
+### Research Question
+
+To what extent do the behavioural characteristics of the education system - individualistic, group-oriented, self-esteem reinforcing - affect the rate of entrepreneurship in OECD countries?
+
+### Estimation Strategy
+
+### Causal Chain
+
+Stronger culture of positive reinforcement ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
+
+### Data
+
+To find out, we need to gather quantitative data about entrepreneurship on the one hand, and some measures of these behavioural characteristics on the other hand.
+
+Regarding entrepreneurship, we intend to look into three dimensions.
+We intend to look at established entrepreneurship in the country, whether it is successful or not, nascent entrepreneurship (less than three months), again whether it is successful or not, and entrepreneurial intention.
+We may well observe different effects, studying them successively.
+
+>>>>>>> d492a8dcde27e8a4480f0504d410e52e7c2d7e6e

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd
Data Collection Comment

@@
 We intend to look at established entrepreneurship in the country, whether it is successful or not, nascent entrepreneurship (less than three months), again whether it is successful or not, and entrepreneurial intention.
-We may well observe different effects, studying them successively.
+We will study them successively as we may well observe different effects.
 
->>>>>>> d492a8dcde27e8a4480f0504d410e52e7c2d7e6e
+### Conclusion
+
+The impact of cultural factors in education on the rate of entrepreneurship in a given country is an important and under-researched topic that should be considered by policymakers constructing public education budgets.
+Through this project, we hope to encourage the consideration of these cultural factors by providing a qualitative and quantitative method for understanding the impact of these factors.
+Although several challenges remain to compiling the indexes discussed in this report, we are confident we can produce a helpful framework for examining and understanding these factors.
+
+### References

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

@@
 
-Stronger culture of positive reinforcement ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
+Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
 

### 2014-11-13 GEMDataSource.Rmd
Updated regression output table and attempted simulation

--- 2014-11-13 GEMDataSource.Rmd
@@
 library(stargazer)
+library(Zelig)
 
@@
 # Run a linear regression
-R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
-           PercentOpportunities, data = CompleteDataset)
+R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
+
+# Obtain summary statistics of R1
 summary(R1)
 
-# Calculate confidence intervals
+# Calculate confidence intervals of R1
 confint(R1)
 
-# Run a linear regression
-R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear + AnnualGDPGrowth, data = CompleteDataset)
+# Run a linear regression of R2
+R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
 
-R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
-           PercentOpportunities, data = CompleteDataset)
-
+# Obtain summary statistics of R2
 summary(R2)
 
-# Calculate confidence intervals
+# Calculate confidence intervals of R2
 confint(R2)
 
-# Run a linear regression
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear + AnnualGDPGrowth, data = CompleteDataset)
+# Run a linear regression of R3
+R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
 
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear + AnnualGDPGrowth + 
-           PercentOpportunities, data = CompleteDataset)
-
+# Obtain summary statistics of R3
 summary(R3)
 
-# Calculate confidence intervals
+# Calculate confidence intervals of R3
 confint(R3)
@@
 labels <- c('Percent Perceived', 'Percent Fear',
-            'Annual GDP Growth', 'Percent Opportunities', '(Intercept)')
+            'Annual GDP Growth', 'Percent Opportunities', 'Percent Fear x Percent Opportunities','(Intercept)')
 
@@
                      title = 'Linear Regression Estimates', digits = 2, type = 'html')
+
+```
+
+```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'}
+library(Zelig)
+
+Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, cite = FALSE,
+            data = CompleteDataset, model = 'ls', param = function(z.out))
+
+z5 <- zls$new()
+
+summary(Z1)
+
+Z1$sim()
+
+sim(setz1)
 
@@
 We may well observe different effects, studying them successively.
-
->>>>>>> d492a8dcde27e8a4480f0504d410e52e7c2d7e6e

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

@@
 
-To what extent do the behavioural characteristics of the education system - individualistic, group-oriented, self-esteem reinforcing - affect the rate of entrepreneurship in OECD countries?
+To what extent do the behavioural characteristics of education systems - individualistic, group-oriented, self-esteem reinforcing - affect the rate of entrepreneurship in OECD countries?
 
@@
 
-Regarding entrepreneurship, we intend to look into three dimensions.
+#### The rate of entrepreneurship at country-level is the variable we intend to explain
+
+We intend to look into three dimensions of entrepreneurship.
 We intend to look at established entrepreneurship in the country, whether it is successful or not, nascent entrepreneurship (less than three months), again whether it is successful or not, and entrepreneurial intention.
-We may well observe different effects, studying them successively.
+We will study them successively as we may well observe different effects.
+
+#### Self-esteem will be our key explanatory variable
+
+#### We will control for classic determinants of entrepreneurship
+
+### Conclusion
+
+The impact of cultural factors in education on the rate of entrepreneurship in a given country is an important and under-researched topic that should be considered by policymakers constructing public education budgets.
+Through this project, we hope to encourage the consideration of these cultural factors by providing a qualitative and quantitative method for understanding the impact of these factors.
+Although several challenges remain to compiling the indexes discussed in this report, we are confident we can produce a helpful framework for examining and understanding these factors.
+
+### References
+
+>>>>>>> 648e7ea9f4a5614384d90351f0cd6454bd142647

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

@@
 
-### Causal Chain
+#### Causal Chain
 
@@
 
-### Data
+#### Data
 
@@
 
-#### The rate of entrepreneurship at country-level is the variable we intend to explain
+##### The rate of entrepreneurship at country-level is the variable we intend to explain
 
@@
 
-#### Self-esteem will be our key explanatory variable
+##### Self-esteem will be our key explanatory variable
 
-#### We will control for classic determinants of entrepreneurship
+##### We will control for classic determinants of entrepreneurship
+
+We will obviously need to control for the economic outlook at the time of data collection about entrepreneurship characteristics.
+We will also need to control for nine key entrepreneurship conditions as defined in the [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection) that may affect the rate of entrepreneurship.
+These nine conditions are the following:
+
+1. Finance  
+2. Government policies  
+3. Government programs  
+4. Entrepreneurial Education and Training  
+5. Research and Development Transfer (R & D)  
+6. Commercial and professional infrastructure  
+7. Internal Market openness  
+8. Physical infrastructure and services  
+9. Cultural and social norms
+
+We are not yet fully sure on how to best control for all these variables though as GEM data does not seem to be available in dataset format as such.
+We may need to build up our own dataset, collecting data from the many national GEM NES reports.
+We will work on this in the coming weeks.
+
+As for now, as a substitute to all these conditions together, we use GEM indicator called "Perceived Opportunities".
+For each country, it is the average percentage of individuals who believe there are opportunities to start a business in the area they live in.
+This is not equivalent to controlling for all the conditions above but it actually tells about all of them from the potential entrepreneur's point of view.
+Since we look at average individual self-esteem in every OECD country, we believe it is consistent to look at the opportunities perceived by the average individual of these countries.
 

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

@@
 
-We will obviously need to control for the economic outlook at the time of data collection about entrepreneurship characteristics.
-We will also need to control for nine key entrepreneurship conditions as defined in the [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection) that may affect the rate of entrepreneurship.
+We will intend to control for the classic determinants of entrepreneurship, that is for economic and structural determinants.
+More specifically, we will control for nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection) that may affect the rate of entrepreneurship.
 These nine conditions are the following:
@@
 
-We are not yet fully sure on how to best control for all these variables though as GEM data does not seem to be available in dataset format as such.
+We are not yet fully sure on how to best control for all these variables though, esspecially as GEM data does not seem to be available in dataset format as such.
 We may need to build up our own dataset, collecting data from the many national GEM NES reports.
@@
 This is not equivalent to controlling for all the conditions above but it actually tells about all of them from the potential entrepreneur's point of view.
-Since we look at average individual self-esteem in every OECD country, we believe it is consistent to look at the opportunities perceived by the average individual of these countries.
+Since we look at average individual self-esteem in every OECD country, we believe it is consistent to look at the opportunities perceived by the same potential entrepreneur, that is by the average 18-64-year-old individual of these countries.
+
+Besides these nine conditions and the GEM "perceived opportunities" measure, we also intend to control for the economic outlook at the time of data collection which is why we chose to include growth rate for each country from 2001 until 2013.
+This is our only data that does not originates from the GEM collection.
 

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

@@
 
-##### Self-esteem will be our key explanatory variable
+##### Degree of Self-esteem reinforcement within the education system will be our key explanatory variable
+
+Inglehart showed how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) does shape the individual, especially in terms of self-esteem.
+Of course, is is not easy to quantify how supportive of students' self-esteem a given education system can be and we are still looking for the most adequate measure.
+
+The closest data we found so far is one of the six items / questions that GEM uses to measure the importance of entrepreneurial education at country-level in its NES Survey. Item D01 states:
+
+In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative.
+
+For now, we use two GEM indicators that relate to self-esteem and confidence. We look at the average "perceived capabilities" of an individual of a given country.
 
@@
 
-We are not yet fully sure on how to best control for all these variables though, esspecially as GEM data does not seem to be available in dataset format as such.
+We are not yet fully sure on how best to control for all these variables, especially as GEM NES data does not seem to be available in dataset format as such.
 We may need to build up our own dataset, collecting data from the many national GEM NES reports.
@@
 This is not equivalent to controlling for all the conditions above but it actually tells about all of them from the potential entrepreneur's point of view.
-Since we look at average individual self-esteem in every OECD country, we believe it is consistent to look at the opportunities perceived by the same potential entrepreneur, that is by the average 18-64-year-old individual of these countries.
+Since we look at average individual self-esteem in every OECD country, we believe it is consistent to look at the opportunities perceived by the average 18-64-year-old individual of these countries.
 

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

@@
 
-The closest data we found so far is one of the six items / questions that GEM uses to measure the importance of entrepreneurial education at country-level in its NES Survey. Item D01 states:
+The closest data we found so far is one of the six items / questions that GEM uses to measure the importance of entrepreneurial education at country-level in its NES Survey.
+Item D01 states: "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative".
 
-In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative.
+For now, we use two GEM indicators that relate to self-esteem and confidence.
 
-For now, we use two GEM indicators that relate to self-esteem and confidence. We look at the average "perceived capabilities" of an individual of a given country.
+We look at the average "perceived capabilities" of an individual (18-64) of a given country to start a business.
+
+We also take into account how likely the "fear of failure" could deter the average individual (18-64) of a country to become an entrepreneur.
 

### 2014-11-13 GEMDataSource.Rmd
Six hours of attempts, no simulation

--- 2014-11-13 GEMDataSource.Rmd
@@
 library(stargazer)
-library(Zelig)
 
@@
 
+CompleteDataset[,"AnnualGDPGrowth"] <- as.numeric(CompleteDataset[,"AnnualGDPGrowth"])
+
 # Remove unncessary data from environment
@@
 ```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'}
+
+library(zoo)
+library(sandwich)
+library(MCMCpack)
+library(coda)
+library(lattice)
+library(mvtnorm)
+library(VGAM)
+library(sna)
+library(systemfit)
+library(nnet)
+library(gee)
+library(mgcv)
 library(Zelig)
+library(ZeligChoice)
 
-Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, cite = FALSE,
-            data = CompleteDataset, model = 'ls', param = function(z.out))
+VectorData <- as.vector(CompleteDataset)
 
-z5 <- zls$new()
+class(CompleteDataset$GDPGrowth)
 
-summary(Z1)
+z.out <- zelig(as.factor(PercentIntention) ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, cite = FALSE, data = VectorData, model = "oprobit")
 
+x.out1 <- setx(z.out, PercentPerceived=10)
+
+x.out2 <- setx(z.out, PercentPerceived=100)
+
+s.out <- sim(z.out)
+
+summary(s.out)
+
+plot(s.out)
+
+names(Z1)
+
+plot(Z1)
+
+Z1$result
+
+sim(Z1)
+
+source("http://r.iq.harvard.edu/install_zelig.R")
 Z1$sim()
@@
 
-To what extent do the behavioural characteristics of education systems - individualistic, group-oriented, self-esteem reinforcing - affect the rate of entrepreneurship in OECD countries?
+To what extent do the behavioural characteristics of the education system - individualistic, group-oriented, self-esteem reinforcing - affect the rate of entrepreneurship in OECD countries?
 
@@
 
-#### Causal Chain
+### Causal Chain
 
@@
 
-#### Data
+### Data
 
@@
 
-##### The rate of entrepreneurship at country-level is the variable we intend to explain
+Regarding entrepreneurship, we intend to look into three dimensions.
+We intend to look at established entrepreneurship in the country, whether it is successful or not, nascent entrepreneurship (less than three months), again whether it is successful or not, and entrepreneurial intention.
+We may well observe different effects, studying them successively.
 
-We intend to look into three dimensions of entrepreneurship.
+Regarding entrepreneurship, we intend to look into three dimensions.
 We intend to look at established entrepreneurship in the country, whether it is successful or not, nascent entrepreneurship (less than three months), again whether it is successful or not, and entrepreneurial intention.
 We will study them successively as we may well observe different effects.
-
-##### Self-esteem will be our key explanatory variable
-
-##### We will control for classic determinants of entrepreneurship
-
-We will intend to control for the classic determinants of entrepreneurship, that is for economic and structural determinants.
-More specifically, we will control for nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection) that may affect the rate of entrepreneurship.
-These nine conditions are the following:
-
-1. Finance  
-2. Government policies  
-3. Government programs  
-4. Entrepreneurial Education and Training  
-5. Research and Development Transfer (R & D)  
-6. Commercial and professional infrastructure  
-7. Internal Market openness  
-8. Physical infrastructure and services  
-9. Cultural and social norms
-
-We are not yet fully sure on how to best control for all these variables though, esspecially as GEM data does not seem to be available in dataset format as such.
-We may need to build up our own dataset, collecting data from the many national GEM NES reports.
-We will work on this in the coming weeks.
-
-As for now, as a substitute to all these conditions together, we use GEM indicator called "Perceived Opportunities".
-For each country, it is the average percentage of individuals who believe there are opportunities to start a business in the area they live in.
-This is not equivalent to controlling for all the conditions above but it actually tells about all of them from the potential entrepreneur's point of view.
-Since we look at average individual self-esteem in every OECD country, we believe it is consistent to look at the opportunities perceived by the same potential entrepreneur, that is by the average 18-64-year-old individual of these countries.
-
-Besides these nine conditions and the GEM "perceived opportunities" measure, we also intend to control for the economic outlook at the time of data collection which is why we chose to include growth rate for each country from 2001 until 2013.
-This is our only data that does not originates from the GEM collection.
 
@@
 ### References
-
->>>>>>> 648e7ea9f4a5614384d90351f0cd6454bd142647

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

--- 2014-11-13 GEMDataSource.Rmd
@@
 
-We look at the average "perceived capabilities" of an individual (18-64) of a given country to start a business.
+We look at the average "perceived capabilities" of an individual (18-64) of a given country to start a business. The data consists of average percentage at country-level.
 
-We also take into account how likely the "fear of failure" could deter the average individual (18-64) of a country to become an entrepreneur.
+We also take into account how the "fear of failure" could deter the average individual (18-64) of a country to become an entrepreneur. The data consists of average percentage at country-level.
+
+##### We will include measures to check how individualistic and group-oriented a given education system is
+
+Literature generally admits that self-confidence partly depends on the integration in social networks.
+Therefore, as we try to determine how supportive of students' self-esteem a given education system, we will look at how individualistic or group-oriented it is.
+To quantify such a behavioural feature is not easy, which is why we will have to rely on another measure: how individualistic or group-oriented an average student is by the end of compulsory education.
+Since OECD PISA collects data about students at the end of compulsory education, we will rely on "the sense of belonging" it defines.
 

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

@@
 
+To measure these three dimensions of entrepreneurship, we will use three [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) indicators:
+
+- Established Business Ownership Rate (Percentage) 
+- Nascent Entrepreneurship Rate (Percentage)
+- Entrepreneurial intention Rate (Percentage)
+
+We chose the GEM measure of entrepreneurship, as it is often referred to, especially in OECD studies.
+
 ##### Degree of Self-esteem reinforcement within the education system will be our key explanatory variable

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

@@
 
-#### Data
+#### Data Collection
 
@@
 
-Besides these nine conditions and the GEM "perceived opportunities" measure, we also intend to control for the economic outlook at the time of data collection which is why we chose to include growth rate for each country from 2001 until 2013.
+Besides these nine conditions and the GEM "perceived opportunities" measure, we also intend to control for the economic outlook at the time of data collection which is why we chose to include GDP annual growth rate for each country from 2001 until 2013.
 This is our only data that does not originates from the GEM collection.
 
-### Conclusion
+#### Data Scraping and Cleaning
+
+In order to scrape our data, we used repmis, tidyr, reshape2, plyr, WDI, stargazer and Zelig packages. We then imported one dataset per variable mentioned above:
+GEM Established Entrepreneurship Rate
+GEM Nascent Entrepreneurship Rate
+GEM Entrepreneurial Intention
+GEM Perceived Capabilities
+GEM Fear of Failure
+GEM Perceived Opportunities
+GDP Annual Growth Rate
+
+.
+
+### Summary
 

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

@@
 In order to scrape our data, we used repmis, tidyr, reshape2, plyr, WDI, stargazer and Zelig packages. We then imported one dataset per variable mentioned above:
+
 GEM Established Entrepreneurship Rate
+
 GEM Nascent Entrepreneurship Rate
+
 GEM Entrepreneurial Intention
+
 GEM Perceived Capabilities
+
 GEM Fear of Failure
+
 GEM Perceived Opportunities
+
 GDP Annual Growth Rate

### 2014-11-13 GEMDataSource.Rmd
Update GEMDataSource.Rmd

@@
 
-In order to scrape our data, we used repmis, tidyr, reshape2, plyr, WDI, stargazer and Zelig packages. We then imported one dataset per variable mentioned above:
+In order to scrape our data, we used repmis, tidyr, reshape2, plyr, WDI, stargazer and Zelig packages before importing one dataset per variable mentioned above:
 
 GEM Established Entrepreneurship Rate  
-
 GEM Nascent Entrepreneurship Rate  
-
 GEM Entrepreneurial Intention  
-
 GEM Perceived Capabilities  
-
 GEM Fear of Failure   
-
 GEM Perceived Opportunities  
-
 GDP Annual Growth Rate
 
-.
+We cleaned our data by getting rid of unnecessary characters like the "X" to which we substituted ""nothing. We called the new versions with different names.
+
+One issue we then faced was to merge our datasets all together into a two-dimension table whilst we had three dimensions to take into account: country, year and variable.
+Therefore, for each dataset, we moved the years from columns to rows, without getting rid of the country labels of course.
+Thus the first column would be the list of countries, the second the list of years (same for each country: 2001 ...
+2013), the third the variable of interest.
+
+We merged the datasets two by two until we we obtained the final dataset that would allow us to test the data and have an attempt at one or two regressions.
 

### 2014-11-14 GEMDataSource.Rmd
Formatting and sims

--- 2014-11-13 GEMDataSource.Rmd
@@
 ---
-title: "The Country-level Impact of Educational Features on the Rate of Entrepreneurship - Data Gathering and Analysis"
+title: Education and the Rate of Entrepreneurship - Data Gathering and Analysis
 author: "Samuel Dundon and Thierry Racaud"
@@
 ---
+***
 
+*Introduction to Collaborative Social Science Data Analysis*
+
+#### Research Question
+
+To what extent do the behavioral characteristics of education systems - individualistic, group-oriented, self-esteem reinforcing - affect the rate of entrepreneurship in OECD countries?  
+<br>
+
+#### Causal Chain
+
+Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
+<br>
+
+##### Dependent Variables: Explaining the Country-level Rate of Entrepreneurship
+
+We have examined three dimensions of entrepreneurship to prepare for this stage of the project.
+We have analyzed established entrepreneurship in the country, nascent entrepreneurship (less than three months), and entrepreneurial intention.
+We will study them successively as we may well observe different effects.
+
+To measure these three dimensions of entrepreneurship, we have used three [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) indicators:
+
+- Established Business Ownership Rate (Percentage) 
+- Nascent Entrepreneurship Rate (Percentage)
+- Entrepreneurial intention Rate (Percentage)
+
+We chose the GEM measure of entrepreneurship, as it is often referred to, especially in OECD studies.
+
+##### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System
+
+As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem.
+Of course, is is not easy to quantify how supportive of students' self-esteem a given education system can be and we are still looking for the most adequate measure.
+
+To begin with, we decided to incorporate to GEM indicators that relate to self-esteem and confidence.
+First, included GEM survey data on the average "perceived capabilities" of an individual (18-64) of a given country to start a business.
+The data consists of average percentage at country-level.
+Second, we included additional GEM data on how the "fear of failure" could deter the average individual (18-64) of a country to become an entrepreneur.
+The data consists of average percentage at country-level.
+
+Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at country-level in its NES Survey.
+Item D01 states: "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative."
+
+##### Control Variables: Controlling for Classic Determinants of Entrepreneurship
+
+To control for the general state of the economy globally and in each country, we included Annual GDP Growth from the World Bank as a control variable in our regression equations.
+We first considered including real GDP, but decided to include growth to more accurately capture fluctuation in the economy.
+In addition, we included a GEM indicator called "Perceived Opportunities." For each country, it is the average percentage of individuals who believe there are opportunities to start a business in the area they live in.
+Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual of these countries.
+
+In the future, we may include lagged GDP growth in recognition of the time taken for governments and individuals to react to the state of the economy, and are planning to include several control variables from GEM.
+Specifically, we intend to control for the classic determinants of entrepreneurship -- economic and structural determinants.
+To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection) that may affect the rate of entrepreneurship.
+
+1. Finance  
+2. Government policies  
+3. Government programs  
+4. Entrepreneurial Education and Training  
+5. Research and Development Transfer (R & D)  
+6. Commercial and professional infrastructure  
+7. Internal Market openness  
+8. Physical infrastructure and services  
+9. Cultural and social norms
+
+The following equations were used to determine the relationship between our dependent and explanatory variables:
+
+<br>
+
+1. $PercentIntention = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
+
+2. $PercentNascent = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
+
+3. $PercentOwner = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$  
+<br>
+
+The variables *Percent Fear* and *Percent Opportunities* were included as an interaction term $PercentFear*PercentOpportunities$ because of the design of the survey. PercentFear is:
+
+>The Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
+
+<br>
+
+#### Data Collection and Cleaning
+
+To collect the data necessary to run these regression equations, we downloaded *.csv* data from GEM and used the WDI API to obtain the necessary Annual GDP growth of OECD Countries.
+
+**Necessary R Packages**
+
+The following packages were needed to complete the data collection portion of this assignment:
+
+* repmis  
+* tidyr  
+* reshape  
+* plyr  
+* WDI
+
+**GEM Data**
+
+GEM data was embedded in an interactive database and was difficult to extract automatically without writing a program.
+To simplify this process, we downloaded the necessary *.csv* files and saved them in our GitHub repository (to reduce complexity, we deleted the first three unnecessary rows before saving).
+We then linked to the RAW version of the files and added the code required to load them from *R*.
+The repmis package is required to load these documents from the repository.
+
+Cleaning the GEM data required deleting unnecessary characters in the year columns, changing the years from columns to rows (changing the data from wide to long), and changing the column names to describe which data was being analyzed.
+In the process of doing this we created new data sets for each of these survey questions, which were called C*dataset* (clean followed by the data set name).
+This was done for each of the six GEM data sets before merging these sets two at a time to create the data set *FinalGEM*.
+
+For all 33 OECD countries we should have 13 observations, one per year from 2001 to 2013, for each variable.
+However, there are a few missing values, especially regarding the perceived opportunities for some countries, namely Estonia, Luxembourg and Slovak Republic.
+
+**World Bank Data**
+
+As mentioned above, one of our control variables, annual GDP growth, was obtained using the [World Development Indicators](http://data.worldbank.org/data-catalog/world-development-indicators) API from the World Bank.
+Using this API, we accessed GDP data from all the OECD countries directly from R and R will pull this information from WDI whenever this code is run.
+To clean this data, we used plyr to change the variable names then recoded the U.S.
+and South Korea country names to maintain consistency with the GEM data set and dropped an unnecessary column that was not included with the GEM data.
+
+Finally, we merged the annual GDP growth data with the *FinalGEM* data set to create *CompleteDataset*.
+This is the data set used to run the regressions and generate the charts and figures outlined in this report.
+To reduce complexity in the environment we also included a command to remove unnecessary objects from the environment (all the individual original and cleaned GEM data, and the intermediate merged data sets used to create *FinalGEM*)
+
+<br>
 ```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
@@
 
-# Library Repmis, Tidy, Reshape2, and plyr packages
+# Library required packages repmis, ridy, reshape2, plyr, WDI, and stargazer packages
 library(repmis)
@@
 
-# Check data to confirm change
-summary(CompleteDataset)
+```
 
-# Run a linear regression
+#### Data Analysis
+
+To review, the three regression equations run for this assignment are the following:
+
+1. $PercentIntention = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
+
+2. $PercentNascent = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
+
+3. $PercentOwner = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
+
+To examine the relationship between these variables, we used least square estimation, the results of which can be found in the following table.
+The package *stargazer* was required to generate this table.
+As evidenced by the equation results, the individual variables selected are statistically significant, but the model only explains a relatively small degree of the variation in the dependent variable.
+For example, the adjusted $R^2$ of regression equation one is .29, the adjusted $R^2$ of regression equation two is .38, and the adjusted $R^2$ is .13.
+<br>
+
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+
+# Run linear regression R1
 R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
@@
 
-# Calculate confidence intervals of R1
-confint(R1)
-
-# Run a linear regression of R2
+# Run linear regression R2
 R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
@@
 
-# Calculate confidence intervals of R2
-confint(R2)
-
-# Run a linear regression of R3
+# Run linear regression R3
 R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
@@
 summary(R3)
-
-# Calculate confidence intervals of R3
-confint(R3)
-
-# Plot graph
-car::scatterplotMatrix(CompleteDataset)
 ```
@@
 ```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'}
+
 # Create regression output table
@@
                      title = 'Linear Regression Estimates', digits = 2, type = 'html')
+```
+<br>
+
+**Simulation Package and Cleaning**
+
+In addition to the output table, a simulation is helpful to visually illustrate the relationship the probability of obtaining a given value in the dependent variables conditional on change in the independent variable.
+We used the *Zelig* package to run a least square regression and generate a simulation of equation 1.
+Prior to running this regression, however, we ran the na.omit command to remove omitted variables from the equation.
+
+To examine the probabilities of achieving given outcomes, we generated three simulations for the first regression equation.  To demonstrate this method, we have included one simulation below.
+
+**Process**
+
+First, we estimated a least square equation with variation in the variable *PercentPerceived* of 20-100 percent.
+The ranges for variance in the independent variables was chosen by identifying the best range for capturing the largest degree of variance for the model.
+The first simulation is below.
+The y axis shows variation in *PercentIntention* conditional on change in *PercentPerceived* and the x axis shows variation in *PercentPerceived*.
+The results may be interpreted as showing that people who believe they have the knowledge required to start a business may or may not do so (with a high degree of variation), while people who do not believe they have this knowledge are consistently unlikely to start a business (there is little variation).
+
+```{r echo = FALSE, cache=TRUE, include=FALSE, results='asis'}
+
+# Library Zelig (can be buggy if loaded to early)
+library(Zelig)
+
+# Omit omitted data from simulation
+CompleteData_omit <- na.omit(CompleteDataset)
+
+# Run a least squares regression with Zelig
+Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteData_omit, model = "ls")
+```
+
+```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis' }
+
+# Set range of PercentPerceived values in simulation
+x.out2 <- setx(Z1, PercentPerceived = 20:100)
+
+# Run simulation (default 1000 trials)
+simz2 <- sim(Z1, x = x.out2)
+
+# Adjust margins
+par(mar=c(2,2,2,2))
+
+# Plot simulation
+plot(simz2)
 
@@
 
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'}
-library(Zelig)
-
-Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, cite = FALSE,
-            data = CompleteDataset, model = 'ls', param = function(z.out))
-
-z5 <- zls$new()
-
-summary(Z1)
-
-Z1$sim()
-
-sim(setz1)
-
-```
-
-*Introduction to Collaborative Social Science Data Analysis*
-
-### Research Question
-
-To what extent do the behavioural characteristics of education systems - individualistic, group-oriented, self-esteem reinforcing - affect the rate of entrepreneurship in OECD countries?
-
-### Estimation Strategy
-
-#### Causal Chain
-
-Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
-
-#### Data Collection
-
-To find out, we need to gather quantitative data about entrepreneurship on the one hand, and some measures of these behavioural characteristics on the other hand.
-
-##### The rate of entrepreneurship at country-level is the variable we intend to explain
-
-We intend to look into three dimensions of entrepreneurship.
-We intend to look at established entrepreneurship in the country, whether it is successful or not, nascent entrepreneurship (less than three months), again whether it is successful or not, and entrepreneurial intention.
-We will study them successively as we may well observe different effects.
-
-To measure these three dimensions of entrepreneurship, we will use three [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) indicators:
-
-- Established Business Ownership Rate (Percentage) 
-- Nascent Entrepreneurship Rate (Percentage)
-- Entrepreneurial intention Rate (Percentage)
-
-We chose the GEM measure of entrepreneurship, as it is often referred to, especially in OECD studies.
-
-##### Degree of Self-esteem reinforcement within the education system will be our key explanatory variable
-
-Inglehart showed how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) does shape the individual, especially in terms of self-esteem.
-Of course, is is not easy to quantify how supportive of students' self-esteem a given education system can be and we are still looking for the most adequate measure.
-
-The closest data we found so far is one of the six items / questions that GEM uses to measure the importance of entrepreneurial education at country-level in its NES Survey.
-Item D01 states: "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative".
-
-For now, we use two GEM indicators that relate to self-esteem and confidence.
-
-We look at the average "perceived capabilities" of an individual (18-64) of a given country to start a business. The data consists of average percentage at country-level.
-
-We also take into account how the "fear of failure" could deter the average individual (18-64) of a country to become an entrepreneur. The data consists of average percentage at country-level.
-
-##### We will include measures to check how individualistic and group-oriented a given education system is
-
-Literature generally admits that self-confidence partly depends on the integration in social networks.
-Therefore, as we try to determine how supportive of students' self-esteem a given education system, we will look at how individualistic or group-oriented it is.
-To quantify such a behavioural feature is not easy, which is why we will have to rely on another measure: how individualistic or group-oriented an average student is by the end of compulsory education.
-Since OECD PISA collects data about students at the end of compulsory education, we will rely on "the sense of belonging" it defines.
-
-##### We will control for classic determinants of entrepreneurship
-
-We will intend to control for the classic determinants of entrepreneurship, that is for economic and structural determinants.
-More specifically, we will control for nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection) that may affect the rate of entrepreneurship.
-These nine conditions are the following:
-
-1. Finance  
-2. Government policies  
-3. Government programs  
-4. Entrepreneurial Education and Training  
-5. Research and Development Transfer (R & D)  
-6. Commercial and professional infrastructure  
-7. Internal Market openness  
-8. Physical infrastructure and services  
-9. Cultural and social norms
-
-We are not yet fully sure on how best to control for all these variables, especially as GEM NES data does not seem to be available in dataset format as such.
-We may need to build up our own dataset, collecting data from the many national GEM NES reports.
-We will work on this in the coming weeks.
-
-As for now, as a substitute to all these conditions together, we use GEM indicator called "Perceived Opportunities".
-For each country, it is the average percentage of individuals who believe there are opportunities to start a business in the area they live in.
-This is not equivalent to controlling for all the conditions above but it actually tells about all of them from the potential entrepreneur's point of view.
-Since we look at average individual self-esteem in every OECD country, we believe it is consistent to look at the opportunities perceived by the average 18-64-year-old individual of these countries.
-
-Besides these nine conditions and the GEM "perceived opportunities" measure, we also intend to control for the economic outlook at the time of data collection which is why we chose to include GDP annual growth rate for each country from 2001 until 2013.
-This is our only data that does not originates from the GEM collection.
-
-#### Data Scraping and Cleaning
-
-In order to scrape our data, we used repmis, tidyr, reshape2, plyr, WDI, stargazer and Zelig packages. We then imported one dataset per variable mentioned above:
-
-GEM Established Entrepreneurship Rate
-
-GEM Nascent Entrepreneurship Rate
-
-GEM Entrepreneurial Intention
-
-GEM Perceived Capabilities
-
-GEM Fear of Failure
-
-GEM Perceived Opportunities
-
-GDP Annual Growth Rate
-
-.
+<br>
 

### 2014-11-14 GEMDataSource.Rmd
Edits to markdown for consistency, organized repository, and created new README

@@
 ---
-title: Education and the Rate of Entrepreneurship - Data Gathering and Analysis
+title: "Education and the Rate of Entrepreneurship - Data Gathering and Analysis"
 author: "Samuel Dundon and Thierry Racaud"
@@
 
-We have examined three dimensions of entrepreneurship to prepare for this stage of the project.
-We have analyzed established entrepreneurship in the country, nascent entrepreneurship (less than three months), and entrepreneurial intention.
-We will study them successively as we may well observe different effects.
+We have examined three dimensions of entrepreneurship to prepare for this stage of the project, established entrepreneurship in the country, nascent entrepreneurship (less than three months), and entrepreneurial intention.
+We will study each of these successively as we may well observe different effects.
 
@@
 
-We chose the GEM measure of entrepreneurship, as it is often referred to, especially in OECD studies.
-
 ##### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System
@@
 As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem.
-Of course, is is not easy to quantify how supportive of students' self-esteem a given education system can be and we are still looking for the most adequate measure.
-
-To begin with, we decided to incorporate to GEM indicators that relate to self-esteem and confidence.
-First, included GEM survey data on the average "perceived capabilities" of an individual (18-64) of a given country to start a business.
-The data consists of average percentage at country-level.
-Second, we included additional GEM data on how the "fear of failure" could deter the average individual (18-64) of a country to become an entrepreneur.
-The data consists of average percentage at country-level.
+To do so, we decided to incorporate GEM indicators that relate to self-esteem and confidence.
+First, we included GEM survey data on the average "perceived capabilities" of an individual (18-64) in a given country to start a business.
+Second, we included additional GEM data on how the "fear of failure" could deter an average individual (18-64) in a country to become an entrepreneur.
+Both of these data sets indicate the average percentage for each characteristic at the country-level.
 
@@
 
-To control for the general state of the economy globally and in each country, we included Annual GDP Growth from the World Bank as a control variable in our regression equations.
-We first considered including real GDP, but decided to include growth to more accurately capture fluctuation in the economy.
-In addition, we included a GEM indicator called "Perceived Opportunities." For each country, it is the average percentage of individuals who believe there are opportunities to start a business in the area they live in.
-Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual of these countries.
+To control for the general state of the economy, we included annual GDP Growth from the World Bank [World Development Indicators](http://data.worldbank.org/data-catalog/world-development-indicators) as a control variable in our regression equations.
+In addition, we included a GEM indicator called "Perceived Opportunities." For each country, it is the average percentage of individuals who believe there are opportunities to start a business in their area.
+Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.
 
-In the future, we may include lagged GDP growth in recognition of the time taken for governments and individuals to react to the state of the economy, and are planning to include several control variables from GEM.
+In the future, we may revise this to include lagged GDP growth in recognition of the time taken for governments and individuals to react to the state of the economy, and are planning to include control variables from GEM.
 Specifically, we intend to control for the classic determinants of entrepreneurship -- economic and structural determinants.
-To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection) that may affect the rate of entrepreneurship.
+To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection).
 
@@
 
-To collect the data necessary to run these regression equations, we downloaded *.csv* data from GEM and used the WDI API to obtain the necessary Annual GDP growth of OECD Countries.
+To collect the data necessary to run these regression equations, we downloaded *.csv* data from GEM and used the WDI API to obtain the necessary annual GDP growth of OECD Countries.
 
@@
 
-As mentioned above, one of our control variables, annual GDP growth, was obtained using the [World Development Indicators](http://data.worldbank.org/data-catalog/world-development-indicators) API from the World Bank.
-Using this API, we accessed GDP data from all the OECD countries directly from R and R will pull this information from WDI whenever this code is run.
-To clean this data, we used plyr to change the variable names then recoded the U.S.
+As mentioned above, one of our control variables, annual GDP growth, was obtained using the WDI API from the World Bank.
+Using this API, we accessed GDP data from all the OECD countries directly from *R*.
+To clean this data, we used *plyr* to change the variable names then recoded the U.S.
 and South Korea country names to maintain consistency with the GEM data set and dropped an unnecessary column that was not included with the GEM data.
@@
 Finally, we merged the annual GDP growth data with the *FinalGEM* data set to create *CompleteDataset*.
-This is the data set used to run the regressions and generate the charts and figures outlined in this report.
-To reduce complexity in the environment we also included a command to remove unnecessary objects from the environment (all the individual original and cleaned GEM data, and the intermediate merged data sets used to create *FinalGEM*)
+This is the data set used to run the regressions and generate the charts and figures outlined in this document.
+To reduce complexity in the environment we also included a command to remove unnecessary objects in the environment.
 
@@
 As evidenced by the equation results, the individual variables selected are statistically significant, but the model only explains a relatively small degree of the variation in the dependent variable.
-For example, the adjusted $R^2$ of regression equation one is .29, the adjusted $R^2$ of regression equation two is .38, and the adjusted $R^2$ is .13.
+For example, the adjusted $R^2$ of regression equation one is 0.29, the adjusted $R^2$ of regression equation two is 0.38, and the adjusted $R^2$ is 0.13.
 <br>
@@
 
-### Summary
+#### Summary
 
@@
 Although several challenges remain to compiling the indexes discussed in this report, we are confident we can produce a helpful framework for examining and understanding these factors.
-
-### References

### 2014-11-14 GEMDataSource.Rmd
Cleaned document and added citations

@@
 # Library required packages repmis, ridy, reshape2, plyr, WDI, and stargazer packages
+library(plyr)
 library(repmis)
@@
 library(reshape2)
-library(plyr)
 library(WDI)
@@
 # Load citation package
-pkgs <- c('repmis', 'tidyr', 'reshape2', 'plyr', 'WDI')
+pkgs <- c('plyr','repmis', 'tidyr', 'reshape2', 'WDI', 'stargazer', 'Zelig')
 repmis::LoadandCite(pkgs, file= 'DataRpackageCitations.bib')

### 2014-11-14 GEMDataSource.Rmd
Update GEMDataSource.Rmd

@@
 
-#### Causal Chain
+#### Estimation Strategy
+
+##### Causal Chain
 
@@
 
-Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at country-level in its NES Survey.
-Item D01 states: "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative."
-
 ##### Control Variables: Controlling for Classic Determinants of Entrepreneurship
@@
 9. Cultural and social norms
+
+##### Regressions
 
@@
 
-# Library required packages repmis, ridy, reshape2, plyr, WDI, and stargazer packages
+# Library required packages repmis, ridy, reshape2, plyr and WDI packages
 library(plyr)
@@
 library(WDI)
-library(stargazer)
 
@@
 
+# Library Stargazer for regression output tables
+library(stargazer)
+
 # Create regression output table
@@
 
-#### Summary
+#### Outlook
 
-The impact of cultural factors in education on the rate of entrepreneurship in a given country is an important and under-researched topic that should be considered by policymakers constructing public education budgets.
-Through this project, we hope to encourage the consideration of these cultural factors by providing a qualitative and quantitative method for understanding the impact of these factors.
-Although several challenges remain to compiling the indexes discussed in this report, we are confident we can produce a helpful framework for examining and understanding these factors.
+Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at country-level in its NES Survey.
+Item D01 states: "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self-esteem a given education system is.
+
+We may also want to quantify how individualistic or group-oriented an average student is by the end of compulsory education, as the literature holds social inclusion as an explanatory factor for self-esteem.
+We will use OECD PISA data on "the sense of belonging" for this.
+
+Next steps will also include looking more thoroughly into control variables.
+To do so we may need to extract data from various national NES reports and put together a table, as it does not seem to exist as such.

### 2014-11-14 GEMDataSource.Rmd
Update GEMDataSource.Rmd
Difficulties with errors about text formatting that was fine 2 hours ago

@@
 ---
-title: "Education and the Rate of Entrepreneurship - Data Gathering and Analysis"
+title: "Impact of Education on Entrepreneurship - Data Gathering and Analysis"
 author: "Samuel Dundon and Thierry Racaud"
@@
 Specifically, we intend to control for the classic determinants of entrepreneurship -- economic and structural determinants.
-To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://http://www.gemconsortium.org/Data-Collection).
+To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://www.gemconsortium.org/Data-Collection).
 
@@
 
-The variables *Percent Fear* and *Percent Opportunities* were included as an interaction term $PercentFear*PercentOpportunities$ because of the design of the survey. PercentFear is:
-
->The Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
+The variables *Percent Fear* and *Percent Opportunities* were included as an interaction term $PercentFear*PercentOpportunities$ because of the design of the survey.
+PercentFear is: "the Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business."
 
@@
 <br>
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
 
@@
 
-To review, the three regression equations run for this assignment are the following:
+To review, the three regression equations used for this assignment are included below.
 
@@
 
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
 
@@
 
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis'}
+```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
 
@@
 
-```{r echo = FALSE, cache=TRUE, include=FALSE, results='asis'}
+```{r echo = FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
 
@@
 
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis' }
+```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE }
 
@@
 
-Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at country-level in its NES Survey.
-Item D01 states: "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self-esteem a given education system is.
+Going forward, we are considering adding one oof the six questions used by GEM to measure the importance of entrepreneurial education at the country level in its NES Survey.
+Item D01 states "in my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self esteem a given education system is.
 
@@
 
-Next steps will also include looking more thoroughly into control variables.
+Next steps will also include looking more thoroughly into control variables and determining the most appropriate way to present our results.
 To do so we may need to extract data from various national NES reports and put together a table, as it does not seem to exist as such.

### 2014-11-14 GEMDataSource.Rmd
Final commit for assignment 3, minor text
Corrected spelling error

@@
 
-Going forward, we are considering adding one oof the six questions used by GEM to measure the importance of entrepreneurial education at the country level in its NES Survey.
+Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at the country level in its NES Survey.
 Item D01 states "in my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self esteem a given education system is.

### 2014-11-20 GEMDataSource.Rmd
Minor edits
Found appropriate range for Sim
minor

@@
 ***
+
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
+
+# Set working directory
+setwd('~/Assign2Education/')
+
+# Library required packages repmis, ridy, reshape2, plyr and WDI packages
+library(plyr)
+library(repmis)
+library(tidyr)
+library(reshape2)
+library(WDI)
+
+# Load citation package
+pkgs <- c('plyr','repmis', 'tidyr', 'reshape2', 'WDI', 'stargazer', 'Zelig')
+repmis::LoadandCite(pkgs, file= 'DataRpackageCitations.bib')
+
+```
 
@@
 
-* repmis  
-* tidyr  
-* reshape  
-* plyr  
-* WDI
+- repmis  
+- tidyr  
+- reshape  
+- plyr  
+- WDI
 
@@
 ```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
-
-# Set working directory
-setwd('~/Assign2Education/')
-
-# Library required packages repmis, ridy, reshape2, plyr and WDI packages
-library(plyr)
-library(repmis)
-library(tidyr)
-library(reshape2)
-library(WDI)
-
-# Load citation package
-pkgs <- c('plyr','repmis', 'tidyr', 'reshape2', 'WDI', 'stargazer', 'Zelig')
-repmis::LoadandCite(pkgs, file= 'DataRpackageCitations.bib')
 
@@
 
+# Find appropriate range for PercentPerceived
+summary(CompleteData_omit$PercentPerceived)
+
 # Set range of PercentPerceived values in simulation
-x.out2 <- setx(Z1, PercentPerceived = 20:100)
+x.out2 <- setx(Z1, PercentPerceived = 9:67)
 
@@
 # Plot simulation
-plot(simz2)
+plot(simz2, xlab= 'PercentPerceived')
 

### 2014-11-20 index.Rmd
First commit

---
title: 'Index'
author: "Sam"
date: "November 20, 2014"
output: html_document
---

### Under Construction

### 2014-11-21 GEMDataSource.Rmd
New data for equations

@@
 
-1. $PercentIntention = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
+1. $PercentIntention = PercentPerceived(Perceived Capabilities) + GEM D01 way of teaching + PercentOpportunities(Perceived Opportunities)$
 
@@
 # Create regression output table
-labels <- c('Percent Perceived', 'Percent Fear',
-            'Annual GDP Growth', 'Percent Opportunities', 'Percent Fear x Percent Opportunities','(Intercept)')
+labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
+            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')
 
-stargazer::stargazer(R1, R2, R3, covariate.labels = labels, 
+dlables <- c('National Level Average Percent Entrepreneurial Intention', 'National Level Nascent Entrepreneural Activity', 'National Level Average Percent Owning a Business')
+
+stargazer::stargazer(R1, R2, R3, covariate.labels = labels, dep.var.labels = dlables,
                      title = 'Linear Regression Estimates', digits = 2, type = 'html')
@@
 <br>  
+National-level average of people perceiving opportunities but acknowledging fear of failure will prevent them from creating a business (FF)
 
@@
 To do so we may need to extract data from various national NES reports and put together a table, as it does not seem to exist as such.
+
+```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
+library(xtable)
+Table1 <- xtable(summary(CompleteDataset))
+xtable(CompleteDataset, type = 'html')
+
+library(stargazer)
+stargazer(CompleteDataset, column.sep.width = "20pt", type = 'html')
+
+```

### 2014-11-21 GEMDataSource.Rmd
Import NES 2010

@@
 PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE)
+
+# Import GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is
+SupportiveTeaching <- repmis::source_data("https://https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/NES2010CSV/2010GEMNES-Table%201.csv", header = TRUE, cache = FALSE)
 

### 2014-11-21 GEMDataSource.Rmd
Trying to get stargazer to work well

--- 2014-11-21 GEMDataSource.Rmd
@@
 ```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
-library(xtable)
-Table1 <- xtable(summary(CompleteDataset))
-xtable(CompleteDataset, type = 'html')
 
 library(stargazer)
-stargazer(CompleteDataset, column.sep.width = "20pt", type = 'html')
+stargazer(CompleteDataset, column.separate = TRUE, type = 'html')
 

### 2014-11-21 GEMDataSource.Rmd
Corrected link to new dataframe

@@
 
+# Import GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is
+
+SupportiveTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEMAvgIndicators.csv", header = TRUE, cache = FALSE)
+
 #### Clean data using tidy ####
@@
                                                   "value" = "PercentOpportunities"))
+
+### Clean SupportiveTeaching
+
+#
 
@@
 library(stargazer)
-stargazer(CompleteDataset, column.separate = TRUE, type = 'html')
+stargazer(CompleteDataset, type = 'html')
 

### 2014-11-27 GEMDataSource.Rmd
Adding new dataset GEM2009

@@
 
-#
+### Create new data frame without unnecessary data
+WayOfTeaching <- SupportiveTeaching[, c("NES10CRNAME", "NES10_D01_MEAN")]
+
+## as.factor("WayOfTeaching")
+
+##TWayofTeaching <- SupportiveTeaching[c("Australia", "Austria", "Belgium", "Canada", "Chile", "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Japan", "Korea", "Luxemburg", "Mexico", "Netherlands", "New Zealand", "Norway", "Poland", "Portugal", "Slovak Republic", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom", "United States"),])
 

### 2014-11-27 GEMDataSource.Rmd
Added new GEM data

@@
 library(WDI)
+library(foreign)
 
@@
 
-1. $PercentIntention = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
+1. $PercentIntention = PercentPerceived(Perceived Capabilities) + Way of Teaching + PercentOpportunities(Perceived Opportunities)$
 
@@
 3. $PercentOwner = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
-<br>
 
@@
 
-# Import GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is
+# Import 2010GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is
 
 SupportiveTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEMAvgIndicators.csv", header = TRUE, cache = FALSE)
+
+# Import GEM 2009 supportive teaching data
+setwd('~/Assign2Education/GEMData')
+
+GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
+GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
+GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
+GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
+GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)
+
+Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
+Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
+Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
+Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
+Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]
+
+names(Clean06) <- gsub("KI06D01_mean", "2006", names(Clean06))
+names(Clean07) <- gsub("ki07d01_", "2007", names(Clean07))
 
@@
 
-To review, the three regression equations used for this assignment are included below.
-
-1. $PercentIntention = PercentPerceived(Perceived Capabilities) + GEM D01 way of teaching + PercentOpportunities(Perceived Opportunities)$
-
-2. $PercentNascent = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
-
-3. $PercentOwner = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
-
 To examine the relationship between these variables, we used least square estimation, the results of which can be found in the following table.

### 2014-11-27 GEMDataSource.Rmd
Imported, cleaned, and began merging new GEM data

@@
 
+GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
+GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
+GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
+GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
+GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
 GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
@@
 GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)
-
-Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
-Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
-Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
-Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
-Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]
-
-names(Clean06) <- gsub("KI06D01_mean", "2006", names(Clean06))
-names(Clean07) <- gsub("ki07d01_", "2007", names(Clean07))
 
@@
 
+### Clean GEM NES Datasets
+# Draw out Country and D01 only
+Clean01 <- GEM2001[,c("country", "ki01d01")]
+Clean02 <- GEM2002[,c("country", "ki02d01")]
+Clean03 <- GEM2003[,c("country", "ki03d01")]
+Clean04 <- GEM2004[,c("ki04ctry", "ki04d01")]
+Clean05 <- GEM2005[,c("KI05ctry", "KI05D01")]
+Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
+Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
+Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
+Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
+Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]
+
+remove(GEM2001, GEM2002, GEM2003, GEM2004, GEM2005, GEM2006, GEM2007, GEM2008, GEM2009, GEM2010)
+
+# Edit column names for each dataframe
+names(Clean01) <- gsub("ki01d01", "2001", names(Clean01))
+names(Clean01) <- gsub("country", "Country", names(Clean01))
+names(Clean02) <- gsub("ki02d01", "2002", names(Clean02))
+names(Clean02) <- gsub("country", "Country", names(Clean02))
+names(Clean03) <- gsub("ki03d01", "2003", names(Clean03))
+names(Clean03) <- gsub("country", "Country", names(Clean03))
+names(Clean04) <- gsub("ki04d01", "2004", names(Clean04))
+names(Clean04) <- gsub("ki04ctry", "Country", names(Clean04))
+names(Clean05) <- gsub("KI05D01", "2005", names(Clean05))
+names(Clean05) <- gsub("KI05ctry", "Country", names(Clean05))
+names(Clean06) <- gsub("KI06D01_mean", "2006", names(Clean06))
+names(Clean06) <- gsub("KI06CTRY", "Country", names(Clean06))
+names(Clean07) <- gsub("ki07d01_", "2007", names(Clean07))
+names(Clean07) <- gsub("ki07ctry", "Country", names(Clean07))
+names(Clean08) <- gsub("NES08_D01_MEAN", "2008", names(Clean08))
+names(Clean08) <- gsub("NES08COUNTRY", "Country", names(Clean08))
+names(Clean09) <- gsub("NES09_D01_MEAN", "2009", names(Clean09))
+names(Clean09) <- gsub("NES09COUNTRY", "Country", names(Clean09))
+names(Clean10) <- gsub("NES10_D01_MEAN", "2009", names(Clean10))
+names(Clean10) <- gsub("NES10CRNAME", "Country", names(Clean10))
+
 #### Merge the data ####
@@
 
+# Merge GEMNES country level data
+Merged1 <- merge(Clean01, Clean02,
+                   union("Country")
+                   all = TRUE)
+
+# Grab the rows we need
+myvars <- c("Australia", "Austria", "Belgium", "Canada", "Chile", "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Japan", "Korea", "Luxemburg", "Mexico", "Netherlands", "New Zealand", "Norway", "Poland", "Portugal", "Slovak Republic", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom", "United States")
+
+NewData <- Data[myvars, 1]
+
 ```
@@
 # Run linear regression R1
-R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
+R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)
 
@@
 # Run linear regression R2
-R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
+R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)
 
@@
 ```
+
+Estonia
+Luxemburg
+Slovak Republic

### 2014-11-27 GEMDataSource.Rmd
New data and cleaning
Latest attempt at cleaning 2001-2010 data

@@
 The following equations were used to determine the relationship between our dependent and explanatory variables:
-
-<br>
 
@@
 names(Clean09) <- gsub("NES09COUNTRY", "Country", names(Clean09))
-names(Clean10) <- gsub("NES10_D01_MEAN", "2009", names(Clean10))
+names(Clean10) <- gsub("NES10_D01_MEAN", "2010", names(Clean10))
 names(Clean10) <- gsub("NES10CRNAME", "Country", names(Clean10))
@@
 # Merge GEMNES country level data
-Merged1 <- merge(Clean01, Clean02,
-                   union("Country")
-                   all = TRUE)
+Merged1 <- merge(Clean01, Clean02, all = TRUE)
+Merged2 <- merge(Clean03, Clean04, all = TRUE)
+Merged3 <- merge(Clean05, Clean06, all = TRUE)
+Merged4 <- merge(Clean07, Clean08, all = TRUE)
+Merged5 <- merge(Clean09, Clean10, all = TRUE)
+Merged6 <- merge(Merged1, Merged2, all = TRUE)
+Merged7 <- merge(Merged3, Merged4, all = TRUE)
+Merged8 <- merge(Merged5, Merged6, all = TRUE)
+Merged9 <- merge(Merged7, Merged8, all = TRUE)
+
+# Recode countries
+Merged9$Country[Merged9$Country == "AUSTRALIA"] <- "Australia"
+Merged9$Country[Merged9$Country == "AUSTRIA"] <- "Austria"
+Merged9$Country[Merged9$Country == "BELGIUM"] <- "Belgium"
+Merged9$Country[Merged9$Country == "CANADA"] <- "Canada"
+Merged9$Country[Merged9$Country == "CHILE"] <- "Chile"
+Merged9$Country[Merged9$Country == "CZECH REPUBLIC"] <- "Czech Republic"
+Merged9$Country[Merged9$Country == "DENMARK"] <- "Denmark"
+Merged9$Country[Merged9$Country == "ESTONIA"] <- "Estonia"
+Merged9$Country[Merged9$Country == "FINLAND"] <- "Finland"
+Merged9$Country[Merged9$Country == "FRANCE"] <- "France"
+Merged9$Country[Merged9$Country == "GERMANY"] <- "Germany"
+Merged9$Country[Merged9$Country == "GREECE"] <- "Greece"
+Merged9$Country[Merged9$Country == "HUNGARY"] <- "Hungary"
+Merged9$Country[Merged9$Country == "ICELAND"] <- "Iceland"
+Merged9$Country[Merged9$Country == "IRELAND"] <- "Ireland"
+Merged9$Country[Merged9$Country == "ISRAEL"] <- "Israel"
+Merged9$Country[Merged9$Country == "ITALY"] <- "Italy"
+Merged9$Country[Merged9$Country == "JAPAN"] <- "Japan"
+Merged9$Country[Merged9$Country == "KOREA"] <- "South Korea"
+Merged9$Country[Merged9$Country == "LUXEMBURG"] <- "Luxemburg"
+Merged9$Country[Merged9$Country == "MEXICO"] <- "Mexico"
+Merged9$Country[Merged9$Country == "NETHERLANDS"] <- "Netherlands"
+Merged9$Country[Merged9$Country == "NEW ZEALAND"] <- "New Zealand"
+Merged9$Country[Merged9$Country == "NORWAY"] <- "Norway"
+Merged9$Country[Merged9$Country == "POLAND"] <- "Poland"
+Merged9$Country[Merged9$Country == "PORTUGAL"] <- "Portugal"
+Merged9$Country[Merged9$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
+Merged9$Country[Merged9$Country == "SLOVENIA"] <- "SLOVENIA"
+Merged9$Country[Merged9$Country == "SPAIN"] <- "Spain"
+Merged9$Country[Merged9$Country == "SWEDEN"] <- "Sweden"
+Merged9$Country[Merged9$Country == "SWITZERLAND"] <- "Switzerland"
+Merged9$Country[Merged9$Country == "TURKEY"] <- "Turkey"
+Merged9$Country[Merged9$Country == "UNITED KINGDOM"] <- "United Kingdom"
+Merged9$Country[Merged9$Country == "UK"] <- "United Kingdom"
+Merged9$Country[Merged9$Country == "USA"] <- "United States"
+Merged9$Country[Merged9$Country == "UNITED STATES"] <- "United States"
+
+LongGEM<- melt(data = Merged9,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Rename columns
+names(LongGEM) <- gsub("variable", "Year", names(LongGEM))
+names(LongGEM) <- gsub("value", "Support", names(LongGEM))
+
+################### Difficult Section #####################
 
@@
 
-NewData <- Data[myvars, 1]
+MYVARS1 <- c("AUSTRALIA", "AUSTRIA", "BELGIUM", "CANADA", "CHILE", "CZECH REPUBLIC", "DENMARK", "ESTONIA", "FINLAND", "FRANCE", "GERMANY", "GREECE", "HUNGARY", "ICELAND", "IRELAND", "ISRAEL", "ITALY", "JAPAN", "KOREA", "LUXEMBURG", "MEXICO", "NETHERLANDS", "NEW ZEALAND", "NORWAY", "POLAND", "PORTUGAL", "SLOVAK REPUBLIC", "SLOVENIA", "SPAIN", "SWEDEN", "SWITZERLAND", "TURKEY", "UNITED KINGDOM", "UNITED STATES")
+
+Long2[,"Support"] <- as.numeric(Long2[,"Support"])
+Long2[,"Year"] <- as.numeric(Long2[,"Year"])
+Long2[,"Country"] <- as.factor(Long2[,"Country"])
+
+Long2
+
+Long2[c("Australia", "Austria", "Belgium", "Canada", "Chile", "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Japan", "Korea", "Luxemburg", "Mexico", "Netherlands", "New Zealand", "Norway", "Poland", "Portugal", "Slovak Republic", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom", "United States"), ]
+
+# Grab only countries we need
+NewData <- Long2[rownames = myvars, 
+                 colnames = mystats]
+
+mystats <- c("Country", "Year", "Support")
+
+NewData1 <- data.frame(NewData)
 

### 2014-11-27 GEMDataSource.Rmd
Minor edit to GEM 2001-10 section

@@
 
-MYVARS1 <- c("AUSTRALIA", "AUSTRIA", "BELGIUM", "CANADA", "CHILE", "CZECH REPUBLIC", "DENMARK", "ESTONIA", "FINLAND", "FRANCE", "GERMANY", "GREECE", "HUNGARY", "ICELAND", "IRELAND", "ISRAEL", "ITALY", "JAPAN", "KOREA", "LUXEMBURG", "MEXICO", "NETHERLANDS", "NEW ZEALAND", "NORWAY", "POLAND", "PORTUGAL", "SLOVAK REPUBLIC", "SLOVENIA", "SPAIN", "SWEDEN", "SWITZERLAND", "TURKEY", "UNITED KINGDOM", "UNITED STATES")
-
 Long2[,"Support"] <- as.numeric(Long2[,"Support"])

### 2014-11-28 GEMDataSource.Rmd
Created subset of new GEM data

@@
 Merged9$Country[Merged9$Country == "UNITED STATES"] <- "United States"
+Merged9$Country[Merged9$Country == "Korea"] <- "South Korea"
 
+# Change merged data from wide to long
 LongGEM<- melt(data = Merged9,
@@
 
-################### Difficult Section #####################
+# Create a vector with OECD countries
+myvars <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')
 
-# Grab the rows we need
-myvars <- c("Australia", "Austria", "Belgium", "Canada", "Chile", "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Japan", "Korea", "Luxemburg", "Mexico", "Netherlands", "New Zealand", "Norway", "Poland", "Portugal", "Slovak Republic", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom", "United States")
+# Subset LongGEM with the countries we need
+subset_data <- subset(LongGEM, Country %in% myvars)
 
-Long2[,"Support"] <- as.numeric(Long2[,"Support"])
-Long2[,"Year"] <- as.numeric(Long2[,"Year"])
-Long2[,"Country"] <- as.factor(Long2[,"Country"])
+# Delete unnecessary column
+subset_data$row.name <- NULL
 
-Long2
+# Arrange subset_data by country and year
+GrandData <- arrange(subset_data, Country, Year)
 
-Long2[c("Australia", "Austria", "Belgium", "Canada", "Chile", "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Japan", "Korea", "Luxemburg", "Mexico", "Netherlands", "New Zealand", "Norway", "Poland", "Portugal", "Slovak Republic", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom", "United States"), ]
+########### STUCK #############
 
-# Grab only countries we need
-NewData <- Long2[rownames = myvars, 
-                 colnames = mystats]
-
-mystats <- c("Country", "Year", "Support")
-
-NewData1 <- data.frame(NewData)
+FinalData <- merge(CompleteDataset, subset_data,
+                   union("Country", "Year"),
+                   all = TRUE)
 

### 2014-11-29 GEMDataSource.Rmd
Merged GEMAnnual data

@@
 
-# Library required packages repmis, ridy, reshape2, plyr and WDI packages
+# Library required packages repmis, ridy, reshape2, and plyr packages
 library(plyr)
@@
 library(reshape2)
-library(WDI)
 library(foreign)
@@
 # Load citation package
-pkgs <- c('plyr','repmis', 'tidyr', 'reshape2', 'WDI', 'stargazer', 'Zelig')
+pkgs <- c('plyr','repmis', 'tidyr', 'reshape2', 'stargazer', 'Zelig')
 repmis::LoadandCite(pkgs, file= 'DataRpackageCitations.bib')
@@
 # Import 2010GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is
-
 SupportiveTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEMAvgIndicators.csv", header = TRUE, cache = FALSE)
@@
 
-### Clean SupportiveTeaching
-
-### Create new data frame without unnecessary data
-WayOfTeaching <- SupportiveTeaching[, c("NES10CRNAME", "NES10_D01_MEAN")]
-
-## as.factor("WayOfTeaching")
-
-##TWayofTeaching <- SupportiveTeaching[c("Australia", "Austria", "Belgium", "Canada", "Chile", "Czech Republic", "Denmark", "Estonia", "Finland", "France", "Germany", "Greece", "Hungary", "Iceland", "Ireland", "Israel", "Italy", "Japan", "Korea", "Luxemburg", "Mexico", "Netherlands", "New Zealand", "Norway", "Poland", "Portugal", "Slovak Republic", "Slovenia", "Spain", "Sweden", "Switzerland", "Turkey", "United Kingdom", "United States"),])
-
 ### Clean GEM NES Datasets
@@
 # Edit column names for each dataframe
-names(Clean01) <- gsub("ki01d01", "2001", names(Clean01))
-names(Clean01) <- gsub("country", "Country", names(Clean01))
-names(Clean02) <- gsub("ki02d01", "2002", names(Clean02))
-names(Clean02) <- gsub("country", "Country", names(Clean02))
-names(Clean03) <- gsub("ki03d01", "2003", names(Clean03))
-names(Clean03) <- gsub("country", "Country", names(Clean03))
-names(Clean04) <- gsub("ki04d01", "2004", names(Clean04))
-names(Clean04) <- gsub("ki04ctry", "Country", names(Clean04))
-names(Clean05) <- gsub("KI05D01", "2005", names(Clean05))
-names(Clean05) <- gsub("KI05ctry", "Country", names(Clean05))
-names(Clean06) <- gsub("KI06D01_mean", "2006", names(Clean06))
-names(Clean06) <- gsub("KI06CTRY", "Country", names(Clean06))
-names(Clean07) <- gsub("ki07d01_", "2007", names(Clean07))
-names(Clean07) <- gsub("ki07ctry", "Country", names(Clean07))
-names(Clean08) <- gsub("NES08_D01_MEAN", "2008", names(Clean08))
-names(Clean08) <- gsub("NES08COUNTRY", "Country", names(Clean08))
-names(Clean09) <- gsub("NES09_D01_MEAN", "2009", names(Clean09))
-names(Clean09) <- gsub("NES09COUNTRY", "Country", names(Clean09))
-names(Clean10) <- gsub("NES10_D01_MEAN", "2010", names(Clean10))
-names(Clean10) <- gsub("NES10CRNAME", "Country", names(Clean10))
+
+Clean01 <- plyr::rename(x = Clean01, 
+                                      replace = c("ki01d01" = "Year01",
+                                                  "country" = "Country"))
+
+Clean02 <- plyr::rename(x = Clean02, 
+                                      replace = c("ki02d01" = "Year02",
+                                                  "country" = "Country"))
+
+Clean03 <- plyr::rename(x = Clean03, 
+                                      replace = c("ki03d01" = "Year03",
+                                                  "country" = "Country"))
+
+Clean04 <- plyr::rename(x = Clean04, 
+                                      replace = c("ki04d01" = "Year04",
+                                                  "ki04ctry" = "Country"))
+
+Clean05 <- plyr::rename(x = Clean05, 
+                                      replace = c("KI05D01" = "Year05",
+                                                  "KI05ctry" = "Country"))
+
+Clean06 <- plyr::rename(x = Clean06, 
+                                      replace = c("KI06D01_mean" = "Year06",
+                                                  "KI06CTRY" = "Country"))
+Clean07 <- plyr::rename(x = Clean07, 
+                                      replace = c("ki07d01_" = "Year07",
+                                                  "ki07ctry" = "Country"))
+
+Clean08 <- plyr::rename(x = Clean08, 
+                                      replace = c("NES08_D01_MEAN" = "Year08",
+                                                  "NES08COUNTRY" = "Country"))
+
+Clean09 <- plyr::rename(x = Clean09, 
+                                      replace = c("NES09_D01_MEAN" = "Year09",
+                                                  "NES09COUNTRY" = "Country"))
+
+Clean10 <- plyr::rename(x = Clean10, 
+                                      replace = c("NES10_D01_MEAN" = "Year10",
+                                                  "NES10CRNAME" = "Country"))
 
@@
 
-#### Import WDI Annual GDP Growth Data ####
-GDPGrowth = WDI(indicator='NY.GDP.MKTP.KD.ZG', country=c('MX','CA','US','FR','AU','AT','BE',
-                                                         'CL','CZ','DK','EE','FI','DE','HU', 
-                                                         'IS','IE','IL','IT','JP','KR','LU',
-                                                         'NL','NZ','NO','PL','PT','SK','SI',
-                                                         'ES','SE','CH','TR','GB','US','GR'), 
-                start=2001, end=2013)
-# Rename columns
-GDPGrowth <- plyr::rename(x = GDPGrowth, 
-                                      replace = c("year" = "Year",
-                                                  "NY.GDP.MKTP.KD.ZG" = "AnnualGDPGrowth",
-                                                  "country" = "Country"))
-
-# Recode country == "United States" to "United States of America" and Korea, Rep. to Korea (South)
-GDPGrowth$Country[GDPGrowth$Country == "United States"] <- "United States of America"
-
-# Recode country == "Korea, Rep."" to "Korea (South)"
-GDPGrowth$Country[GDPGrowth$Country == "Korea, Rep."] <- "Korea (South)"
-
-# Remove iso2c data to ease merge with FinalMerge data
-GDPGrowth$iso2c <- NULL
-
-# Merge GDPGrowth and FinalGEM
-CompleteDataset <- merge(FinalGEM, GDPGrowth,
-                   union("Country", "Year"),
-                   all = TRUE)
-
 # Remove unncessary data from environment
@@
 
-# Merge GEMNES country level data
-Merged1 <- merge(Clean01, Clean02, all = TRUE)
-Merged2 <- merge(Clean03, Clean04, all = TRUE)
-Merged3 <- merge(Clean05, Clean06, all = TRUE)
-Merged4 <- merge(Clean07, Clean08, all = TRUE)
-Merged5 <- merge(Clean09, Clean10, all = TRUE)
-Merged6 <- merge(Merged1, Merged2, all = TRUE)
-Merged7 <- merge(Merged3, Merged4, all = TRUE)
-Merged8 <- merge(Merged5, Merged6, all = TRUE)
-Merged9 <- merge(Merged7, Merged8, all = TRUE)
+CleanMerge <- cbind(names = c(rownames(Clean01), rownames(Clean02), rownames(Clean03),
+                              rownames(Clean04), rownames(Clean05), rownames(Clean06),
+                              rownames(Clean07), rownames(Clean08), rownames(Clean09),
+                              rownames(Clean10)),
+                    rbind.fill(list(Clean01, Clean02, Clean03, Clean04, Clean05, Clean06,
+                                    Clean07, Clean08, Clean09, Clean10)))
 
 # Recode countries
-Merged9$Country[Merged9$Country == "AUSTRALIA"] <- "Australia"
-Merged9$Country[Merged9$Country == "AUSTRIA"] <- "Austria"
-Merged9$Country[Merged9$Country == "BELGIUM"] <- "Belgium"
-Merged9$Country[Merged9$Country == "CANADA"] <- "Canada"
-Merged9$Country[Merged9$Country == "CHILE"] <- "Chile"
-Merged9$Country[Merged9$Country == "CZECH REPUBLIC"] <- "Czech Republic"
-Merged9$Country[Merged9$Country == "DENMARK"] <- "Denmark"
-Merged9$Country[Merged9$Country == "ESTONIA"] <- "Estonia"
-Merged9$Country[Merged9$Country == "FINLAND"] <- "Finland"
-Merged9$Country[Merged9$Country == "FRANCE"] <- "France"
-Merged9$Country[Merged9$Country == "GERMANY"] <- "Germany"
-Merged9$Country[Merged9$Country == "GREECE"] <- "Greece"
-Merged9$Country[Merged9$Country == "HUNGARY"] <- "Hungary"
-Merged9$Country[Merged9$Country == "ICELAND"] <- "Iceland"
-Merged9$Country[Merged9$Country == "IRELAND"] <- "Ireland"
-Merged9$Country[Merged9$Country == "ISRAEL"] <- "Israel"
-Merged9$Country[Merged9$Country == "ITALY"] <- "Italy"
-Merged9$Country[Merged9$Country == "JAPAN"] <- "Japan"
-Merged9$Country[Merged9$Country == "KOREA"] <- "South Korea"
-Merged9$Country[Merged9$Country == "LUXEMBURG"] <- "Luxemburg"
-Merged9$Country[Merged9$Country == "MEXICO"] <- "Mexico"
-Merged9$Country[Merged9$Country == "NETHERLANDS"] <- "Netherlands"
-Merged9$Country[Merged9$Country == "NEW ZEALAND"] <- "New Zealand"
-Merged9$Country[Merged9$Country == "NORWAY"] <- "Norway"
-Merged9$Country[Merged9$Country == "POLAND"] <- "Poland"
-Merged9$Country[Merged9$Country == "PORTUGAL"] <- "Portugal"
-Merged9$Country[Merged9$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
-Merged9$Country[Merged9$Country == "SLOVENIA"] <- "SLOVENIA"
-Merged9$Country[Merged9$Country == "SPAIN"] <- "Spain"
-Merged9$Country[Merged9$Country == "SWEDEN"] <- "Sweden"
-Merged9$Country[Merged9$Country == "SWITZERLAND"] <- "Switzerland"
-Merged9$Country[Merged9$Country == "TURKEY"] <- "Turkey"
-Merged9$Country[Merged9$Country == "UNITED KINGDOM"] <- "United Kingdom"
-Merged9$Country[Merged9$Country == "UK"] <- "United Kingdom"
-Merged9$Country[Merged9$Country == "USA"] <- "United States"
-Merged9$Country[Merged9$Country == "UNITED STATES"] <- "United States"
-Merged9$Country[Merged9$Country == "Korea"] <- "South Korea"
+CleanMerge$Country[CleanMerge$Country == "AUSTRALIA"] <- "Australia"
+CleanMerge$Country[CleanMerge$Country == "AUSTRIA"] <- "Austria"
+CleanMerge$Country[CleanMerge$Country == "BELGIUM"] <- "Belgium"
+CleanMerge$Country[CleanMerge$Country == "CANADA"] <- "Canada"
+CleanMerge$Country[CleanMerge$Country == "CHILE"] <- "Chile"
+CleanMerge$Country[CleanMerge$Country == "CZECH REPUBLIC"] <- "Czech Republic"
+CleanMerge$Country[CleanMerge$Country == "DENMARK"] <- "Denmark"
+CleanMerge$Country[CleanMerge$Country == "ESTONIA"] <- "Estonia"
+CleanMerge$Country[CleanMerge$Country == "FINLAND"] <- "Finland"
+CleanMerge$Country[CleanMerge$Country == "FRANCE"] <- "France"
+CleanMerge$Country[CleanMerge$Country == "GERMANY"] <- "Germany"
+CleanMerge$Country[CleanMerge$Country == "GREECE"] <- "Greece"
+CleanMerge$Country[CleanMerge$Country == "HUNGARY"] <- "Hungary"
+CleanMerge$Country[CleanMerge$Country == "ICELAND"] <- "Iceland"
+CleanMerge$Country[CleanMerge$Country == "IRELAND"] <- "Ireland"
+CleanMerge$Country[CleanMerge$Country == "ISRAEL"] <- "Israel"
+CleanMerge$Country[CleanMerge$Country == "ITALY"] <- "Italy"
+CleanMerge$Country[CleanMerge$Country == "JAPAN"] <- "Japan"
+CleanMerge$Country[CleanMerge$Country == "KOREA"] <- "South Korea"
+CleanMerge$Country[CleanMerge$Country == "LUXEMBURG"] <- "Luxemburg"
+CleanMerge$Country[CleanMerge$Country == "MEXICO"] <- "Mexico"
+CleanMerge$Country[CleanMerge$Country == "NETHERLANDS"] <- "Netherlands"
+CleanMerge$Country[CleanMerge$Country == "NEW ZEALAND"] <- "New Zealand"
+CleanMerge$Country[CleanMerge$Country == "NORWAY"] <- "Norway"
+CleanMerge$Country[CleanMerge$Country == "POLAND"] <- "Poland"
+CleanMerge$Country[CleanMerge$Country == "PORTUGAL"] <- "Portugal"
+CleanMerge$Country[CleanMerge$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
+CleanMerge$Country[CleanMerge$Country == "SLOVENIA"] <- "SLOVENIA"
+CleanMerge$Country[CleanMerge$Country == "SPAIN"] <- "Spain"
+CleanMerge$Country[CleanMerge$Country == "SWEDEN"] <- "Sweden"
+CleanMerge$Country[CleanMerge$Country == "SWITZERLAND"] <- "Switzerland"
+CleanMerge$Country[CleanMerge$Country == "TURKEY"] <- "Turkey"
+CleanMerge$Country[CleanMerge$Country == "UNITED KINGDOM"] <- "United Kingdom"
+CleanMerge$Country[CleanMerge$Country == "UK"] <- "United Kingdom"
+CleanMerge$Country[CleanMerge$Country == "USA"] <- "United States"
+CleanMerge$Country[CleanMerge$Country == "UNITED STATES"] <- "United States"
+CleanMerge$Country[CleanMerge$Country == "Korea"] <- "South Korea"
+CleanMerge$Country[CleanMerge$Country == "US"] <- "United States"
+
+# Set columns to numeric
+CleanMerge[,"Year01"] <- as.numeric(CleanMerge[,"Year01"])
+CleanMerge[,"Year02"] <- as.numeric(CleanMerge[,"Year02"])
+CleanMerge[,"Year03"] <- as.numeric(CleanMerge[,"Year03"])
+CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year04"])
+CleanMerge[,"Year05"] <- as.numeric(CleanMerge[,"Year05"])
+CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year06"])
+CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year07"])
+CleanMerge[,"Year08"] <- as.numeric(CleanMerge[,"Year08"])
+CleanMerge[,"Year09"] <- as.numeric(CleanMerge[,"Year09"])
+CleanMerge[,"Year10"] <- as.numeric(CleanMerge[,"Year10"])
+
+ddply(pp, .(names), function(x) colSums(x[,-1], na.rm = TRUE))
+
+ddply(CleanMerge, .(names), function(x) colSums(x[,-1], na.rm = TRUE))
+
+arrange()
 
@@
 # Delete unnecessary column
-subset_data$row.name <- NULL
+subset_data$row.names <- NULL
 
@@
 
+GrandData1 <- GrandData[order("Country",)]
+
 ########### STUCK #############
 
-FinalData <- merge(CompleteDataset, subset_data,
-                   union("Country", "Year"),
-                   all = TRUE)
+FinalData <- merge(FinalGEM, GrandData,
+                   union("Country", "Year"))
 

### 2014-11-29 Misc/TrialFile.Rmd
Merged GEMAnnual data

--- 2014-10-21 TrialFile.Rmd
@@
 
+<p align="center">
+[<img align="center" src="img/OECDChart.png" alt="Factors Affecting Entrepreneurship" height=350 width=450 />](img/OECDChart.png)</br>
+</p>
+<p align="center">
+Source: OECD Local Entrepreneurship Reviews [@OECD2009]
+</p>
+
 ![Untitled.png](~/DataAnalysis)
+
+``` {r}
+
+#### Import WDI Annual GDP Growth Data ####
+GDPGrowth = WDI(indicator='NY.GDP.MKTP.KD.ZG', country=c('MX','CA','US','FR','AU','AT','BE',
+                                                         'CL','CZ','DK','EE','FI','DE','HU', 
+                                                         'IS','IE','IL','IT','JP','KR','LU',
+                                                         'NL','NZ','NO','PL','PT','SK','SI',
+                                                         'ES','SE','CH','TR','GB','US','GR'), 
+                start=2001, end=2013)
+# Rename columns
+GDPGrowth <- plyr::rename(x = GDPGrowth, 
+                                      replace = c("year" = "Year",
+                                                  "NY.GDP.MKTP.KD.ZG" = "AnnualGDPGrowth",
+                                                  "country" = "Country"))
+
+# Recode country == "United States" to "United States of America" and Korea, Rep. to Korea (South)
+GDPGrowth$Country[GDPGrowth$Country == "United States"] <- "United States of America"
+
+# Recode country == "Korea, Rep."" to "Korea (South)"
+GDPGrowth$Country[GDPGrowth$Country == "Korea, Rep."] <- "Korea (South)"
+
+# Remove iso2c data to ease merge with FinalMerge data
+GDPGrowth$iso2c <- NULL
+
+# Merge GDPGrowth and FinalGEM
+CompleteDataset <- merge(FinalGEM, GDPGrowth,
+                   union("Country", "Year"),
+                   all = TRUE)

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
New Rmd

---
title: "From Education To Entrepreneurship"
author: "Thierry Racaud"
date: "29 novembre 2014"
output: html_document
---

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
Clean Rmd
Cleaning

@@
 title: "From Education To Entrepreneurship"
-author: "Thierry Racaud"
+author: "Sam Dundon and Thierry Racaud"
 date: "29 novembre 2014"
@@
 
-```{r}
-summary(cars)
+* * * 
+```{r echo=FALSE, cache=TRUE, include=FALSE}
+
+# Set working directory
+setwd('~/Assign2Education/Proposal')
+
+# Install necessary packages
+
+# Install rempis from Christpher Gandrud's website
+devtools::install_github('christophergandrud/repmis')
+library(repmis)
+
+# Load citation package
+pkgs <- c('repmis')
+repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')
+
 ```
-
-You can also embed plots, for example:
-
-```{r, echo=FALSE}
-plot(cars)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
Research Interest, Question and Literature Review

@@
 ```
+
+*Introduction to Collaborative Social Science Data Analysis*
+
+### Research Interest
+
+The process of allocating public funds for education is an opportunity to make calculated long-term investments in a nation's populace.
+The rationale for decisions made during this process, however, is often difficult to understand.
+For example, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors -- not just structural and economic factors -- in determining individual and societal tendencies to start a business, these factors are often not included in the decisionmaking process.
+As a matter of fact, only a few empirical studies have actually been carried out on this topic and most of them focused on which attitudes were favorable to starting a business, while almost none explored how cultural patterns affected these dispositions.
+
+When cultural factors are examined, they are considered as a given feature that can hardly be traced.
+By having a closer look at education systems, however, we intend to explore the processes through which some of these cultural patterns are enhanced and passed from one generation to the next.
+Aside from parental education, schools are indeed the very place where children are taught how to fit into society.
+This research is an attempt to analyze  one trait in particular, self-confidence.
+
+### Research Question
+
+Drawing a comparison between France and Britain, to what extent do the behavioral characteristics of the education system - individualistic, group-oriented, and more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
+
+### Literature Review
+
+What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
+However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] .
+Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done, as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
+
+Over a hundred years has passed since Max Weber tried to explain how religious-ethical motivations affect entrepreneurship [@weberprotestant], and religion may be less effective in justifying why some are more likely to start businesses than others.
+Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” [@OECD2009].
+
+Despite various claims of the existence of a cultural effect, few empirical studies have actually been carried out.
+It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), and then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors -- mainly economic, and cultural factors.
+As they compared two Swedish regions similar in terms of structure and observed different outcomes, they concluded there may be a small cultural effect in attitudes toward start-up activities.
+
+This thesis is an attempt at finding out whether different patterns in education lead to different outcomes in terms of start-up activities.
+Indeed, like many in the education literature tend to assert, we believe school personnel have an affect on student self-esteem [@Scott1996].
+We will further explore how this mechanism works.
+As for entrepreneurship literature, it generally acknowledges the influence of self-confidence on start-up activities, although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” [@OECD2009].
+We intend to show that these individual characteristics are partly shaped at an institutional and collective level through the education systems and staff attitudes.
+
+Of course, King and Sobel [@Kerry2008], among others, have already tried to show how school choice can increase the rate of youth entrepreneurship, but their perspective was slightly different.
+They  asserted that a more business-like environment in K-12 education was the key, which was favored by voucher programs.
+We believe there is a more widely spread systematic effect of cultural and educational patterns.
+David Watkins [@Watkins2010] cross-cultural perspective on teaching and learning shall be useful in that respect.
+Kai-Ming Cheng and Kam-Cheung Wong’s study about school effectiveness in East Asia [@Cheng2006] could also be of help.
+
+Also, as self-confidence is considered to rely partly on one’s integration within social networks [@OECD2009], we will refer to cross-cultural studies such as that of Green, Deschamps and Páez [@green2005variation] about individualism and collectivism, what Freeman [@freeman1997demographic] called idiocentrism and allocentrism.
+Raeff, Greenfield and Quiroz [-@raeff2000conceptualizing] have also conceptualized interpersonal relationships in both contexts.
+More school-focused, Yamauchi [@yamauchi1998individualism] as well as Davies and Aurini [@davies2003homeschooling] have looked at individualism and collectivism in the classroom and in pedagogy respectively.
+All these will be important on the way.
+
+Besides direct or indirect school effects, we will necessarily look into entrepreneurship and its determinants at large.
+Thus we will quote Grilo and Thurik’s research [@Grilo2005b] about what determines entrepreneurship engagement levels throughout the European Union, and also Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries [@Wennekers2002].
+Eventually, with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
Estimation Strategy, Causal Chain, Variables

@@
 
-### Research Question
+#### Research Question
 
-Drawing a comparison between France and Britain, to what extent do the behavioral characteristics of the education system - individualistic, group-oriented, and more or less positive reinforcement in teaching - affect the rate of entrepreneurship in each country?
+To what extent do the behavioral characteristics of education systems - individualistic, group-oriented, self-esteem reinforcing - affect the rate of entrepreneurship in OECD countries?
 
@@
 Eventually, with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.
+
+#### Estimation Strategy
+
+##### Causal Chain
+
+Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
+<br>
+
+##### Dependent Variables: Explaining the Country-level Rate of Entrepreneurship
+
+We have examined three dimensions of entrepreneurship to prepare for this stage of the project, established entrepreneurship in the country, nascent entrepreneurship (less than three months), and entrepreneurial intention.
+We will study each of these successively as we may well observe different effects.
+
+To measure these three dimensions of entrepreneurship, we have used three [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) indicators:
+
+- Established Business Ownership Rate (Percentage) 
+- Nascent Entrepreneurship Rate (Percentage)
+- Entrepreneurial intention Rate (Percentage)
+
+##### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System
+
+As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem.
+To do so, we decided to incorporate GEM indicators that relate to self-esteem and confidence.
+First, we included GEM survey data on the average "perceived capabilities" of an individual (18-64) in a given country to start a business.
+Second, we included additional GEM data on how the "fear of failure" could deter an average individual (18-64) in a country to become an entrepreneur.
+Both of these data sets indicate the average percentage for each characteristic at the country-level.
+
+##### Control Variables: Controlling for Classic Determinants of Entrepreneurship
+
+To control for the general state of the economy, we included annual GDP Growth from the World Bank [World Development Indicators](http://data.worldbank.org/data-catalog/world-development-indicators) as a control variable in our regression equations.
+In addition, we included a GEM indicator called "Perceived Opportunities." For each country, it is the average percentage of individuals who believe there are opportunities to start a business in their area.
+Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.
+
+In the future, we may revise this to include lagged GDP growth in recognition of the time taken for governments and individuals to react to the state of the economy, and are planning to include control variables from GEM.
+Specifically, we intend to control for the classic determinants of entrepreneurship -- economic and structural determinants.
+To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://www.gemconsortium.org/Data-Collection).
+
+1. Finance  
+2. Government policies  
+3. Government programs  
+4. Entrepreneurial Education and Training  
+5. Research and Development Transfer (R & D)  
+6. Commercial and professional infrastructure  
+7. Internal Market openness  
+8. Physical infrastructure and services  
+9. Cultural and social norms
+
+##### Regressions
+
+The following equations were used to determine the relationship between our dependent and explanatory variables:
+
+1. $PercentIntention = PercentPerceived(Perceived Capabilities) + Way of Teaching + PercentOpportunities(Perceived Opportunities)$
+
+2. $PercentNascent = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
+
+3. $PercentOwner = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
+
+The variables *Percent Fear* and *Percent Opportunities* were included as an interaction term $PercentFear*PercentOpportunities$ because of the design of the survey.
+PercentFear is: "the Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business."
+
+<br>
+
+#### Data Collection and Cleaning
+
+To collect the data necessary to run these regression equations, we downloaded *.csv* data from GEM and used the WDI API to obtain the necessary annual GDP growth of OECD Countries.
+
+**Necessary R Packages**
+
+The following packages were needed to complete the data collection portion of this assignment:
+
+- repmis  
+- tidyr  
+- reshape  
+- plyr  
+- WDI
+
+**GEM Data**
+
+GEM data was embedded in an interactive database and was difficult to extract automatically without writing a program.
+To simplify this process, we downloaded the necessary *.csv* files and saved them in our GitHub repository (to reduce complexity, we deleted the first three unnecessary rows before saving).
+We then linked to the RAW version of the files and added the code required to load them from *R*.
+The repmis package is required to load these documents from the repository.
+
+Cleaning the GEM data required deleting unnecessary characters in the year columns, changing the years from columns to rows (changing the data from wide to long), and changing the column names to describe which data was being analyzed.
+In the process of doing this we created new data sets for each of these survey questions, which were called C*dataset* (clean followed by the data set name).
+This was done for each of the six GEM data sets before merging these sets two at a time to create the data set *FinalGEM*.
+
+For all 33 OECD countries we should have 13 observations, one per year from 2001 to 2013, for each variable.
+However, there are a few missing values, especially regarding the perceived opportunities for some countries, namely Estonia, Luxembourg and Slovak Republic.
+
+**World Bank Data**
+
+As mentioned above, one of our control variables, annual GDP growth, was obtained using the WDI API from the World Bank.
+Using this API, we accessed GDP data from all the OECD countries directly from *R*.
+To clean this data, we used *plyr* to change the variable names then recoded the U.S.
+and South Korea country names to maintain consistency with the GEM data set and dropped an unnecessary column that was not included with the GEM data.
+
+Finally, we merged the annual GDP growth data with the *FinalGEM* data set to create *CompleteDataset*.
+This is the data set used to run the regressions and generate the charts and figures outlined in this document.
+To reduce complexity in the environment we also included a command to remove unnecessary objects in the environment.
+
+<br>
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
+
+#### Import data from GEM Survey ####
+
+# Import GEM fear of failure data
+FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE)
+
+# Import GEM estblished entrepreneurship - current owner data
+CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = FALSE)
+
+# Import GEM entrepreneurial intention data
+EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = FALSE)
+
+# Import GEM nascent entrepreneur data
+NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = FALSE)
+
+# Import GEM perceived capabilities data
+PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE)
+
+# Import GEM perceived opportunities data as a proxy for potential control variables
+PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE)
+
+# Import 2010GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is
+SupportiveTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEMAvgIndicators.csv", header = TRUE, cache = FALSE)
+
+# Import GEM 2009 supportive teaching data
+setwd('~/Assign2Education/GEMData')
+
+GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
+GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
+GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
+GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
+GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
+GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
+GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
+GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
+GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
+GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)
+
+#### Clean data using tidy ####
+
+### Clean FearFail ###
+# Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
+
+# Remove X's in FearFail year columns
+names(FearFail) <- gsub("X", "", names(FearFail))
+
+# Change years from columns to rows and create CFearFail
+CFearFail <- melt(data = FearFail,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010", "2011", "2012",
+                                   "2013"))
+
+# Rename columns
+CFearFail <- plyr::rename(x = CFearFail, 
+                                      replace = c("variable" = "Year",
+                                                  "value" = "PercentFear"))
+
+### Clean CurrentOwner ###
+# Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid sallaries, wages, or any other payments to the owners for more than 42 months
+
+# Remove X's in CurrentOwner year columns
+names(CurrentOwner) <- gsub("X", "", names(CurrentOwner))
+
+# Change years from columns to rows and create CCurrentOwner
+CCurrentOwner <- melt(data = CurrentOwner,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010", "2011", "2012",
+                                   "2013"))
+
+# Rename columns
+CCurrentOwner <- plyr::rename(x = CCurrentOwner, 
+                                      replace = c("variable" = "Year",
+                                                  "value" = "PercentOwner"))
+
+### Clean EntreIntention ###
+# Percentage of 18-64 population (individuals involved in any stage of entrepenerurial activity excluded) who intend to start a business within three years.
+
+# Remove X's in EntreIntention year columns
+names(EntreIntention) <- gsub("X", "", names(EntreIntention))
+
+# Change years from columns to rows and create CEntreIntention (No 2001 data available)
+CEntreIntention <- melt(data = EntreIntention,
+                  id.vars = c("Country"),
+                  measure.vars = c("2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010", "2011", "2012",
+                                   "2013"))
+
+# Rename columns
+CEntreIntention <- plyr::rename(x = CEntreIntention, 
+                                      replace = c("variable" = "Year",
+                                                  "value" = "PercentIntention"))
+
+### Clean NascentEntre ###
+# Percentage of 18-64 population who are currently a nascent entrepreneur, i.e., actively involved in setting up a business they will own or co-own; this business has not paid salaries, wages, or any other payments to the owners for more than three months.
+
+# Remove X's in NascentEntre year columns
+names(NascentEntre) <- gsub("X", "", names(NascentEntre))
+
+# Change years from columns to rows and create CNascentEntre
+CNascentEntre <- melt(data = NascentEntre,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010", "2011", "2012",
+                                   "2013"))
+
+# Rename columns
+CNascentEntre <- plyr::rename(x = CNascentEntre, 
+                                      replace = c("variable" = "Year",
+                                                  "value" = "PercentNascent"))
+
+### Clean PerceivedCapabilities ###
+# Percentage of 18-64 population who believe to have the required skills and knowledge to start a business
+
+# Remove X's in PerceivedCapabilities year columns
+names(PerceivedCapabilities) <- gsub("X", "", names(PerceivedCapabilities))
+
+# Change years from columns to rows and create CPreceivedCapabilities
+CPerceivedCapabilities<- melt(data = PerceivedCapabilities,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010", "2011", "2012",
+                                   "2013"))
+
+# Rename columns
+CPerceivedCapabilities <- plyr::rename(x = CPerceivedCapabilities, 
+                                      replace = c("variable" = "Year",
+                                                  "value" = "PercentPerceived"))
+
+### Clean PerceivedOpportunities ###
+# Percentage of 18-64 population who see good opportunities to start a firm in the area where they live
+
+# Remove X's in PerceivedOpportunities year columns
+names(PerceivedOpportunities) <- gsub("X", "", names(PerceivedOpportunities))
+
+# Change years from columns to rows and create CPreceivedOpportunities
+CPerceivedOpportunities<- melt(data = PerceivedOpportunities,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010", "2011", "2012",
+                                   "2013"))
+
+# Rename columns
+CPerceivedOpportunities <- plyr::rename(x = CPerceivedOpportunities, 
+                                      replace = c("variable" = "Year",
+                                                  "value" = "PercentOpportunities"))
+
+### Clean GEM NES Datasets
+# Draw out Country and D01 only
+Clean01 <- GEM2001[,c("country", "ki01d01")]
+Clean02 <- GEM2002[,c("country", "ki02d01")]
+Clean03 <- GEM2003[,c("country", "ki03d01")]
+Clean04 <- GEM2004[,c("ki04ctry", "ki04d01")]
+Clean05 <- GEM2005[,c("KI05ctry", "KI05D01")]
+Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
+Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
+Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
+Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
+Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]
+
+remove(GEM2001, GEM2002, GEM2003, GEM2004, GEM2005, GEM2006, GEM2007, GEM2008, GEM2009, GEM2010)
+
+# Edit column names for each dataframe
+
+Clean01 <- plyr::rename(x = Clean01, 
+                                      replace = c("ki01d01" = "Year01",
+                                                  "country" = "Country"))
+
+Clean02 <- plyr::rename(x = Clean02, 
+                                      replace = c("ki02d01" = "Year02",
+                                                  "country" = "Country"))
+
+Clean03 <- plyr::rename(x = Clean03, 
+                                      replace = c("ki03d01" = "Year03",
+                                                  "country" = "Country"))
+
+Clean04 <- plyr::rename(x = Clean04, 
+                                      replace = c("ki04d01" = "Year04",
+                                                  "ki04ctry" = "Country"))
+
+Clean05 <- plyr::rename(x = Clean05, 
+                                      replace = c("KI05D01" = "Year05",
+                                                  "KI05ctry" = "Country"))
+
+Clean06 <- plyr::rename(x = Clean06, 
+                                      replace = c("KI06D01_mean" = "Year06",
+                                                  "KI06CTRY" = "Country"))
+Clean07 <- plyr::rename(x = Clean07, 
+                                      replace = c("ki07d01_" = "Year07",
+                                                  "ki07ctry" = "Country"))
+
+Clean08 <- plyr::rename(x = Clean08, 
+                                      replace = c("NES08_D01_MEAN" = "Year08",
+                                                  "NES08COUNTRY" = "Country"))
+
+Clean09 <- plyr::rename(x = Clean09, 
+                                      replace = c("NES09_D01_MEAN" = "Year09",
+                                                  "NES09COUNTRY" = "Country"))
+
+Clean10 <- plyr::rename(x = Clean10, 
+                                      replace = c("NES10_D01_MEAN" = "Year10",
+                                                  "NES10CRNAME" = "Country"))
+
+#### Merge the data ####
+MergedGEM <- merge(CCurrentOwner, CEntreIntention,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+MergedGem2 <- merge(CFearFail, CNascentEntre,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+MergedGem3 <- merge(CPerceivedCapabilities, MergedGEM,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+MergedGem4 <- merge(MergedGem2, MergedGem3,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+FinalGEM <- merge(MergedGem4, CPerceivedOpportunities,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+# Convert percent columns from character to numeric
+FinalGEM[,"PercentPerceived"] <- as.numeric(FinalGEM[,"PercentPerceived"])
+FinalGEM[,"PercentFear"] <- as.numeric(FinalGEM[,"PercentFear"])
+FinalGEM[,"PercentNascent"] <- as.numeric(FinalGEM[,"PercentNascent"])
+FinalGEM[,"PercentOwner"] <- as.numeric(FinalGEM[,"PercentOwner"])
+FinalGEM[,"PercentIntention"] <- as.numeric(FinalGEM[,"PercentIntention"])
+FinalGEM[,"PercentOpportunities"] <- as.numeric(FinalGEM[,"PercentOpportunities"])
+
+# Remove unncessary data from environment
+remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre)
+
+CleanMerge <- cbind(names = c(rownames(Clean01), rownames(Clean02), rownames(Clean03),
+                              rownames(Clean04), rownames(Clean05), rownames(Clean06),
+                              rownames(Clean07), rownames(Clean08), rownames(Clean09),
+                              rownames(Clean10)),
+                    rbind.fill(list(Clean01, Clean02, Clean03, Clean04, Clean05, Clean06,
+                                    Clean07, Clean08, Clean09, Clean10)))
+
+# Recode countries
+CleanMerge$Country[CleanMerge$Country == "AUSTRALIA"] <- "Australia"
+CleanMerge$Country[CleanMerge$Country == "AUSTRIA"] <- "Austria"
+CleanMerge$Country[CleanMerge$Country == "BELGIUM"] <- "Belgium"
+CleanMerge$Country[CleanMerge$Country == "CANADA"] <- "Canada"
+CleanMerge$Country[CleanMerge$Country == "CHILE"] <- "Chile"
+CleanMerge$Country[CleanMerge$Country == "CZECH REPUBLIC"] <- "Czech Republic"
+CleanMerge$Country[CleanMerge$Country == "DENMARK"] <- "Denmark"
+CleanMerge$Country[CleanMerge$Country == "ESTONIA"] <- "Estonia"
+CleanMerge$Country[CleanMerge$Country == "FINLAND"] <- "Finland"
+CleanMerge$Country[CleanMerge$Country == "FRANCE"] <- "France"
+CleanMerge$Country[CleanMerge$Country == "GERMANY"] <- "Germany"
+CleanMerge$Country[CleanMerge$Country == "GREECE"] <- "Greece"
+CleanMerge$Country[CleanMerge$Country == "HUNGARY"] <- "Hungary"
+CleanMerge$Country[CleanMerge$Country == "ICELAND"] <- "Iceland"
+CleanMerge$Country[CleanMerge$Country == "IRELAND"] <- "Ireland"
+CleanMerge$Country[CleanMerge$Country == "ISRAEL"] <- "Israel"
+CleanMerge$Country[CleanMerge$Country == "ITALY"] <- "Italy"
+CleanMerge$Country[CleanMerge$Country == "JAPAN"] <- "Japan"
+CleanMerge$Country[CleanMerge$Country == "KOREA"] <- "South Korea"
+CleanMerge$Country[CleanMerge$Country == "LUXEMBURG"] <- "Luxemburg"
+CleanMerge$Country[CleanMerge$Country == "MEXICO"] <- "Mexico"
+CleanMerge$Country[CleanMerge$Country == "NETHERLANDS"] <- "Netherlands"
+CleanMerge$Country[CleanMerge$Country == "NEW ZEALAND"] <- "New Zealand"
+CleanMerge$Country[CleanMerge$Country == "NORWAY"] <- "Norway"
+CleanMerge$Country[CleanMerge$Country == "POLAND"] <- "Poland"
+CleanMerge$Country[CleanMerge$Country == "PORTUGAL"] <- "Portugal"
+CleanMerge$Country[CleanMerge$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
+CleanMerge$Country[CleanMerge$Country == "SLOVENIA"] <- "SLOVENIA"
+CleanMerge$Country[CleanMerge$Country == "SPAIN"] <- "Spain"
+CleanMerge$Country[CleanMerge$Country == "SWEDEN"] <- "Sweden"
+CleanMerge$Country[CleanMerge$Country == "SWITZERLAND"] <- "Switzerland"
+CleanMerge$Country[CleanMerge$Country == "TURKEY"] <- "Turkey"
+CleanMerge$Country[CleanMerge$Country == "UNITED KINGDOM"] <- "United Kingdom"
+CleanMerge$Country[CleanMerge$Country == "UK"] <- "United Kingdom"
+CleanMerge$Country[CleanMerge$Country == "USA"] <- "United States"
+CleanMerge$Country[CleanMerge$Country == "UNITED STATES"] <- "United States"
+CleanMerge$Country[CleanMerge$Country == "Korea"] <- "South Korea"
+CleanMerge$Country[CleanMerge$Country == "US"] <- "United States"
+
+# Set columns to numeric
+CleanMerge[,"Year01"] <- as.numeric(CleanMerge[,"Year01"])
+CleanMerge[,"Year02"] <- as.numeric(CleanMerge[,"Year02"])
+CleanMerge[,"Year03"] <- as.numeric(CleanMerge[,"Year03"])
+CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year04"])
+CleanMerge[,"Year05"] <- as.numeric(CleanMerge[,"Year05"])
+CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year06"])
+CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year07"])
+CleanMerge[,"Year08"] <- as.numeric(CleanMerge[,"Year08"])
+CleanMerge[,"Year09"] <- as.numeric(CleanMerge[,"Year09"])
+CleanMerge[,"Year10"] <- as.numeric(CleanMerge[,"Year10"])
+
+ddply(pp, .(names), function(x) colSums(x[,-1], na.rm = TRUE))
+
+ddply(CleanMerge, .(names), function(x) colSums(x[,-1], na.rm = TRUE))
+
+arrange()
+
+# Change merged data from wide to long
+LongGEM<- melt(data = Merged9,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Rename columns
+names(LongGEM) <- gsub("variable", "Year", names(LongGEM))
+names(LongGEM) <- gsub("value", "Support", names(LongGEM))
+
+# Create a vector with OECD countries
+myvars <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')
+
+# Subset LongGEM with the countries we need
+subset_data <- subset(LongGEM, Country %in% myvars)
+
+# Delete unnecessary column
+subset_data$row.names <- NULL
+
+# Arrange subset_data by country and year
+GrandData <- arrange(subset_data, Country, Year)
+
+GrandData1 <- GrandData[order("Country",)]
+
+########### STUCK #############
+
+FinalData <- merge(FinalGEM, GrandData,
+                   union("Country", "Year"))
+
+```
+
+#### Data Analysis
+
+To examine the relationship between these variables, we used least square estimation, the results of which can be found in the following table.
+The package *stargazer* was required to generate this table.
+As evidenced by the equation results, the individual variables selected are statistically significant, but the model only explains a relatively small degree of the variation in the dependent variable.
+For example, the adjusted $R^2$ of regression equation one is 0.29, the adjusted $R^2$ of regression equation two is 0.38, and the adjusted $R^2$ is 0.13.
+<br>
+
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
+
+# Run linear regression R1
+R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)
+
+# Obtain summary statistics of R1
+summary(R1)
+
+# Run linear regression R2
+R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)
+
+# Obtain summary statistics of R2
+summary(R2)
+
+# Run linear regression R3
+R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
+
+# Obtain summary statistics of R3
+summary(R3)
+```
+
+```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
+
+# Library Stargazer for regression output tables
+library(stargazer)
+
+# Create regression output table
+labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
+            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')
+
+dlables <- c('National Level Average Percent Entrepreneurial Intention', 'National Level Nascent Entrepreneural Activity', 'National Level Average Percent Owning a Business')
+
+stargazer::stargazer(R1, R2, R3, covariate.labels = labels, dep.var.labels = dlables,
+                     title = 'Linear Regression Estimates', digits = 2, type = 'html')
+```
+<br>  
+National-level average of people perceiving opportunities but acknowledging fear of failure will prevent them from creating a business (FF)
+
+**Simulation Package and Cleaning**
+
+In addition to the output table, a simulation is helpful to visually illustrate the relationship the probability of obtaining a given value in the dependent variables conditional on change in the independent variable.
+We used the *Zelig* package to run a least square regression and generate a simulation of equation 1.
+Prior to running this regression, however, we ran the na.omit command to remove omitted variables from the equation.
+
+To examine the probabilities of achieving given outcomes, we generated three simulations for the first regression equation.  To demonstrate this method, we have included one simulation below.
+
+**Process**
+
+First, we estimated a least square equation with variation in the variable *PercentPerceived* of 20-100 percent.
+The ranges for variance in the independent variables was chosen by identifying the best range for capturing the largest degree of variance for the model.
+The first simulation is below.
+The y axis shows variation in *PercentIntention* conditional on change in *PercentPerceived* and the x axis shows variation in *PercentPerceived*.
+The results may be interpreted as showing that people who believe they have the knowledge required to start a business may or may not do so (with a high degree of variation), while people who do not believe they have this knowledge are consistently unlikely to start a business (there is little variation).
+
+```{r echo = FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
+
+# Library Zelig (can be buggy if loaded to early)
+library(Zelig)
+
+# Omit omitted data from simulation
+CompleteData_omit <- na.omit(CompleteDataset)
+
+# Run a least squares regression with Zelig
+Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteData_omit, model = "ls")
+```
+
+```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE }
+
+# Find appropriate range for PercentPerceived
+summary(CompleteData_omit$PercentPerceived)
+
+# Set range of PercentPerceived values in simulation
+x.out2 <- setx(Z1, PercentPerceived = 9:67)
+
+# Run simulation (default 1000 trials)
+simz2 <- sim(Z1, x = x.out2)
+
+# Adjust margins
+par(mar=c(2,2,2,2))
+
+# Plot simulation
+plot(simz2, xlab= 'PercentPerceived')
+
+```
+
+<br>
+
+#### Outlook
+
+Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at the country level in its NES Survey.
+Item D01 states "in my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self esteem a given education system is.
+
+We may also want to quantify how individualistic or group-oriented an average student is by the end of compulsory education, as the literature holds social inclusion as an explanatory factor for self-esteem.
+We will use OECD PISA data on "the sense of belonging" for this.
+
+Next steps will also include looking more thoroughly into control variables and determining the most appropriate way to present our results.
+To do so we may need to extract data from various national NES reports and put together a table, as it does not seem to exist as such.
+
+```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
+
+library(stargazer)
+stargazer(CompleteDataset, type = 'html')
+
+```
+
+Estonia
+Luxemburg
+Slovak Republic

### 2014-11-29 GEMDataSource.Rmd
Temporary fix for GEM data cleaning

@@
 
-CleanMerge <- cbind(names = c(rownames(Clean01), rownames(Clean02), rownames(Clean03),
-                              rownames(Clean04), rownames(Clean05), rownames(Clean06),
-                              rownames(Clean07), rownames(Clean08), rownames(Clean09),
-                              rownames(Clean10)),
-                    rbind.fill(list(Clean01, Clean02, Clean03, Clean04, Clean05, Clean06,
-                                    Clean07, Clean08, Clean09, Clean10)))
-
-# Recode countries
-CleanMerge$Country[CleanMerge$Country == "AUSTRALIA"] <- "Australia"
-CleanMerge$Country[CleanMerge$Country == "AUSTRIA"] <- "Austria"
-CleanMerge$Country[CleanMerge$Country == "BELGIUM"] <- "Belgium"
-CleanMerge$Country[CleanMerge$Country == "CANADA"] <- "Canada"
-CleanMerge$Country[CleanMerge$Country == "CHILE"] <- "Chile"
-CleanMerge$Country[CleanMerge$Country == "CZECH REPUBLIC"] <- "Czech Republic"
-CleanMerge$Country[CleanMerge$Country == "DENMARK"] <- "Denmark"
-CleanMerge$Country[CleanMerge$Country == "ESTONIA"] <- "Estonia"
-CleanMerge$Country[CleanMerge$Country == "FINLAND"] <- "Finland"
-CleanMerge$Country[CleanMerge$Country == "FRANCE"] <- "France"
-CleanMerge$Country[CleanMerge$Country == "GERMANY"] <- "Germany"
-CleanMerge$Country[CleanMerge$Country == "GREECE"] <- "Greece"
-CleanMerge$Country[CleanMerge$Country == "HUNGARY"] <- "Hungary"
-CleanMerge$Country[CleanMerge$Country == "ICELAND"] <- "Iceland"
-CleanMerge$Country[CleanMerge$Country == "IRELAND"] <- "Ireland"
-CleanMerge$Country[CleanMerge$Country == "ISRAEL"] <- "Israel"
-CleanMerge$Country[CleanMerge$Country == "ITALY"] <- "Italy"
-CleanMerge$Country[CleanMerge$Country == "JAPAN"] <- "Japan"
-CleanMerge$Country[CleanMerge$Country == "KOREA"] <- "South Korea"
-CleanMerge$Country[CleanMerge$Country == "LUXEMBURG"] <- "Luxemburg"
-CleanMerge$Country[CleanMerge$Country == "MEXICO"] <- "Mexico"
-CleanMerge$Country[CleanMerge$Country == "NETHERLANDS"] <- "Netherlands"
-CleanMerge$Country[CleanMerge$Country == "NEW ZEALAND"] <- "New Zealand"
-CleanMerge$Country[CleanMerge$Country == "NORWAY"] <- "Norway"
-CleanMerge$Country[CleanMerge$Country == "POLAND"] <- "Poland"
-CleanMerge$Country[CleanMerge$Country == "PORTUGAL"] <- "Portugal"
-CleanMerge$Country[CleanMerge$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
-CleanMerge$Country[CleanMerge$Country == "SLOVENIA"] <- "SLOVENIA"
-CleanMerge$Country[CleanMerge$Country == "SPAIN"] <- "Spain"
-CleanMerge$Country[CleanMerge$Country == "SWEDEN"] <- "Sweden"
-CleanMerge$Country[CleanMerge$Country == "SWITZERLAND"] <- "Switzerland"
-CleanMerge$Country[CleanMerge$Country == "TURKEY"] <- "Turkey"
-CleanMerge$Country[CleanMerge$Country == "UNITED KINGDOM"] <- "United Kingdom"
-CleanMerge$Country[CleanMerge$Country == "UK"] <- "United Kingdom"
-CleanMerge$Country[CleanMerge$Country == "USA"] <- "United States"
-CleanMerge$Country[CleanMerge$Country == "UNITED STATES"] <- "United States"
-CleanMerge$Country[CleanMerge$Country == "Korea"] <- "South Korea"
-CleanMerge$Country[CleanMerge$Country == "US"] <- "United States"
-
-# Set columns to numeric
-CleanMerge[,"Year01"] <- as.numeric(CleanMerge[,"Year01"])
-CleanMerge[,"Year02"] <- as.numeric(CleanMerge[,"Year02"])
-CleanMerge[,"Year03"] <- as.numeric(CleanMerge[,"Year03"])
-CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year04"])
-CleanMerge[,"Year05"] <- as.numeric(CleanMerge[,"Year05"])
-CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year06"])
-CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year07"])
-CleanMerge[,"Year08"] <- as.numeric(CleanMerge[,"Year08"])
-CleanMerge[,"Year09"] <- as.numeric(CleanMerge[,"Year09"])
-CleanMerge[,"Year10"] <- as.numeric(CleanMerge[,"Year10"])
-
-ddply(pp, .(names), function(x) colSums(x[,-1], na.rm = TRUE))
-
-ddply(CleanMerge, .(names), function(x) colSums(x[,-1], na.rm = TRUE))
-
-arrange()
-
-# Change merged data from wide to long
-LongGEM<- melt(data = Merged9,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010"))
-
-# Rename columns
-names(LongGEM) <- gsub("variable", "Year", names(LongGEM))
-names(LongGEM) <- gsub("value", "Support", names(LongGEM))
-
-# Create a vector with OECD countries
-myvars <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')
-
-# Subset LongGEM with the countries we need
-subset_data <- subset(LongGEM, Country %in% myvars)
-
-# Delete unnecessary column
-subset_data$row.names <- NULL
-
-# Arrange subset_data by country and year
-GrandData <- arrange(subset_data, Country, Year)
-
-GrandData1 <- GrandData[order("Country",)]
-
-########### STUCK #############
-
-FinalData <- merge(FinalGEM, GrandData,
-                   union("Country", "Year"))
-
 ```

### 2014-11-29 Misc/TrialFile.Rmd
Temporary fix for GEM data cleaning

@@
                    all = TRUE)
+
+```
+
+``` {r}
+
+CleanMerge <- cbind(names = c(rownames(Clean01), rownames(Clean02), rownames(Clean03),
+                              rownames(Clean04), rownames(Clean05), rownames(Clean06),
+                              rownames(Clean07), rownames(Clean08), rownames(Clean09),
+                              rownames(Clean10)),
+                    rbind.fill(list(Clean01, Clean02, Clean03, Clean04, Clean05, Clean06,
+                                    Clean07, Clean08, Clean09, Clean10)))
+
+# Change merged data from wide to long
+LongGEM<- melt(data = Merged9,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Rename columns
+names(LongGEM) <- gsub("variable", "Year", names(LongGEM))
+names(LongGEM) <- gsub("value", "Support", names(LongGEM))
+
+# Create a vector with OECD countries
+myvars <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'South Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')
+
+# Subset LongGEM with the countries we need
+subset_data <- subset(LongGEM, Country %in% myvars)
+
+# Delete unnecessary column
+subset_data$row.names <- NULL
+
+# Arrange subset_data by country and year
+GrandData <- arrange(subset_data, Country, Year)
+
+GrandData1 <- GrandData[order("Country",)]
+
+########### STUCK #############
+
+FinalData <- merge(FinalGEM, GrandData,
+                   union("Country", "Year"))
+```

### 2014-11-29 FromEducationToEntrepreneurship.Rmd

@@
 
-### Research Interest
+### Policy Relevance
 
@@
 The rationale for decisions made during this process, however, is often difficult to understand.
-For example, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors -- not just structural and economic factors -- in determining individual and societal tendencies to start a business, these factors are often not included in the decisionmaking process.
-As a matter of fact, only a few empirical studies have actually been carried out on this topic and most of them focused on which attitudes were favorable to starting a business, while almost none explored how cultural patterns affected these dispositions.
-
-When cultural factors are examined, they are considered as a given feature that can hardly be traced.
-By having a closer look at education systems, however, we intend to explore the processes through which some of these cultural patterns are enhanced and passed from one generation to the next.
-Aside from parental education, schools are indeed the very place where children are taught how to fit into society.
-This research is an attempt to analyze  one trait in particular, self-confidence.
+That is, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors -- not just structural and economic factors -- in determining individual and societal tendencies to start a business, these factors are often not included in the decision-making process.
+Actually, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.
 

### 2014-11-29 FromEducationToEntrepreneurship.Rmd

@@
 What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
-However, as Freytag and Thurik stated in 2007, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] .
+Still, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007].
 Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done, as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
@@
 Despite various claims of the existence of a cultural effect, few empirical studies have actually been carried out.
-It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), and then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors -- mainly economic, and cultural factors.
+It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors.
 As they compared two Swedish regions similar in terms of structure and observed different outcomes, they concluded there may be a small cultural effect in attitudes toward start-up activities.
 
-This thesis is an attempt at finding out whether different patterns in education lead to different outcomes in terms of start-up activities.
-Indeed, like many in the education literature tend to assert, we believe school personnel have an affect on student self-esteem [@Scott1996].
-We will further explore how this mechanism works.
-As for entrepreneurship literature, it generally acknowledges the influence of self-confidence on start-up activities, although “self-confidence in one’s own capabilities to start a business has been found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks” [@OECD2009].
-We intend to show that these individual characteristics are partly shaped at an institutional and collective level through the education systems and staff attitudes.
+Rather than trying to trace cultural patterns at large, we intend to focus on one key cultural institution, that is the education system.
+Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on student self-confidence [@Scott1996].
+Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" [@OECD2009].
+Yet, we intend to understand to what extent these individual characteristics are partly shaped through education systems and staff attitudes.
 
-Of course, King and Sobel [@Kerry2008], among others, have already tried to show how school choice can increase the rate of youth entrepreneurship, but their perspective was slightly different.
-They  asserted that a more business-like environment in K-12 education was the key, which was favored by voucher programs.
-We believe there is a more widely spread systematic effect of cultural and educational patterns.
-David Watkins [@Watkins2010] cross-cultural perspective on teaching and learning shall be useful in that respect.
-Kai-Ming Cheng and Kam-Cheung Wong’s study about school effectiveness in East Asia [@Cheng2006] could also be of help.
+King and Sobel [@Kerry2008], among others, have already tried to show how school choice can increase the rate of youth entrepreneurship, but their perspective was slightly different.
+They  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
+We believe there is a more widely spread systematic effect of educational features.
+The cross-cultural perspective on teaching and learning proposed by Watkins [@Watkins2010] shall help us compare countries.
+Cheng and Wong’s study about school effectiveness in East Asia [@Cheng2006] will also help.
 

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
Editing Literature Review 2

@@
 What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
-Still, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007].
+Still, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ??????
+2010 VERSION MAIN BIB ?????.
 Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done, as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
@@
 
-Also, as self-confidence is considered to rely partly on one’s integration within social networks [@OECD2009], we will refer to cross-cultural studies such as that of Green, Deschamps and Páez [@green2005variation] about individualism and collectivism, what Freeman [@freeman1997demographic] called idiocentrism and allocentrism.
-Raeff, Greenfield and Quiroz [-@raeff2000conceptualizing] have also conceptualized interpersonal relationships in both contexts.
-More school-focused, Yamauchi [@yamauchi1998individualism] as well as Davies and Aurini [@davies2003homeschooling] have looked at individualism and collectivism in the classroom and in pedagogy respectively.
-All these will be important on the way.
+Further, since self-confidence is considered to rely partly on one’s integration within social networks [@OECD2009], we will refer to cross-cultural studies about individualism and collectivism such as those of Green, Deschamps and Páez [@green2005variation], Pinillos and Reyes ????????
+MAIN BIB ??????, Freeman [@freeman1997demographic], Raeff, Greenfield and Quiroz [-@raeff2000conceptualizing].
+We will also cite more school-focused research like Yamauchi [@yamauchi1998individualism], Davies and Aurini [@davies2003homeschooling] for these have looked at individualism and collectivism in the classroom and in pedagogy respectively.
 
-Besides direct or indirect school effects, we will necessarily look into entrepreneurship and its determinants at large.
-Thus we will quote Grilo and Thurik’s research [@Grilo2005b] about what determines entrepreneurship engagement levels throughout the European Union, and also Wennekers Sander, Ulhaner Lorraine and Thurik Roy’s explanation of variation across countries [@Wennekers2002].
-Eventually, with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, along with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.
+Besides potential educational effects on self-confidence and social capital, we will need to control for all classic entrepreneurship determinants.
+Therefore, we will quote Grilo and Thurik’s research [@Grilo2005b] about what determines entrepreneurship engagement levels throughout the European Union and the US, Wennekers, Ulhaner and Thurik’s about variation across countries [@Wennekers2002], Freytag and Thurik about determinants in a cross-country setting ?????
+2010 VERSION MAINBIB ?????.
+
+Eventually, to put all these into perspective, along with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.
 

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
Minor editing

@@
 ---
-title: "From Education To Entrepreneurship"
+title: "Country-Level Impact of Education on Entrepreneurship"
 author: "Sam Dundon and Thierry Racaud"
@@
 The rationale for decisions made during this process, however, is often difficult to understand.
-That is, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors -- not just structural and economic factors -- in determining individual and societal tendencies to start a business, these factors are often not included in the decision-making process.
+That is, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors - not just structural and economic factors - in determining individual and societal tendencies to start a business, these factors are often not included in the decision-making process.
 Actually, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.
@@
 
-To what extent do the behavioral characteristics of education systems - individualistic, group-oriented, self-esteem reinforcing - affect the rate of entrepreneurship in OECD countries?
+To what extent do the behavioral characteristics of education systems - individualistic, group-oriented, reinforcing self-confidence - affect the rate of entrepreneurship in OECD countries?
 

### 2014-11-29 FromEducationToEntrepreneurship.Rmd

@@
 
-To what extent do the behavioral characteristics of education systems - individualistic, group-oriented, reinforcing self-confidence - affect the rate of entrepreneurship in OECD countries?
+To what extent do the behavioural characteristics of education systems - individualistic, group-oriented, reinforcing self-confidence - affect the rate of entrepreneurship across OECD countries?
 

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
Minor editing

@@
 It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors.
-As they compared two Swedish regions similar in terms of structure and observed different outcomes, they concluded there may be a small cultural effect in attitudes toward start-up activities.
+As they compared two Swedish regions similar in terms of structure and observed different outcomes, they concluded that there might be a small cultural effect in attitudes toward start-up activities.
 
@@
 Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" [@OECD2009].
-Yet, we intend to understand to what extent these individual characteristics are partly shaped through education systems and staff attitudes.
+Yet, we intend to understand to what extent these individual characteristics are partly shaped through education systems and their personnel's attitudes.
 

### 2014-11-29 GEMDataSource.Rmd
All data included

@@
 
+# Import tempfix for GEM data (created this by copying data frame, editing outide R, and saving .csv in repository)
+
+GEMAnnualData <- repmis::source_data("https://github.com/SamDund/Assign2Education/raw/master/GEMData/Gemyears.csv", header = TRUE, cache = FALSE)
+
+##### Clean and merge tempfix GEM Data ####
+
+# Change column names
+names(GEMAnnualData) <- gsub("Year01", "2001", names(GEMAnnualData))
+names(GEMAnnualData) <- gsub("Year02", "2002", names(GEMAnnualData))
+names(GEMAnnualData) <- gsub("Year03", "2003", names(GEMAnnualData))
+names(GEMAnnualData) <- gsub("Year04", "2004", names(GEMAnnualData))
+names(GEMAnnualData) <- gsub("Year05", "2005", names(GEMAnnualData))
+names(GEMAnnualData) <- gsub("Year06", "2006", names(GEMAnnualData))
+names(GEMAnnualData) <- gsub("Year07", "2007", names(GEMAnnualData))
+names(GEMAnnualData) <- gsub("Year08", "2008", names(GEMAnnualData))
+names(GEMAnnualData) <- gsub("Year09", "2009", names(GEMAnnualData))
+names(GEMAnnualData) <- gsub("Year10", "2010", names(GEMAnnualData))
+
+# Change years from columns to rows and create CleanGEM
+CleanGEM <- melt(data = GEMAnnualData,
+                 id.vars = c("Country"),
+                 measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Rename columns
+CleanGEM <- plyr::rename(x = CleanGEM,
+                         replace = c("variable" = "Year",
+                                     "value" = "WayofTeach"))
+
+# Merge Clean CleanGEM with FinalGEM 
+CompleteData <- merge(CleanGEM, FinalGEM,
+                   union("Country", "Year"),
+                   all = TRUE)
+
 ```
@@
 # Run linear regression R1
-R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)
+R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)
 
@@
 # Run linear regression R2
-R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)
+R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)
 
@@
 # Run linear regression R3
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
+R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + lm(WayofTeach) + Country, data = CompleteData)
 

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
Minor editing

@@
 
-#### Research Question
+### Research Question
 
@@
 
-#### Estimation Strategy
+### Estimation Strategy
 
-##### Causal Chain
+#### Causal Chain
 
@@
 
-##### Dependent Variables: Explaining the Country-level Rate of Entrepreneurship
+#### Dependent Variables: Explaining the Country-level Rate of Entrepreneurship
 
@@
 
-##### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System
+#### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System
 
@@
 
-##### Control Variables: Controlling for Classic Determinants of Entrepreneurship
+#### Control Variables: Controlling for Classic Determinants of Entrepreneurship
 
@@
 
-##### Regressions
+#### Regressions
 

### 2014-11-29 FromEducationToEntrepreneurship.Rmd
Minor editing
Fixed regression equations, Zelig sim, and regression table output

@@
 ---
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
 
@@
 # Install necessary packages
+library(plyr)
+library(repmis)
+library(tidyr)
+library(reshape2)
+library(foreign)
 
@@
 
-ddply(pp, .(names), function(x) colSums(x[,-1], na.rm = TRUE))
-
-ddply(CleanMerge, .(names), function(x) colSums(x[,-1], na.rm = TRUE))
-
-arrange()
-
 # Change merged data from wide to long

### 2014-11-29 Source/EduDataSource.Rmd
Fixed regression equations, Zelig sim, and regression table output

--- 2014-11-29 GEMDataSource.Rmd
@@
 ---
-title: "Impact of Education on Entrepreneurship - Data Gathering and Analysis"
-author: "Samuel Dundon and Thierry Racaud"
-date: "November 14, 2014"
+title: "EduDataSource"
+author: "Sam"
+date: "November 29, 2014"
 output: html_document
 ---
-***
 
@@
 
-*Introduction to Collaborative Social Science Data Analysis*
-
-#### Research Question
-
-To what extent do the behavioral characteristics of education systems - individualistic, group-oriented, self-esteem reinforcing - affect the rate of entrepreneurship in OECD countries?  
-<br>
-
-#### Estimation Strategy
-
-##### Causal Chain
-
-Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
-<br>
-
-##### Dependent Variables: Explaining the Country-level Rate of Entrepreneurship
-
-We have examined three dimensions of entrepreneurship to prepare for this stage of the project, established entrepreneurship in the country, nascent entrepreneurship (less than three months), and entrepreneurial intention.
-We will study each of these successively as we may well observe different effects.
-
-To measure these three dimensions of entrepreneurship, we have used three [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) indicators:
-
-- Established Business Ownership Rate (Percentage) 
-- Nascent Entrepreneurship Rate (Percentage)
-- Entrepreneurial intention Rate (Percentage)
-
-##### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System
-
-As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem.
-To do so, we decided to incorporate GEM indicators that relate to self-esteem and confidence.
-First, we included GEM survey data on the average "perceived capabilities" of an individual (18-64) in a given country to start a business.
-Second, we included additional GEM data on how the "fear of failure" could deter an average individual (18-64) in a country to become an entrepreneur.
-Both of these data sets indicate the average percentage for each characteristic at the country-level.
-
-##### Control Variables: Controlling for Classic Determinants of Entrepreneurship
-
-To control for the general state of the economy, we included annual GDP Growth from the World Bank [World Development Indicators](http://data.worldbank.org/data-catalog/world-development-indicators) as a control variable in our regression equations.
-In addition, we included a GEM indicator called "Perceived Opportunities." For each country, it is the average percentage of individuals who believe there are opportunities to start a business in their area.
-Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.
-
-In the future, we may revise this to include lagged GDP growth in recognition of the time taken for governments and individuals to react to the state of the economy, and are planning to include control variables from GEM.
-Specifically, we intend to control for the classic determinants of entrepreneurship -- economic and structural determinants.
-To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://www.gemconsortium.org/Data-Collection).
-
-1. Finance  
-2. Government policies  
-3. Government programs  
-4. Entrepreneurial Education and Training  
-5. Research and Development Transfer (R & D)  
-6. Commercial and professional infrastructure  
-7. Internal Market openness  
-8. Physical infrastructure and services  
-9. Cultural and social norms
-
-##### Regressions
-
-The following equations were used to determine the relationship between our dependent and explanatory variables:
-
-1. $PercentIntention = PercentPerceived(Perceived Capabilities) + Way of Teaching + PercentOpportunities(Perceived Opportunities)$
-
-2. $PercentNascent = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
-
-3. $PercentOwner = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
-
-The variables *Percent Fear* and *Percent Opportunities* were included as an interaction term $PercentFear*PercentOpportunities$ because of the design of the survey.
-PercentFear is: "the Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business."
-
-<br>
-
-#### Data Collection and Cleaning
-
-To collect the data necessary to run these regression equations, we downloaded *.csv* data from GEM and used the WDI API to obtain the necessary annual GDP growth of OECD Countries.
-
-**Necessary R Packages**
-
-The following packages were needed to complete the data collection portion of this assignment:
-
-- repmis  
-- tidyr  
-- reshape  
-- plyr  
-- WDI
-
-**GEM Data**
-
-GEM data was embedded in an interactive database and was difficult to extract automatically without writing a program.
-To simplify this process, we downloaded the necessary *.csv* files and saved them in our GitHub repository (to reduce complexity, we deleted the first three unnecessary rows before saving).
-We then linked to the RAW version of the files and added the code required to load them from *R*.
-The repmis package is required to load these documents from the repository.
-
-Cleaning the GEM data required deleting unnecessary characters in the year columns, changing the years from columns to rows (changing the data from wide to long), and changing the column names to describe which data was being analyzed.
-In the process of doing this we created new data sets for each of these survey questions, which were called C*dataset* (clean followed by the data set name).
-This was done for each of the six GEM data sets before merging these sets two at a time to create the data set *FinalGEM*.
-
-For all 33 OECD countries we should have 13 observations, one per year from 2001 to 2013, for each variable.
-However, there are a few missing values, especially regarding the perceived opportunities for some countries, namely Estonia, Luxembourg and Slovak Republic.
-
-**World Bank Data**
-
-As mentioned above, one of our control variables, annual GDP growth, was obtained using the WDI API from the World Bank.
-Using this API, we accessed GDP data from all the OECD countries directly from *R*.
-To clean this data, we used *plyr* to change the variable names then recoded the U.S.
-and South Korea country names to maintain consistency with the GEM data set and dropped an unnecessary column that was not included with the GEM data.
-
-Finally, we merged the annual GDP growth data with the *FinalGEM* data set to create *CompleteDataset*.
-This is the data set used to run the regressions and generate the charts and figures outlined in this document.
-To reduce complexity in the environment we also included a command to remove unnecessary objects in the environment.
-
-<br>
 ```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
 
-#### Import data from GEM Survey ####
+############# Import data from GEM Survey #############
 
@@
 
+############# Import Annual GEM Country Level Data (means) #############
+
 # Import GEM 2009 supportive teaching data
@@
 
-#### Clean data using tidy ####
+##################### Clean GEM Survey Data  ###################
 
 ### Clean FearFail ###
-# Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
+# Question: Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
 
@@
 ### Clean CurrentOwner ###
-# Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid sallaries, wages, or any other payments to the owners for more than 42 months
+# Question: Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid sallaries, wages, or any other payments to the owners for more than 42 months
 
@@
 
-### Clean GEM NES Datasets
+########## Clean Annual GEM NES Datasets ##########
+
 # Draw out Country and D01 only
@@
 # Edit column names for each dataframe
-
 Clean01 <- plyr::rename(x = Clean01, 
@@
                                                   "KI06CTRY" = "Country"))
+
 Clean07 <- plyr::rename(x = Clean07, 
@@
 
-#### Merge the data ####
+#### Merge Annual GEM data
+
 MergedGEM <- merge(CCurrentOwner, CEntreIntention,
@@
 
-# Import tempfix for GEM data (created this by copying data frame, editing outide R, and saving .csv in repository)
+####### Import tempfix for GEM data (created this by copying data frame (extra code for generating data frame is in misc/TrialFile.Rmd), editing outide R, and saving .csv in repository)
 
@@
 
-```
+write.csv(CompleteData, file = "CompleteData.csv")
 
-#### Data Analysis
-
-To examine the relationship between these variables, we used least square estimation, the results of which can be found in the following table.
-The package *stargazer* was required to generate this table.
-As evidenced by the equation results, the individual variables selected are statistically significant, but the model only explains a relatively small degree of the variation in the dependent variable.
-For example, the adjusted $R^2$ of regression equation one is 0.29, the adjusted $R^2$ of regression equation two is 0.38, and the adjusted $R^2$ is 0.13.
-<br>
-
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
-
-# Run linear regression R1
-R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)
-
-# Obtain summary statistics of R1
-summary(R1)
-
-# Run linear regression R2
-R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)
-
-# Obtain summary statistics of R2
-summary(R2)
-
-# Run linear regression R3
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + lm(WayofTeach) + Country, data = CompleteData)
-
-# Obtain summary statistics of R3
-summary(R3)
-```
-
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
-
-# Library Stargazer for regression output tables
-library(stargazer)
-
-# Create regression output table
-labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
-            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')
-
-dlables <- c('National Level Average Percent Entrepreneurial Intention', 'National Level Nascent Entrepreneural Activity', 'National Level Average Percent Owning a Business')
-
-stargazer::stargazer(R1, R2, R3, covariate.labels = labels, dep.var.labels = dlables,
-                     title = 'Linear Regression Estimates', digits = 2, type = 'html')
-```
-<br>  
-National-level average of people perceiving opportunities but acknowledging fear of failure will prevent them from creating a business (FF)
-
-**Simulation Package and Cleaning**
-
-In addition to the output table, a simulation is helpful to visually illustrate the relationship the probability of obtaining a given value in the dependent variables conditional on change in the independent variable.
-We used the *Zelig* package to run a least square regression and generate a simulation of equation 1.
-Prior to running this regression, however, we ran the na.omit command to remove omitted variables from the equation.
-
-To examine the probabilities of achieving given outcomes, we generated three simulations for the first regression equation.  To demonstrate this method, we have included one simulation below.
-
-**Process**
-
-First, we estimated a least square equation with variation in the variable *PercentPerceived* of 20-100 percent.
-The ranges for variance in the independent variables was chosen by identifying the best range for capturing the largest degree of variance for the model.
-The first simulation is below.
-The y axis shows variation in *PercentIntention* conditional on change in *PercentPerceived* and the x axis shows variation in *PercentPerceived*.
-The results may be interpreted as showing that people who believe they have the knowledge required to start a business may or may not do so (with a high degree of variation), while people who do not believe they have this knowledge are consistently unlikely to start a business (there is little variation).
-
-```{r echo = FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
-
-# Library Zelig (can be buggy if loaded to early)
-library(Zelig)
-
-# Omit omitted data from simulation
-CompleteData_omit <- na.omit(CompleteDataset)
-
-# Run a least squares regression with Zelig
-Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteData_omit, model = "ls")
-```
-
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE }
-
-# Find appropriate range for PercentPerceived
-summary(CompleteData_omit$PercentPerceived)
-
-# Set range of PercentPerceived values in simulation
-x.out2 <- setx(Z1, PercentPerceived = 9:67)
-
-# Run simulation (default 1000 trials)
-simz2 <- sim(Z1, x = x.out2)
-
-# Adjust margins
-par(mar=c(2,2,2,2))
-
-# Plot simulation
-plot(simz2, xlab= 'PercentPerceived')
+# Remove unncessary data from environment
+remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre, Clean01, Clean02, Clean03, Clean04, Clean05, Clean06, Clean07, Clean08, Clean09, Clean10, CleanGEM, FinalGEM, GEMAnnualData, SupportiveTeaching)
 
 ```
-
-<br>
-
-#### Outlook
-
-Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at the country level in its NES Survey.
-Item D01 states "in my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self esteem a given education system is.
-
-We may also want to quantify how individualistic or group-oriented an average student is by the end of compulsory education, as the literature holds social inclusion as an explanatory factor for self-esteem.
-We will use OECD PISA data on "the sense of belonging" for this.
-
-Next steps will also include looking more thoroughly into control variables and determining the most appropriate way to present our results.
-To do so we may need to extract data from various national NES reports and put together a table, as it does not seem to exist as such.
-
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
-
-library(stargazer)
-stargazer(CompleteDataset, type = 'html')
-
-```
-
-Estonia
-Luxemburg
-Slovak Republic

### 2014-12-01 GEMDataSource.Rmd
Cleaned up code to show professor tomorrow

@@
 
-#### Import data from GEM Survey ####
+############# Import data from GEM Survey #############
 
@@
 # Edit column names for each dataframe
-
 Clean01 <- plyr::rename(x = Clean01, 
-                                      replace = c("ki01d01" = "Year01",
+                                      replace = c("ki01d01" = "2001",
                                                   "country" = "Country"))
@@
 Clean02 <- plyr::rename(x = Clean02, 
-                                      replace = c("ki02d01" = "Year02",
+                                      replace = c("ki02d01" = "2002",
                                                   "country" = "Country"))
@@
 Clean03 <- plyr::rename(x = Clean03, 
-                                      replace = c("ki03d01" = "Year03",
+                                      replace = c("ki03d01" = "2003",
                                                   "country" = "Country"))
@@
 Clean04 <- plyr::rename(x = Clean04, 
-                                      replace = c("ki04d01" = "Year04",
+                                      replace = c("ki04d01" = "2004",
                                                   "ki04ctry" = "Country"))
@@
 Clean05 <- plyr::rename(x = Clean05, 
-                                      replace = c("KI05D01" = "Year05",
+                                      replace = c("KI05D01" = "2005",
                                                   "KI05ctry" = "Country"))
@@
 Clean06 <- plyr::rename(x = Clean06, 
-                                      replace = c("KI06D01_mean" = "Year06",
+                                      replace = c("KI06D01_mean" = "2006",
                                                   "KI06CTRY" = "Country"))
+
 Clean07 <- plyr::rename(x = Clean07, 
-                                      replace = c("ki07d01_" = "Year07",
+                                      replace = c("ki07d01_" = "2007",
                                                   "ki07ctry" = "Country"))
@@
 Clean08 <- plyr::rename(x = Clean08, 
-                                      replace = c("NES08_D01_MEAN" = "Year08",
+                                      replace = c("NES08_D01_MEAN" = "2008",
                                                   "NES08COUNTRY" = "Country"))
@@
 Clean09 <- plyr::rename(x = Clean09, 
-                                      replace = c("NES09_D01_MEAN" = "Year09",
+                                      replace = c("NES09_D01_MEAN" = "2009",
                                                   "NES09COUNTRY" = "Country"))
@@
 Clean10 <- plyr::rename(x = Clean10, 
-                                      replace = c("NES10_D01_MEAN" = "Year10",
+                                      replace = c("NES10_D01_MEAN" = "2010",
                                                   "NES10CRNAME" = "Country"))
 
-#### Merge the data ####
+#### Merge Annual GEM data
+
 MergedGEM <- merge(CCurrentOwner, CEntreIntention,
@@
 
+write.csv(CompleteData, file = "CompleteData.csv")
+
+# Remove unncessary data from environment
+remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre, Clean01, Clean02, Clean03, Clean04, Clean05, Clean06, Clean07, Clean08, Clean09, Clean10, CleanGEM, FinalGEM, GEMAnnualData, SupportiveTeaching)
+
 ```
@@
 # Run linear regression R3
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + lm(WayofTeach) + Country, data = CompleteData)
+R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)
 
@@
 labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
-            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')
+            'National Level Avg Perceived Good Opportunities', 'Way of Teaching', 'Austria',
+            'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Finland', 'France',
+            'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan',
+            'Korea (South)', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland',
+            'Portugal', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey',
+            'United Kingdom','United States', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities', '(Intercept)')
 
@@
 # Omit omitted data from simulation
-CompleteData_omit <- na.omit(CompleteDataset)
+CompleteData_omit <- na.omit(CompleteData)
 
 # Run a least squares regression with Zelig
-Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteData_omit, model = "ls")
+Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach, data = CompleteData_omit, model = "ls")
+
 ```
@@
 
+H1 <- hist(CompleteData$PercentPerceived)
+
 # Set range of PercentPerceived values in simulation
-x.out2 <- setx(Z1, PercentPerceived = 9:67)
+x.out2 <- setx(Z1, PercentPerceived = 20:70)
 
@@
 # Adjust margins
-par(mar=c(2,2,2,2))
+par(mar=c(5,5,5,5))
 
 # Plot simulation
-plot(simz2, xlab= 'PercentPerceived')
+plot(simz2, xlab = 'PercentPerceived', ylab = 'PercentIntention | PercentPerceived')
 
@@
 ```
-
-Estonia
-Luxemburg
-Slovak Republic

### 2014-12-01 Misc/TrialFile.Rmd
Cleaned up code to show professor tomorrow

@@
 
+### Data for final project
+
 ``` {r}
@@
 # Change merged data from wide to long
-LongGEM<- melt(data = Merged9,
+LongGEM<- melt(data = CleanMerge,
                   id.vars = c("Country"),
@@
 # Rename columns
-names(LongGEM) <- gsub("variable", "Year", names(LongGEM))
-names(LongGEM) <- gsub("value", "Support", names(LongGEM))
+names(CleanMerge) <- gsub("variable", "Year", names(CleanMerge))
+names(CleanMerge) <- gsub("value", "Support", names(CleanMerge))
 
@@
 
-# Subset LongGEM with the countries we need
-subset_data <- subset(LongGEM, Country %in% myvars)
+# Subset LongGEM with the countries we need  (Why does 2001 and 2010 data disappear?)
+subset_data <- subset(CleanMerge, Country %in% myvars)
 

### 2014-12-01 Source/EduDataSource.Rmd
Cleaned up code to show professor tomorrow

@@
 SupportiveTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEMAvgIndicators.csv", header = TRUE, cache = FALSE)
-
-############# Import Annual GEM Country Level Data (means) #############
-
-# Import GEM 2009 supportive teaching data
-setwd('~/Assign2Education/GEMData')
-
-GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
-GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
-GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
-GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
-GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
-GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
-GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
-GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
-GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
-GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)
 
@@
 
-########## Clean Annual GEM NES Datasets ##########
-
-# Draw out Country and D01 only
-Clean01 <- GEM2001[,c("country", "ki01d01")]
-Clean02 <- GEM2002[,c("country", "ki02d01")]
-Clean03 <- GEM2003[,c("country", "ki03d01")]
-Clean04 <- GEM2004[,c("ki04ctry", "ki04d01")]
-Clean05 <- GEM2005[,c("KI05ctry", "KI05D01")]
-Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
-Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
-Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
-Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
-Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]
-
-remove(GEM2001, GEM2002, GEM2003, GEM2004, GEM2005, GEM2006, GEM2007, GEM2008, GEM2009, GEM2010)
-
-# Edit column names for each dataframe
-Clean01 <- plyr::rename(x = Clean01, 
-                                      replace = c("ki01d01" = "Year01",
-                                                  "country" = "Country"))
-
-Clean02 <- plyr::rename(x = Clean02, 
-                                      replace = c("ki02d01" = "Year02",
-                                                  "country" = "Country"))
-
-Clean03 <- plyr::rename(x = Clean03, 
-                                      replace = c("ki03d01" = "Year03",
-                                                  "country" = "Country"))
-
-Clean04 <- plyr::rename(x = Clean04, 
-                                      replace = c("ki04d01" = "Year04",
-                                                  "ki04ctry" = "Country"))
-
-Clean05 <- plyr::rename(x = Clean05, 
-                                      replace = c("KI05D01" = "Year05",
-                                                  "KI05ctry" = "Country"))
-
-Clean06 <- plyr::rename(x = Clean06, 
-                                      replace = c("KI06D01_mean" = "Year06",
-                                                  "KI06CTRY" = "Country"))
-
-Clean07 <- plyr::rename(x = Clean07, 
-                                      replace = c("ki07d01_" = "Year07",
-                                                  "ki07ctry" = "Country"))
-
-Clean08 <- plyr::rename(x = Clean08, 
-                                      replace = c("NES08_D01_MEAN" = "Year08",
-                                                  "NES08COUNTRY" = "Country"))
-
-Clean09 <- plyr::rename(x = Clean09, 
-                                      replace = c("NES09_D01_MEAN" = "Year09",
-                                                  "NES09COUNTRY" = "Country"))
-
-Clean10 <- plyr::rename(x = Clean10, 
-                                      replace = c("NES10_D01_MEAN" = "Year10",
-                                                  "NES10CRNAME" = "Country"))
-
 #### Merge Annual GEM data
@@
 remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre)
+
+############# Import Annual GEM Country Level Data (means) #############
+
+# Import GEM 2009 supportive teaching data
+setwd('~/Assign2Education/GEMData')
+
+GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
+GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
+GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
+GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
+GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
+GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
+GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
+GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
+GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
+GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)
+
+########## Clean Annual GEM NES Datasets ##########
+
+# Draw out Country and D01 only
+Clean01 <- GEM2001[,c("country", "ki01d01")]
+Clean02 <- GEM2002[,c("country", "ki02d01")]
+Clean03 <- GEM2003[,c("country", "ki03d01")]
+Clean04 <- GEM2004[,c("ki04ctry", "ki04d01")]
+Clean05 <- GEM2005[,c("KI05ctry", "KI05D01")]
+Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
+Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
+Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
+Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
+Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]
+
+remove(GEM2001, GEM2002, GEM2003, GEM2004, GEM2005, GEM2006, GEM2007, GEM2008, GEM2009, GEM2010)
+
+# Edit column names for each dataframe
+Clean01 <- plyr::rename(x = Clean01, 
+                                      replace = c("ki01d01" = "2001",
+                                                  "country" = "Country"))
+
+Clean02 <- plyr::rename(x = Clean02, 
+                                      replace = c("ki02d01" = "2002",
+                                                  "country" = "Country"))
+
+Clean03 <- plyr::rename(x = Clean03, 
+                                      replace = c("ki03d01" = "2003",
+                                                  "country" = "Country"))
+
+Clean04 <- plyr::rename(x = Clean04, 
+                                      replace = c("ki04d01" = "2004",
+                                                  "ki04ctry" = "Country"))
+
+Clean05 <- plyr::rename(x = Clean05, 
+                                      replace = c("KI05D01" = "2005",
+                                                  "KI05ctry" = "Country"))
+
+Clean06 <- plyr::rename(x = Clean06, 
+                                      replace = c("KI06D01_mean" = "2006",
+                                                  "KI06CTRY" = "Country"))
+
+Clean07 <- plyr::rename(x = Clean07, 
+                                      replace = c("ki07d01_" = "2007",
+                                                  "ki07ctry" = "Country"))
+
+Clean08 <- plyr::rename(x = Clean08, 
+                                      replace = c("NES08_D01_MEAN" = "2008",
+                                                  "NES08COUNTRY" = "Country"))
+
+Clean09 <- plyr::rename(x = Clean09, 
+                                      replace = c("NES09_D01_MEAN" = "2009",
+                                                  "NES09COUNTRY" = "Country"))
+
+Clean10 <- plyr::rename(x = Clean10, 
+                                      replace = c("NES10_D01_MEAN" = "2010",
+                                                  "NES10CRNAME" = "Country"))
+
+CleanMerge <- cbind(names = c(rownames(Clean01), rownames(Clean02), rownames(Clean03),
+                              rownames(Clean04), rownames(Clean05), rownames(Clean06),
+                              rownames(Clean07), rownames(Clean08), rownames(Clean09),
+                              rownames(Clean10)),
+                    rbind.fill(list(Clean01, Clean02, Clean03, Clean04, Clean05, Clean06,
+                                    Clean07, Clean08, Clean09, Clean10)))
+
+########## Recode Country Names in Annual GEM NES Datasets ##########
+
+# Recode countries
+CleanMerge$Country[CleanMerge$Country == "AUSTRALIA"] <- "Australia"
+CleanMerge$Country[CleanMerge$Country == "AUSTRIA"] <- "Austria"
+CleanMerge$Country[CleanMerge$Country == "BELGIUM"] <- "Belgium"
+CleanMerge$Country[CleanMerge$Country == "CANADA"] <- "Canada"
+CleanMerge$Country[CleanMerge$Country == "CHILE"] <- "Chile"
+CleanMerge$Country[CleanMerge$Country == "CZECH REPUBLIC"] <- "Czech Republic"
+CleanMerge$Country[CleanMerge$Country == "DENMARK"] <- "Denmark"
+CleanMerge$Country[CleanMerge$Country == "ESTONIA"] <- "Estonia"
+CleanMerge$Country[CleanMerge$Country == "FINLAND"] <- "Finland"
+CleanMerge$Country[CleanMerge$Country == "FRANCE"] <- "France"
+CleanMerge$Country[CleanMerge$Country == "GERMANY"] <- "Germany"
+CleanMerge$Country[CleanMerge$Country == "GREECE"] <- "Greece"
+CleanMerge$Country[CleanMerge$Country == "HUNGARY"] <- "Hungary"
+CleanMerge$Country[CleanMerge$Country == "ICELAND"] <- "Iceland"
+CleanMerge$Country[CleanMerge$Country == "IRELAND"] <- "Ireland"
+CleanMerge$Country[CleanMerge$Country == "ISRAEL"] <- "Israel"
+CleanMerge$Country[CleanMerge$Country == "ITALY"] <- "Italy"
+CleanMerge$Country[CleanMerge$Country == "JAPAN"] <- "Japan"
+CleanMerge$Country[CleanMerge$Country == "KOREA"] <- "South Korea"
+CleanMerge$Country[CleanMerge$Country == "MEXICO"] <- "Mexico"
+CleanMerge$Country[CleanMerge$Country == "NETHERLANDS"] <- "Netherlands"
+CleanMerge$Country[CleanMerge$Country == "NEW ZEALAND"] <- "New Zealand"
+CleanMerge$Country[CleanMerge$Country == "NORWAY"] <- "Norway"
+CleanMerge$Country[CleanMerge$Country == "POLAND"] <- "Poland"
+CleanMerge$Country[CleanMerge$Country == "PORTUGAL"] <- "Portugal"
+CleanMerge$Country[CleanMerge$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
+CleanMerge$Country[CleanMerge$Country == "SLOVENIA"] <- "SLOVENIA"
+CleanMerge$Country[CleanMerge$Country == "SPAIN"] <- "Spain"
+CleanMerge$Country[CleanMerge$Country == "SWEDEN"] <- "Sweden"
+CleanMerge$Country[CleanMerge$Country == "SWITZERLAND"] <- "Switzerland"
+CleanMerge$Country[CleanMerge$Country == "TURKEY"] <- "Turkey"
+CleanMerge$Country[CleanMerge$Country == "UNITED KINGDOM"] <- "United Kingdom"
+CleanMerge$Country[CleanMerge$Country == "UK"] <- "United Kingdom"
+
+CleanMerge$Country[CleanMerge$Country == "UNITED STATES"] <- "United States"
+CleanMerge$Country[CleanMerge$Country == "Korea"] <- "South Korea"
+CleanMerge$Country[CleanMerge$Country == "US"] <- "United States"
+
+# This one doesn't work
+CleanMerge$Country[CleanMerge$Country == "USA"] <- "United States"
+
+########## Subset Annual GEM NES Datasets ##########
+
+# Create a vector with OECD countries
+myvars <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'South Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')
+
+# Subset LongGEM with the countries we need
+subset_data <- subset(CleanMerge, Country %in% myvars)
+
+# Delete unnecessary column
+S1 <- subset_data$names <- NULL
+
+########## Change Column names in Subset Annual GEM NES Dataset ##########
+
+# Change merged data from wide to long
+LongGEM<- melt(data = Merged9,
+                  id.vars = c("Country"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Rename columns
+names(LongGEM) <- gsub("variable", "Year", names(LongGEM))
+names(LongGEM) <- gsub("value", "Support", names(LongGEM))
+
+# Arrange subset_data by country and year
+GrandData <- arrange(subset_data, Country, Year)
+
+GrandData1 <- GrandData[order("Country",)]
+
+########### STUCK #############
+
+FinalData <- merge(FinalGEM, GrandData,
+                   union("Country", "Year"))
 

### 2014-12-01 Source/Untitled.Rmd
Cleaned up code to show professor tomorrow

---
title: "Untitled"
author: "Sam"
date: "November 29, 2014"
output: html_document
---

```{r}

library(RCurl)
library(devtools)
install_github(c('rstudio/htmltools',
            'ramnathv/htmlwidgets',
            'christophergandrud/networkD3'))
library(htmltools)
library(htmlwidgets)
library(networkD3)

# Plot
forceNetwork(Links = MisLinks, Nodes = MisNodes,
            Source = "source", Target = "target",
            Value = "value", NodeID = "name",
            Group = "group", opacity = 0.8)
```

```{r}
library(htmltools)
library(htmlwidgets)
library(networkD3)
library(RCurl)
library(devtools)
library(repmis)

Data1 <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, cache = FALSE)

DLinks <- Data1toDF(Data1$PercentPerceived = Energy,
                    array = "links")
DNodes <- Data1toDF(Data1$Country = Energy,
                    array = "nodes")

```

### 2014-12-02 EdEntrePres.Rmd
Created a map of Opportunity data and worked on cleaning WayofTeaching data

---
title: "EdEntrePres"
author: "Sam"
date: "December 2, 2014"
output: ioslides_presentation
---

## Education to Entrepreneurship

```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}

# Library required packages
library(googleVis)
library(countrycode)
library(repmis)

# Import GEM data frame
PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE)

## Add country codes and place new column at beginning of the data frame
# Create a vector of country codes
D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")

# Create a new column and insert the country code vector
PerceivedOpportunities$new.col <- D2

# Reorder columns so country code is first
D3 <- PerceivedOpportunities[,c(15,1:14)]

# Rename first column
D4 <- plyr::rename(x = D3, 
                   replace = c("new.col" = "iso2c"))

# Remove X's in D4 year columns
names(D4) <- gsub("X", "", names(D4))

# Set columns as numeric
D4[,"2001"] <- as.numeric(D4[,"2001"])
D4[,"2002"] <- as.numeric(D4[,"2002"])
D4[,"2003"] <- as.numeric(D4[,"2003"])
D4[,"2004"] <- as.numeric(D4[,"2004"])
D4[,"2005"] <- as.numeric(D4[,"2005"])
D4[,"2006"] <- as.numeric(D4[,"2006"])
D4[,"2007"] <- as.numeric(D4[,"2007"])
D4[,"2008"] <- as.numeric(D4[,"2008"])
D4[,"2009"] <- as.numeric(D4[,"2009"])
D4[,"2010"] <- as.numeric(D4[,"2010"])
D4[,"2011"] <- as.numeric(D4[,"2011"])
D4[,"2012"] <- as.numeric(D4[,"2012"])
D4[,"2013"] <- as.numeric(D4[,"2013"])

# Generate a new column with mean of all other columns
D4$mean <- rowMeans(subset(D4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)

# Drop year columns, leaving only mean column
D4$'2001' <- NULL
D4$'2002' <- NULL
D4$'2003' <- NULL
D4$'2004' <- NULL
D4$'2005' <- NULL
D4$'2006' <- NULL
D4$'2007' <- NULL
D4$'2008' <- NULL
D4$'2009' <- NULL
D4$'2010' <- NULL
D4$'2011' <- NULL
D4$'2012' <- NULL
D4$'2013' <- NULL

# Create 
D4[, 3] <- round(log(D4[, 3]), digits = 2)
```

```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis'}
# Plot
Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                          colors = "['#fff7bc', '#d95f0e']"
))

print(Opp_map, tag = 'chart')

```

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

### 2014-12-02 Misc/TrialFile.Rmd
Created a map of Opportunity data and worked on cleaning WayofTeaching data

@@
 
-``` {r}
+``` {r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
+
+# Country code
+rm(CleanGEM)
+dfs <- ls()[1:max(grep(pattern = 'Clean[0-1]*', x = ls()))]
+
+for (i in dfs){
+  message(i)
+  temp <- get(i)
+  names_temp <- names(temp)
+  temp[, 'year'] <- names_temp[2]
+  names(temp) <- c('Country', 'WayofTeaching', 'year')
+
+    if (i == 'Clean01') {
+      cleaned <- temp
+  } else if (i != 'Clean01'){
+      cleaned <- rbind(cleaned, temp)
+  }
+}
+
+# Country code
+# Subset
 
@@
 # Arrange subset_data by country and year
-GrandData <- arrange(subset_data, Country, Year)
+GData <- arrange(subset_data, Country, Year)
 
-GrandData1 <- GrandData[order("Country",)]
+GData <- GData[order("Country",)]
 

### 2014-12-02 EdEntrePres.Rmd
Maps, new data cleaning
Indicated where we are stuck
Fixed the avg figure for presentation

@@
 
-## Education to Entrepreneurship
+## Education -> Entrepreneurship
+
+## Different Country-level Perceptions of Good Opportunities to Start a Business
 
@@
 # Import GEM data frame
-PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE)
+PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE, na.strings = "-")
 
@@
 
-## Slide with Bullets
+## Distribution of Perception Differences
 
-- Bullet 1
-- Bullet 2
-- Bullet 3
+```{r}
+hist(D4$mean)
 
+```
 ## Slide with R Code and Output

### 2014-12-02 FromEducationToEntrepreneurship.Rmd
Created a map of Opportunity data and worked on cleaning WayofTeaching data

@@
 *Introduction to Collaborative Social Science Data Analysis*
+
+(The impact of self confidence on entrepreneurship.)
 
@@
 
-#### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System
+#### Key Explanatory Variable: Degree of Self-confidence Reinforcement within the Education System
 
 As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem.
-To do so, we decided to incorporate GEM indicators that relate to self-esteem and confidence.
+To do so, we decided to incorporate GEM indicators that relate to self- confidence.
 First, we included GEM survey data on the average "perceived capabilities" of an individual (18-64) in a given country to start a business.
 Second, we included additional GEM data on how the "fear of failure" could deter an average individual (18-64) in a country to become an entrepreneur.
-Both of these data sets indicate the average percentage for each characteristic at the country-level.
+Both of these data sets indicate the average percentage for each characteristic at the country-level but they are solely describing a level of self-confidence in one's abilities to become an entrepreneur.
+We chose to use them as such even if they do not trace the specific causal chain between education systems and entrepreneurship that we intend to focus on.
+
+In order to trace specifically how supportive of one's self-confidence a given education system is, we chose to use one specific item of the GEM [National Experts Survey (NES)](http://www.gemconsortium.org/Data-Collection) as a proxy, namely D01.
+
+"In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative"
+
+Regarding this statement, the experts surveyed had to state whether it is:
+
+1 completely false
+2 somewhat false
+3 neither true nor false
+4 somewhat true
+5 completely true
+
+97 do not know
+98 not applicable
 
@@
 
-GEM data was embedded in an interactive database and was difficult to extract automatically without writing a program.
+GEM data was embedded in an interactive database and was difficult to extract automatically without writing a programme.
 To simplify this process, we downloaded the necessary *.csv* files and saved them in our GitHub repository (to reduce complexity, we deleted the first three unnecessary rows before saving).
@@
 
-Cleaning the GEM data required deleting unnecessary characters in the year columns, changing the years from columns to rows (changing the data from wide to long), and changing the column names to describe which data was being analyzed.
+Cleaning the GEM data required deleting unnecessary characters in the year columns, changing the years from columns to rows (changing the data from wide to long), and changing the column names to describe which data was being analysed.
 In the process of doing this we created new data sets for each of these survey questions, which were called C*dataset* (clean followed by the data set name).
@@
 summary(R3)
+
 ```

### 2014-12-02 Presentation/PresMisc/MiscPresStuff.Rmd
Reorganized repository and created histogram

---
title: "Untitled"
author: "Sam"
date: "December 2, 2014"
output: ioslides_presentation
---

## R Markdown
```{r}
# Create googleVis chart
line_plot <- gvisLineChart(D1)
plot(line_plot)

# Create vector of OECD countries
places <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')

# Find latitude and longitude for OECD countries
geocode(places)

# Generate a map
qmap(location = 'Australia', zoom = 4)
```
## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

### 2014-12-02 Presentation/EdEntrePres.Rmd
Reorganized repository and created histogram
Created interactive and static histograms

--- 2014-12-02 EdEntrePres.Rmd
@@
 ## Distribution of Perception Differences
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library(ggvis)
 
-```{r}
-hist(D4$mean)
+D4 %>% ggvis(~mean, fill := "#2c7fb8") %>% layer_histograms(width = 0.2)
 
 ```
+
 ## Slide with R Code and Output
 
-```{r}
-summary(cars)
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+D4 %>% 
+  ggvis(~mean, fill := "#2c7fb8") %>% 
+  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
+                   center = input_slider(0, 2, step = 0.05, label = "center"))
+
 ```
@@
 ```{r, echo=FALSE}
-plot(cars)
+
 ```

### 2014-12-02 index.Rmd
second commit
Added web content

@@
 ---
-title: 'Index'
+title: 'From Education to Entrepreneurship'
 author: "Sam"
@@
 
-### Under Construction
+### Under construction, but here's a preview
+
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+
+# Library required packages
+library(googleVis)
+library(countrycode)
+library(repmis)
+
+# Import GEM data frame
+PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE, na.strings = "-")
+
+## Add country codes and place new column at beginning of the data frame
+# Create a vector of country codes
+D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")
+
+# Create a new column and insert the country code vector
+PerceivedOpportunities$new.col <- D2
+
+# Reorder columns so country code is first
+D3 <- PerceivedOpportunities[,c(15,1:14)]
+
+# Rename first column
+D4 <- plyr::rename(x = D3, 
+                   replace = c("new.col" = "iso2c"))
+
+# Remove X's in D4 year columns
+names(D4) <- gsub("X", "", names(D4))
+
+# Set columns as numeric
+D4[,"2001"] <- as.numeric(D4[,"2001"])
+D4[,"2002"] <- as.numeric(D4[,"2002"])
+D4[,"2003"] <- as.numeric(D4[,"2003"])
+D4[,"2004"] <- as.numeric(D4[,"2004"])
+D4[,"2005"] <- as.numeric(D4[,"2005"])
+D4[,"2006"] <- as.numeric(D4[,"2006"])
+D4[,"2007"] <- as.numeric(D4[,"2007"])
+D4[,"2008"] <- as.numeric(D4[,"2008"])
+D4[,"2009"] <- as.numeric(D4[,"2009"])
+D4[,"2010"] <- as.numeric(D4[,"2010"])
+D4[,"2011"] <- as.numeric(D4[,"2011"])
+D4[,"2012"] <- as.numeric(D4[,"2012"])
+D4[,"2013"] <- as.numeric(D4[,"2013"])
+
+# Generate a new column with mean of all other columns
+D4$mean <- rowMeans(subset(D4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
+                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)
+
+# Drop year columns, leaving only mean column
+D4$'2001' <- NULL
+D4$'2002' <- NULL
+D4$'2003' <- NULL
+D4$'2004' <- NULL
+D4$'2005' <- NULL
+D4$'2006' <- NULL
+D4$'2007' <- NULL
+D4$'2008' <- NULL
+D4$'2009' <- NULL
+D4$'2010' <- NULL
+D4$'2011' <- NULL
+D4$'2012' <- NULL
+D4$'2013' <- NULL
+
+# Create 
+D4[, 3] <- round(log(D4[, 3]), digits = 2)
+```
+
+# Variation in Perceived Opportunities in OECD
+```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis'}
+# Plot
+Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
+                      colorvar = 'mean',
+                      options = list(
+                        colors = "['#fff7bc', '#d95f0e']"
+))
+
+print(Opp_map, tag = 'chart')
+
+```
+
+# Distribution of Perceived Opportunities in OECD Countries
+
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+D4 %>% 
+  ggvis(~mean, fill := "#2c7fb8") %>% 
+  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
+                   center = input_slider(0, 2, step = 0.05, label = "center"))

### 2014-12-02 index.Rmd
Added lib and fixed index page
Realized ggvis isn't interactive w/ knitted docs, changed web content

@@
 
-# Variation in Perceived Opportunities in OECD
+### Variation in Perceived Opportunities in OECD
 ```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis'}
@@
 
-# Distribution of Perceived Opportunities in OECD Countries
+<br>
+
+<br
+
+### Distribution of Perceived Opportunities in OECD Countries
 
 ```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library(ggvis)
 
-D4 %>% 
-  ggvis(~mean, fill := "#2c7fb8") %>% 
-  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
-                   center = input_slider(0, 2, step = 0.05, label = "center"))
+D4 %>% ggvis(~mean, fill := "#2c7fb8") %>% layer_histograms(width = 0.2)
+
+#D4 %>% 
+ # ggvis(~mean, fill := "#2c7fb8") %>% 
+  #layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
+   #                center = input_slider(0, 2, step = 0.05, label = "center"))

### 2014-12-02 Presentation/EdEntrePres.Rmd
Added new histogram, Zelig sim, and cleaned up regression output table

@@
 ---
-title: "EdEntrePres"
-author: "Sam"
+title: "The Impact of Education <br>
+on Entrepreneurship"
+author: "Sam Dundon and Thierry Racaud"
 date: "December 2, 2014"
@@
 
-## Education -> Entrepreneurship
+## From Education to Entrepreneurship
+
+*Text from Thierry*
 
@@
 
-```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis'}
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
 # Plot
@@
 ## Slide with R Code and Output
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library(stargazer)
 
-```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+# Create new DF for PerceivedOpportunities
+D5 <- PerceivedOpportunities
 
-D4 %>% 
-  ggvis(~mean, fill := "#2c7fb8") %>% 
-  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
-                   center = input_slider(0, 2, step = 0.05, label = "center"))
+# Eliminate X's in header
+names(D5) <- gsub("X", "", names(D5))  
+D5$new.col <- NULL
+
+# Create descriptive statistics table
+T1 <- stargazer(D5, type = 'html', column.sep.width = "20pt", digits = 2)
+```
+## Slide with Plot
+
+```{r, echo =FALSE, cache=FALSE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+library(Zelig)
+library(ZeligMultilevel)
+
+# Import CompleteData
+CompleteData <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE)
+
+CompleteData_omit <- na.omit(CompleteData)
+
+# Run a RE regression
+Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach, data = CompleteData_omit, model = "ls")
+
+# Set range of PercentPerceived values in simulation
+x.out2 <- setx(Z1, PercentPerceived = 20:70)
+
+# Run simulation (default 1000 trials)
+simz2 <- sim(Z1, x = x.out2)
+
+# Adjust margins
+par(mar=c(5,5,5,5))
 
@@
 
-## Slide with Plot
-
-```{r, echo=FALSE}
-
+```{r, echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+# Plot simulation
+plot(simz2, xlab = 'PercentPerceived', ylab = 'PercentIntention | PercentPerceived')
 ```

### 2014-12-02 Presentation/PresMisc/MiscPresStuff.Rmd
Added new histogram, Zelig sim, and cleaned up regression output table

@@
 
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+# Interactive histgram (isn't interactive in knitted docs)
+D4 %>% 
+  ggvis(~mean, fill := "#2c7fb8") %>% 
+  layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
+                   center = input_slider(0, 2, step = 0.05, label = "center"))
+
+```
+
 - Bullet 1

### 2014-12-03 Presentation/EdEntrePres.Rmd
Added table to map slide
Minor edits to pres

@@
                       options = list(
-                        colors = "['#fff7bc', '#d95f0e']"
+                        colors = "['#ece7f2', '#2b8cbe']"
 ))
+
+# Duplicate D4 df
+Dropped4 <- D4
+
+# Drop iso2c in Dropped4
+Dropped4$iso2c <- NULL
+
+Table <- gvisTable(Dropped4, 
+               options=list(width=230, height=300))
+
+MT <- gvisMerge(Opp_map, Table, horizontal = TRUE)
 
@@
 ```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+# Library stargazer
 library(stargazer)
@@
 
-```{r, echo =FALSE, cache=FALSE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+```{r, echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
 
@@
 ```
+
+## New
+```{r, echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+```

### 2014-12-03 index.Rmd
Added temp gvis hist
Added chart to troubleshoot

@@
    #                center = input_slider(0, 2, step = 0.05, label = "center"))
+
+```
+
+```{r}
+library(googleVis)
+
+set.seed(123)
+Dropped4=data.frame(A=rpois(100, 20),
+             B=rpois(100, 5),
+             C=rpois(100, 50))
+print( 
+  gvisHistogram(Dropped4, options=list(
+    legend="{ position: 'top', maxLines: 2 }",
+    colors="['#5C3292', '#1A8763', '#871B47']",
+    width=600, gvis.plot.tag = 'chart'),
+    chartid="Histogram")
+)
+```
+
+```{r}
+library(googleVis)
+
+# Import CompleteData
+C1 <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", stringsAsFactors = TRUE)
+
+# Drop unecessary column in C1
+C1$X <- NULL
+
+C1$WayofTeach <- NULL
+C1$PercentFear <- NULL
+C1$PercentNascent <- NULL
+C1$PercentOwner <- NULL
+C1$PercentPerceived <- NULL
+C1$PercentIntention <- NULL
+
+# Change format of Year column
+C1[,"Year"] <- as.factor(C1[,"Year"])
+
+##### Can't get gsub to change date format
+names(C1$Year) <- gsub("2001", "2001-01-01", names(C1$Year))
+
+C2 <- as.Date(C1$Year, origin = "2001-01-01")
+
+# Set value as numeric
+C1[,"PercentOpportunities"] <- as.numeric(C1[,"PercentOpportunities"])
+
+A1 <- gvisAnnotatedTimeLine(C1, datevar = "Year", numvar = "PerceivedOpportunities", idvar = "Country", 
+    titlevar = "Title", annotationvar = "Annotation", options = list(displayAnnotations = TRUE, 
+        legendPosition = "newRow", width = 600, height = 300), chartid = "ATL")
+
+plot(A1)
+```

### 2014-12-03 GEMDataSource.Rmd
Completed data merge in R

@@
 library(foreign)
+library(countrycode)
 
@@
 
-############# Import Annual GEM Country Level Data (means) #############
-
-# Import GEM 2009 supportive teaching data
-setwd('~/Assign2Education/GEMData')
-
-GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
-GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
-GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
-GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
-GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
-GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
-GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
-GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
-GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
-GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)
-
 ##################### Clean GEM Survey Data  ###################
@@
 
-########## Clean Annual GEM NES Datasets ##########
+##################### Merge GEM Survey Data  ###################
+
+MergedGEM <- merge(CCurrentOwner, CEntreIntention,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+MergedGem2 <- merge(CFearFail, CNascentEntre,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+MergedGem3 <- merge(CPerceivedCapabilities, MergedGEM,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+MergedGem4 <- merge(MergedGem2, MergedGem3,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+FinalGEM <- merge(MergedGem4, CPerceivedOpportunities,
+                   union("Country", "Year"),
+                   all = TRUE)
+
+# Convert percent columns from character to numeric
+FinalGEM[,"PercentPerceived"] <- as.numeric(FinalGEM[,"PercentPerceived"])
+FinalGEM[,"PercentFear"] <- as.numeric(FinalGEM[,"PercentFear"])
+FinalGEM[,"PercentNascent"] <- as.numeric(FinalGEM[,"PercentNascent"])
+FinalGEM[,"PercentOwner"] <- as.numeric(FinalGEM[,"PercentOwner"])
+FinalGEM[,"PercentIntention"] <- as.numeric(FinalGEM[,"PercentIntention"])
+FinalGEM[,"PercentOpportunities"] <- as.numeric(FinalGEM[,"PercentOpportunities"])
+
+# Remove unncessary data from environment
+remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre)
+
+### Insert iso2c country code for easier merging
+
+## Add country codes and place new column at beginning of the data frame
+
+# Create a vector of country codes
+F1 <- countrycode(FinalGEM$Country, "country.name", "iso2c")
+
+# Create a new column and insert the country code vector
+FinalGEM$new.col <- F1
+
+# Change the order of columns so country code is first
+FinalGEM <- FinalGEM[,c(9,1:8)]
+
+# Change the name of new.col
+names(FinalGEM) <- gsub("new.col", "iso2c", names(FinalGEM))
+
+##################### Import GEM NES National Survey Data  ###################
+
+# Set working directory
+setwd('~/Assign2Education/GEMData')
+
+# Import GEM NES 2001-2010 Data
+GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
+GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
+GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
+GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
+GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
+GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
+GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
+GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
+GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
+GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)
+
+##################### Clean GEM NES National Survey Data  ###################
 
@@
 
+# Remove unnecessary dataframes from environment
 remove(GEM2001, GEM2002, GEM2003, GEM2004, GEM2005, GEM2006, GEM2007, GEM2008, GEM2009, GEM2010)
@@
 
-#### Merge Annual GEM data
+# Clean and cbind ataframes
+dfs <- ls()[1:max(grep(pattern = 'Clean[0-1]*', x = ls()))]
 
-MergedGEM <- merge(CCurrentOwner, CEntreIntention,
-                   union("Country", "Year"),
+for (i in dfs){
+  message(i)
+  temp <- get(i)
+  names_temp <- names(temp)
+  temp[, 'year'] <- names_temp[2]
+  names(temp) <- c('Country', 'WayofTeaching', 'year')
+
+    if (i == 'Clean01') {
+      cleaned <- temp
+  } else if (i != 'Clean01'){
+      cleaned <- rbind(cleaned, temp)
+  }
+}
+
+## Add country codes and place new column at beginning of the data frame
+
+# Create a vector of country codes
+W1 <- countrycode(cleaned$Country, "country.name", "iso2c")
+
+# Create a new column and insert the country code vector
+cleaned$new.col <- W1
+
+# Change the order of columns so country code is first
+W2 <- cleaned[,c(4,1:3)]
+
+# Change the name of new.col
+names(W2) <- gsub("new.col", "iso2c", names(W2))
+
+# Capitalize 'year' 
+names(W2) <- gsub("year", "Year", names(W2))
+
+## Subset W2 to OECD countries
+
+# Create matrix of OECD countries by iso2c code
+myvars <- c('MX','CA','US','FR','AU','AT','BE','CL','CZ','DK','EE','FI','DE','HU', 'IS','IE','IL',
+            'IT','JP','KR','LU', 'NL','NZ','NO','PL','PT','SK','SI', 'ES','SE','CH','TR','GB','US','GR')
+
+# Subset W2 with myvars
+subW2 <- subset(W2, iso2c %in% myvars)
+
+# Delete unnecessary column
+subW2$row.names <- NULL
+
+##################### Merge two GEM Datasets  ###################
+
+# Merge subW2 and FinalGem
+CompleteData <- merge(subW2, FinalGEM,
+                   union("iso2c", "Year"),
                    all = TRUE)
 
-MergedGem2 <- merge(CFearFail, CNascentEntre,
-                   union("Country", "Year"),
-                   all = TRUE)
+# Delete conflicting country names
+CompleteData$Country.x <- NULL
+CompleteData$Country.y <- NULL
 
-MergedGem3 <- merge(CPerceivedCapabilities, MergedGEM,
-                   union("Country", "Year"),
-                   all = TRUE)
+## Add a column with country names
 
-MergedGem4 <- merge(MergedGem2, MergedGem3,
-                   union("Country", "Year"),
-                   all = TRUE)
+# Create a vector of names
+C1 <- countrycode(CompleteData$iso2c, "iso2c", "country.name")
 
-FinalGEM <- merge(MergedGem4, CPerceivedOpportunities,
-                   union("Country", "Year"),
-                   all = TRUE)
+# Insert new row with C1
+CompleteData$new.col <- C1
 
-# Convert percent columns from character to numeric
-FinalGEM[,"PercentPerceived"] <- as.numeric(FinalGEM[,"PercentPerceived"])
-FinalGEM[,"PercentFear"] <- as.numeric(FinalGEM[,"PercentFear"])
-FinalGEM[,"PercentNascent"] <- as.numeric(FinalGEM[,"PercentNascent"])
-FinalGEM[,"PercentOwner"] <- as.numeric(FinalGEM[,"PercentOwner"])
-FinalGEM[,"PercentIntention"] <- as.numeric(FinalGEM[,"PercentIntention"])
-FinalGEM[,"PercentOpportunities"] <- as.numeric(FinalGEM[,"PercentOpportunities"])
+# Reorganize columns to make Country second
+CompleteData <- CompleteData[,c(1,10,2:9)]
 
-# Remove unncessary data from environment
-remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre)
-
-####### Import tempfix for GEM data (created this by copying data frame (extra code for generating data frame is in misc/TrialFile.Rmd), editing outide R, and saving .csv in repository)
-
-GEMAnnualData <- repmis::source_data("https://github.com/SamDund/Assign2Education/raw/master/GEMData/Gemyears.csv", header = TRUE, cache = FALSE)
-
-##### Clean and merge tempfix GEM Data ####
-
-# Change column names
-names(GEMAnnualData) <- gsub("Year01", "2001", names(GEMAnnualData))
-names(GEMAnnualData) <- gsub("Year02", "2002", names(GEMAnnualData))
-names(GEMAnnualData) <- gsub("Year03", "2003", names(GEMAnnualData))
-names(GEMAnnualData) <- gsub("Year04", "2004", names(GEMAnnualData))
-names(GEMAnnualData) <- gsub("Year05", "2005", names(GEMAnnualData))
-names(GEMAnnualData) <- gsub("Year06", "2006", names(GEMAnnualData))
-names(GEMAnnualData) <- gsub("Year07", "2007", names(GEMAnnualData))
-names(GEMAnnualData) <- gsub("Year08", "2008", names(GEMAnnualData))
-names(GEMAnnualData) <- gsub("Year09", "2009", names(GEMAnnualData))
-names(GEMAnnualData) <- gsub("Year10", "2010", names(GEMAnnualData))
-
-# Change years from columns to rows and create CleanGEM
-CleanGEM <- melt(data = GEMAnnualData,
-                 id.vars = c("Country"),
-                 measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010"))
-
-# Rename columns
-CleanGEM <- plyr::rename(x = CleanGEM,
-                         replace = c("variable" = "Year",
-                                     "value" = "WayofTeach"))
-
-# Merge Clean CleanGEM with FinalGEM 
-CompleteData <- merge(CleanGEM, FinalGEM,
-                   union("Country", "Year"),
-                   all = TRUE)
-
-write.csv(CompleteData, file = "CompleteData.csv")
+# Rename Country column
+names(CompleteData) <- gsub("new.col", "Country", names(CompleteData))
 
@@
 remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre, Clean01, Clean02, Clean03, Clean04, Clean05, Clean06, Clean07, Clean08, Clean09, Clean10, CleanGEM, FinalGEM, GEMAnnualData, SupportiveTeaching)
+
+write.csv(CompleteData, file = "CompleteData.csv")
 

### 2014-12-03 Presentation/EdEntrePres.Rmd
Attempted chart...
Completed data merge in R

@@
 library(repmis)
+
+#### Wrong Datasest
 
@@
 ```
+
+## WayofTeaching
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+# Import GEM data frame
+WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, cache = FALSE, na.strings = "-")
+
+## Add country codes and place new column at beginning of the data frame
+# Create a vector of country codes
+W1 <- countrycode(WayofTeaching$Country, "country.name", "iso2c")
+
+# Create a new column and insert the country code vector
+WayofTeaching$new.col <- W1
+
+# Drop unnecessary column 1
+WayofTeaching$X <- NULL
+
+# Reorder columns so country code is first
+W2 <- WayofTeaching[,c(10,1:9)]
+
+# Rename first column
+W3 <- plyr::rename(x = W2, 
+                   replace = c("new.col" = "iso2c"))
+
+# Remove X's in D4 year columns
+names(D4) <- gsub("X", "", names(D4))
+
+# Set columns as numeric
+D4[,"2001"] <- as.numeric(D4[,"2001"])
+D4[,"2002"] <- as.numeric(D4[,"2002"])
+D4[,"2003"] <- as.numeric(D4[,"2003"])
+D4[,"2004"] <- as.numeric(D4[,"2004"])
+D4[,"2005"] <- as.numeric(D4[,"2005"])
+D4[,"2006"] <- as.numeric(D4[,"2006"])
+D4[,"2007"] <- as.numeric(D4[,"2007"])
+D4[,"2008"] <- as.numeric(D4[,"2008"])
+D4[,"2009"] <- as.numeric(D4[,"2009"])
+D4[,"2010"] <- as.numeric(D4[,"2010"])
+D4[,"2011"] <- as.numeric(D4[,"2011"])
+D4[,"2012"] <- as.numeric(D4[,"2012"])
+D4[,"2013"] <- as.numeric(D4[,"2013"])
+
+# Generate a new column with mean of all other columns
+D4$mean <- rowMeans(subset(D4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
+                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)
+
+# Drop year columns, leaving only mean column
+D4$'2001' <- NULL
+D4$'2002' <- NULL
+D4$'2003' <- NULL
+D4$'2004' <- NULL
+D4$'2005' <- NULL
+D4$'2006' <- NULL
+D4$'2007' <- NULL
+D4$'2008' <- NULL
+D4$'2009' <- NULL
+D4$'2010' <- NULL
+D4$'2011' <- NULL
+D4$'2012' <- NULL
+D4$'2013' <- NULL
+
+# Create 
+D4[, 3] <- round(log(D4[, 3]), digits = 2)
+```
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+# Plot
+Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
+                      colorvar = 'mean',
+                      options = list(
+                        colors = "['#ece7f2', '#2b8cbe']"
+))
+
+# Duplicate D4 df
+Dropped4 <- D4
+
+# Drop iso2c in Dropped4
+Dropped4$iso2c <- NULL
+
+Table <- gvisTable(Dropped4, 
+               options=list(width=230, height=300))
+
+MT <- gvisMerge(Opp_map, Table, horizontal = TRUE)
+
+print(Opp_map, tag = 'chart')
+
+```
+
 ## Slide with Plot

### 2014-12-03 Presentation/PresMisc/MiscPresStuff.Rmd
Completed data merge in R

@@
 ```{r, echo=FALSE}
-plot(cars)
+# sankeyNetwork
+library(RCurl)
+library(devtools)
+install_github(c('rstudio/htmltools',
+            'ramnathv/htmlwidgets',
+            'christophergandrud/networkD3'))
+library(htmltools)
+library(htmlwidgets)
+library(networkD3)
+
+URL <- "https://raw.githubusercontent.com/christophergandrud/d3Network/sankey/JSONdata/energy.json"
+Energy <- getURL(URL, ssl.verifypeer = FALSE)
+
+# Convert to data frame
+EngLinks <- JSONtoDF(jsonStr = Energy, array = "links")
+EngNodes <- JSONtoDF(jsonStr = Energy, array = "nodes")
+
 ```

### 2014-12-03 GEMDataSource.Rmd
Edit Zelig sim and write csv of WayofTeaching Data

@@
 
+write.csv(subW2, file = "WayofTeaching")
+
 ##################### Merge two GEM Datasets  ###################
@@
 # Run linear regression R1
-R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)
+R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeaching, data = CompleteData)
 
@@
 # Run linear regression R2
-R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)
+R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeaching, data = CompleteData)
 
@@
 # Run linear regression R3
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)
+R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeaching, data = CompleteData)
 

### 2014-12-03 Presentation/EdEntrePres.Rmd
Edit Zelig sim and write csv of WayofTeaching Data

--- 2014-12-03 Presentation/EdEntrePres.Rmd
@@
                    replace = c("new.col" = "iso2c"))
+
+# Remove X's in D4 year columns
+names(D4) <- gsub("X", "", names(D4))
+
+# Set columns as numeric
+D4[,"2001"] <- as.numeric(D4[,"2001"])
+D4[,"2002"] <- as.numeric(D4[,"2002"])
+D4[,"2003"] <- as.numeric(D4[,"2003"])
+D4[,"2004"] <- as.numeric(D4[,"2004"])
+D4[,"2005"] <- as.numeric(D4[,"2005"])
+D4[,"2006"] <- as.numeric(D4[,"2006"])
+D4[,"2007"] <- as.numeric(D4[,"2007"])
+D4[,"2008"] <- as.numeric(D4[,"2008"])
+D4[,"2009"] <- as.numeric(D4[,"2009"])
+D4[,"2010"] <- as.numeric(D4[,"2010"])
+D4[,"2011"] <- as.numeric(D4[,"2011"])
+D4[,"2012"] <- as.numeric(D4[,"2012"])
+D4[,"2013"] <- as.numeric(D4[,"2013"])
+
+# Save cleaned df
+Opp1 <- D4
+
+# Generate a new column with mean of all other columns
+D4$mean <- rowMeans(subset(D4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
+                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)
+
+# Drop year columns, leaving only mean column
+D4$'2001' <- NULL
+D4$'2002' <- NULL
+D4$'2003' <- NULL
+D4$'2004' <- NULL
+D4$'2005' <- NULL
+D4$'2006' <- NULL
+D4$'2007' <- NULL
+D4$'2008' <- NULL
+D4$'2009' <- NULL
+D4$'2010' <- NULL
+D4$'2011' <- NULL
+D4$'2012' <- NULL
+D4$'2013' <- NULL
+
+# Create 
+D4[, 3] <- round(log(D4[, 3]), digits = 2)
+```
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+# Plot
+Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
+                      colorvar = 'mean',
+                      options = list(
+                        colors = "['#ece7f2', '#2b8cbe']"
+))
+
+# Duplicate D4 df
+Dropped4 <- D4
+
+# Drop iso2c in Dropped4
+Dropped4$iso2c <- NULL
+
+Table <- gvisTable(Dropped4, 
+               options=list(width=230, height=300))
+
+MT <- gvisMerge(Opp_map, Table, horizontal = TRUE)
+
+print(Opp_map, tag = 'chart')
+
+```
+
+## Distribution of Perception Differences
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library(ggvis)
+
+line_plot <- gvisLineChart(Opp1)
+print(line_plot, tag = 'chart')
+
+```
+
+## Slide with R Code and Output
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+```
+
+## WayofTeaching
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+# Import GEM data frame
+WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, cache = FALSE, na.strings = "-")
+
+# Drop unnecessary column 1
+WayofTeaching$X <- NULL
 
@@
 
-## Distribution of Perception Differences
-```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-library(ggvis)
-
-D4 %>% ggvis(~mean, fill := "#2c7fb8") %>% layer_histograms(width = 0.2)
-
-```
-
-## Slide with R Code and Output
-```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-
-# Library stargazer
-library(stargazer)
-
-# Create new DF for PerceivedOpportunities
-D5 <- PerceivedOpportunities
-
-# Eliminate X's in header
-names(D5) <- gsub("X", "", names(D5))  
-D5$new.col <- NULL
-
-# Create descriptive statistics table
-T1 <- stargazer(D5, type = 'html', column.sep.width = "20pt", digits = 2)
-```
 ## Slide with Plot
@@
 # Run a RE regression
-Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach, data = CompleteData_omit, model = "ls")
+Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeaching, data = CompleteData_omit, model = "ls")
 

### 2014-12-03 Presentation/PresMisc/MiscPresStuff.Rmd
Edit Zelig sim and write csv of WayofTeaching Data

@@
 ```
+
+```{r}
+# Histogram
+D4 %>% ggvis(~mean, fill := "#2c7fb8") %>% layer_histograms(width = 0.2)
+
+# Library stargazer
+library(stargazer)
+
+# Create new DF for PerceivedOpportunities
+D5 <- PerceivedOpportunities
+
+# Eliminate X's in header
+names(D5) <- gsub("X", "", names(D5))  
+D5$new.col <- NULL
+
+# Create descriptive statistics table
+T1 <- stargazer(D5, type = 'html', column.sep.width = "20pt", digits = 2)
+
+```

### 2014-12-03 GEMDataSource.Rmd
D01 Indicator - Flaws

--- 2014-12-01 GEMDataSource.Rmd
@@
 
-############# Import data from GEM Survey #############
+#### Import data from GEM Survey ####
 
@@
 
-############# Import Annual GEM Country Level Data (means) #############
-
 # Import GEM 2009 supportive teaching data
@@
 
-##################### Clean GEM Survey Data  ###################
+#### Clean data using tidy ####
 
 ### Clean FearFail ###
-# Question: Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
+# Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
 
@@
 ### Clean CurrentOwner ###
-# Question: Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid sallaries, wages, or any other payments to the owners for more than 42 months
+# Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid sallaries, wages, or any other payments to the owners for more than 42 months
 
@@
 
-########## Clean Annual GEM NES Datasets ##########
-
+### Clean GEM NES Datasets
 # Draw out Country and D01 only
@@
 # Edit column names for each dataframe
+
 Clean01 <- plyr::rename(x = Clean01, 
-                                      replace = c("ki01d01" = "2001",
+                                      replace = c("ki01d01" = "Year01",
                                                   "country" = "Country"))
@@
 Clean02 <- plyr::rename(x = Clean02, 
-                                      replace = c("ki02d01" = "2002",
+                                      replace = c("ki02d01" = "Year02",
                                                   "country" = "Country"))
@@
 Clean03 <- plyr::rename(x = Clean03, 
-                                      replace = c("ki03d01" = "2003",
+                                      replace = c("ki03d01" = "Year03",
                                                   "country" = "Country"))
@@
 Clean04 <- plyr::rename(x = Clean04, 
-                                      replace = c("ki04d01" = "2004",
+                                      replace = c("ki04d01" = "Year04",
                                                   "ki04ctry" = "Country"))
@@
 Clean05 <- plyr::rename(x = Clean05, 
-                                      replace = c("KI05D01" = "2005",
+                                      replace = c("KI05D01" = "Year05",
                                                   "KI05ctry" = "Country"))
@@
 Clean06 <- plyr::rename(x = Clean06, 
-                                      replace = c("KI06D01_mean" = "2006",
+                                      replace = c("KI06D01_mean" = "Year06",
                                                   "KI06CTRY" = "Country"))
-
 Clean07 <- plyr::rename(x = Clean07, 
-                                      replace = c("ki07d01_" = "2007",
+                                      replace = c("ki07d01_" = "Year07",
                                                   "ki07ctry" = "Country"))
@@
 Clean08 <- plyr::rename(x = Clean08, 
-                                      replace = c("NES08_D01_MEAN" = "2008",
+                                      replace = c("NES08_D01_MEAN" = "Year08",
                                                   "NES08COUNTRY" = "Country"))
@@
 Clean09 <- plyr::rename(x = Clean09, 
-                                      replace = c("NES09_D01_MEAN" = "2009",
+                                      replace = c("NES09_D01_MEAN" = "Year09",
                                                   "NES09COUNTRY" = "Country"))
@@
 Clean10 <- plyr::rename(x = Clean10, 
-                                      replace = c("NES10_D01_MEAN" = "2010",
+                                      replace = c("NES10_D01_MEAN" = "Year10",
                                                   "NES10CRNAME" = "Country"))
 
-#### Merge Annual GEM data
-
+#### Merge the data ####
 MergedGEM <- merge(CCurrentOwner, CEntreIntention,
@@
 
-####### Import tempfix for GEM data (created this by copying data frame (extra code for generating data frame is in misc/TrialFile.Rmd), editing outide R, and saving .csv in repository)
+# Import tempfix for GEM data (created this by copying data frame, editing outide R, and saving .csv in repository)
 
@@
 
-write.csv(CompleteData, file = "CompleteData.csv")
-
-# Remove unncessary data from environment
-remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre, Clean01, Clean02, Clean03, Clean04, Clean05, Clean06, Clean07, Clean08, Clean09, Clean10, CleanGEM, FinalGEM, GEMAnnualData, SupportiveTeaching)
-
 ```
@@
 # Run linear regression R3
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach + Country, data = CompleteData)
+R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + lm(WayofTeach) + Country, data = CompleteData)
 
@@
 labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
-            'National Level Avg Perceived Good Opportunities', 'Way of Teaching', 'Austria',
-            'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Finland', 'France',
-            'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan',
-            'Korea (South)', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland',
-            'Portugal', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey',
-            'United Kingdom','United States', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities', '(Intercept)')
+            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')
 
@@
 # Omit omitted data from simulation
-CompleteData_omit <- na.omit(CompleteData)
+CompleteData_omit <- na.omit(CompleteDataset)
 
 # Run a least squares regression with Zelig
-Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeach, data = CompleteData_omit, model = "ls")
-
+Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteData_omit, model = "ls")
 ```
@@
 
-H1 <- hist(CompleteData$PercentPerceived)
-
 # Set range of PercentPerceived values in simulation
-x.out2 <- setx(Z1, PercentPerceived = 20:70)
+x.out2 <- setx(Z1, PercentPerceived = 9:67)
 
@@
 # Adjust margins
-par(mar=c(5,5,5,5))
+par(mar=c(2,2,2,2))
 
 # Plot simulation
-plot(simz2, xlab = 'PercentPerceived', ylab = 'PercentIntention | PercentPerceived')
+plot(simz2, xlab= 'PercentPerceived')
 

### 2014-12-03 Misc/TrialFile.Rmd

@@
 ``` {r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
+library(plyr)
+library(repmis)
+library(tidyr)
+library(reshape2)
+library(foreign)
+library(countrycode)
 
-# Country code
-rm(CleanGEM)
+# Set working directory
+setwd('~/Assign2Education/GEMData')
+
+# Import GEM NES 2001-2010 Data
+GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
+GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
+GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
+GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
+GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
+GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
+GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
+GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
+GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
+GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)
+
+## Clean Annual GEM NES Datasets
+
+# Draw out Country and D01 only
+Clean01 <- GEM2001[,c("country", "ki01d01")]
+Clean02 <- GEM2002[,c("country", "ki02d01")]
+Clean03 <- GEM2003[,c("country", "ki03d01")]
+Clean04 <- GEM2004[,c("ki04ctry", "ki04d01")]
+Clean05 <- GEM2005[,c("KI05ctry", "KI05D01")]
+Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
+Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
+Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
+Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
+Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]
+
+# Remove unnecessary dataframes from environment
+remove(GEM2001, GEM2002, GEM2003, GEM2004, GEM2005, GEM2006, GEM2007, GEM2008, GEM2009, GEM2010)
+
+# Edit column names for each dataframe
+Clean01 <- plyr::rename(x = Clean01, 
+                                      replace = c("ki01d01" = "2001",
+                                                  "country" = "Country"))
+
+Clean02 <- plyr::rename(x = Clean02, 
+                                      replace = c("ki02d01" = "2002",
+                                                  "country" = "Country"))
+
+Clean03 <- plyr::rename(x = Clean03, 
+                                      replace = c("ki03d01" = "2003",
+                                                  "country" = "Country"))
+
+Clean04 <- plyr::rename(x = Clean04, 
+                                      replace = c("ki04d01" = "2004",
+                                                  "ki04ctry" = "Country"))
+
+Clean05 <- plyr::rename(x = Clean05, 
+                                      replace = c("KI05D01" = "2005",
+                                                  "KI05ctry" = "Country"))
+
+Clean06 <- plyr::rename(x = Clean06, 
+                                      replace = c("KI06D01_mean" = "2006",
+                                                  "KI06CTRY" = "Country"))
+
+Clean07 <- plyr::rename(x = Clean07, 
+                                      replace = c("ki07d01_" = "2007",
+                                                  "ki07ctry" = "Country"))
+
+Clean08 <- plyr::rename(x = Clean08, 
+                                      replace = c("NES08_D01_MEAN" = "2008",
+                                                  "NES08COUNTRY" = "Country"))
+
+Clean09 <- plyr::rename(x = Clean09, 
+                                      replace = c("NES09_D01_MEAN" = "2009",
+                                                  "NES09COUNTRY" = "Country"))
+
+Clean10 <- plyr::rename(x = Clean10, 
+                                      replace = c("NES10_D01_MEAN" = "2010",
+                                                  "NES10CRNAME" = "Country"))
+
+# Clean Dataframes
 dfs <- ls()[1:max(grep(pattern = 'Clean[0-1]*', x = ls()))]
@@
 
-# Country code
-# Subset
+## Add country codes and place new column at beginning of the data frame
 
-     CleanMerge <- cbind(names = c(rownames(Clean01), rownames(Clean02), rownames(Clean03),
-                              rownames(Clean04), rownames(Clean05), rownames(Clean06),
-                              rownames(Clean07), rownames(Clean08), rownames(Clean09),
-                              rownames(Clean10)),
-                    rbind.fill(list(Clean01, Clean02, Clean03, Clean04, Clean05, Clean06,
-                                    Clean07, Clean08, Clean09, Clean10)))
+# Create a vector of country codes
+W1 <- countrycode(cleaned$Country, "country.name", "iso2c")
 
-# Change merged data from wide to long
-LongGEM<- melt(data = CleanMerge,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010"))
+# Create a new column and insert the country code vector
+cleaned$new.col <- W1
 
-# Rename columns
-names(CleanMerge) <- gsub("variable", "Year", names(CleanMerge))
-names(CleanMerge) <- gsub("value", "Support", names(CleanMerge))
+# Change the order of columns so country code is first
+W2 <- cleaned[,c(4,1:3)]
 
-# Create a vector with OECD countries
-myvars <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'South Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')
+# Change the name of new.col
+names(W2) <- gsub("new.col", "iso2c", names(W2))
 
-# Subset LongGEM with the countries we need  (Why does 2001 and 2010 data disappear?)
-subset_data <- subset(CleanMerge, Country %in% myvars)
+## Subset W2 to OECD countries
+
+# Create matrix of OECD countries by iso2c code
+myvars <- c('MX','CA','US','FR','AU','AT','BE','CL','CZ','DK','EE','FI','DE','HU', 'IS','IE','IL',
+            'IT','JP','KR','LU', 'NL','NZ','NO','PL','PT','SK','SI', 'ES','SE','CH','TR','GB','US','GR')
+
+# Subset W2 with myvars
+subW2 <- subset(W2, iso2c %in% myvars)
 
 # Delete unnecessary column
-subset_data$row.names <- NULL
+subW2$row.names <- NULL
 
-# Arrange subset_data by country and year
-GData <- arrange(subset_data, Country, Year)
-
-GData <- GData[order("Country",)]
-
-########### STUCK #############
-
-FinalData <- merge(FinalGEM, GrandData,
-                   union("Country", "Year"))
 ```

### 2014-12-03 Presentation/EdEntrePres.Rmd

@@
 ```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
-# Plot
+
+# Plot perceived opportunties map
 Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
@@
 
-# Duplicate D4 df
+# Duplicate D4 (perceived opportunities) df
 Dropped4 <- D4
@@
 
-Table <- gvisTable(Dropped4, 
-               options=list(width=230, height=300))
-
-MT <- gvisMerge(Opp_map, Table, horizontal = TRUE)
-
+# Print the table
 print(Opp_map, tag = 'chart')
@@
 ## Distribution of Perception Differences
-```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-library(ggvis)
+```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library("ggplot2")
 
-line_plot <- gvisLineChart(Opp1)
-print(line_plot, tag = 'chart')
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
+
+# Subset Opp2
+Opp2 <- subset(Opp1, iso2c %in% myvars2)
+
+# Melt Opp2 df
+Opp3 <- melt(data = Opp2,
+                  id.vars = c("Country", "iso2c"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Edit column names
+names(Opp3) <- gsub("value", "WayofTeaching", names(Opp3))
+names(Opp3) <- gsub("variable", "Year", names(Opp3))
+
+Opp3$iso2c <- NULL
+
+# Create plot
+ggplot(Opp3,aes(x=Year,y=WayofTeaching,colour=Country,group=Country)) + geom_line()
 
 ```
+
+subset
+ggplot1
+geom_line color each country
+colors by country 4-5
 
@@
 # Import GEM data frame
-WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, cache = FALSE, na.strings = "-")
+WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")
 
@@
 
-# Remove X's in D4 year columns
-names(D4) <- gsub("X", "", names(D4))
+# Change data from long to wide format
+WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")
 
-# Set columns as numeric
-D4[,"2001"] <- as.numeric(D4[,"2001"])
-D4[,"2002"] <- as.numeric(D4[,"2002"])
-D4[,"2003"] <- as.numeric(D4[,"2003"])
-D4[,"2004"] <- as.numeric(D4[,"2004"])
-D4[,"2005"] <- as.numeric(D4[,"2005"])
-D4[,"2006"] <- as.numeric(D4[,"2006"])
-D4[,"2007"] <- as.numeric(D4[,"2007"])
-D4[,"2008"] <- as.numeric(D4[,"2008"])
-D4[,"2009"] <- as.numeric(D4[,"2009"])
-D4[,"2010"] <- as.numeric(D4[,"2010"])
-D4[,"2011"] <- as.numeric(D4[,"2011"])
-D4[,"2012"] <- as.numeric(D4[,"2012"])
-D4[,"2013"] <- as.numeric(D4[,"2013"])
+# Delete variable name in Year columns
+names(WT) <- gsub("WayofTeaching.", "", names(WT))
 
 # Generate a new column with mean of all other columns
-D4$mean <- rowMeans(subset(D4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
-                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)
+WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
+                                          "2009", "2010")), na.rm = TRUE)
 
 # Drop year columns, leaving only mean column
-D4$'2001' <- NULL
-D4$'2002' <- NULL
-D4$'2003' <- NULL
-D4$'2004' <- NULL
-D4$'2005' <- NULL
-D4$'2006' <- NULL
-D4$'2007' <- NULL
-D4$'2008' <- NULL
-D4$'2009' <- NULL
-D4$'2010' <- NULL
-D4$'2011' <- NULL
-D4$'2012' <- NULL
-D4$'2013' <- NULL
+WT$'2001' <- NULL
+WT$'2002' <- NULL
+WT$'2003' <- NULL
+WT$'2004' <- NULL
+WT$'2005' <- NULL
+WT$'2006' <- NULL
+WT$'2007' <- NULL
+WT$'2008' <- NULL
+WT$'2009' <- NULL
+WT$'2010' <- NULL
+WT$'2011' <- NULL
+WT$'2012' <- NULL
+WT$'2013' <- NULL
+WT$row.names <- NULL
 
 # Create 
-D4[, 3] <- round(log(D4[, 3]), digits = 2)
+WT[, 3] <- round(log(WT[, 3]), digits = 2)
 ```
@@
 ```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+library(googleVis)
+
 # Plot
-Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
+WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
                       colorvar = 'mean',
@@
 
-# Duplicate D4 df
-Dropped4 <- D4
-
-# Drop iso2c in Dropped4
-Dropped4$iso2c <- NULL
-
-Table <- gvisTable(Dropped4, 
+Table2 <- gvisTable(WT, 
                options=list(width=230, height=300))
 
-MT <- gvisMerge(Opp_map, Table, horizontal = TRUE)
+WTT <- gvisMerge(WT_map, Table, horizontal = TRUE)
 
-print(Opp_map, tag = 'chart')
+print(WT_map, tag = 'chart')
 

### 2014-12-03 Presentation/PresMisc/MiscPresStuff.Rmd

@@
 ```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-
+library("ggvis")
 # Interactive histgram (isn't interactive in knitted docs)
@@
 
+##################
+
+###################################################
+
+library(googleVis)
+library(reshape2)
+
+# Melt Opp1 (Perceived opportunities 2001:2013 OECD)
+dfChart1 <- melt(data = Opp2,
+                  id.vars = c("Country", "iso2c"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Change column name of value and variable
+names(dfChart1) <- gsub("value", "WayofTeaching", names(dfChart1))
+names(dfChart1) <- gsub("variable", "Year", names(dfChart1))
+
+library(rCharts)
+
+# rChart
+Try1 <- transform(dfChart1, Year = as.character('Year'))
+
+sub_aust <- subset(Try1, Country == "Australia")
+
+m1 <- mPlot(y = "WayofTeaching", x = "Year", type = "Line", data = Opp3)
+
+m1$set(pointSize = 0, lineWidth = 1)
+
+m1$print('chartTest')
 ```

### 2014-12-04 Presentation/EdEntrePres.Rmd
Edited DF for WayofTeaching, added ggplot2 charts

@@
 
-## Different Country-level Perceptions of Good Opportunities to Start a Business
+## Varying Perceptions of Good Opportunities to Start a Business in OECD Countries
 
@@
 
-## Distribution of Perception Differences
-```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+## Variation in Perceived Opportunities to Start a Business
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
 library("ggplot2")
+library("reshape2")
 
@@
 # Edit column names
-names(Opp3) <- gsub("value", "WayofTeaching", names(Opp3))
+names(Opp3) <- gsub("value", "PerceivedOpportunities", names(Opp3))
 names(Opp3) <- gsub("variable", "Year", names(Opp3))
@@
 Opp3$iso2c <- NULL
+```
+
+```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
 
 # Create plot
-ggplot(Opp3,aes(x=Year,y=WayofTeaching,colour=Country,group=Country)) + geom_line()
+ggplot(Opp3,aes(x = Year, y = PerceivedOpportunities, colour = Country, group = Country)) + geom_line()
 
@@
 
-subset
-ggplot1
-geom_line color each country
-colors by country 4-5
+## Variation in how well Education encourages Self Confidence in OECD Countries
 
-## Slide with R Code and Output
-```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-
-```
-
-## WayofTeaching
 ```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
@@
 names(WT) <- gsub("WayofTeaching.", "", names(WT))
+
+# Duplicate df for future use
+WT2 <- WT
 
@@
 
-Table2 <- gvisTable(WT, 
-               options=list(width=230, height=300))
-
-WTT <- gvisMerge(WT_map, Table, horizontal = TRUE)
-
 print(WT_map, tag = 'chart')
@@
 
-## Slide with Plot
+## Variation in Impact of Education on Self Confidence
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library("ggplot2")
+library("reshape2")
+
+# Import df
+Wdf <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv")
+
+# Delete unnessesary columns
+Wdf$X <- NULL
+Wdf$PercentFear <- NULL
+Wdf$PercentNascent <- NULL
+Wdf$PercentPerceived <- NULL
+Wdf$PercentOwner <- NULL
+Wdf$PercentIntention <- NULL
+Wdf$PercentOpportunities <- NULL
+
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
+
+# Subset WT2
+Wdf2 <- subset(Wdf, iso2c %in% myvars2)
+
+```
+
+```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+# Create plot
+ggplot(Wdf2,aes(x = Year, y = WayofTeaching, colour = Country, group = Country)) + geom_line()
+
+```
 

### 2014-12-04 Presentation/EdEntrePres.Rmd
Added final map and chart for FearFail.  Next step is adding two more Zelig charts (format is already set)

@@
 
+## Variation in Fear Perception in OECD Countries
+
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+
+# Library required packages
+library(googleVis)
+library(countrycode)
+library(repmis)
+
+# Import GEM data frame
+PercentFear <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE, na.strings = "-")
+
+## Add country codes and place new column at beginning of the data frame
+# Create a vector of country codes
+F2 <- countrycode(PercentFear$Country, "country.name", "iso2c")
+
+# Create a new column and insert the country code vector
+PercentFear$new.col <- F2
+
+# Reorder columns so country code is first
+F3 <- PercentFear[,c(15,1:14)]
+
+# Rename first column
+F4 <- plyr::rename(x = F3, 
+                   replace = c("new.col" = "iso2c"))
+
+# Remove X's in D4 year columns
+names(F4) <- gsub("X", "", names(F4))
+
+# Set columns as numeric
+F4[,"2001"] <- as.numeric(F4[,"2001"])
+F4[,"2002"] <- as.numeric(F4[,"2002"])
+F4[,"2003"] <- as.numeric(F4[,"2003"])
+F4[,"2004"] <- as.numeric(F4[,"2004"])
+F4[,"2005"] <- as.numeric(F4[,"2005"])
+F4[,"2006"] <- as.numeric(F4[,"2006"])
+F4[,"2007"] <- as.numeric(F4[,"2007"])
+F4[,"2008"] <- as.numeric(F4[,"2008"])
+F4[,"2009"] <- as.numeric(F4[,"2009"])
+F4[,"2010"] <- as.numeric(F4[,"2010"])
+F4[,"2011"] <- as.numeric(F4[,"2011"])
+F4[,"2012"] <- as.numeric(F4[,"2012"])
+F4[,"2013"] <- as.numeric(F4[,"2013"])
+
+# Save cleaned df
+Fear1 <- F4
+
+# Generate a new column with mean of all other columns
+F4$mean <- rowMeans(subset(F4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
+                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)
+
+# Drop year columns, leaving only mean column
+F4$'2001' <- NULL
+F4$'2002' <- NULL
+F4$'2003' <- NULL
+F4$'2004' <- NULL
+F4$'2005' <- NULL
+F4$'2006' <- NULL
+F4$'2007' <- NULL
+F4$'2008' <- NULL
+F4$'2009' <- NULL
+F4$'2010' <- NULL
+F4$'2011' <- NULL
+F4$'2012' <- NULL
+F4$'2013' <- NULL
+
+# Create 
+F4[, 3] <- round(log(F4[, 3]), digits = 2)
+```
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+
+# Plot perceived opportunties map
+FF_map <- gvisGeoChart(F4, locationvar = 'iso2c',
+                      colorvar = 'mean',
+                      options = list(
+                        colors = "['#ece7f2', '#2b8cbe']"
+))
+
+# Duplicate F4 (perceived opportunities) df
+DroppedF4 <- F4
+
+# Drop iso2c in Dropped4
+DroppedF4$iso2c <- NULL
+
+# Print the table
+print(FF_map, tag = 'chart')
+
+```
+
+## Variation in Fear of Failure
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library("ggplot2")
+library("reshape2")
+
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
+
+# Subset Opp2
+Fear2 <- subset(Fear1, iso2c %in% myvars2)
+
+# Melt Opp2 df
+Fear3 <- melt(data = Fear2,
+                  id.vars = c("Country", "iso2c"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Edit column names
+names(Fear3) <- gsub("value", "FearFail", names(Fear3))
+names(Fear3) <- gsub("variable", "Year", names(Fear3))
+
+Fear3$iso2c <- NULL
+```
+
+```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+# Create plot
+ggplot(Fear3,aes(x = Year, y = FearFail, colour = Country, group = Country)) + geom_line()
+
+```
+
+## Regression Results
+
+We decided to ignore country-specific effects because the change in the intercept resulting from fixed effects was small and the slope of the fixed effects and OLS models are very similar.
+
 ```{r, echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

### 2014-12-04 Presentation/EdEntrePres.Rmd
Updated slides

@@
 
-## From Education to Entrepreneurship
+## Research Interest
 
@@
 
-## Varying Perceptions of Good Opportunities to Start a Business in OECD Countries
+## Causal Chain
 
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+## Where our intuition came from
 
-# Library required packages
-library(googleVis)
-library(countrycode)
-library(repmis)
+Variable | France | UK
+-------------|---------------|---------
+Fear of Failure (GEM 2012) | 43% | 36%
+Perceived Capabilities (GEM 2012) | 36% | 47%
+Sense of belonging (PISA 2012) | 47% | 79%
 
-# Import GEM data frame
-PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE, na.strings = "-")
+## What is PISA
 
-## Add country codes and place new column at beginning of the data frame
-# Create a vector of country codes
-D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")
+- PISA: "Programme for International Student Assessment is a triennial international survey which aims to evaluate education systems worldwide by testing the skills and knowledge of 15 year old students."
 
-# Create a new column and insert the country code vector
-PerceivedOpportunities$new.col <- D2
+- Data availability prevented us from using PISA data for this project
 
-# Reorder columns so country code is first
-D3 <- PerceivedOpportunities[,c(15,1:14)]
+## What is GEM
 
-# Rename first column
-D4 <- plyr::rename(x = D3, 
-                   replace = c("new.col" = "iso2c"))
+- GEM: Global Entrepreneurship Monitor project is an annual assessment of the entrepreneurial activity, aspirations, and attitudes of individuals across a wide range of countries.
 
-# Remove X's in D4 year columns
-names(D4) <- gsub("X", "", names(D4))
+-
 
-# Set columns as numeric
-D4[,"2001"] <- as.numeric(D4[,"2001"])
-D4[,"2002"] <- as.numeric(D4[,"2002"])
-D4[,"2003"] <- as.numeric(D4[,"2003"])
-D4[,"2004"] <- as.numeric(D4[,"2004"])
-D4[,"2005"] <- as.numeric(D4[,"2005"])
-D4[,"2006"] <- as.numeric(D4[,"2006"])
-D4[,"2007"] <- as.numeric(D4[,"2007"])
-D4[,"2008"] <- as.numeric(D4[,"2008"])
-D4[,"2009"] <- as.numeric(D4[,"2009"])
-D4[,"2010"] <- as.numeric(D4[,"2010"])
-D4[,"2011"] <- as.numeric(D4[,"2011"])
-D4[,"2012"] <- as.numeric(D4[,"2012"])
-D4[,"2013"] <- as.numeric(D4[,"2013"])
+## Estimation Strategy
 
-# Save cleaned df
-Opp1 <- D4
+Variable | Indicator 
+-------------|---------------
+Y Dependent Vaiable | Rate of Entrepreneurship (Intention, Nascent, Established)
+X1 Explanatory Variable | Way of Teaching
+X2 Control Variable | Perceived Capabilities
+X3 Control Variable | Fear of Failure / Perceived Opportunities
+X4 Control Variable | Perceived Opportunities
 
-# Generate a new column with mean of all other columns
-D4$mean <- rowMeans(subset(D4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
-                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)
+## Explaining Way of Teaching
 
-# Drop year columns, leaving only mean column
-D4$'2001' <- NULL
-D4$'2002' <- NULL
-D4$'2003' <- NULL
-D4$'2004' <- NULL
-D4$'2005' <- NULL
-D4$'2006' <- NULL
-D4$'2007' <- NULL
-D4$'2008' <- NULL
-D4$'2009' <- NULL
-D4$'2010' <- NULL
-D4$'2011' <- NULL
-D4$'2012' <- NULL
-D4$'2013' <- NULL
-
-# Create 
-D4[, 3] <- round(log(D4[, 3]), digits = 2)
-```
-
-```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
-
-# Plot perceived opportunties map
-Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
-                      colorvar = 'mean',
-                      options = list(
-                        colors = "['#ece7f2', '#2b8cbe']"
-))
-
-# Duplicate D4 (perceived opportunities) df
-Dropped4 <- D4
-
-# Drop iso2c in Dropped4
-Dropped4$iso2c <- NULL
-
-# Print the table
-print(Opp_map, tag = 'chart')
-
-```
-
-## Variation in Perceived Opportunities to Start a Business
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-library("ggplot2")
-library("reshape2")
-
-# Create country vector to subset
-myvars2 <- c('US','FR','DE','JP','GB')
-
-# Subset Opp2
-Opp2 <- subset(Opp1, iso2c %in% myvars2)
-
-# Melt Opp2 df
-Opp3 <- melt(data = Opp2,
-                  id.vars = c("Country", "iso2c"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010"))
-
-# Edit column names
-names(Opp3) <- gsub("value", "PerceivedOpportunities", names(Opp3))
-names(Opp3) <- gsub("variable", "Year", names(Opp3))
-
-Opp3$iso2c <- NULL
-```
-
-```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-
-# Create plot
-ggplot(Opp3,aes(x = Year, y = PerceivedOpportunities, colour = Country, group = Country)) + geom_line()
-
-```
+*How is it measured*
 
@@
 ggplot(Wdf2,aes(x = Year, y = WayofTeaching, colour = Country, group = Country)) + geom_line()
+
+```
+
+## Perceived Capabilities
+
+*What about it*
+
+## Perceived Capabilities
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+
+# Library required packages
+library(googleVis)
+library(countrycode)
+library(repmis)
+
+# Import GEM data frame
+PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE, na.strings = "-")
+
+## Add country codes and place new column at beginning of the data frame
+# Create a vector of country codes
+C2 <- countrycode(PerceivedCapabilities$Country, "country.name", "iso2c")
+
+# Create a new column and insert the country code vector
+PerceivedCapabilities$new.col <- C2
+
+# Reorder columns so country code is first
+C3 <- PerceivedCapabilities[,c(15,1:14)]
+
+# Rename first column
+C4 <- plyr::rename(x = C3, 
+                   replace = c("new.col" = "iso2c"))
+
+# Remove X's in D4 year columns
+names(C4) <- gsub("X", "", names(C4))
+
+# Set columns as numeric
+C4[,"2001"] <- as.numeric(C4[,"2001"])
+C4[,"2002"] <- as.numeric(C4[,"2002"])
+C4[,"2003"] <- as.numeric(C4[,"2003"])
+C4[,"2004"] <- as.numeric(C4[,"2004"])
+C4[,"2005"] <- as.numeric(C4[,"2005"])
+C4[,"2006"] <- as.numeric(C4[,"2006"])
+C4[,"2007"] <- as.numeric(C4[,"2007"])
+C4[,"2008"] <- as.numeric(C4[,"2008"])
+C4[,"2009"] <- as.numeric(C4[,"2009"])
+C4[,"2010"] <- as.numeric(C4[,"2010"])
+C4[,"2011"] <- as.numeric(C4[,"2011"])
+C4[,"2012"] <- as.numeric(C4[,"2012"])
+C4[,"2013"] <- as.numeric(C4[,"2013"])
+
+# Save cleaned df
+Cap1 <- C4
+
+# Generate a new column with mean of all other columns
+C4$mean <- rowMeans(subset(C4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
+                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)
+
+# Drop year columns, leaving only mean column
+C4$'2001' <- NULL
+C4$'2002' <- NULL
+C4$'2003' <- NULL
+C4$'2004' <- NULL
+C4$'2005' <- NULL
+C4$'2006' <- NULL
+C4$'2007' <- NULL
+C4$'2008' <- NULL
+C4$'2009' <- NULL
+C4$'2010' <- NULL
+C4$'2011' <- NULL
+C4$'2012' <- NULL
+C4$'2013' <- NULL
+
+# Create 
+C4[, 3] <- round(log(C4[, 3]), digits = 2)
+```
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+
+# Plot perceived opportunties map
+Cap1_map <- gvisGeoChart(C4, locationvar = 'iso2c',
+                      colorvar = 'mean',
+                      options = list(
+                        colors = "['#ece7f2', '#2b8cbe']"
+))
+
+# Duplicate D4 (perceived capabilities) df
+Cap4 <- C4
+
+# Drop iso2c in Dropped4
+C4$iso2c <- NULL
+
+# Print the table
+print(Cap1_map, tag = 'chart')
+
+```
+
+## Variation in Perceived Opportunities to Start a Business
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library("ggplot2")
+library("reshape2")
+
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
+
+# Subset Cap4
+Cap5 <- subset(Cap4, iso2c %in% myvars2)
+
+# Melt Opp2 df
+Cap6 <- melt(data = Cap5,
+                  id.vars = c("Country", "iso2c"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Edit column names
+names(Cap6) <- gsub("value", "Capabilities", names(Cap6))
+names(Cap6) <- gsub("variable", "Year", names(Cap6))
+
+Cap6$iso2c <- NULL
+```
+
+```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+# Create plot
+ggplot(Cap6,aes(x = Year, y = PerceivedCapabilities, colour = Country, group = Country)) + geom_line()
 
@@
 
+## Varying Perceptions of Good Opportunities to Start a Business in OECD Countries
+
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+
+# Library required packages
+library(googleVis)
+library(countrycode)
+library(repmis)
+
+# Import GEM data frame
+PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE, na.strings = "-")
+
+## Add country codes and place new column at beginning of the data frame
+# Create a vector of country codes
+D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")
+
+# Create a new column and insert the country code vector
+PerceivedOpportunities$new.col <- D2
+
+# Reorder columns so country code is first
+D3 <- PerceivedOpportunities[,c(15,1:14)]
+
+# Rename first column
+D4 <- plyr::rename(x = D3, 
+                   replace = c("new.col" = "iso2c"))
+
+# Remove X's in D4 year columns
+names(D4) <- gsub("X", "", names(D4))
+
+# Set columns as numeric
+D4[,"2001"] <- as.numeric(D4[,"2001"])
+D4[,"2002"] <- as.numeric(D4[,"2002"])
+D4[,"2003"] <- as.numeric(D4[,"2003"])
+D4[,"2004"] <- as.numeric(D4[,"2004"])
+D4[,"2005"] <- as.numeric(D4[,"2005"])
+D4[,"2006"] <- as.numeric(D4[,"2006"])
+D4[,"2007"] <- as.numeric(D4[,"2007"])
+D4[,"2008"] <- as.numeric(D4[,"2008"])
+D4[,"2009"] <- as.numeric(D4[,"2009"])
+D4[,"2010"] <- as.numeric(D4[,"2010"])
+D4[,"2011"] <- as.numeric(D4[,"2011"])
+D4[,"2012"] <- as.numeric(D4[,"2012"])
+D4[,"2013"] <- as.numeric(D4[,"2013"])
+
+# Save cleaned df
+Opp1 <- D4
+
+# Generate a new column with mean of all other columns
+D4$mean <- rowMeans(subset(D4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
+                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)
+
+# Drop year columns, leaving only mean column
+D4$'2001' <- NULL
+D4$'2002' <- NULL
+D4$'2003' <- NULL
+D4$'2004' <- NULL
+D4$'2005' <- NULL
+D4$'2006' <- NULL
+D4$'2007' <- NULL
+D4$'2008' <- NULL
+D4$'2009' <- NULL
+D4$'2010' <- NULL
+D4$'2011' <- NULL
+D4$'2012' <- NULL
+D4$'2013' <- NULL
+
+# Create 
+D4[, 3] <- round(log(D4[, 3]), digits = 2)
+```
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+
+# Plot perceived opportunties map
+Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
+                      colorvar = 'mean',
+                      options = list(
+                        colors = "['#ece7f2', '#2b8cbe']"
+))
+
+# Duplicate D4 (perceived opportunities) df
+Dropped4 <- D4
+
+# Drop iso2c in Dropped4
+Dropped4$iso2c <- NULL
+
+# Print the table
+print(Opp_map, tag = 'chart')
+
+```
+
+## Variation in Perceived Opportunities to Start a Business
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library("ggplot2")
+library("reshape2")
+
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
+
+# Subset Opp2
+Opp2 <- subset(Opp1, iso2c %in% myvars2)
+
+# Melt Opp2 df
+Opp3 <- melt(data = Opp2,
+                  id.vars = c("Country", "iso2c"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Edit column names
+names(Opp3) <- gsub("value", "PerceivedOpportunities", names(Opp3))
+names(Opp3) <- gsub("variable", "Year", names(Opp3))
+
+Opp3$iso2c <- NULL
+```
+
+```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+# Create plot
+ggplot(Opp3,aes(x = Year, y = PerceivedOpportunities, colour = Country, group = Country)) + geom_line()
+
+```
+
 ## Regression Results
@@
 # Run a RE regression
-Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeaching, data = CompleteData_omit, model = "ls")
+Z1 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CompleteData_omit, model = "ls")
 

### 2014-12-04 Presentation/EdEntrePres.Rmd
Updated slides

@@
 
-*Text from Thierry*
+What determines entrepreneurship?  
+Economic and structural factors - Already searched
+Educational and cultural factors - Hardly searched
+
+Even when focused on attitudes / Entrepreneurship,  
+Studies look more at what attitudes are favourable  
+Almost none searched what determines these attitudes.
 
 ## Causal Chain
+
+Education System that reinforces Self-confidence
+
+Higher degree of individual self-esteem
+
+Higher probability an individual becomes an entrepreneur
+
+Higher rate of entrepreneurship at a country-level
 
@@
 
-- Data availability prevented us from using PISA data for this project
+- Data availability prevented us from using PISA data for this project. For instance, for 2015 PISA will be looking at science education.
 
@@
 
-- GEM: Global Entrepreneurship Monitor project is an annual assessment of the entrepreneurial activity, aspirations, and attitudes of individuals across a wide range of countries.
+- The Global Entrepreneurship Monitor project is an annual assessment of the entrepreneurial activity, aspirations, and attitudes of individuals across a wide range of countries.
 
--
+- Only 10 countries at first, now covering 75% of world population and 89% of world GDP
+
+- GEM is being used is regularly refered to in research, including in OECD reports.
+
+- GEM uses primary data collection which results in massive comprehensive datasets. That is the 2001-2010 multi-year APS Database covers over 1.3 million observations over 85 countries.
+
+- APS or Adult Population Survey (at least 2000 sample size) looks at activity, attitudes and aspirations.
+
+- NES or National Expert Survey looks at 9 entrepreneurial framework conditions (4 national experts for each)
 
@@
 
-*How is it measured*
+In the absence of indicator directly aligned with our research design, we turned to an item of the NES survey as a proxy, D01:
+
+"In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative"
+
+But there is a clear lack of consistency in the data.
+
+Many flaws : scale, methodology for collection (poor time management, personal connections)
 

### 2014-12-04 Presentation/EdEntrePres.Rmd
Added Zelig chart

--- 2014-12-04 Presentation/EdEntrePres.Rmd
@@
 
-## From Education to Entrepreneurship
+## Research Interest
 
-*Text from Thierry*
+**What determines entrepreneurship?**
+
+- Economic and structural factors: Already searched
+
+- Educational and cultural factors: Hardly searched
+
+- Even when focused on attitudes / Entrepreneurship, studies look more at what attitudes are favourable, almost none searched what determines these attitudes.
+
+## Causal Chain
+
+1. Education System that reinforces Self-confidence
+
+2. Higher degree of individual self-esteem
+
+3. Higher probability an individual becomes an entrepreneur
+
+4. Higher rate of entrepreneurship at a country-level
+
+## Where our Intuition Came From
+
+Variable | France | UK
+-------------|---------------|---------
+Fear of Failure (GEM 2012) | 43% | 36%
+Perceived Capabilities (GEM 2012) | 36% | 47%
+Sense of belonging (PISA 2012) | 47% | 79%
+
+## What is PISA
+
+- PISA: "Programme for International Student Assessment is a triennial international survey which aims to evaluate education systems worldwide by testing the skills and knowledge of 15 year old students."
+
+- Data availability prevented us from using PISA data for this project. For instance, for 2015 PISA will be looking at science education.
+
+## What is GEM
+
+- The Global Entrepreneurship Monitor project is an annual assessment of the entrepreneurial activity, aspirations, and attitudes of individuals across a wide range of countries.
+
+- Only 10 countries at first, now covering 75% of world population and 89% of world GDP
+
+- GEM is being used is regularly refered to in research, including in OECD reports.
+
+- GEM uses primary data collection which results in massive comprehensive datasets. That is the 2001-2010 multi-year APS Database covers over 1.3 million observations over 85 countries.
+
+- NES or National Expert Survey looks at 9 entrepreneurial framework conditions (4 national experts for each)
+
+## Estimation Strategy
+
+Variable | Indicator 
+-------------|---------------
+Y Dependent Vaiable | Rate of Entrepreneurship (Intention, Nascent, Established)
+X1 Explanatory Variable | Way of Teaching
+X2 Control Variable | Perceived Capabilities
+X3 Control Variable | Fear of Failure / Perceived Opportunities
+X4 Control Variable | Perceived Opportunities
+
+## Explaining Way of Teaching
+
+- In the absence of an  indicator directly aligned with our research design, we turned to an item of the GEM NES survey as a proxy, question D01:
+
+- "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative"
+
+- But there is a clear lack of consistency in the data.
+
+- Many flaws : scale, methodology for collection (poor time management, personal connections)
+
+## Variation in how well Education encourages Self Confidence in OECD Countries
+
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+# Import GEM data frame
+WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")
+
+# Drop unnecessary column 1
+WayofTeaching$X <- NULL
+
+# Change data from long to wide format
+WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")
+
+# Delete variable name in Year columns
+names(WT) <- gsub("WayofTeaching.", "", names(WT))
+
+# Duplicate df for future use
+WT2 <- WT
+
+# Generate a new column with mean of all other columns
+WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
+                                          "2009", "2010")), na.rm = TRUE)
+
+# Drop year columns, leaving only mean column
+WT$'2001' <- NULL
+WT$'2002' <- NULL
+WT$'2003' <- NULL
+WT$'2004' <- NULL
+WT$'2005' <- NULL
+WT$'2006' <- NULL
+WT$'2007' <- NULL
+WT$'2008' <- NULL
+WT$'2009' <- NULL
+WT$'2010' <- NULL
+WT$'2011' <- NULL
+WT$'2012' <- NULL
+WT$'2013' <- NULL
+WT$row.names <- NULL
+
+# Create 
+WT[, 3] <- round(log(WT[, 3]), digits = 2)
+```
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+library(googleVis)
+
+# Plot
+WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
+                      colorvar = 'mean',
+                      options = list(
+                        colors = "['#ece7f2', '#2b8cbe']"
+))
+
+print(WT_map, tag = 'chart')
+
+```
+
+## Variation in Impact of Education on Self Confidence
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library("ggplot2")
+library("reshape2")
+
+# Import df
+Wdf <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv")
+
+# Delete unnessesary columns
+Wdf$X <- NULL
+Wdf$PercentFear <- NULL
+Wdf$PercentNascent <- NULL
+Wdf$PercentPerceived <- NULL
+Wdf$PercentOwner <- NULL
+Wdf$PercentIntention <- NULL
+Wdf$PercentOpportunities <- NULL
+
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
+
+# Subset WT2
+Wdf2 <- subset(Wdf, iso2c %in% myvars2)
+
+```
+
+```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+# Create plot
+ggplot(Wdf2,aes(x = Year, y = WayofTeaching, colour = Country, group = Country)) + geom_line()
+
+```
+
+## Perceived Capabilities
+
+- "Percentage of 18-64 population who believe they have the required skills and knowledge to start a business"
+
+- This figure is a national-level precentage
+
+- This measure was chosen to provide some insight on how personal values are shaped, especially in terms of self-confidence.
+
+## Differences in Perceived Capability in OECD Countries
+
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+
+# Library required packages
+library(googleVis)
+library(countrycode)
+library(repmis)
+
+# Import GEM data frame
+PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE, na.strings = "-")
+
+## Add country codes and place new column at beginning of the data frame
+# Create a vector of country codes
+PC1 <- countrycode(PerceivedCapabilities$Country, "country.name", "iso2c")
+
+# Create a new column and insert the country code vector
+PerceivedCapabilities$new.col <- PC1
+
+# Reorder columns so country code is first
+PC2 <- PerceivedCapabilities[,c(15,1:14)]
+
+# Rename first column
+PC3 <- plyr::rename(x = PC2, 
+                   replace = c("new.col" = "iso2c"))
+
+# Remove X's in D4 year columns
+names(PC3) <- gsub("X", "", names(PC3))
+
+# Set columns as numeric
+PC3[,"2001"] <- as.numeric(PC3[,"2001"])
+PC3[,"2002"] <- as.numeric(PC3[,"2002"])
+PC3[,"2003"] <- as.numeric(PC3[,"2003"])
+PC3[,"2004"] <- as.numeric(PC3[,"2004"])
+PC3[,"2005"] <- as.numeric(PC3[,"2005"])
+PC3[,"2006"] <- as.numeric(PC3[,"2006"])
+PC3[,"2007"] <- as.numeric(PC3[,"2007"])
+PC3[,"2008"] <- as.numeric(PC3[,"2008"])
+PC3[,"2009"] <- as.numeric(PC3[,"2009"])
+PC3[,"2010"] <- as.numeric(PC3[,"2010"])
+PC3[,"2011"] <- as.numeric(PC3[,"2011"])
+PC3[,"2012"] <- as.numeric(PC3[,"2012"])
+PC3[,"2013"] <- as.numeric(PC3[,"2013"])
+
+# Save cleaned df
+PC4 <- PC3
+
+# Generate a new column with mean of all other columns
+PC3$mean <- rowMeans(subset(PC3, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007",
+                                            "2008", "2009", "2010", "2011", "2012", "2013")),
+                     na.rm = TRUE)
+
+# Drop year columns, leaving only mean column
+PC3$'2001' <- NULL
+PC3$'2002' <- NULL
+PC3$'2003' <- NULL
+PC3$'2004' <- NULL
+PC3$'2005' <- NULL
+PC3$'2006' <- NULL
+PC3$'2007' <- NULL
+PC3$'2008' <- NULL
+PC3$'2009' <- NULL
+PC3$'2010' <- NULL
+PC3$'2011' <- NULL
+PC3$'2012' <- NULL
+PC3$'2013' <- NULL
+
+# Create 
+PC3[, 3] <- round(log(PC3[, 3]), digits = 2)
+```
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+
+# Plot perceived capabilities map
+PC_map <- gvisGeoChart(PC3, locationvar = 'iso2c',
+                      colorvar = 'mean',
+                      options = list(
+                        colors = "['#ece7f2', '#2b8cbe']"
+))
+
+# Duplicate F4 (perceived capabilities) df
+#DroppedPC4 <- PC4
+
+# Drop iso2c in Dropped4
+#DroppedF4$iso2c <- NULL
+
+# Print the map
+print(PC_map, tag = 'chart')
+
+```
+
+## Time Variation in Perceived Capabilities
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library("ggplot2")
+library("reshape2")
+
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
+
+# Subset Opp2
+PC5 <- subset(PC4, iso2c %in% myvars2)
+
+# Melt Opp2 df
+PC6 <- melt(data = PC5,
+                  id.vars = c("Country", "iso2c"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Edit column names
+names(PC6) <- gsub("value", "PerceivedCapabilities", names(PC6))
+names(PC6) <- gsub("variable", "Year", names(PC6))
+
+PC6$iso2c <- NULL
+```
+
+```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+# Create plot
+ggplot(PC6,aes(x = Year, y = PerceivedCapabilities, colour = Country, group = Country)) + geom_line()
+
+```
+
+## Fear of Failure
+
+- "Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business."
+
+## Variation in Fear Perception in OECD Countries
+
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+
+# Library required packages
+library(googleVis)
+library(countrycode)
+library(repmis)
+
+# Import GEM data frame
+PercentFear <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE, na.strings = "-")
+
+## Add country codes and place new column at beginning of the data frame
+# Create a vector of country codes
+F2 <- countrycode(PercentFear$Country, "country.name", "iso2c")
+
+# Create a new column and insert the country code vector
+PercentFear$new.col <- F2
+
+# Reorder columns so country code is first
+F3 <- PercentFear[,c(15,1:14)]
+
+# Rename first column
+F4 <- plyr::rename(x = F3, 
+                   replace = c("new.col" = "iso2c"))
+
+# Remove X's in D4 year columns
+names(F4) <- gsub("X", "", names(F4))
+
+# Set columns as numeric
+F4[,"2001"] <- as.numeric(F4[,"2001"])
+F4[,"2002"] <- as.numeric(F4[,"2002"])
+F4[,"2003"] <- as.numeric(F4[,"2003"])
+F4[,"2004"] <- as.numeric(F4[,"2004"])
+F4[,"2005"] <- as.numeric(F4[,"2005"])
+F4[,"2006"] <- as.numeric(F4[,"2006"])
+F4[,"2007"] <- as.numeric(F4[,"2007"])
+F4[,"2008"] <- as.numeric(F4[,"2008"])
+F4[,"2009"] <- as.numeric(F4[,"2009"])
+F4[,"2010"] <- as.numeric(F4[,"2010"])
+F4[,"2011"] <- as.numeric(F4[,"2011"])
+F4[,"2012"] <- as.numeric(F4[,"2012"])
+F4[,"2013"] <- as.numeric(F4[,"2013"])
+
+# Save cleaned df
+Fear1 <- F4
+
+# Generate a new column with mean of all other columns
+F4$mean <- rowMeans(subset(F4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
+                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)
+
+# Drop year columns, leaving only mean column
+F4$'2001' <- NULL
+F4$'2002' <- NULL
+F4$'2003' <- NULL
+F4$'2004' <- NULL
+F4$'2005' <- NULL
+F4$'2006' <- NULL
+F4$'2007' <- NULL
+F4$'2008' <- NULL
+F4$'2009' <- NULL
+F4$'2010' <- NULL
+F4$'2011' <- NULL
+F4$'2012' <- NULL
+F4$'2013' <- NULL
+
+# Create 
+F4[, 3] <- round(log(F4[, 3]), digits = 2)
+```
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+
+# Plot perceived opportunties map
+FF_map <- gvisGeoChart(F4, locationvar = 'iso2c',
+                      colorvar = 'mean',
+                      options = list(
+                        colors = "['#ece7f2', '#2b8cbe']"
+))
+
+# Duplicate F4 (perceived opportunities) df
+DroppedF4 <- F4
+
+# Drop iso2c in Dropped4
+DroppedF4$iso2c <- NULL
+
+# Print the table
+print(FF_map, tag = 'chart')
+
+```
+
+## Variation in Fear of Failure
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library("ggplot2")
+library("reshape2")
+
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
+
+# Subset Opp2
+Fear2 <- subset(Fear1, iso2c %in% myvars2)
+
+# Melt Opp2 df
+Fear3 <- melt(data = Fear2,
+                  id.vars = c("Country", "iso2c"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Edit column names
+names(Fear3) <- gsub("value", "FearFail", names(Fear3))
+names(Fear3) <- gsub("variable", "Year", names(Fear3))
+
+Fear3$iso2c <- NULL
+```
+
+```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+# Create plot
+ggplot(Fear3,aes(x = Year, y = FearFail, colour = Country, group = Country)) + geom_line()
+
+```
+
+## Perceived Opportunities
+
+- "Percentage of 18-64 population who see good opportunities to start a firm in the area where they live"
+
+- Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.
 
@@
 
-## Variation in how well Education encourages Self Confidence in OECD Countries
-
-```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-# Import GEM data frame
-WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")
-
-# Drop unnecessary column 1
-WayofTeaching$X <- NULL
-
-# Change data from long to wide format
-WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")
-
-# Delete variable name in Year columns
-names(WT) <- gsub("WayofTeaching.", "", names(WT))
-
-# Duplicate df for future use
-WT2 <- WT
-
-# Generate a new column with mean of all other columns
-WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
-                                          "2009", "2010")), na.rm = TRUE)
-
-# Drop year columns, leaving only mean column
-WT$'2001' <- NULL
-WT$'2002' <- NULL
-WT$'2003' <- NULL
-WT$'2004' <- NULL
-WT$'2005' <- NULL
-WT$'2006' <- NULL
-WT$'2007' <- NULL
-WT$'2008' <- NULL
-WT$'2009' <- NULL
-WT$'2010' <- NULL
-WT$'2011' <- NULL
-WT$'2012' <- NULL
-WT$'2013' <- NULL
-WT$row.names <- NULL
-
-# Create 
-WT[, 3] <- round(log(WT[, 3]), digits = 2)
-```
-
-```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
-library(googleVis)
-
-# Plot
-WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
-                      colorvar = 'mean',
-                      options = list(
-                        colors = "['#ece7f2', '#2b8cbe']"
-))
-
-print(WT_map, tag = 'chart')
-
-```
-
-## Variation in Impact of Education on Self Confidence
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-library("ggplot2")
-library("reshape2")
-
-# Import df
-Wdf <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv")
-
-# Delete unnessesary columns
-Wdf$X <- NULL
-Wdf$PercentFear <- NULL
-Wdf$PercentNascent <- NULL
-Wdf$PercentPerceived <- NULL
-Wdf$PercentOwner <- NULL
-Wdf$PercentIntention <- NULL
-Wdf$PercentOpportunities <- NULL
-
-# Create country vector to subset
-myvars2 <- c('US','FR','DE','JP','GB')
-
-# Subset WT2
-Wdf2 <- subset(Wdf, iso2c %in% myvars2)
-
-```
-
-```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-
-# Create plot
-ggplot(Wdf2,aes(x = Year, y = WayofTeaching, colour = Country, group = Country)) + geom_line()
-
-```
-
-## Variation in Fear Perception in OECD Countries
-
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
-
-# Library required packages
-library(googleVis)
-library(countrycode)
-library(repmis)
-
-# Import GEM data frame
-PercentFear <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE, na.strings = "-")
-
-## Add country codes and place new column at beginning of the data frame
-# Create a vector of country codes
-F2 <- countrycode(PercentFear$Country, "country.name", "iso2c")
-
-# Create a new column and insert the country code vector
-PercentFear$new.col <- F2
-
-# Reorder columns so country code is first
-F3 <- PercentFear[,c(15,1:14)]
-
-# Rename first column
-F4 <- plyr::rename(x = F3, 
-                   replace = c("new.col" = "iso2c"))
-
-# Remove X's in D4 year columns
-names(F4) <- gsub("X", "", names(F4))
-
-# Set columns as numeric
-F4[,"2001"] <- as.numeric(F4[,"2001"])
-F4[,"2002"] <- as.numeric(F4[,"2002"])
-F4[,"2003"] <- as.numeric(F4[,"2003"])
-F4[,"2004"] <- as.numeric(F4[,"2004"])
-F4[,"2005"] <- as.numeric(F4[,"2005"])
-F4[,"2006"] <- as.numeric(F4[,"2006"])
-F4[,"2007"] <- as.numeric(F4[,"2007"])
-F4[,"2008"] <- as.numeric(F4[,"2008"])
-F4[,"2009"] <- as.numeric(F4[,"2009"])
-F4[,"2010"] <- as.numeric(F4[,"2010"])
-F4[,"2011"] <- as.numeric(F4[,"2011"])
-F4[,"2012"] <- as.numeric(F4[,"2012"])
-F4[,"2013"] <- as.numeric(F4[,"2013"])
-
-# Save cleaned df
-Fear1 <- F4
-
-# Generate a new column with mean of all other columns
-F4$mean <- rowMeans(subset(F4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
-                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)
-
-# Drop year columns, leaving only mean column
-F4$'2001' <- NULL
-F4$'2002' <- NULL
-F4$'2003' <- NULL
-F4$'2004' <- NULL
-F4$'2005' <- NULL
-F4$'2006' <- NULL
-F4$'2007' <- NULL
-F4$'2008' <- NULL
-F4$'2009' <- NULL
-F4$'2010' <- NULL
-F4$'2011' <- NULL
-F4$'2012' <- NULL
-F4$'2013' <- NULL
-
-# Create 
-F4[, 3] <- round(log(F4[, 3]), digits = 2)
-```
-
-```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
-
-# Plot perceived opportunties map
-FF_map <- gvisGeoChart(F4, locationvar = 'iso2c',
-                      colorvar = 'mean',
-                      options = list(
-                        colors = "['#ece7f2', '#2b8cbe']"
-))
-
-# Duplicate F4 (perceived opportunities) df
-DroppedF4 <- F4
-
-# Drop iso2c in Dropped4
-DroppedF4$iso2c <- NULL
-
-# Print the table
-print(FF_map, tag = 'chart')
-
-```
-
-## Variation in Fear of Failure
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-library("ggplot2")
-library("reshape2")
-
-# Create country vector to subset
-myvars2 <- c('US','FR','DE','JP','GB')
-
-# Subset Opp2
-Fear2 <- subset(Fear1, iso2c %in% myvars2)
-
-# Melt Opp2 df
-Fear3 <- melt(data = Fear2,
-                  id.vars = c("Country", "iso2c"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010"))
-
-# Edit column names
-names(Fear3) <- gsub("value", "FearFail", names(Fear3))
-names(Fear3) <- gsub("variable", "Year", names(Fear3))
-
-Fear3$iso2c <- NULL
-```
-
-```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-
-# Create plot
-ggplot(Fear3,aes(x = Year, y = FearFail, colour = Country, group = Country)) + geom_line()
-
-```
-
 ## Regression Results
 
-We decided to ignore country-specific effects because the change in the intercept resulting from fixed effects was small and the slope of the fixed effects and OLS models are very similar.
+- Our regression equations were run both with and without considering country-specific effects.  For the purposes of illustrating our results, we have chosen to ignore the country-specific effects.
+
+- We decided to do this because the coefficients do not change signficantly when the country-specific effects are ignored.
+
+## Results: PercentIntention as a Dependent Variable
 
@@
 # Run a RE regression
-Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + WayofTeaching, data = CompleteData_omit, model = "ls")
+Z1 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CompleteData_omit, model = "ls")
 
 # Set range of PercentPerceived values in simulation
-x.out2 <- setx(Z1, PercentPerceived = 20:70)
+x.out2 <- setx(Z1, WayofTeaching = 1.53:3.278)
 
@@
 # Plot simulation
-plot(simz2, xlab = 'PercentPerceived', ylab = 'PercentIntention | PercentPerceived')
+plot(simz2, xlab = 'WayofTeaching', ylab = 'PercentIntention | WayofTeaching')
 ```
 
-## New
+## Results: PercentIntention as a Dependent Variable
+
+```{r, echo =FALSE, cache=FALSE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+library(Zelig)
+
+# Run a RE regression
+Z1 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CompleteData_omit, model = "ls")
+
+# Set range of PercentPerceived values in simulation
+x.out3 <- setx(Z1, PercentPerceived = 9:67)
+
+# Run simulation (default 1000 trials)
+simz3 <- sim(Z1, x = x.out3)
+
+# Adjust margins
+par(mar=c(5,5,5,5))
+
+```
+
+```{r, echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+# Plot simulation
+plot(simz3, xlab = 'PercentCapabilities', ylab = 'PercentIntention | PercentCapabilities')
+```
+
 ```{r, echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

### 2014-12-04 Presentation/EdEntrePres.Rmd
Final changes to presentatino

@@
 author: "Sam Dundon and Thierry Racaud"
-date: "December 2, 2014"
+date: "December 4, 2014"
 output: ioslides_presentation
 ---
+
+## Research Question
+
+- To what extent do teaching methods supporting self confidence affect the rate of entrepreneurship in OECD countries?
 
@@
 
-1. Education System that reinforces Self-confidence
+1. Education System that reinforces self-confidence
 
@@
 
-- GEM is being used is regularly refered to in research, including in OECD reports.
+- GEM is being used is regularly referred to in research, including in OECD reports.
 
-- GEM uses primary data collection which results in massive comprehensive datasets. That is the 2001-2010 multi-year APS Database covers over 1.3 million observations over 85 countries.
+- GEM uses primary data collection which results in massive comprehensive data sets. That is the 2001-2010 multi-year APS Database covers over 1.3 million observations over 85 countries.
 
@@
 -------------|---------------
-Y Dependent Vaiable | Rate of Entrepreneurship (Intention, Nascent, Established)
+Y Dependent Variable | Rate of Entrepreneurship (Intention, Nascent, Established)
 X1 Explanatory Variable | Way of Teaching
@@
 
-## Explaining Way of Teaching
+## How Much the Way of Teaching Supports Self-Confidence
 
@@
 
-## Variation in how well Education encourages Self Confidence in OECD Countries
+## Variation in how the Way of Teaching is Perceived to Support Self-Confidence
 
@@
 
-## Variation in Impact of Education on Self Confidence
+## Variation in Perceived Impact of the Way of Teaching on Self Confidence
 ```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
@@
 
-- This figure is a national-level precentage
+- This figure is a national-level percentage
 
-- This measure was chosen to provide some insight on how personal values are shaped, especially in terms of self-confidence.
+- This measure was chosen to provide some insight on self-confidence at the country level
 
-## Differences in Perceived Capability in OECD Countries
+## Differences in Perceived Capabilities to start a Business
 
@@
 
-## Time Variation in Perceived Capabilities
+## Variation in Perceived Capabilities to Start a Business
 ```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
@@
 
-## Fear of Failure
+## Fear of Failure Despite Good Perceived Opportunities
 
@@
 
-## Variation in Fear Perception in OECD Countries
+## Variation in Fear of Failure Despite Perceived Good Opportunities
 
@@
 
-## Variation in Fear of Failure
+## Variation in Fear of Failure Despite Good Perceived Opportunities
 ```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
@@
 
-## Perceived Opportunities
+## Perceived Good Opportunities to Start a Business
 
@@
 
-## Varying Perceptions of Good Opportunities to Start a Business in OECD Countries
+## Varying Perceptions of Good Opportunities to Start a Business
 
@@
 
-- We decided to do this because the coefficients do not change signficantly when the country-specific effects are ignored.
+- We decided to do this because the coefficients do not change significantly when the country-specific effects are ignored.
 
@@
 
-```{r, echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+## Conclusions
 
-```
+- Some expected trends observed
+
+- Inconclusive results
+
+- Lack of reliable data

### 2014-12-04 FinalAssignment/FromEducationToEntrepreneurship.Rmd
Reorganized repository

--- 2014-12-02 FromEducationToEntrepreneurship.Rmd
@@
 98 not applicable
+
+After searching through many potential data sources about education and finding no indicators suitable to trace our causal chain, we were forced to use that one item of a survey however low quality it might be.
+
+As a matter of fact, there are many reasons for which we should be concerned about that data and its quality.
+
+First, it was not always collected which makes any measure hard to follow through time, it is only since 2009 and 2011 that the NES was made compulsory.
+
+Second, the National Expert Surveys are very subjective data. For each entrepreneurial framework condition, that is:
+
+1. Finance  
+2. Government policies  
+3. Government programs  
+4. Entrepreneurial Education and Training  
+5. Research and Development Transfer (R & D)  
+6. Commercial and professional infrastructure  
+7. Internal Market openness  
+8. Physical infrastructure and services  
+9. Cultural and social norms
+
+Only four experts per framework condition are consulted in each country participating.
+
+Third, the collection of data could arguably be improved.
+Indeed, it is outsourced by GEM Coordination Team to national teams which seem to manage the time allowed for collection poorly ???METHODOLOGY NES REPORT HERE MAIN BIB ???
+.
+The national teams also tend to rely solely on their own personal networks.
+Which does not guarantee to get the best experts on each topic.
+
+Fourth, as a result of the flows above mentioned, we observe a lot of variation from year to year up to 0.73 on a scale from 1 to 5, that is up to 14.6% (UK 2007 / UK 2009).
+Which is far from what one would expect.
+Indeed, it seems very doubtful to say that the way of teaching in any country varies so much over time.
+Educational reforms are much more rare and one should on the contrary expect to see much more stability, almost a constant over a decade.
 

### 2014-12-04 index.Rmd
Try to set panels

@@
 
-print(Opp_map, tag = 'chart')
-
 ```
@@
              C=rpois(100, 50))
+
 print( 
@@
 )
+
+print(Opp_map, tag = 'chart')
+
 ```

### 2014-12-06 index.Rmd
Added interactive chart

--- 2014-12-02 index.Rmd
@@
 
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
-
-# Library required packages
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+library(ggvis)
+library("devtools")
 library(googleVis)
@@
 library(repmis)
+library(reshape2)
+library(RJSONIO)
+library(shiny)
+library(httpuv)
 
@@
 # Create a vector of country codes
+
 D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")
@@
 
+# Melt D4 df
+D6 <- melt(data = D4,
+                  id.vars = c("Country", "iso2c"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Change column titles to  year and PerceivedOpportunities
+names(D6) <- gsub("value", "PerceivedOpportunities", names(D6))    
+names(D6) <- gsub("variable", "Year", names(D6))
+
 # Set columns as numeric
-D4[,"2001"] <- as.numeric(D4[,"2001"])
-D4[,"2002"] <- as.numeric(D4[,"2002"])
-D4[,"2003"] <- as.numeric(D4[,"2003"])
-D4[,"2004"] <- as.numeric(D4[,"2004"])
-D4[,"2005"] <- as.numeric(D4[,"2005"])
-D4[,"2006"] <- as.numeric(D4[,"2006"])
-D4[,"2007"] <- as.numeric(D4[,"2007"])
-D4[,"2008"] <- as.numeric(D4[,"2008"])
-D4[,"2009"] <- as.numeric(D4[,"2009"])
-D4[,"2010"] <- as.numeric(D4[,"2010"])
-D4[,"2011"] <- as.numeric(D4[,"2011"])
-D4[,"2012"] <- as.numeric(D4[,"2012"])
-D4[,"2013"] <- as.numeric(D4[,"2013"])
+D6[,"PerceivedOpportunities"] <- as.numeric(D6[,"PerceivedOpportunities"])
 
-# Generate a new column with mean of all other columns
-D4$mean <- rowMeans(subset(D4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
-                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)
+# Save cleaned df
+D7 <- D6
 
-# Drop year columns, leaving only mean column
-D4$'2001' <- NULL
-D4$'2002' <- NULL
-D4$'2003' <- NULL
-D4$'2004' <- NULL
-D4$'2005' <- NULL
-D4$'2006' <- NULL
-D4$'2007' <- NULL
-D4$'2008' <- NULL
-D4$'2009' <- NULL
-D4$'2010' <- NULL
-D4$'2011' <- NULL
-D4$'2012' <- NULL
-D4$'2013' <- NULL
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
 
-# Create 
-D4[, 3] <- round(log(D4[, 3]), digits = 2)
-```
+# Subset D6
+D8 <- subset(D6, iso2c %in% myvars2)
 
-### Variation in Perceived Opportunities in OECD
-```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis'}
-# Plot
-Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
-                      colorvar = 'mean',
-                      options = list(
-                        colors = "['#fff7bc', '#d95f0e']"
-))
+# Create a scatterplot
+D8 %>% 
+  ggvis(~Year, ~PerceivedOpportunities) %>%
+  layer_points(fill = ~factor(Country)) %>%
+  group_by(Country)
 
-print(Opp_map, tag = 'chart')
+D8 %>%
+  ggvis(~Year, ~PerceivedOpportunities) %>%
+  layer_points(fill = ~factor(Country)) %>%
+  group_by(Country)
 
@@
 
-<br>
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
 
-<br
+CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")
 
-### Distribution of Perceived Opportunities in OECD Countries
+# Melt CD df
 
-```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-library(ggvis)
+CD2 <- melt(data = CD,
+                  id.vars = c("Country", "Year"),
+                  measure.vars = c("WayofTeaching", "PercentFear", "PercentNascent", "PercentPerceived",
+                                   "PercentOwner", "PercentIntention", "PercentOpportunities"))
 
-D4 %>% ggvis(~mean, fill := "#2c7fb8") %>% layer_histograms(width = 0.2)
+names(CD2) <- gsub("variable", "Survey Question", names(CD2))
+names(CD2) <- gsub("value", "Response", names(CD2))
 
-#D4 %>% 
- # ggvis(~mean, fill := "#2c7fb8") %>% 
-  #layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
-   #                center = input_slider(0, 2, step = 0.05, label = "center"))
+CD3 <- na.omit(CD2)
+
+CD$Year <- as.Date(as.character(CD$Year), format = "%Y")
+
+R <- gvisMotionChart(CD, idvar = "Country", timevar = "Year")
+
+print(R, tag = 'chart')
+```

### 2014-12-06 index.Rmd
Deleted unnecessary variable in interactive webchart

@@
 
-# Melt CD df
+# Set Year column as a date
+CD$Year <- as.Date(as.character(CD$Year), format = "%Y")
 
-CD2 <- melt(data = CD,
-                  id.vars = c("Country", "Year"),
-                  measure.vars = c("WayofTeaching", "PercentFear", "PercentNascent", "PercentPerceived",
-                                   "PercentOwner", "PercentIntention", "PercentOpportunities"))
-
-names(CD2) <- gsub("variable", "Survey Question", names(CD2))
-names(CD2) <- gsub("value", "Response", names(CD2))
-
-CD3 <- na.omit(CD2)
-
-CD$Year <- as.Date(as.character(CD$Year), format = "%Y")
+# Dropp X column
+CD$X <- NULL
 

### 2014-12-06 ExtraCharts_index/ExtraCharts.Rmd
Removed unnecessary charts and added website text

--- 2014-12-06 index.Rmd
@@
 ---
-title: 'From Education to Entrepreneurship'
+title: "Untitled"
 author: "Sam"
-date: "November 20, 2014"
+date: "December 6, 2014"
 output: html_document
@@
 
-### Under construction, but here's a preview
-
 ```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-library(ggvis)
-library("devtools")
-library(googleVis)
-library(countrycode)
-library(repmis)
-library(reshape2)
-library(RJSONIO)
-library(shiny)
-library(httpuv)
 
@@
 ```
-
-```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-
-CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")
-
-# Set Year column as a date
-CD$Year <- as.Date(as.character(CD$Year), format = "%Y")
-
-# Dropp X column
-CD$X <- NULL
-
-R <- gvisMotionChart(CD, idvar = "Country", timevar = "Year")
-
-print(R, tag = 'chart')
-```

### 2014-12-06 index.Rmd
Removed unnecessary charts and added website text

@@
 title: 'From Education to Entrepreneurship'
-author: "Sam"
-date: "November 20, 2014"
+author: "Sam Dundon and Thierry Racaud"
+date: "December 6, 2014"
 output: html_document
@@
 
-### Under construction, but here's a preview
+**Key Question**
+To what extent do teaching methods supporting self-confidence affect the rate of entrepreneurship in OECD countries?
+
+We have drawn on publicly availabile data from the Global Entrepreneurship Monitor (GEM) National Entrepreneurship Survey (NES) and Adult Population Survey (APS) to create graphic visualizations of participants' responses to surveys about entrepreneurship.
+
+The following interactive chart can be utilized to see the relationship between the variables we investigated.
+Among other features, the independent and dependent variables can be selected to see the relationship between each of the variables.
 
@@
 library(ggvis)
-library("devtools")
+library(devtools)
 library(googleVis)
@@
 library(httpuv)
-
-# Import GEM data frame
-PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE, na.strings = "-")
-
-## Add country codes and place new column at beginning of the data frame
-# Create a vector of country codes
-
-D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")
-
-# Create a new column and insert the country code vector
-PerceivedOpportunities$new.col <- D2
-
-# Reorder columns so country code is first
-D3 <- PerceivedOpportunities[,c(15,1:14)]
-
-# Rename first column
-D4 <- plyr::rename(x = D3, 
-                   replace = c("new.col" = "iso2c"))
-
-# Remove X's in D4 year columns
-names(D4) <- gsub("X", "", names(D4))
-
-# Melt D4 df
-D6 <- melt(data = D4,
-                  id.vars = c("Country", "iso2c"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010"))
-
-# Change column titles to  year and PerceivedOpportunities
-names(D6) <- gsub("value", "PerceivedOpportunities", names(D6))    
-names(D6) <- gsub("variable", "Year", names(D6))
-
-# Set columns as numeric
-D6[,"PerceivedOpportunities"] <- as.numeric(D6[,"PerceivedOpportunities"])
-
-# Save cleaned df
-D7 <- D6
-
-# Create country vector to subset
-myvars2 <- c('US','FR','DE','JP','GB')
-
-# Subset D6
-D8 <- subset(D6, iso2c %in% myvars2)
-
-# Create a scatterplot
-D8 %>% 
-  ggvis(~Year, ~PerceivedOpportunities) %>%
-  layer_points(fill = ~factor(Country)) %>%
-  group_by(Country)
-
-D8 %>%
-  ggvis(~Year, ~PerceivedOpportunities) %>%
-  layer_points(fill = ~factor(Country)) %>%
-  group_by(Country)
-
-```
-
-```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
 
@@
 ```
+
+As indicated in the chart, our analysis investigated the variation among OECD countries in each of the following variables.

### 2014-12-06 index.Rmd
Added and revised text, added map for WayofTeaching

@@
 
-**Key Question**
+### Key Question 
 To what extent do teaching methods supporting self-confidence affect the rate of entrepreneurship in OECD countries?
@@
 
+### Selected Variables
+
 As indicated in the chart, our analysis investigated the variation among OECD countries in each of the following variables.
+
+Variable | Indicator 
+-------------|---------------
+Y Dependent Variable | Rate of Entrepreneurship (Intention, Nascent, Established)
+X1 Explanatory Variable | Way of Teaching
+X2 Control Variable | Perceived Capabilities
+X3 Control Variable | Fear of Failure / Perceived Opportunities
+X4 Control Variable | Perceived Opportunities
+
+### Causal Chain
+
+Our decision to select and investigate these variables was based on the following causal chain
+
+1. An education system that reinforces self-confidence
+
+2. Higher degree of individual self-esteem
+
+3. Higher probability an individual becomes an entrepreneur
+
+4. Higher rate of entrepreneurship at a country-level
+
+### Geographic Variation in our Explanatory Variable
+
+As expected, there is significant variation among OECD countries with respect to each of the variables investigated.
+The most important of these variables is our explanatory variable, "WayofTeaching".
+This is a measure of how well teaching methods support self-confidence in each country.
+The following interactive chart displays variation in self confidence with the log of the mean survey response from each country over 2001-2013 timeframe.
+
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+# Import GEM data frame
+WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")
+
+# Drop unnecessary column 1
+WayofTeaching$X <- NULL
+
+# Change data from long to wide format
+WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")
+
+# Delete variable name in Year columns
+names(WT) <- gsub("WayofTeaching.", "", names(WT))
+
+# Duplicate df for future use
+WT2 <- WT
+
+# Generate a new column with mean of all other columns
+WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
+                                          "2009", "2010")), na.rm = TRUE)
+
+# Drop year columns, leaving only mean column
+WT$'2001' <- NULL
+WT$'2002' <- NULL
+WT$'2003' <- NULL
+WT$'2004' <- NULL
+WT$'2005' <- NULL
+WT$'2006' <- NULL
+WT$'2007' <- NULL
+WT$'2008' <- NULL
+WT$'2009' <- NULL
+WT$'2010' <- NULL
+WT$'2011' <- NULL
+WT$'2012' <- NULL
+WT$'2013' <- NULL
+WT$row.names <- NULL
+
+# Create 
+WT[, 3] <- round(log(WT[, 3]), digits = 2)
+```
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+library(googleVis)
+
+# Plot
+WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
+                      colorvar = 'mean',
+                      options = list(
+                        colors = "['#ece7f2', '#2b8cbe']"
+))
+
+print(WT_map, tag = 'chart')
+
+```

### 2014-12-06 index.Rmd
Minor formatting additions

@@
 
+<br>
+
 ### Key Question 
@@
 
-We have drawn on publicly availabile data from the Global Entrepreneurship Monitor (GEM) National Entrepreneurship Survey (NES) and Adult Population Survey (APS) to create graphic visualizations of participants' responses to surveys about entrepreneurship.
+We have drawn on publicly availabile data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) National Expert Survey (NES) and Adult Population Survey (APS) to create graphic visualizations of participants' responses to surveys about entrepreneurship.
 
@@
 Among other features, the independent and dependent variables can be selected to see the relationship between each of the variables.
+The variables are defined in detail below.
 
@@
 
-### Selected Variables
+<br>
 
-As indicated in the chart, our analysis investigated the variation among OECD countries in each of the following variables.
+### Variables:
 
-Variable | Indicator 
--------------|---------------
-Y Dependent Variable | Rate of Entrepreneurship (Intention, Nascent, Established)
-X1 Explanatory Variable | Way of Teaching
-X2 Control Variable | Perceived Capabilities
-X3 Control Variable | Fear of Failure / Perceived Opportunities
-X4 Control Variable | Perceived Opportunities
+1. **Entrepreneurial Intention**: Percentage of 18-64 population (individuals involved in any stage of entrepenerurial activity excluded) who intend to start a business within three years.
+
+2.
+**Nascent Entrepreneurship**: Percentage of 18-64 population who are currently a nascent entrepreneur, i.e., actively involved in setting up a business they will own or co-own; this business has not paid salaries, wages, or any other payments to the owners for more than three months.
+
+3.
+**Established Entrepreneur**: Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid sallaries, wages, or any other payments to the owners for more than 42 months.
+
+4. **Way of Teaching**: In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative.
+
+5. **Perceived Capabilities**: Percentage of 18-64 population who believe to have the required skills and knowledge to start a business
+
+6. **Fear of Failure**: Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
+
+7. **Perceived Opportunities**: Percentage of 18-64 population who see good opportunities to start a firm in the area where they live
+
+<br>
 
@@
 4. Higher rate of entrepreneurship at a country-level
+
+<br>
 
@@
 ```
+
+<br>
+
+### Statistical Analysis
+
+The variables indicated above were used to obtain inferential statistics:
+
+Variable | Indicator 
+-------------|---------------
+Y Dependent Variable | Rate of Entrepreneurship (Intention, Nascent, Established)
+X1 Explanatory Variable | Way of Teaching
+X2 Control Variable | Perceived Capabilities
+X3 Control Variable | Fear of Failure / Perceived Opportunities
+X4 Control Variable | Perceived Opportunities
+
+Controlling for country-specific effects,

### 2014-12-06 index.Rmd
Created imputed dataframes
Added imputed dfs

@@
 Controlling for country-specific effects,
+
+```{r echo = FALSE, cache= TRUE, include= FALSE, results= 'asis'}
+RG1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+
+# Library Zelig (can be buggy if loaded to early)
+library(Zelig)
+library("Amelia")
+
+# Omit omitted data from simulation
+CD_omit <- na.omit(CD)
+
+# Run a least squares regression with Zelig
+Z1 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omit, model = "ls")
+
+summary(Z1)
+
+# Impute missing values for regression analysis (Amelia)
+Cimputed <- Amelia::amelia(CD, m = 5, idvars = c("iso2c", "Country"), ts = "Year")
+
+# Create CSV of imputed values
+write.amelia(Cimputed, "Cimputed", separate = TRUE, format = "csv")
+
+# Set working directory to local repository
+setwd('~/Assign2Education/')
+
+# Open csv
+Cimputed <- read.table("Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)
+
+# Regression equation with imputed values
+Z2 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = Cimputed, model = "ls")
+```

### 2014-12-07 Index_sources/Ameila_source.Rmd
Added Zelig sims

--- 2014-12-06 index.Rmd
@@
 ---
-title: 'From Education to Entrepreneurship'
-author: "Sam Dundon and Thierry Racaud"
-date: "December 6, 2014"
+title: "Index_sources"
+author: "Sam"
+date: "December 7, 2014"
 output: html_document
@@
 
-### Key Question 
-To what extent do teaching methods supporting self-confidence affect the rate of entrepreneurship in OECD countries?
+``````{r echo = FALSE, cache= TRUE, include= FALSE, results= 'asis'}
 
-We have drawn on publicly availabile data from the Global Entrepreneurship Monitor (GEM) National Entrepreneurship Survey (NES) and Adult Population Survey (APS) to create graphic visualizations of participants' responses to surveys about entrepreneurship.
-
-The following interactive chart can be utilized to see the relationship between the variables we investigated.
-Among other features, the independent and dependent variables can be selected to see the relationship between each of the variables.
-
-```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-library(ggvis)
-library(devtools)
-library(googleVis)
-library(countrycode)
-library(repmis)
-library(reshape2)
-library(RJSONIO)
-library(shiny)
-library(httpuv)
+### Generate a version of "CompleteDataset" with imputed values for additional analysis
 
@@
 
-R <- gvisMotionChart(CD, idvar = "Country", timevar = "Year")
+# Impute missing values for regression analysis (Amelia)
+Cimputed <- Amelia::amelia(CD, m = 5, idvars = c("iso2c", "Country"), ts = "Year")
 
-print(R, tag = 'chart')
-```
-
-### Selected Variables
-
-As indicated in the chart, our analysis investigated the variation among OECD countries in each of the following variables.
-
-Variable | Indicator 
--------------|---------------
-Y Dependent Variable | Rate of Entrepreneurship (Intention, Nascent, Established)
-X1 Explanatory Variable | Way of Teaching
-X2 Control Variable | Perceived Capabilities
-X3 Control Variable | Fear of Failure / Perceived Opportunities
-X4 Control Variable | Perceived Opportunities
-
-### Causal Chain
-
-Our decision to select and investigate these variables was based on the following causal chain
-
-1. An education system that reinforces self-confidence
-
-2. Higher degree of individual self-esteem
-
-3. Higher probability an individual becomes an entrepreneur
-
-4. Higher rate of entrepreneurship at a country-level
-
-### Geographic Variation in our Explanatory Variable
-
-As expected, there is significant variation among OECD countries with respect to each of the variables investigated.
-The most important of these variables is our explanatory variable, "WayofTeaching".
-This is a measure of how well teaching methods support self-confidence in each country.
-The following interactive chart displays variation in self confidence with the log of the mean survey response from each country over 2001-2013 timeframe.
-
-```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-# Import GEM data frame
-WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")
-
-# Drop unnecessary column 1
-WayofTeaching$X <- NULL
-
-# Change data from long to wide format
-WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")
-
-# Delete variable name in Year columns
-names(WT) <- gsub("WayofTeaching.", "", names(WT))
-
-# Duplicate df for future use
-WT2 <- WT
-
-# Generate a new column with mean of all other columns
-WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
-                                          "2009", "2010")), na.rm = TRUE)
-
-# Drop year columns, leaving only mean column
-WT$'2001' <- NULL
-WT$'2002' <- NULL
-WT$'2003' <- NULL
-WT$'2004' <- NULL
-WT$'2005' <- NULL
-WT$'2006' <- NULL
-WT$'2007' <- NULL
-WT$'2008' <- NULL
-WT$'2009' <- NULL
-WT$'2010' <- NULL
-WT$'2011' <- NULL
-WT$'2012' <- NULL
-WT$'2013' <- NULL
-WT$row.names <- NULL
-
-# Create 
-WT[, 3] <- round(log(WT[, 3]), digits = 2)
-```
-
-```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
-library(googleVis)
-
-# Plot
-WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
-                      colorvar = 'mean',
-                      options = list(
-                        colors = "['#ece7f2', '#2b8cbe']"
-))
-
-print(WT_map, tag = 'chart')
+# Create CSV of imputed values
+write.amelia(Cimputed, "Cimputed", separate = TRUE, format = "csv")
 

### 2014-12-07 index.Rmd
Added Zelig sims

--- 2014-12-06 index.Rmd
@@
 
-We have drawn on publicly availabile data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) National Expert Survey (NES) and Adult Population Survey (APS) to create graphic visualizations of participants' responses to surveys about entrepreneurship.
+We have drawn on publicly availabile data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) National Expert Survey (NES) and Adult Population Survey (APS) to create graphic visualizations of participants' responses to surveys about entrepreneurship in [OECD (Organisation for Economic Co-operation and Development)](http://www.oecd.org/) countries.
 
@@
 
+# Import "CompleteData" df from repository
 CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")
@@
 Controlling for country-specific effects,
+
+```{r echo = FALSE, cache= TRUE, include= FALSE, results= 'asis'}
+
+# Library Zelig (can be buggy if loaded to early)
+library(Zelig)
+
+# Library Amelia for imputed data
+library(Amelia)
+
+############ Running a regression with full df (including omitted variables)
+RG1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+
+############ Running a regression omitting omitted variables
+
+# Generate a df omitting omitted variables
+CD_omitted <- na.omit(CD)
+
+# Run a least squares regression with Zelig
+Z1 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")
+
+# Set range of PercentPerceived values in simulation
+x.out1 <- setx(Z1, PercentPerceived = 9:67)
+
+# Run simulation (default 1000 trials)
+simz1 <- sim(Z1, x = x.out1)
+
+# Plot simulation
+
+############ Runnig a Zelig regression with imputed data and omitting remaining omitted variables
+
+# Import csv of df with imputed figures (created in Index_sources/Amelia_source)
+CI <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/gh-pages/Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)
+
+CI_omitted <- na.omit(CI)
+
+# Regression equation with imputed values
+Z2 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")
+
+# Set range of PercentPerceived values in simulation
+x.out2 <- setx(Z2, PercentPerceived = 9:67)
+
+# Run simulation (default 1000 trials)
+simz2 <- sim(Z2, x = x.out2)
+
+```
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+
+par(mfrow = c(1, 2))
+plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurial Intention', main = "Unimputed")
+plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurial Intention', main = "Imputed")
+
+```

### 2014-12-07 index.Rmd
Added formatted Zelig tables and began explanation of results

@@
 
-Controlling for country-specific effects,
+Our original intention was to conduct a country- the relationship between the way of teaching and the rate of entrepreneurship in each OECD country.
+To do so, we should run a fixed effects regression for each country.
+When doing so, however, we find that our explanatory variable has a negative coefficient and our regression equation contains a negative slope.
+This may be due to a lack of available data, a flawed survey method, or inaccurate expectations.
 
@@
 ############ Running a regression with full df (including omitted variables)
-RG1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+RG1 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
 
@@
 # Run a least squares regression with Zelig
-Z1 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")
+Z1 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")
 
@@
 
-# Plot simulation
-
 ############ Runnig a Zelig regression with imputed data and omitting remaining omitted variables
@@
 
+# Omit variables that could not be imputed by Adelia (b/c of lack of data)
 CI_omitted <- na.omit(CI)
@@
 # Regression equation with imputed values
-Z2 <- zelig(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")
+Z2 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")
+
+############ Set range of values for Z1 and Z2
 
@@
 
+# Set range of WayofTeaching values in simulation
+x.out3 <- setx(Z1, WayofTeaching = 1.353:3.278)
+
+# Run simulation (default 1000 trials)
+simz3 <- sim(Z1, x = x.out3)
+
+# Set range of WayofTeaching values in simulation
+x.out4 <- setx(Z2, WayofTeaching = 1.128:3.312)
+
+# Run simulation (default 1000 trials)
+simz4 <- sim(Z2, x = x.out4)
+
 ```
 
-```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
+library("Zelig")
 
-par(mfrow = c(1, 2))
-plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurial Intention', main = "Unimputed")
-plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurial Intention', main = "Imputed")
+# Set layout
+par(mfrow = c(2, 2))
+
+# Plot simz1 (unimputed)
+plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner', main = "Unimputed")
+
+# Plot simz2 (imputed)
+plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner', main = "Imputed")
+
+# Plot simz3 (unimputed)
+plot(simz3, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner', main = "Unimputed")
+
+# Plot simz4 (imputed)
+plot(simz4, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner', main = "Imputed")
 

### 2014-12-07 index.Rmd
Updated Zelig sims and added explanatory text

@@
 
-The following interactive chart can be utilized to see the relationship between the variables we investigated.
+The following interactive chart can be utilized to see the relationship between the variables we investigated (this can be best viewed in a browser such as [Chrome](https://www.google.com/chrome/)).
 Among other features, the independent and dependent variables can be selected to see the relationship between each of the variables.
@@
 
-Our original intention was to conduct a country- the relationship between the way of teaching and the rate of entrepreneurship in each OECD country.
-To do so, we should run a fixed effects regression for each country.
-When doing so, however, we find that our explanatory variable has a negative coefficient and our regression equation contains a negative slope.
-This may be due to a lack of available data, a flawed survey method, or inaccurate expectations.
+Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between higher self-confidence reinforcement in teaching and our dependent variables selected as indicators of the entrepreneurship rate.
+Instead, we found that the Way of Teaching is not significant, and when controlling for country-specific effects, has a negative relationship with our explanatory variables.
+Overall, however, we can demonstrate the results of our least square regression equation in the four charts below (omitting the country-specific effects).
+We chose to simulate different values in "Percent Perceived Capabilities" and "Way of Teaching" because they are both proxies for self-confidence.
 
-```{r echo = FALSE, cache= TRUE, include= FALSE, results= 'asis'}
+The charts labled "Unimputed" were created using only data collected from GEM.
+This simulation is not possible with missing data, so observations with missing data were omitted.
+To try to address this, we used the R program Amelia to generate an imputed data frame.
+This program uses statistical inference to generate this data (more information on Amelia can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).
+Simulations titled "Imputed" were calculated using this imputed data frame.
 
-# Library Zelig (can be buggy if loaded to early)
+```{r echo = FALSE, cache= FALSE, include= FALSE}
+
+# Library Zelig (can be buggy if loaded too early)
 library(Zelig)
@@
 RG1 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
+
+RG2 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
 

### 2014-12-07 index.Rmd
Added formatted Zelig charts, fixed syntax and organized code chunks, added conclusion and explanation of regression estimation and results

@@
 
-Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between higher self-confidence reinforcement in teaching and our dependent variables selected as indicators of the entrepreneurship rate.
-Instead, we found that the Way of Teaching is not significant, and when controlling for country-specific effects, has a negative relationship with our explanatory variables.
-Overall, however, we can demonstrate the results of our least square regression equation in the four charts below (omitting the country-specific effects).
-We chose to simulate different values in "Percent Perceived Capabilities" and "Way of Teaching" because they are both proxies for self-confidence.
+Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the  dependent variables we selected as indicators of the entrepreneurship rate.
+Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant and has a negative relationship with our explanatory variables.
 
-The charts labled "Unimputed" were created using only data collected from GEM.
+Overall, however, if we omit country-specific effects, we can demonstrate that the Way of Teaching and the Percent Perceived Good Opportunities are statistically significant in the model indicated below.
+
+<br>
+
+$Percent Perceived Opportunities = -6.82 + 1.03WayofTeaching + 0.10Percent Perceived Capability + 0.21Percent Fear Failure$
+
+$+$ $0.12Percent Perceived Opportunities - 0.005Percent Fear Failure$ $*$ $Percent Perceived Opportunities$
+
+<br>
+
+We can show the relationship between the dependent and explanatory variables in the four simulations below.
+The R package Zelig allows us to set parameters for an explanatory variable and simulate 1000 trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).
+We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.
+A regression output table has also been included below.
+
+The simulations labled "Unimputed" were created using only data collected from GEM.
 This simulation is not possible with missing data, so observations with missing data were omitted.
-To try to address this, we used the R program Amelia to generate an imputed data frame.
-This program uses statistical inference to generate this data (more information on Amelia can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).
+In an attempt to increase the accuracy of this model, we used the R program Amelia to generate an imputed data frame.
+This program uses statistical inference to generate this data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).
 Simulations titled "Imputed" were calculated using this imputed data frame.
@@
 
-# Set range of PercentPerceived values in simulation
-x.out1 <- setx(Z1, PercentPerceived = 9:67)
-
-# Run simulation (default 1000 trials)
-simz1 <- sim(Z1, x = x.out1)
-
 ############ Runnig a Zelig regression with imputed data and omitting remaining omitted variables
@@
 
-############ Set range of values for Z1 and Z2
+############ Set range of values for Z1 and Z2 using imputed and not imputed dfs
 
-# Set range of PercentPerceived values in simulation
+####### Simulate Percent Perceived
+
+# Set range of PercentPerceived values in simulation (NOT IMPUTED)
+x.out1 <- setx(Z1, PercentPerceived = 9:67)
+
+# Run simulation (default 1000 trials) (NOT IMPUTED)
+simz1 <- sim(Z1, x = x.out1)
+
+# Set range of PercentPerceived values in siumlation (IMPUTED)
 x.out2 <- setx(Z2, PercentPerceived = 9:67)
 
-# Run simulation (default 1000 trials)
+# Run simulation (default 1000 trials) (IMPUTED)
 simz2 <- sim(Z2, x = x.out2)
 
-# Set range of WayofTeaching values in simulation
+####### Simulate Way of Teaching
+
+# Set range of WayofTeaching values in simulation (NOT IMPUTED)
 x.out3 <- setx(Z1, WayofTeaching = 1.353:3.278)
 
-# Run simulation (default 1000 trials)
+# Run simulation (default 1000 trials) (NOT IMPUTED)
 simz3 <- sim(Z1, x = x.out3)
 
-# Set range of WayofTeaching values in simulation
+# Set range of WayofTeaching values in simulation (IMPUTED)
 x.out4 <- setx(Z2, WayofTeaching = 1.128:3.312)
 
-# Run simulation (default 1000 trials)
+# Run simulation (default 1000 trials) (IMPUTED)
 simz4 <- sim(Z2, x = x.out4)
@@
 # Plot simz1 (unimputed)
-plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner', main = "Unimputed")
+plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
+     main = "Unimputed (Equation 1)")
 
 # Plot simz2 (imputed)
-plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner', main = "Imputed")
+plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
+     main = "Imputed (Equation 2)")
 
 # Plot simz3 (unimputed)
-plot(simz3, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner', main = "Unimputed")
+plot(simz3, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner',
+     main = "Unimputed (Equation 1)")
 
 # Plot simz4 (imputed)
-plot(simz4, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner', main = "Imputed")
+plot(simz4, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner',
+     main = "Imputed (Equation 2)")
 
 ```
+
+```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
+library(stargazer)
+
+# Create regression output table
+labels <- c('Way of Teaching', 'National Level Perceived Capabilities', 'National Level Avg Fear of Failure',
+            'National Level Avg Perceived Good Opportunities', 
+            'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities',
+            '(Intercept)')
+
+dlabels <- c('National Level Average Percent Owning a Business')
+
+```
+
+<br>
+
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
+
+stargazer::stargazer(Z1, Z2, covariate.labels = labels, dep.var.labels = dlabels,
+                     title = 'Linear Regression Estimates', notes = "Regression equation 1 is unimputed, regression equation 2 is imputed", digits = 2, type = 'html')
+
+```
+
+<br>
+
+### Conclusions
+
+Significant work remains to more clearly understand the extent of the relationship between teaching menthods supporting self-confidence and a country's rate of entrepreneurship.
+This research, however, does show that a positive relationship exists.
+One clear requirement of further analysis in this field is increased availability and consistency in collected data.
+Missing data generates substantial uncertainty and limits our ability to strongly state conclusions.
+This will need to be addressed for future projects.

### 2014-12-07 index.Rmd
Added space in subheadings
fixed spelling errors

@@
 
-### Key Question 
+### Key Research Question 
 To what extent do teaching methods supporting self-confidence affect the rate of entrepreneurship in OECD countries?
 
-We have drawn on publicly availabile data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) National Expert Survey (NES) and Adult Population Survey (APS) to create graphic visualizations of participants' responses to surveys about entrepreneurship in [OECD (Organisation for Economic Co-operation and Development)](http://www.oecd.org/) countries.
+<br>
+
+### Project Overview
+
+We have drawn on publicly available data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) National Expert Survey (NES) and Adult Population Survey (APS) to create graphic visualizations of participants' responses to surveys about entrepreneurship in [OECD (Organisation for Economic Co-operation and Development)](http://www.oecd.org/) countries.
 
@@
 
-1. **Entrepreneurial Intention**: Percentage of 18-64 population (individuals involved in any stage of entrepenerurial activity excluded) who intend to start a business within three years.
+1. **Entrepreneurial Intention**: Percentage of 18-64 population (individuals involved in any stage of entrepreneurial activity excluded) who intend to start a business within three years.
 
@@
 3.
-**Established Entrepreneur**: Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid sallaries, wages, or any other payments to the owners for more than 42 months.
+**Established Entrepreneur**: Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid salaries, wages, or any other payments to the owners for more than 42 months.
 
@@
 This is a measure of how well teaching methods support self-confidence in each country.
-The following interactive chart displays variation in self confidence with the log of the mean survey response from each country over 2001-2013 timeframe.
+The following interactive chart displays variation in self confidence with the log of the mean survey response from each country over 2001-2013 time frame.
 
@@
 
-The simulations labled "Unimputed" were created using only data collected from GEM.
+The simulations labeled "Unimputed" were created using only data collected from GEM.
 This simulation is not possible with missing data, so observations with missing data were omitted.
@@
 
-Significant work remains to more clearly understand the extent of the relationship between teaching menthods supporting self-confidence and a country's rate of entrepreneurship.
+Significant work remains to more clearly understand the extent of the relationship between teaching methods supporting self-confidence and a country's rate of entrepreneurship.
 This research, however, does show that a positive relationship exists.

### 2014-12-07 index.Rmd
Added R package citations

@@
 library(reshape2)
-library(RJSONIO)
 library(shiny)
 library(httpuv)
+
+pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny',
+          'httpuv', 'Zelig', 'stargazer', 'Amelia')
+repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')
 

### 2014-12-07 index.Rmd
Updated link to reflect reorganized repository

@@
 # Import csv of df with imputed figures (created in Index_sources/Amelia_source)
-CI <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/gh-pages/Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)
+CI <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/gh-pages/GEMData/Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)
 

### 2014-12-07 index.Rmd
Updated the branch README and fixed spelling errors

@@
 
-pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny',
-          'httpuv', 'Zelig', 'stargazer', 'Amelia')
+# Create a vector of packages used
+pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv', 'Zelig',
+          'stargazer', 'Amelia')
+
+# Create citations txt file
 repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')
@@
 
-# Dropp X column
+# Drop X column
 CD$X <- NULL

### 2014-12-07 PresentationandPaper/Presentation/EdEntrePres.Rmd
Created missing README files, deleted unneccesary files, and cleaned repository.

--- 2014-12-04 Presentation/EdEntrePres.Rmd
@@
 
-- Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.
+- Since we look at average individual self-confidence in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.
 

### 2014-12-09 index.Rmd
revised equation
Revised interactive chart and began building others

@@
 
+CD_copy <- CD
+
 # Drop X column
 CD$X <- NULL
+CD$iso2c <- NULL
 
-R <- gvisMotionChart(CD, idvar = "Country", timevar = "Year")
+R <- gvisMotionChart(CD, idvar = "Country", timevar = "Year", options = list(state='{"showTrails":false};'))
 
@@
 
-$Percent Perceived Opportunities = -6.82 + 1.03WayofTeaching + 0.10Percent Perceived Capability + 0.21Percent Fear Failure$
-
-$+$ $0.12Percent Perceived Opportunities - 0.005Percent Fear Failure$ $*$ $Percent Perceived Opportunities$
+$NationalLevelAveragePercentOwningaBusiness = -6.82 + 1.03WayofTeaching + 0.10Percent Perceived Capability +$  
+$0.21Percent Fear Failure$ $+$ $0.12Percent Perceived Opportunities - 0.005Percent Fear Failure$ $*$ $Percent Perceived Opportunities$
 
@@
 Simulations titled "Imputed" were calculated using this imputed data frame.
+
+```{r echo = FALSE, cache= FALSE, include= FALSE}
+
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
+
+# Subset CD
+CD_subset <- subset(CD_copy, iso2c %in% myvars2)
+
+```
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

--- 2014-12-04 FinalAssignment/FromEducationToEntrepreneurship.Rmd
@@
 author: "Sam Dundon and Thierry Racaud"
-date: "29 novembre 2014"
+date: "10 décembre 2014"
 output: html_document
@@
 
-### Policy Relevance
+### Abstract
+
+### Why we chose to look into Education to explain Entrepreneurship
 
@@
 That is, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors - not just structural and economic factors - in determining individual and societal tendencies to start a business, these factors are often not included in the decision-making process.
+
+Of course, what determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
+Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ??????
+2010 VERSION MAIN BIB ?????.
+Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done.
+
+Over a hundred years have passed since Max Weber tried to explain how religious-ethical motivations affect entrepreneurship [@weberprotestant], and today religion may be less effective in justifying why some are more likely to start businesses than others.
+Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” [@OECD2009].
+
 Actually, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.
-
-### Research Question
-
-To what extent do the behavioural characteristics of education systems - individualistic, group-oriented, reinforcing self-confidence - affect the rate of entrepreneurship across OECD countries?
-
-### Literature Review
-
-What determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
-Still, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ??????
-2010 VERSION MAIN BIB ?????.
-Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done, as the few studies that explored the relationship between attitudes and foundation activities barely searched what determined these attitudes.
-
-Over a hundred years has passed since Max Weber tried to explain how religious-ethical motivations affect entrepreneurship [@weberprotestant], and religion may be less effective in justifying why some are more likely to start businesses than others.
-Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” [@OECD2009].
 
@@
 Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on student self-confidence [@Scott1996].
-Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration into social networks" [@OECD2009].
-Yet, we intend to understand to what extent these individual characteristics are partly shaped through education systems and their personnel's attitudes.
+Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person ????????????and his or her integration into social networks????????" [@OECD2009].
+
+Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012 and the OECD PISA (Programme for International Student Assessment) LINK ?????
+also from 2012, there seem to be different amounts of entrepreneurial self-efficacy ?????and collectivism?????
+between countries.
+By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur.
+Here, the variable "perceived capabilites" has to be understood in a narrow sense, it refers only to the perceived capabilities to start a business.
+Seemingly the variable "fear of failure" only refers to the fear of failure as an obstacle that would prevent the people surveyed from starting a business, despite the good opportunities they may perceive.
+
+Variable | France | UK
+-------------|---------------|---------
+Fear of Failure (GEM 2012) | 43% | 36%
+Perceived Capabilities (GEM 2012) | 36% | 47%
+Sense of belonging (PISA 2012) | 47% | 79%
+
+So, although the research tends to hold self-confidence but also entrepreneurial self-efficacy as an individual feature, we intend to understand to what extent these individual characteristics are partly shaped at a collective societal level, and more specifically through education systems and their personnel's attitudes.
+Indeed, in the education literature, .....
 
@@
 Eventually, to put all these into perspective, along with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.
+
+Entrepreneurial self-efficacy has been widely called upon to explain both entrepreneurial intentions and actions. Especially by Boyd and Vozikis
+
+### Research Question
+
+To what extent do teaching methods supporting self-confidence impact the rate of entrepreneurship across OECD countries?
+
+### Literature Review
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-So, although the research tends to hold self-confidence but also entrepreneurial self-efficacy as an individual feature, we intend to understand to what extent these individual characteristics are partly shaped at a collective societal level, and more specifically through education systems and their personnel's attitudes.
-Indeed, in the education literature, .....
+So, although the research tends to hold self-confidence and also entrepreneurial self-efficacy as individual features, we intend to understand to what extent these individual characteristics are partly shaped at a collective or societal level by looking at the potential impact of education systems.
+Specifically, we wonder to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries.
+Indeed, regarding France and the United Kingdom, many cultural and educational parameters differ but, one stands out that is the positive reinforcement effectively in use throughout the compulsory education system in the UK.
+We would like to verify if this has to do with the amount of self-efficacy mentioned above.
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Actually, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.
+More recently, Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors.
+As they compared two Swedish regions similar in terms of structure and observed different outcomes, they too concluded that there might be a small cultural effect in attitudes toward start-up activities.
+Yet, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.
 
-Despite various claims of the existence of a cultural effect, few empirical studies have actually been carried out.
-It took a few decades more before Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors.
-As they compared two Swedish regions similar in terms of structure and observed different outcomes, they concluded that there might be a small cultural effect in attitudes toward start-up activities.
-
-Rather than trying to trace cultural patterns at large, we intend to focus on one key cultural institution, that is the education system.
+Rather than trying to trace cultural features at large, we intend to focus on one key cultural institution, that is the education system.
 Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on student self-confidence [@Scott1996].
-Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person ????????????and his or her integration into social networks????????" [@OECD2009].
+Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person" [@OECD2009].
 
 Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012 and the OECD PISA (Programme for International Student Assessment) LINK ?????
-also from 2012, there seem to be different amounts of entrepreneurial self-efficacy ?????and collectivism?????
-between countries.
+also from 2012, there seem to be different amounts of entrepreneurial self-efficacy between countries.
 By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur.
 Here, the variable "perceived capabilites" has to be understood in a narrow sense, it refers only to the perceived capabilities to start a business.
-Seemingly the variable "fear of failure" only refers to the fear of failure as an obstacle that would prevent the people surveyed from starting a business, despite the good opportunities they may perceive.
+Seemingly the variable "fear of failure" only refers to the fear of failure as an obstacle in starting a business, despite the perceived good opportunities.
 
@@
 Perceived Capabilities (GEM 2012) | 36% | 47%
-Sense of belonging (PISA 2012) | 47% | 79%
 
 So, although the research tends to hold self-confidence and also entrepreneurial self-efficacy as individual features, we intend to understand to what extent these individual characteristics are partly shaped at a collective or societal level by looking at the potential impact of education systems.
-Specifically, we wonder to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries.
-Indeed, regarding France and the United Kingdom, many cultural and educational parameters differ but, one stands out that is the positive reinforcement effectively in use throughout the compulsory education system in the UK.
-We would like to verify if this has to do with the amount of self-efficacy mentioned above.
+Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries.
+Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement.
+Indeed, positive reinforcement is effectively in use throughout the compulsory education system in the UK.
+We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-So, although the research tends to hold self-confidence and also entrepreneurial self-efficacy as individual features, we intend to understand to what extent these individual characteristics are partly shaped at a collective or societal level by looking at the potential impact of education systems.
+So, although the research tends to hold self-confidence and also entrepreneurial self-efficacy as individual features, we intend to understand to what extent these individual characteristics are partly shaped at a collective or societal level by looking at the potential impact of education systems and their personnel.
 Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries.
 Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement.
-Indeed, positive reinforcement is effectively in use throughout the compulsory education system in the UK.
+Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is more rarely activitated in France, and only on an voluntary individual teacher's basis.
 We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement.
-Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is more rarely activitated in France, and only on an voluntary individual teacher's basis.
+Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, but it is much more rarely activitated in France, and only on an voluntary individual teacher's basis.
 We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.
+
+This assumption draws from Boyd and Vozikis's ???????
+MAIN BIB ????????
+stating how entrepreneurial intentions are at least partially the result of thought processes, which " underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour".
+Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours".
+To assert this, they rely on Fishbein and Ajzen 1975 ??????
+MAIN BIB ????????
+who illustrate the relation between beliefs and behaviour as follows:
+
+1 Beliefs  
+2 Attitudes  
+3 Intentions  
+4 Behaviour
+
+There could even be an incidence of the intention to perform a certain behaviour and the actual performance of that behaviour, which could lead to look into skills, abilities and willpower.
+It is almost like "individuals would be predisposed to entrepreneurial intentions based upon a combination of both personal and contextual factors" ?????
+Boyd and Vosikis MAIN BIB ?????
+but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality.
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-There could even be an incidence of the intention to perform a certain behaviour and the actual performance of that behaviour, which could lead to look into skills, abilities and willpower.
+There could even be an incidence of the intention to perform a certain behaviour on the actual performance of that behaviour, which could lead to look into skills, abilities and willpower.
 It is almost like "individuals would be predisposed to entrepreneurial intentions based upon a combination of both personal and contextual factors" ?????
 Boyd and Vosikis MAIN BIB ?????
-but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality.
+but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality for "self-efficacy will moderate the relationship between the development of entrepreneurial intentions and the likelihood that these intentions will result in entrepreneurial actions or behaviour".
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality for "self-efficacy will moderate the relationship between the development of entrepreneurial intentions and the likelihood that these intentions will result in entrepreneurial actions or behaviour".
+Therefore, we will have to control for this entrepreneurial self-efficacy as we research potential effects of positive reinforcement.
 
-King and Sobel [@Kerry2008], among others, have already tried to show how school choice can increase the rate of youth entrepreneurship, but their perspective was slightly different.
+Another interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions, can increase the rate of youth entrepreneurship, but their perspective was slightly different.
 They  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Further, since self-confidence is considered to rely partly on one’s integration within social networks [@OECD2009], we will refer to cross-cultural studies about individualism and collectivism such as those of Green, Deschamps and Páez [@green2005variation], Pinillos and Reyes ????????
-MAIN BIB ??????, Freeman [@freeman1997demographic], Raeff, Greenfield and Quiroz [-@raeff2000conceptualizing].
-We will also cite more school-focused research like Yamauchi [@yamauchi1998individualism], Davies and Aurini [@davies2003homeschooling] for these have looked at individualism and collectivism in the classroom and in pedagogy respectively.
-
 Besides potential educational effects on self-confidence and social capital, we will need to control for all classic entrepreneurship determinants.
@@
 Eventually, to put all these into perspective, along with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.
-
-Entrepreneurial self-efficacy has been widely called upon to explain both entrepreneurial intentions and actions. Especially by Boyd and Vozikis
 

### 2014-12-11 index.Rmd
Revised website with simple charts

@@
 
+We have included our findings in a detailed paper available here.
+In sum, however, the most statistically significant and important findings from our analysis are that there is some evidence of a postitive relationship between higher levels of self-confidence reinforcement in teaching (a higher "WayofTeaching" score) and the rate of people owning their own business.
+This can be seen in the chart below.
+As we can see, however, when we add a trendline for each country the relationship becomes less certain.
+For example, in the case of the United States and the United Kingdom, the country-specific trend line has a decreasing slope.
+We believe this may be due to inconsistency in the survey and that a larger data set would allow us to more accurately describe the relationship between these variables.
+
+<br>
+
+```{r echo = FALSE, cache= FALSE, include= TRUE}
+
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
+
+# Subset CD
+CD_subset <- subset(CD_copy, iso2c %in% myvars2)
+
+CD_subset2 <- subset(CD_copy, iso2c %in% myvars2)
+
+# Remove unecessary columns
+CD_subset$X <- NULL
+CD_subset$iso2c <- NULL
+CD_subset$PercentFear <- NULL
+CD_subset$PercentNascent <- NULL
+CD_subset$PercentPerceived <- NULL
+CD_subset$PercentIntention <- NULL
+CD_subset$PercentOpportunities <- NULL
+
+# Create plot of WoT and PercentOwner
+CD_subset %>% 
+  ggvis(~WayofTeaching, ~PercentOwner) %>% 
+  layer_points(fill = ~factor(Country)) %>%
+  group_by(Country) %>%
+  layer_model_predictions(model = "lm")
+```
+
+<br>
+
+In addiiton, we can see a positive relationship between the percentage of respondents who believe there are opportunities to establish their own business (the percentage of people perceiving opportunities) and the rate of business ownership as reported in the survey.
+This relationship can be seen in the following chart.
+Similar to our findings above, this chart seems to show an overall positive relationship, but looking at country-specific factors, we can see that data from Japan indicates a negative slope.
+We believe access to additional data would allow us to more accurately describe the relationship between these variables and then to investigate why these differences exist.
+
+<br>
+
+```{r echo = FALSE, cache= FALSE, include= TRUE}
+
+# Drop unnecesssary columns in copied df
+CD_subset2$X <- NULL
+CD_subset2$iso2c <- NULL
+CD_subset2$PercentFear <- NULL
+CD_subset2$PercentNascent <- NULL
+CD_subset2$PercentPerceived <- NULL
+CD_subset2$PercentIntention <- NULL
+CD_subset2$WayofTeaching <- NULL
+
+# Create plot of PercentOpp and PercentOwner
+CD_subset2 %>% 
+  ggvis(~PercentOpportunities, ~PercentOwner) %>% 
+  layer_points(fill = ~factor(Country)) %>%
+  group_by(Country) %>%
+  layer_model_predictions(model = "lm")
+
+```
+
+(Take this for the paper)
+
 Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the  dependent variables we selected as indicators of the entrepreneurship rate.
@@
 Simulations titled "Imputed" were calculated using this imputed data frame.
-
-```{r echo = FALSE, cache= FALSE, include= FALSE}
-
-# Create country vector to subset
-myvars2 <- c('US','FR','DE','JP','GB')
-
-# Subset CD
-CD_subset <- subset(CD_copy, iso2c %in% myvars2)
-
-```
 

### 2014-12-11 index.Rmd
Edited code block
Editing output from charts

@@
 
-```{r echo = FALSE, cache= FALSE, include= TRUE}
+```{r echo = FALSE, cache= FALSE, include= TRUE, results='asis', warning=FALSE}
 
@@
 CD_subset %>% 
-  ggvis(~WayofTeaching, ~PercentOwner) %>% 
+  ggvis(x = ~WayofTeaching, y = ~PercentOwner) %>% 
   layer_points(fill = ~factor(Country)) %>%
@@
 CD_subset2 %>% 
-  ggvis(~PercentOpportunities, ~PercentOwner) %>% 
+  ggvis(x = ~PercentOpportunities, y = ~PercentOwner) %>% 
   layer_points(fill = ~factor(Country)) %>%

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on student self-confidence [@Scott1996].
-Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person" [@OECD2009].
+Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].
 
@@
 
+Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009]
+
+Variable | France | UK
+-------------|---------------|---------
+Sense of belonging (PISA 2012) | 47% | 79%
+
 Another interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions, can increase the rate of youth entrepreneurship, but their perspective was slightly different.
@@
 We believe there is a more widely spread systematic effect of educational features.
+
 The cross-cultural perspective on teaching and learning proposed by Watkins [@Watkins2010] shall help us compare countries.
+
 Cheng and Wong’s study about school effectiveness in East Asia [@Cheng2006] will also help.

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-The process of allocating public funds for education is an opportunity to make calculated long-term investments in a nation's populace.
-The rationale for decisions made during this process, however, is often difficult to understand.
-That is, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors - not just structural and economic factors - in determining individual and societal tendencies to start a business, these factors are often not included in the decision-making process.
+Whilst it is tempting to look at education systems in a very pragmatic way with ratios of teahers per student, of students per class, we suggest to use another kind of indicators in order to trace the potential long-term investment made by governments.
+Indeed, we believe that education systems can favour entrepreneurship and, beyond, GDP growth at the country-level, depending on how supportive of students' self-confidence and how socially inclusive they are.
+We see this process as manyfold but will only focus here on one of the potential causal relations.
+We want to understand specifically to want extent the support of individual self-confidence within education systems can affect the likelihood to become an entrepreneur, and thus impact the rate of entrepreneurship at the country level.
+
+In trying to explore what supports entrepreneurship at the country-level, one should start by refering to what research asserted for that matter.
+For this purpose, we refer here to the OECD reports availbale online here http://www.oecd.org/std/business-stats/48129925.pdf.
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 author: "Sam Dundon and Thierry Racaud"
-date: "10 décembre 2014"
+date: "10 december 2014"
 output: html_document
@@
 
-Whilst it is tempting to look at education systems in a very pragmatic way with ratios of teahers per student, of students per class, we suggest to use another kind of indicators in order to trace the potential long-term investment made by governments.
+Whilst it is tempting to look at education systems in a very pragmatic way with ratios of teachers per student, or students per class, we suggest to use another kind of indicators in order to trace the potential long-term investment made by governments.
 Indeed, we believe that education systems can favour entrepreneurship and, beyond, GDP growth at the country-level, depending on how supportive of students' self-confidence and how socially inclusive they are.
@@
 In trying to explore what supports entrepreneurship at the country-level, one should start by refering to what research asserted for that matter.
-For this purpose, we refer here to the OECD reports availbale online here http://www.oecd.org/std/business-stats/48129925.pdf.
+For this purpose, we refer here to the OECD reports available online here http://www.oecd.org/std/business-stats/48129925.pdf.
+Two main sorts of determinants or favourable conditions have been looked into, that is environmental factors and individual factors.
+Although we intend to focus more on individual factors, we
+want to mention here the environmental factors as they should be controled for. They actually divide into six broad categories:
+
+The regulatory framework, which includes administrative burdens, regulations and frameworks, as well as fiscal policy parameters.
+
+The market conditions, which include anti-trust laws, rules for competition, access to foreign markets, degree of public involvement and level of private demand.
+
+The access to finance, which includes access to debt financing, access to venture capital, and stock markets.
+
+The creation and diffusion of knowledge, which include research and development activity, transfer of non-commercial knowledge, co-operation among firms, technology availability and take-up.
+
+The entrepreneurial capabilities, which includes business and entrepreneurship education as well as immigration.
+
+The entrepreneurship culture of a given area or population (The OECD refers partially to the Global Entrepreneurship Monitor or GEM data).
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Of course, what determines entrepreneurship at a country-level has been long searched already but although economic, demographic or geographic factors have been looked at extensively, much less has been done regarding cultural or educational factors.
+Grilo and Thurik’s research [@Grilo2005b] is also often refered to about what determines entrepreneurship engagement levels throughout the European Union and the US.
+
+Wennekers, Ulhaner and Thurik have looked more into variation across countries [@Wennekers2002]
+
+Also focused on environmental factors, Freytag and Thurik have studied determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.
+
+Thus, what determines entrepreneurship at a country-level has been long searched already but although structural factors have been looked at extensively, much less has been done regarding cultural or educational factors.
 Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ??????
@@
 Cheng and Wong’s study about school effectiveness in East Asia [@Cheng2006] will also help.
-
-Besides potential educational effects on self-confidence and social capital, we will need to control for all classic entrepreneurship determinants.
-Therefore, we will quote Grilo and Thurik’s research [@Grilo2005b] about what determines entrepreneurship engagement levels throughout the European Union and the US, Wennekers, Ulhaner and Thurik’s about variation across countries [@Wennekers2002], Freytag and Thurik about determinants in a cross-country setting ?????
-2010 VERSION MAINBIB ?????.
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Grilo and Thurik’s research [@Grilo2005b] is also often refered to about what determines entrepreneurship engagement levels throughout the European Union and the US.
+Grilo and Thurik [@Grilo2005b] who looked into what determines entrepreneurship engagement levels throughout the European Union and the US pointed especially at the level of financial support available for entrepreneurs in the country and at administrative complexities.
 
-Wennekers, Ulhaner and Thurik have looked more into variation across countries [@Wennekers2002]
-
-Also focused on environmental factors, Freytag and Thurik have studied determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.
-
-Thus, what determines entrepreneurship at a country-level has been long searched already but although structural factors have been looked at extensively, much less has been done regarding cultural or educational factors.
+Actually, what determines entrepreneurship at a country-level has been long searched already but although structural and environmental factors have been looked at extensively, less has been done regarding cultural or educational factors.
 Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ??????
@@
 Perceived Capabilities (GEM 2012) | 36% | 47%
+
+In 2010, 
+Also focused on environmental factors, Freytag and Thurik have studied determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Rather than trying to trace cultural features at large, we intend to focus on one key cultural institution, that is the education system.
-Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on student self-confidence [@Scott1996].
+Rather than trying to trace cultural features at large, as we mentioned earlier, we intend to focus specifically on one key cultural institution, that is the education system.
+Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996].
 Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].
@@
 Perceived Capabilities (GEM 2012) | 36% | 47%
-
-In 2010, 
-Also focused on environmental factors, Freytag and Thurik have studied determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.
 
@@
 We believe there is a more widely spread systematic effect of educational features.
+
+In 2010, 
+Also focused on environmental factors, Freytag and Thurik have studied determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012 and the OECD PISA (Programme for International Student Assessment) LINK ?????
-also from 2012, there seem to be different amounts of entrepreneurial self-efficacy between countries.
+Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012, there seem to be different amounts of entrepreneurial self-efficacy between countries.
 By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur.
@@
 So, although the research tends to hold self-confidence and also entrepreneurial self-efficacy as individual features, we intend to understand to what extent these individual characteristics are partly shaped at a collective or societal level by looking at the potential impact of education systems and their personnel.
+
 Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries.

### 2014-12-11 PresentationandPaper/Draft1.Rmd
Created a rmd file with section on data selection and usage

--- 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
@@
 ---
-title: "Country-Level Impact of Education on Entrepreneurship"
-author: "Sam Dundon and Thierry Racaud"
-date: "10 december 2014"
+title: "Draft1"
+author: "Sam"
+date: "December 11, 2014"
 output: html_document
@@
 
-* * * 
-```{r echo=FALSE, cache=TRUE, include=FALSE}
+#### Quantitative Analysis of the Impact of Education on Entrepreneurship
 
-# Set working directory
-setwd('~/Assign2Education/Proposal')
+**Data Sources**  
+To complete a quantitative analysis of the impact of educational factors -- specifically the encouragement of creatitivity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship, we have drawn on publicly available data from the Global Entrepreneurship Monitor (GEM) National Expert Survey (NES) and Adult Population Survey (APS).
 
-# Install necessary packages
-library(plyr)
-library(repmis)
-library(tidyr)
-library(reshape2)
-library(foreign)
+The Global Entrepreneurship Monitor project is an annual assessment of the entrepreneurial activity, aspirations, and attitudes of individuals across a wide range of countries.
+The countries covered have grown from a low of ten to covering 75% of world population and 89% of world GDP by 2013.
+The 2001-2010 multi-year APS data base, for example, contains over 1.3 million observations of a total of 85 countries.
+This data is often cited in academic research, including reports by the Organisation for Economic Co-operation and Development.
 
-# Install rempis from Christpher Gandrud's website
-devtools::install_github('christophergandrud/repmis')
-library(repmis)
+The NES is structured around nine entrepreneurial framework contitions evaluated by thirty-six experts in each surveyed country.
+These nine entrepreneurial framework conditions are included below (a minimum of four experts must be interviewed on each of the framework conditions).
 
-# Load citation package
-pkgs <- c('repmis')
-repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')
+1. Finance  
+2. Government policies  
+3. Government programs  
+4. Entrepreneurial Education and Training  
+5. Research and Development Transfer (R & D)  
+6. Commercial and professional infrastructure  
+7. Internal Market openness  
+8. Physical infrastructure and services  
+9. Cultural and social norms
 
-```
+The APS is a questionnaire distrubuted to a minimum of 2,000 adults in each participating country.
+The survey is created by a central GEM team, but the implementation is managed by national teams that compete for the role of implementing the survey.
+Experts are chosen based on experience and specialization and are expected to represent the entire country (including urban and rural areas).
 
-*Introduction to Collaborative Social Science Data Analysis*
+**Data Selection**
 
-(The impact of self confidence on entrepreneurship.)
+After reviewing the available data, we decided to select the following variables for our analysis.
 
-### Abstract
+Source | Indicator 
+-------------|---------------
+APS | Rate of Entrepreneurship (Intention, Nascent, Established)
+NES | Way of Teaching
+APS | Perceived Capabilities
+APS | Fear of Failure / Perceived Opportunities
+APS | Perceived Opportunities
 
-### Why we chose to look into Education to explain Entrepreneurship
-
-Whilst it is tempting to look at education systems in a very pragmatic way with ratios of teachers per student, or students per class, we suggest to use another kind of indicators in order to trace the potential long-term investment made by governments.
-Indeed, we believe that education systems can favour entrepreneurship and, beyond, GDP growth at the country-level, depending on how supportive of students' self-confidence and how socially inclusive they are.
-We see this process as manyfold but will only focus here on one of the potential causal relations.
-We want to understand specifically to want extent the support of individual self-confidence within education systems can affect the likelihood to become an entrepreneur, and thus impact the rate of entrepreneurship at the country level.
-
-In trying to explore what supports entrepreneurship at the country-level, one should start by refering to what research asserted for that matter.
-For this purpose, we refer here to the OECD reports available online here http://www.oecd.org/std/business-stats/48129925.pdf.
-Two main sorts of determinants or favourable conditions have been looked into, that is environmental factors and individual factors.
-Although we intend to focus more on individual factors, we
-want to mention here the environmental factors as they should be controled for. They actually divide into six broad categories:
-
-The regulatory framework, which includes administrative burdens, regulations and frameworks, as well as fiscal policy parameters.
-
-The market conditions, which include anti-trust laws, rules for competition, access to foreign markets, degree of public involvement and level of private demand.
-
-The access to finance, which includes access to debt financing, access to venture capital, and stock markets.
-
-The creation and diffusion of knowledge, which include research and development activity, transfer of non-commercial knowledge, co-operation among firms, technology availability and take-up.
-
-The entrepreneurial capabilities, which includes business and entrepreneurship education as well as immigration.
-
-The entrepreneurship culture of a given area or population (The OECD refers partially to the Global Entrepreneurship Monitor or GEM data).
-
-Grilo and Thurik [@Grilo2005b] who looked into what determines entrepreneurship engagement levels throughout the European Union and the US pointed especially at the level of financial support available for entrepreneurs in the country and at administrative complexities.
-
-Actually, what determines entrepreneurship at a country-level has been long searched already but although structural and environmental factors have been looked at extensively, less has been done regarding cultural or educational factors.
-Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ??????
-2010 VERSION MAIN BIB ?????.
-Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done.
-
-Over a hundred years have passed since Max Weber tried to explain how religious-ethical motivations affect entrepreneurship [@weberprotestant], and today religion may be less effective in justifying why some are more likely to start businesses than others.
-Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” [@OECD2009].
-
-More recently, Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors.
-As they compared two Swedish regions similar in terms of structure and observed different outcomes, they too concluded that there might be a small cultural effect in attitudes toward start-up activities.
-Yet, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.
-
-Rather than trying to trace cultural features at large, as we mentioned earlier, we intend to focus specifically on one key cultural institution, that is the education system.
-Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996].
-Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].
-
-Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012, there seem to be different amounts of entrepreneurial self-efficacy between countries.
-By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur.
-Here, the variable "perceived capabilites" has to be understood in a narrow sense, it refers only to the perceived capabilities to start a business.
-Seemingly the variable "fear of failure" only refers to the fear of failure as an obstacle in starting a business, despite the perceived good opportunities.
-
-Variable | France | UK
--------------|---------------|---------
-Fear of Failure (GEM 2012) | 43% | 36%
-Perceived Capabilities (GEM 2012) | 36% | 47%
-
-So, although the research tends to hold self-confidence and also entrepreneurial self-efficacy as individual features, we intend to understand to what extent these individual characteristics are partly shaped at a collective or societal level by looking at the potential impact of education systems and their personnel.
-
-Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries.
-Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement.
-Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, but it is much more rarely activitated in France, and only on an voluntary individual teacher's basis.
-We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.
-
-This assumption draws from Boyd and Vozikis's ???????
-MAIN BIB ????????
-stating how entrepreneurial intentions are at least partially the result of thought processes, which " underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour".
-Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours".
-To assert this, they rely on Fishbein and Ajzen 1975 ??????
-MAIN BIB ????????
-who illustrate the relation between beliefs and behaviour as follows:
-
-1 Beliefs  
-2 Attitudes  
-3 Intentions  
-4 Behaviour
-
-There could even be an incidence of the intention to perform a certain behaviour on the actual performance of that behaviour, which could lead to look into skills, abilities and willpower.
-It is almost like "individuals would be predisposed to entrepreneurial intentions based upon a combination of both personal and contextual factors" ?????
-Boyd and Vosikis MAIN BIB ?????
-but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality for "self-efficacy will moderate the relationship between the development of entrepreneurial intentions and the likelihood that these intentions will result in entrepreneurial actions or behaviour".
-Therefore, we will have to control for this entrepreneurial self-efficacy as we research potential effects of positive reinforcement.
-
-Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009]
-
-Variable | France | UK
--------------|---------------|---------
-Sense of belonging (PISA 2012) | 47% | 79%
-
-Another interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions, can increase the rate of youth entrepreneurship, but their perspective was slightly different.
-They  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
-We believe there is a more widely spread systematic effect of educational features.
-
-In 2010, 
-Also focused on environmental factors, Freytag and Thurik have studied determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.
-
-The cross-cultural perspective on teaching and learning proposed by Watkins [@Watkins2010] shall help us compare countries.
-
-Cheng and Wong’s study about school effectiveness in East Asia [@Cheng2006] will also help.
-
-Eventually, to put all these into perspective, along with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.
-
-### Research Question
-
-To what extent do teaching methods supporting self-confidence impact the rate of entrepreneurship across OECD countries?
-
-### Literature Review
-
-### Estimation Strategy
-
-#### Causal Chain
-
-Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
-<br>
-
-#### Dependent Variables: Explaining the Country-level Rate of Entrepreneurship
-
-We have examined three dimensions of entrepreneurship to prepare for this stage of the project, established entrepreneurship in the country, nascent entrepreneurship (less than three months), and entrepreneurial intention.
-We will study each of these successively as we may well observe different effects.
-
-To measure these three dimensions of entrepreneurship, we have used three [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) indicators:
-
-- Established Business Ownership Rate (Percentage) 
-- Nascent Entrepreneurship Rate (Percentage)
-- Entrepreneurial intention Rate (Percentage)
-
-#### Key Explanatory Variable: Degree of Self-confidence Reinforcement within the Education System
-
-As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem.
-To do so, we decided to incorporate GEM indicators that relate to self- confidence.
-First, we included GEM survey data on the average "perceived capabilities" of an individual (18-64) in a given country to start a business.
-Second, we included additional GEM data on how the "fear of failure" could deter an average individual (18-64) in a country to become an entrepreneur.
-Both of these data sets indicate the average percentage for each characteristic at the country-level but they are solely describing a level of self-confidence in one's abilities to become an entrepreneur.
-We chose to use them as such even if they do not trace the specific causal chain between education systems and entrepreneurship that we intend to focus on.
+After looking through the entire 2001-2010 NES data set and considering the nine entrepreneurial conditions, we decided to use this data set to
 
@@
 
-1. Finance  
-2. Government policies  
-3. Government programs  
-4. Entrepreneurial Education and Training  
-5. Research and Development Transfer (R & D)  
-6. Commercial and professional infrastructure  
-7. Internal Market openness  
-8. Physical infrastructure and services  
-9. Cultural and social norms
-
 Only four experts per framework condition are consulted in each country participating.
@@
 
-#### Control Variables: Controlling for Classic Determinants of Entrepreneurship
+The NES at 9 entrepreneurial framework conditions (4 national experts for each)
+
+to create graphic visualizations of participants' responses to surveys about entrepreneurship in OECD (Organisation for Economic Co-operation and Development) countries.
+
+##### Dependent Variables: Explaining the Country-level Rate of Entrepreneurship
+
+We have examined three dimensions of entrepreneurship to prepare for this stage of the project, established entrepreneurship in the country, nascent entrepreneurship (less than three months), and entrepreneurial intention.
+We will study each of these successively as we may well observe different effects.
+
+To measure these three dimensions of entrepreneurship, we have used three [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) indicators:
+
+- Established Business Ownership Rate (Percentage) 
+- Nascent Entrepreneurship Rate (Percentage)
+- Entrepreneurial intention Rate (Percentage)
+
+##### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System
+
+As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem.
+To do so, we decided to incorporate GEM indicators that relate to self-esteem and confidence.
+First, we included GEM survey data on the average "perceived capabilities" of an individual (18-64) in a given country to start a business.
+Second, we included additional GEM data on how the "fear of failure" could deter an average individual (18-64) in a country to become an entrepreneur.
+Both of these data sets indicate the average percentage for each characteristic at the country-level.
+
+##### Control Variables: Controlling for Classic Determinants of Entrepreneurship
 
@@
 
-#### Regressions
+##### Regressions
 
@@
 
-GEM data was embedded in an interactive database and was difficult to extract automatically without writing a programme.
+GEM data was embedded in an interactive database and was difficult to extract automatically without writing a program.
 To simplify this process, we downloaded the necessary *.csv* files and saved them in our GitHub repository (to reduce complexity, we deleted the first three unnecessary rows before saving).
@@
 
-Cleaning the GEM data required deleting unnecessary characters in the year columns, changing the years from columns to rows (changing the data from wide to long), and changing the column names to describe which data was being analysed.
+Cleaning the GEM data required deleting unnecessary characters in the year columns, changing the years from columns to rows (changing the data from wide to long), and changing the column names to describe which data was being analyzed.
 In the process of doing this we created new data sets for each of these survey questions, which were called C*dataset* (clean followed by the data set name).
@@
 However, there are a few missing values, especially regarding the perceived opportunities for some countries, namely Estonia, Luxembourg and Slovak Republic.
-
-**World Bank Data**
-
-As mentioned above, one of our control variables, annual GDP growth, was obtained using the WDI API from the World Bank.
-Using this API, we accessed GDP data from all the OECD countries directly from *R*.
-To clean this data, we used *plyr* to change the variable names then recoded the U.S.
-and South Korea country names to maintain consistency with the GEM data set and dropped an unnecessary column that was not included with the GEM data.
-
-Finally, we merged the annual GDP growth data with the *FinalGEM* data set to create *CompleteDataset*.
-This is the data set used to run the regressions and generate the charts and figures outlined in this document.
-To reduce complexity in the environment we also included a command to remove unnecessary objects in the environment.
-
-<br>
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
-
-#### Import data from GEM Survey ####
-
-# Import GEM fear of failure data
-FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE)
-
-# Import GEM estblished entrepreneurship - current owner data
-CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = FALSE)
-
-# Import GEM entrepreneurial intention data
-EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = FALSE)
-
-# Import GEM nascent entrepreneur data
-NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = FALSE)
-
-# Import GEM perceived capabilities data
-PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE)
-
-# Import GEM perceived opportunities data as a proxy for potential control variables
-PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE)
-
-# Import 2010GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is
-SupportiveTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEMAvgIndicators.csv", header = TRUE, cache = FALSE)
-
-# Import GEM 2009 supportive teaching data
-setwd('~/Assign2Education/GEMData')
-
-GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
-GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
-GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
-GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
-GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
-GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
-GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
-GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
-GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
-GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)
-
-#### Clean data using tidy ####
-
-### Clean FearFail ###
-# Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
-
-# Remove X's in FearFail year columns
-names(FearFail) <- gsub("X", "", names(FearFail))
-
-# Change years from columns to rows and create CFearFail
-CFearFail <- melt(data = FearFail,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010", "2011", "2012",
-                                   "2013"))
-
-# Rename columns
-CFearFail <- plyr::rename(x = CFearFail, 
-                                      replace = c("variable" = "Year",
-                                                  "value" = "PercentFear"))
-
-### Clean CurrentOwner ###
-# Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid sallaries, wages, or any other payments to the owners for more than 42 months
-
-# Remove X's in CurrentOwner year columns
-names(CurrentOwner) <- gsub("X", "", names(CurrentOwner))
-
-# Change years from columns to rows and create CCurrentOwner
-CCurrentOwner <- melt(data = CurrentOwner,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010", "2011", "2012",
-                                   "2013"))
-
-# Rename columns
-CCurrentOwner <- plyr::rename(x = CCurrentOwner, 
-                                      replace = c("variable" = "Year",
-                                                  "value" = "PercentOwner"))
-
-### Clean EntreIntention ###
-# Percentage of 18-64 population (individuals involved in any stage of entrepenerurial activity excluded) who intend to start a business within three years.
-
-# Remove X's in EntreIntention year columns
-names(EntreIntention) <- gsub("X", "", names(EntreIntention))
-
-# Change years from columns to rows and create CEntreIntention (No 2001 data available)
-CEntreIntention <- melt(data = EntreIntention,
-                  id.vars = c("Country"),
-                  measure.vars = c("2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010", "2011", "2012",
-                                   "2013"))
-
-# Rename columns
-CEntreIntention <- plyr::rename(x = CEntreIntention, 
-                                      replace = c("variable" = "Year",
-                                                  "value" = "PercentIntention"))
-
-### Clean NascentEntre ###
-# Percentage of 18-64 population who are currently a nascent entrepreneur, i.e., actively involved in setting up a business they will own or co-own; this business has not paid salaries, wages, or any other payments to the owners for more than three months.
-
-# Remove X's in NascentEntre year columns
-names(NascentEntre) <- gsub("X", "", names(NascentEntre))
-
-# Change years from columns to rows and create CNascentEntre
-CNascentEntre <- melt(data = NascentEntre,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010", "2011", "2012",
-                                   "2013"))
-
-# Rename columns
-CNascentEntre <- plyr::rename(x = CNascentEntre, 
-                                      replace = c("variable" = "Year",
-                                                  "value" = "PercentNascent"))
-
-### Clean PerceivedCapabilities ###
-# Percentage of 18-64 population who believe to have the required skills and knowledge to start a business
-
-# Remove X's in PerceivedCapabilities year columns
-names(PerceivedCapabilities) <- gsub("X", "", names(PerceivedCapabilities))
-
-# Change years from columns to rows and create CPreceivedCapabilities
-CPerceivedCapabilities<- melt(data = PerceivedCapabilities,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010", "2011", "2012",
-                                   "2013"))
-
-# Rename columns
-CPerceivedCapabilities <- plyr::rename(x = CPerceivedCapabilities, 
-                                      replace = c("variable" = "Year",
-                                                  "value" = "PercentPerceived"))
-
-### Clean PerceivedOpportunities ###
-# Percentage of 18-64 population who see good opportunities to start a firm in the area where they live
-
-# Remove X's in PerceivedOpportunities year columns
-names(PerceivedOpportunities) <- gsub("X", "", names(PerceivedOpportunities))
-
-# Change years from columns to rows and create CPreceivedOpportunities
-CPerceivedOpportunities<- melt(data = PerceivedOpportunities,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010", "2011", "2012",
-                                   "2013"))
-
-# Rename columns
-CPerceivedOpportunities <- plyr::rename(x = CPerceivedOpportunities, 
-                                      replace = c("variable" = "Year",
-                                                  "value" = "PercentOpportunities"))
-
-### Clean GEM NES Datasets
-# Draw out Country and D01 only
-Clean01 <- GEM2001[,c("country", "ki01d01")]
-Clean02 <- GEM2002[,c("country", "ki02d01")]
-Clean03 <- GEM2003[,c("country", "ki03d01")]
-Clean04 <- GEM2004[,c("ki04ctry", "ki04d01")]
-Clean05 <- GEM2005[,c("KI05ctry", "KI05D01")]
-Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
-Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
-Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
-Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
-Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]
-
-remove(GEM2001, GEM2002, GEM2003, GEM2004, GEM2005, GEM2006, GEM2007, GEM2008, GEM2009, GEM2010)
-
-# Edit column names for each dataframe
-
-Clean01 <- plyr::rename(x = Clean01, 
-                                      replace = c("ki01d01" = "Year01",
-                                                  "country" = "Country"))
-
-Clean02 <- plyr::rename(x = Clean02, 
-                                      replace = c("ki02d01" = "Year02",
-                                                  "country" = "Country"))
-
-Clean03 <- plyr::rename(x = Clean03, 
-                                      replace = c("ki03d01" = "Year03",
-                                                  "country" = "Country"))
-
-Clean04 <- plyr::rename(x = Clean04, 
-                                      replace = c("ki04d01" = "Year04",
-                                                  "ki04ctry" = "Country"))
-
-Clean05 <- plyr::rename(x = Clean05, 
-                                      replace = c("KI05D01" = "Year05",
-                                                  "KI05ctry" = "Country"))
-
-Clean06 <- plyr::rename(x = Clean06, 
-                                      replace = c("KI06D01_mean" = "Year06",
-                                                  "KI06CTRY" = "Country"))
-
-Clean07 <- plyr::rename(x = Clean07, 
-                                      replace = c("ki07d01_" = "Year07",
-                                                  "ki07ctry" = "Country"))
-
-Clean08 <- plyr::rename(x = Clean08, 
-                                      replace = c("NES08_D01_MEAN" = "Year08",
-                                                  "NES08COUNTRY" = "Country"))
-
-Clean09 <- plyr::rename(x = Clean09, 
-                                      replace = c("NES09_D01_MEAN" = "Year09",
-                                                  "NES09COUNTRY" = "Country"))
-
-Clean10 <- plyr::rename(x = Clean10, 
-                                      replace = c("NES10_D01_MEAN" = "Year10",
-                                                  "NES10CRNAME" = "Country"))
-
-#### Merge the data ####
-MergedGEM <- merge(CCurrentOwner, CEntreIntention,
-                   union("Country", "Year"),
-                   all = TRUE)
-
-MergedGem2 <- merge(CFearFail, CNascentEntre,
-                   union("Country", "Year"),
-                   all = TRUE)
-
-MergedGem3 <- merge(CPerceivedCapabilities, MergedGEM,
-                   union("Country", "Year"),
-                   all = TRUE)
-
-MergedGem4 <- merge(MergedGem2, MergedGem3,
-                   union("Country", "Year"),
-                   all = TRUE)
-
-FinalGEM <- merge(MergedGem4, CPerceivedOpportunities,
-                   union("Country", "Year"),
-                   all = TRUE)
-
-# Convert percent columns from character to numeric
-FinalGEM[,"PercentPerceived"] <- as.numeric(FinalGEM[,"PercentPerceived"])
-FinalGEM[,"PercentFear"] <- as.numeric(FinalGEM[,"PercentFear"])
-FinalGEM[,"PercentNascent"] <- as.numeric(FinalGEM[,"PercentNascent"])
-FinalGEM[,"PercentOwner"] <- as.numeric(FinalGEM[,"PercentOwner"])
-FinalGEM[,"PercentIntention"] <- as.numeric(FinalGEM[,"PercentIntention"])
-FinalGEM[,"PercentOpportunities"] <- as.numeric(FinalGEM[,"PercentOpportunities"])
-
-# Remove unncessary data from environment
-remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre)
-
-CleanMerge <- cbind(names = c(rownames(Clean01), rownames(Clean02), rownames(Clean03),
-                              rownames(Clean04), rownames(Clean05), rownames(Clean06),
-                              rownames(Clean07), rownames(Clean08), rownames(Clean09),
-                              rownames(Clean10)),
-                    rbind.fill(list(Clean01, Clean02, Clean03, Clean04, Clean05, Clean06,
-                                    Clean07, Clean08, Clean09, Clean10)))
-
-# Recode countries
-CleanMerge$Country[CleanMerge$Country == "AUSTRALIA"] <- "Australia"
-CleanMerge$Country[CleanMerge$Country == "AUSTRIA"] <- "Austria"
-CleanMerge$Country[CleanMerge$Country == "BELGIUM"] <- "Belgium"
-CleanMerge$Country[CleanMerge$Country == "CANADA"] <- "Canada"
-CleanMerge$Country[CleanMerge$Country == "CHILE"] <- "Chile"
-CleanMerge$Country[CleanMerge$Country == "CZECH REPUBLIC"] <- "Czech Republic"
-CleanMerge$Country[CleanMerge$Country == "DENMARK"] <- "Denmark"
-CleanMerge$Country[CleanMerge$Country == "ESTONIA"] <- "Estonia"
-CleanMerge$Country[CleanMerge$Country == "FINLAND"] <- "Finland"
-CleanMerge$Country[CleanMerge$Country == "FRANCE"] <- "France"
-CleanMerge$Country[CleanMerge$Country == "GERMANY"] <- "Germany"
-CleanMerge$Country[CleanMerge$Country == "GREECE"] <- "Greece"
-CleanMerge$Country[CleanMerge$Country == "HUNGARY"] <- "Hungary"
-CleanMerge$Country[CleanMerge$Country == "ICELAND"] <- "Iceland"
-CleanMerge$Country[CleanMerge$Country == "IRELAND"] <- "Ireland"
-CleanMerge$Country[CleanMerge$Country == "ISRAEL"] <- "Israel"
-CleanMerge$Country[CleanMerge$Country == "ITALY"] <- "Italy"
-CleanMerge$Country[CleanMerge$Country == "JAPAN"] <- "Japan"
-CleanMerge$Country[CleanMerge$Country == "KOREA"] <- "South Korea"
-CleanMerge$Country[CleanMerge$Country == "LUXEMBURG"] <- "Luxemburg"
-CleanMerge$Country[CleanMerge$Country == "MEXICO"] <- "Mexico"
-CleanMerge$Country[CleanMerge$Country == "NETHERLANDS"] <- "Netherlands"
-CleanMerge$Country[CleanMerge$Country == "NEW ZEALAND"] <- "New Zealand"
-CleanMerge$Country[CleanMerge$Country == "NORWAY"] <- "Norway"
-CleanMerge$Country[CleanMerge$Country == "POLAND"] <- "Poland"
-CleanMerge$Country[CleanMerge$Country == "PORTUGAL"] <- "Portugal"
-CleanMerge$Country[CleanMerge$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
-CleanMerge$Country[CleanMerge$Country == "SLOVENIA"] <- "SLOVENIA"
-CleanMerge$Country[CleanMerge$Country == "SPAIN"] <- "Spain"
-CleanMerge$Country[CleanMerge$Country == "SWEDEN"] <- "Sweden"
-CleanMerge$Country[CleanMerge$Country == "SWITZERLAND"] <- "Switzerland"
-CleanMerge$Country[CleanMerge$Country == "TURKEY"] <- "Turkey"
-CleanMerge$Country[CleanMerge$Country == "UNITED KINGDOM"] <- "United Kingdom"
-CleanMerge$Country[CleanMerge$Country == "UK"] <- "United Kingdom"
-CleanMerge$Country[CleanMerge$Country == "USA"] <- "United States"
-CleanMerge$Country[CleanMerge$Country == "UNITED STATES"] <- "United States"
-CleanMerge$Country[CleanMerge$Country == "Korea"] <- "South Korea"
-CleanMerge$Country[CleanMerge$Country == "US"] <- "United States"
-
-# Set columns to numeric
-CleanMerge[,"Year01"] <- as.numeric(CleanMerge[,"Year01"])
-CleanMerge[,"Year02"] <- as.numeric(CleanMerge[,"Year02"])
-CleanMerge[,"Year03"] <- as.numeric(CleanMerge[,"Year03"])
-CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year04"])
-CleanMerge[,"Year05"] <- as.numeric(CleanMerge[,"Year05"])
-CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year06"])
-CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year07"])
-CleanMerge[,"Year08"] <- as.numeric(CleanMerge[,"Year08"])
-CleanMerge[,"Year09"] <- as.numeric(CleanMerge[,"Year09"])
-CleanMerge[,"Year10"] <- as.numeric(CleanMerge[,"Year10"])
-
-# Change merged data from wide to long
-LongGEM<- melt(data = Merged9,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010"))
-
-# Rename columns
-names(LongGEM) <- gsub("variable", "Year", names(LongGEM))
-names(LongGEM) <- gsub("value", "Support", names(LongGEM))
-
-# Create a vector with OECD countries
-myvars <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')
-
-# Subset LongGEM with the countries we need
-subset_data <- subset(LongGEM, Country %in% myvars)
-
-# Delete unnecessary column
-subset_data$row.names <- NULL
-
-# Arrange subset_data by country and year
-GrandData <- arrange(subset_data, Country, Year)
-
-GrandData1 <- GrandData[order("Country",)]
-
-########### STUCK #############
-
-FinalData <- merge(FinalGEM, GrandData,
-                   union("Country", "Year"))
-
-```
-
-#### Data Analysis
-
-To examine the relationship between these variables, we used least square estimation, the results of which can be found in the following table.
-The package *stargazer* was required to generate this table.
-As evidenced by the equation results, the individual variables selected are statistically significant, but the model only explains a relatively small degree of the variation in the dependent variable.
-For example, the adjusted $R^2$ of regression equation one is 0.29, the adjusted $R^2$ of regression equation two is 0.38, and the adjusted $R^2$ is 0.13.
-<br>
-
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
-
-# Run linear regression R1
-R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)
-
-# Obtain summary statistics of R1
-summary(R1)
-
-# Run linear regression R2
-R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)
-
-# Obtain summary statistics of R2
-summary(R2)
-
-# Run linear regression R3
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
-
-# Obtain summary statistics of R3
-summary(R3)
-
-```
-
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
-
-# Library Stargazer for regression output tables
-library(stargazer)
-
-# Create regression output table
-labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
-            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')
-
-dlables <- c('National Level Average Percent Entrepreneurial Intention', 'National Level Nascent Entrepreneural Activity', 'National Level Average Percent Owning a Business')
-
-stargazer::stargazer(R1, R2, R3, covariate.labels = labels, dep.var.labels = dlables,
-                     title = 'Linear Regression Estimates', digits = 2, type = 'html')
-```
-<br>  
-National-level average of people perceiving opportunities but acknowledging fear of failure will prevent them from creating a business (FF)
-
-**Simulation Package and Cleaning**
-
-In addition to the output table, a simulation is helpful to visually illustrate the relationship the probability of obtaining a given value in the dependent variables conditional on change in the independent variable.
-We used the *Zelig* package to run a least square regression and generate a simulation of equation 1.
-Prior to running this regression, however, we ran the na.omit command to remove omitted variables from the equation.
-
-To examine the probabilities of achieving given outcomes, we generated three simulations for the first regression equation.  To demonstrate this method, we have included one simulation below.
-
-**Process**
-
-First, we estimated a least square equation with variation in the variable *PercentPerceived* of 20-100 percent.
-The ranges for variance in the independent variables was chosen by identifying the best range for capturing the largest degree of variance for the model.
-The first simulation is below.
-The y axis shows variation in *PercentIntention* conditional on change in *PercentPerceived* and the x axis shows variation in *PercentPerceived*.
-The results may be interpreted as showing that people who believe they have the knowledge required to start a business may or may not do so (with a high degree of variation), while people who do not believe they have this knowledge are consistently unlikely to start a business (there is little variation).
-
-```{r echo = FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
-
-# Library Zelig (can be buggy if loaded to early)
-library(Zelig)
-
-# Omit omitted data from simulation
-CompleteData_omit <- na.omit(CompleteDataset)
-
-# Run a least squares regression with Zelig
-Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteData_omit, model = "ls")
-```
-
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE }
-
-# Find appropriate range for PercentPerceived
-summary(CompleteData_omit$PercentPerceived)
-
-# Set range of PercentPerceived values in simulation
-x.out2 <- setx(Z1, PercentPerceived = 9:67)
-
-# Run simulation (default 1000 trials)
-simz2 <- sim(Z1, x = x.out2)
-
-# Adjust margins
-par(mar=c(2,2,2,2))
-
-# Plot simulation
-plot(simz2, xlab= 'PercentPerceived')
-
-```
-
-<br>
-
-#### Outlook
-
-Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at the country level in its NES Survey.
-Item D01 states "in my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self esteem a given education system is.
-
-We may also want to quantify how individualistic or group-oriented an average student is by the end of compulsory education, as the literature holds social inclusion as an explanatory factor for self-esteem.
-We will use OECD PISA data on "the sense of belonging" for this.
-
-Next steps will also include looking more thoroughly into control variables and determining the most appropriate way to present our results.
-To do so we may need to extract data from various national NES reports and put together a table, as it does not seem to exist as such.
-
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
-
-library(stargazer)
-stargazer(CompleteDataset, type = 'html')
-
-```
-
-Estonia
-Luxemburg
-Slovak Republic

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement.
-Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, but it is much more rarely activitated in France, and only on an voluntary individual teacher's basis.
+Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is much more rarely activitated in France, and only on an voluntary individual teacher's basis.
 We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.
@@
 MAIN BIB ????????
-stating how entrepreneurial intentions are at least partially the result of thought processes, which " underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour".
+stating how entrepreneurial intentions are at least partially the result of thought processes, which "underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour".
 Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours".
@@
 
-Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009]
+Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009] we should ideally be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too as shows this table:
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009] we should ideally be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too as shows this table:
+Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009] we should ideally be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too as this table shows :
 
@@
 
-Another interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions, can increase the rate of youth entrepreneurship, but their perspective was slightly different.
+The lack of suitable data as well as the fact that OECD PISA tends to focus on different aspects of education systems for every triennal survey lead us to give up on this.
+But we still think that should be included in a future research on that topic.
+
+Of course, we also looked into other studies connecting educational features and entrepreneurship.
+As a matter of fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy ???????
+Boyd and Vosikis MAIN BIB ???????????
+.
+One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions, can increase the rate of youth entrepreneurship, but their perspective was still not directly in lign with our research design.
 They  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-### Why we chose to look into Education to explain Entrepreneurship
+### Why we chose to look into Education to explain Entrepreneurship - What has been done
 
@@
 As they compared two Swedish regions similar in terms of structure and observed different outcomes, they too concluded that there might be a small cultural effect in attitudes toward start-up activities.
+In 2010, Freytag and Thurik ?????
+2010 VERSION MAINBIB ?????
+have also studied determinants of entrepreneurship in a cross-country setting and pointed at cultural features.
+Their results showed that "country specific (cultural) variables seem to explain the preference for entrepreneurship" and self-employment.
 Yet, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.
@@
 
-In 2010, 
-Also focused on environmental factors, Freytag and Thurik have studied determinants in a cross-country setting ????? 2010 VERSION MAINBIB ?????.
+???????????????????????????????????????????????????????????????????????????
 
@@
 Eventually, to put all these into perspective, along with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.
+
+????????????????????????????????????????????????????????????????????????????????????
+
+### What we intend to do
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 Their results showed that "country specific (cultural) variables seem to explain the preference for entrepreneurship" and self-employment.
-Yet, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.
+Yet, not so many empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.
 
@@
 
-???????????????????????????????????????????????????????????????????????????
+????????????????????????????????????????????????????????????????????????????????????????????
 
@@
 
-????????????????????????????????????????????????????????????????????????????????????
+?????????????????????????????????????????????????????????????????????????????????????????????
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-### Research Question
+Henceforth, we expect to find out to what extent the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries.
 
-To what extent do teaching methods supporting self-confidence impact the rate of entrepreneurship across OECD countries?
-
-### Literature Review
-
-### Estimation Strategy
-
-#### Causal Chain
+We expect to observe the following causal chain :
 
 Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
-<br>
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Education system / Teaching reinforcing self-esteem ---> higher degree of individual self-esteem ---> higher probability an individual will become an entrepreneur ---> higher rate of entrepreneurship at a country-level.
+---> Education system reinforcing self-confidence
+
+---> Higher degree of individual self-confidence
+
+---> Higher probability an individual will become an entrepreneur
+
+---> higher rate of entrepreneurship at a country-level.
 

### 2014-12-11 PresentationandPaper/Draft1.Rmd
Added text about data selection and sources and started histogram

@@
 date: "December 11, 2014"
-output: html_document
+output: pdf_document
 ---
 
-#### Quantitative Analysis of the Impact of Education on Entrepreneurship
+**Quantitative Analysis of the Impact of Education on Entrepreneurship**
 
-**Data Sources**  
+*Data Sources*
+
 To complete a quantitative analysis of the impact of educational factors -- specifically the encouragement of creatitivity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship, we have drawn on publicly available data from the Global Entrepreneurship Monitor (GEM) National Expert Survey (NES) and Adult Population Survey (APS).
@@
 
+<br>
+
 **Data Selection**
@@
 
-After looking through the entire 2001-2010 NES data set and considering the nine entrepreneurial conditions, we decided to use this data set to
+The survey questions corresponding to these variables are as follows:
+
+1. **Entrepreneurial Intention**: Percentage of 18-64 population (individuals involved in any stage of entrepreneurial activity excluded) who intend to start a business within three years.
+
+2.
+**Nascent Entrepreneurship**: Percentage of 18-64 population who are currently a nascent entrepreneur, i.e., actively involved in setting up a business they will own or co-own; this business has not paid salaries, wages, or any other payments to the owners for more than three months.
+
+3.
+**Established Entrepreneur**: Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid salaries, wages, or any other payments to the owners for more than 42 months.
+
+4. **Way of Teaching**: In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative.
+
+5. **Perceived Capabilities**: Percentage of 18-64 population who believe to have the required skills and knowledge to start a business
+
+6. **Fear of Failure**: Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
+
+7. **Perceived Opportunities**: Percentage of 18-64 population who see good opportunities to start a firm in the area where they live
+
+The APS data represent the national-level average of values between 1 and 100 that were gathered as responses to surveys within each country.
+The NES data is calculated based on the average answer to a survey to the national experts.
+For each question, the experts surveyed had to state whether it is:
+
+1. Completely false
+2. Somewhat false
+3. Neither true or false
+4. Somewhat true
+5. Completely true
+
+(97. Do not know)  
+(98. Not applicable)
+
+**Analytical Framework**
+
+To examine the specific effect of the Way of Teaching on the rate of entrepreneurship we decided to select the following dependent, control, and explanatory variables.
+
+Variable | Indicator 
+-------------|---------------
+Y Dependent Variable | Rate of Entrepreneurship (Intention, Nascent, Established)
+X1 Explanatory Variable | Way of Teaching
+X2 Control Variable | Perceived Capabilities
+X3 Control Variable | Fear of Failure / Perceived Opportunities
+X4 Control Variable | Perceived Opportunities
+
+..........(Describe why we use the rate of entrepreneurship indicators we chose)
+
+As a reference, we can show the distribution of our explanatory variable "Way of Teaching" in the following histogram.
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+
+# Set working directory
+setwd('~/Assign2Education/PresentationandPaper')
+
+# Library required packages
+library(ggvis)
+library(devtools)
+library(googleVis)
+library(countrycode)
+library(repmis)
+library(reshape2)
+library(shiny)
+library(httpuv)
+
+# Create a vector of packages used
+pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv', 'Zelig',
+          'stargazer', 'Amelia')
+
+# Create citations txt file
+repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')
+
+# Import WayofTeaching data
+wot <- repmis::source_data()
+
+ggvis(wot, props(x= ))
+
+ggvis(faithful, props(x = ~eruptions, fill := "#fff8dc")) +
+  layer_histogram(binwidth = 0.25) +
+  guide_axis("x", title = "eruptions") +
+  guide_axis("y", title = "count")
+
+```
 
@@
 "In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative"
-
-Regarding this statement, the experts surveyed had to state whether it is:
-
-1 completely false  
-2 somewhat false  
-3 neither true nor false  
-4 somewhat true  
-5 completely true
-
-97 do not know  
-98 not applicable
-
-After searching through many potential data sources about education and finding no indicators suitable to trace our causal chain, we were forced to use that one item of a survey however low quality it might be.
-
-As a matter of fact, there are many reasons for which we should be concerned about that data and its quality.
-
-First, it was not always collected which makes any measure hard to follow through time, it is only since 2009 and 2011 that the NES was made compulsory.
-
-Second, the National Expert Surveys are very subjective data. For each entrepreneurial framework condition, that is:
-
-Only four experts per framework condition are consulted in each country participating.
-
-Third, the collection of data could arguably be improved.
-Indeed, it is outsourced by GEM Coordination Team to national teams which seem to manage the time allowed for collection poorly ???METHODOLOGY NES REPORT HERE MAIN BIB ???
-.
-The national teams also tend to rely solely on their own personal networks.
-Which does not guarantee to get the best experts on each topic.
-
-Fourth, as a result of the flows above mentioned, we observe a lot of variation from year to year up to 0.73 on a scale from 1 to 5, that is up to 14.6% (UK 2007 / UK 2009).
-Which is far from what one would expect.
-Indeed, it seems very doubtful to say that the way of teaching in any country varies so much over time.
-Educational reforms are much more rare and one should on the contrary expect to see much more stability, almost a constant over a decade.
-
-The NES at 9 entrepreneurial framework conditions (4 national experts for each)
-
-to create graphic visualizations of participants' responses to surveys about entrepreneurship in OECD (Organisation for Economic Co-operation and Development) countries.
 
@@
 Both of these data sets indicate the average percentage for each characteristic at the country-level.
-
-##### Control Variables: Controlling for Classic Determinants of Entrepreneurship
-
-To control for the general state of the economy, we included annual GDP Growth from the World Bank [World Development Indicators](http://data.worldbank.org/data-catalog/world-development-indicators) as a control variable in our regression equations.
-In addition, we included a GEM indicator called "Perceived Opportunities." For each country, it is the average percentage of individuals who believe there are opportunities to start a business in their area.
-Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.
-
-In the future, we may revise this to include lagged GDP growth in recognition of the time taken for governments and individuals to react to the state of the economy, and are planning to include control variables from GEM.
-Specifically, we intend to control for the classic determinants of entrepreneurship -- economic and structural determinants.
-To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://www.gemconsortium.org/Data-Collection).
-
-1. Finance  
-2. Government policies  
-3. Government programs  
-4. Entrepreneurial Education and Training  
-5. Research and Development Transfer (R & D)  
-6. Commercial and professional infrastructure  
-7. Internal Market openness  
-8. Physical infrastructure and services  
-9. Cultural and social norms
 

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd

@@
 
-Henceforth, we expect to find out to what extent the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries.
+Now, having attempted to show how determinants of entrepreneurship have been looked into, having mentioned how education has been related to entrepreneurship so far, we need to assert here our very research design.
+What we expect to find out is to what extent the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries.
 
@@
 ---> higher rate of entrepreneurship at a country-level.
+
+Here, when we mention that an education system reinforces self-confidence, we mean that teachers practice positive reinforcement when interacting with students.
+This entails providing feedback that will help the students maintain their level of motivation as well as their level of self-esteem.
+Supporting students' taking initiatives, encouraging creativity will also be part of this self-confidence reinforcement.
+
+Ideally we would have also liked to add the social dimension to it, meaning that students that are socially included may have a slightly higher degree of self-confidence, as we saw suggested in the literature.
 

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Added histogram and brief description of data

@@
 ---
+
+```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
+
+# Set working directory
+setwd('~/Assign2Education/PresentationandPaper')
+
+# Library required packages
+library(ggvis)
+library(devtools)
+library(googleVis)
+library(countrycode)
+library(repmis)
+library(reshape2)
+library(shiny)
+library(httpuv)
+library(ggplot2)
+
+# Create a vector of packages used
+pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv', 'Zelig',
+          'stargazer', 'Amelia', 'ggplot2')
+
+# Create citations txt file
+repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')
+
+# Import WayofTeaching data
+wot <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")
+
+```
 
@@
 
+The process of importing, cleaning, and analyzing all of the data used in this project is fully documented and reproducable by referencing our GitHub repository.
+
 **Analytical Framework**
 
-To examine the specific effect of the Way of Teaching on the rate of entrepreneurship we decided to select the following dependent, control, and explanatory variables.
+To understand the impact of educational factors -- specifically the encouragement of creatitivity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship we built our model as outlined in the table below.
 
@@
 
-As a reference, we can show the distribution of our explanatory variable "Way of Teaching" in the following histogram.
+Data on our explanatory variable, Way of Teaching, is available on the GEM website for the years 2001-2010.
+To illustrate the distribution of this data, we have created the following histogram.
+As shown in the histogram, the largest density of scores is approximately 2.3, which lies between the "somewhat false" and "neither true or false" categories.
+This is not a whole number because the scores given by each of the 4 experts surveyed for each frameork condition are averaged to create a national-level number.
+As discussed later in this paper, this presents some difficulties in drawing substantive conclusions from this data.
+Namely, a large number of indifferent responses complicate the process of determining the influence we would like to analyze.
 
-```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis', warning=FALSE}
 
-# Set working directory
-setwd('~/Assign2Education/PresentationandPaper')
-
-# Library required packages
-library(ggvis)
-library(devtools)
-library(googleVis)
-library(countrycode)
-library(repmis)
-library(reshape2)
-library(shiny)
-library(httpuv)
-
-# Create a vector of packages used
-pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv', 'Zelig',
-          'stargazer', 'Amelia')
-
-# Create citations txt file
-repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')
-
-# Import WayofTeaching data
-wot <- repmis::source_data()
-
-ggvis(wot, props(x= ))
-
-ggvis(faithful, props(x = ~eruptions, fill := "#fff8dc")) +
-  layer_histogram(binwidth = 0.25) +
-  guide_axis("x", title = "eruptions") +
-  guide_axis("y", title = "count")
+# Create a histogram showing the distribution of Way of Teaching
+qplot(WayofTeaching, data = wot, geom = "histogram", binwidth = .10)
 
@@
 
-In order to trace specifically how supportive of one's self-confidence a given education system is, we chose to use one specific item of the GEM [National Experts Survey (NES)](http://www.gemconsortium.org/Data-Collection) as a proxy, namely D01.
+Starting with this explanatory variable, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).
+These three regression equations are as follows:
 
-"In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative"
+1. $PercentEntreIntention = \beta_1WayofTeaching  + \beta_2PerceivedCabability + \beta_3PerceivedOpportunities$   
+  $+ \beta_4FearFailure + \beta_5FearFailure*PerceivedOpportunities$
 
-##### Dependent Variables: Explaining the Country-level Rate of Entrepreneurship
+2. $PercentNascent = \beta_1WayofTeaching  + \beta_2PerceivedCabability + \beta_3PerceivedOpportunities$   
+  $+ \beta_4FearFailure + \beta_5FearFailure*PerceivedOpportunities$
 
-We have examined three dimensions of entrepreneurship to prepare for this stage of the project, established entrepreneurship in the country, nascent entrepreneurship (less than three months), and entrepreneurial intention.
-We will study each of these successively as we may well observe different effects.
+3. $PercentOwner = \beta_1WayofTeaching  + \beta_2PerceivedCabability + \beta_3PerceivedOpportunities$   
+  $+ \beta_4FearFailure + \beta_5FearFailure*PerceivedOpportunities$
 
-To measure these three dimensions of entrepreneurship, we have used three [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) indicators:
-
-- Established Business Ownership Rate (Percentage) 
-- Nascent Entrepreneurship Rate (Percentage)
-- Entrepreneurial intention Rate (Percentage)
-
-##### Key Explanatory Variable: Degree of Self-esteem Reinforcement within the Education System
-
-As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem.
-To do so, we decided to incorporate GEM indicators that relate to self-esteem and confidence.
-First, we included GEM survey data on the average "perceived capabilities" of an individual (18-64) in a given country to start a business.
-Second, we included additional GEM data on how the "fear of failure" could deter an average individual (18-64) in a country to become an entrepreneur.
-Both of these data sets indicate the average percentage for each characteristic at the country-level.
-
-##### Regressions
-
-The following equations were used to determine the relationship between our dependent and explanatory variables:
-
-1. $PercentIntention = PercentPerceived(Perceived Capabilities) + Way of Teaching + PercentOpportunities(Perceived Opportunities)$
-
-2. $PercentNascent = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
-
-3. $PercentOwner = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
-
-The variables *Percent Fear* and *Percent Opportunities* were included as an interaction term $PercentFear*PercentOpportunities$ because of the design of the survey.
-PercentFear is: "the Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business."
-
-<br>
-
-#### Data Collection and Cleaning
-
-To collect the data necessary to run these regression equations, we downloaded *.csv* data from GEM and used the WDI API to obtain the necessary annual GDP growth of OECD Countries.
-
-**Necessary R Packages**
-
-The following packages were needed to complete the data collection portion of this assignment:
-
-- repmis  
-- tidyr  
-- reshape  
-- plyr  
-- WDI
-
-**GEM Data**
-
-GEM data was embedded in an interactive database and was difficult to extract automatically without writing a program.
-To simplify this process, we downloaded the necessary *.csv* files and saved them in our GitHub repository (to reduce complexity, we deleted the first three unnecessary rows before saving).
-We then linked to the RAW version of the files and added the code required to load them from *R*.
-The repmis package is required to load these documents from the repository.
-
-Cleaning the GEM data required deleting unnecessary characters in the year columns, changing the years from columns to rows (changing the data from wide to long), and changing the column names to describe which data was being analyzed.
-In the process of doing this we created new data sets for each of these survey questions, which were called C*dataset* (clean followed by the data set name).
-This was done for each of the six GEM data sets before merging these sets two at a time to create the data set *FinalGEM*.
-
-For all 33 OECD countries we should have 13 observations, one per year from 2001 to 2013, for each variable.
-However, there are a few missing values, especially regarding the perceived opportunities for some countries, namely Estonia, Luxembourg and Slovak Republic.
+The interaction term $\beta_5FearFailure*PerceivedOpportunities$ was added to the regression because the survey question regarding "Fear of Failure" was only proposed to survey respondents who indicated they do perceive opportunities

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd

@@
 Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is much more rarely activitated in France, and only on an voluntary individual teacher's basis.
+Drawing from Inglehart research ?????????
+MAIN BIB 2000 ????????, we understand the period between 0 and 20 years of age to be a defining time in terms of personal values and personality construction, thus compulsory education, generally between 6 and 16 years of age, can prove of key importance in the building up of one's self-confidence.
 We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.
@@
 .
-One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions, can increase the rate of youth entrepreneurship, but their perspective was still not directly in lign with our research design.
-They  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
-We believe there is a more widely spread systematic effect of educational features.
+One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions with students, can increase the rate of youth entrepreneurship but their perspective was still not directly in lign with our research design, they  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
 
@@
 
-Now, having attempted to show how determinants of entrepreneurship have been looked into, having mentioned how education has been related to entrepreneurship so far, we need to assert here our very research design.
+Now, having explained how determinants of entrepreneurship have been looked into, having mentioned how education has been related to entrepreneurship so far, we need to assert here our very research design.
 What we expect to find out is to what extent the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries.
@@
 
-Here, when we mention that an education system reinforces self-confidence, we mean that teachers practice positive reinforcement when interacting with students.
+Here, when we mention that an education system reinforces self-confidence, we mean that teachers use positive reinforcement when interacting with students.
 This entails providing feedback that will help the students maintain their level of motivation as well as their level of self-esteem.
-Supporting students' taking initiatives, encouraging creativity will also be part of this self-confidence reinforcement.
+This also entails supporting students' taking initiatives, encouraging creativity will also be part of this self-confidence reinforcement.
 

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Adding regression tables, etc.

@@
 
-The interaction term $\beta_5FearFailure*PerceivedOpportunities$ was added to the regression because the survey question regarding "Fear of Failure" was only proposed to survey respondents who indicated they do perceive opportunities
+The interaction term $\beta_5FearFailure*PerceivedOpportunities$ was added to the regression because the survey question regarding "Fear of Failure" was only proposed to survey respondents who indicated they do perceive opportunities to start a business.
+
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
+
+# Import df of dependent and independent variables
+CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")
+
+# Run linear regression R1
+R1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)
+
+# Run linear regression R2
+R2 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)
+
+# Run linear regression R3
+R3 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)
+
+```
+
+```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
+
+# Library Stargazer for regression output tables
+library(stargazer)
+
+# Create regression output table
+labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
+            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')
+
+dlables <- c('National Level Average Percent Entrepreneurial Intention', 'National Level Nascent Entrepreneural Activity', 'National Level Average Percent Owning a Business')
+
+stargazer::stargazer(R1, R2, R3, covariate.labels = labels, dep.var.labels = dlables,
+                     title = 'Linear Regression Estimates', digits = 2, type = 'html')

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Added regression results to paper draft

@@
 
+(Take this for the paper)
+
+Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the  dependent variables we selected as indicators of the entrepreneurship rate.
+Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant and has a negative relationship with our explanatory variables.
+
+Overall, however, if we omit country-specific effects, we can demonstrate that the Way of Teaching and the Percent Perceived Good Opportunities are statistically significant in the model indicated below.
+
+<br>
+
+$NationalLevelAveragePercentOwningaBusiness = -6.82 + 1.03WayofTeaching + 0.10Percent Perceived Capability +$  
+$0.21Percent Fear Failure$ $+$ $0.12Percent Perceived Opportunities - 0.005Percent Fear Failure$ $*$ $Percent Perceived Opportunities$
+
+<br>
+
+We can show the relationship between the dependent and explanatory variables in the four simulations below.
+The R package Zelig allows us to set parameters for an explanatory variable and simulate 1000 trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).
+We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.
+A regression output table has also been included below.
+
+The simulations labeled "Unimputed" were created using only data collected from GEM.
+This simulation is not possible with missing data, so observations with missing data were omitted.
+In an attempt to increase the accuracy of this model, we used the R program Amelia to generate an imputed data frame.
+This program uses statistical inference to generate this data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).
+Simulations titled "Imputed" were calculated using this imputed data frame.
+
+```{r echo = FALSE, cache= FALSE, include= FALSE}
+
+# Library Zelig (can be buggy if loaded too early)
+library(Zelig)
+
+# Library Amelia for imputed data
+library(Amelia)
+
+# Import df of dependent and independent variables
+CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")
+
+############ Running a regression with full df (including omitted variables)
+RG1 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
+
+RG2 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+
+############ Running a regression omitting omitted variables
+
+# Generate a df omitting omitted variables
+CD_omitted <- na.omit(CD)
+
+# Run a least squares regression with Zelig
+Z1 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")
+
+############ Runnig a Zelig regression with imputed data and omitting remaining omitted variables
+
+# Import csv of df with imputed figures (created in Index_sources/Amelia_source)
+CI <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/gh-pages/GEMData/Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)
+
+# Omit variables that could not be imputed by Adelia (b/c of lack of data)
+CI_omitted <- na.omit(CI)
+
+# Regression equation with imputed values
+Z2 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")
+
+############ Set range of values for Z1 and Z2 using imputed and not imputed dfs
+
+####### Simulate Percent Perceived
+
+# Set range of PercentPerceived values in simulation (NOT IMPUTED)
+x.out1 <- setx(Z1, PercentPerceived = 9:67)
+
+# Run simulation (default 1000 trials) (NOT IMPUTED)
+simz1 <- sim(Z1, x = x.out1)
+
+# Set range of PercentPerceived values in siumlation (IMPUTED)
+x.out2 <- setx(Z2, PercentPerceived = 9:67)
+
+# Run simulation (default 1000 trials) (IMPUTED)
+simz2 <- sim(Z2, x = x.out2)
+
+####### Simulate Way of Teaching
+
+# Set range of WayofTeaching values in simulation (NOT IMPUTED)
+x.out3 <- setx(Z1, WayofTeaching = 1.353:3.278)
+
+# Run simulation (default 1000 trials) (NOT IMPUTED)
+simz3 <- sim(Z1, x = x.out3)
+
+# Set range of WayofTeaching values in simulation (IMPUTED)
+x.out4 <- setx(Z2, WayofTeaching = 1.128:3.312)
+
+# Run simulation (default 1000 trials) (IMPUTED)
+simz4 <- sim(Z2, x = x.out4)
+
+```
+
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
+library("Zelig")
+
+# Set layout
+par(mfrow = c(2, 2))
+
+# Plot simz1 (unimputed)
+plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
+     main = "Unimputed (Equation 1)")
+
+# Plot simz2 (imputed)
+plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
+     main = "Imputed (Equation 2)")
+
+# Plot simz3 (unimputed)
+plot(simz3, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner',
+     main = "Unimputed (Equation 1)")
+
+# Plot simz4 (imputed)
+plot(simz4, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner',
+     main = "Imputed (Equation 2)")
+
+```
+
+```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
+library(stargazer)
+
+# Create regression output table
+labels <- c('Way of Teaching', 'National Level Perceived Capabilities', 'National Level Avg Fear of Failure',
+            'National Level Avg Perceived Good Opportunities', 
+            'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities',
+            '(Intercept)')
+
+dlabels <- c('National Level Average Percent Owning a Business')
+
+```
+
+<br>
+
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
+
+stargazer::stargazer(Z1, Z2, covariate.labels = labels, dep.var.labels = dlabels,
+                     title = 'Linear Regression Estimates', notes = "Regression equation 1 is unimputed, regression equation 2 is imputed", digits = 2, type = 'latex')
+
+```
+
 ```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-We expect to observe the following causal chain :
+Drawing from the literature, we expect to observe the following causal chain :
 
@@
 This also entails supporting students' taking initiatives, encouraging creativity will also be part of this self-confidence reinforcement.
+
+The support of students' self-confidence within education systems as we just defined it can also affect the students' entrepreneurial self-efficacy, which should be controled for.
+Which we will do by looking into average perceived entrepreneurial capabilities and fear of failure
+
+indeed an effective explanatory variable, we will need to control for the entrepreneurial self-efficacy
 

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

--- 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
@@
 
-Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009] we should ideally be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too as this table shows :
-
-Variable | France | UK
--------------|---------------|---------
-Sense of belonging (PISA 2012) | 47% | 79%
-
-The lack of suitable data as well as the fact that OECD PISA tends to focus on different aspects of education systems for every triennal survey lead us to give up on this.
-But we still think that should be included in a future research on that topic.
-
 Of course, we also looked into other studies connecting educational features and entrepreneurship.
@@
 This entails providing feedback that will help the students maintain their level of motivation as well as their level of self-esteem.
-This also entails supporting students' taking initiatives, encouraging creativity will also be part of this self-confidence reinforcement.
+This also entails supporting students taking initiatives, encouraging creativity.
 
-Ideally we would have also liked to add the social dimension to it, meaning that students that are socially included may have a slightly higher degree of self-confidence, as we saw suggested in the literature.
+The support of students' self-confidence within education systems as we just defined it can also affect the students' entrepreneurial self-efficacy, that should be controled for.
+To do so, we will look at average perceived entrepreneurial capabilities and fear of failure in starting a business across the population at the country-level.
+
+Ideally, since the literature suggests that self-confidence depends partly on one's integration within social networks [@OECD2009], we should ideally be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too :
+
+Variable | France | UK
+-------------|---------------|---------
+Sense of belonging (PISA 2012) | 47% | 79%
+
+The lack of suitable data as well as the fact that OECD PISA tends to focus on different aspects of education systems for every triennal survey, lead us to give up on this.
+But we still think that should be included in a future research on that topic.
+
+Regarding potential control variables, we should normally consider including at least the main environmental determinants of entrepreneurship but the lack of consistency in the data at hand for our explanatory variables made us use a summary of those as a proxy.
+We chose to use the level of good opportunities to start a business perceived on average across the population of the given country.
+
+We will now present our quantitative methodology and the indicators we used in greater detail.
 

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Whilst it is tempting to look at education systems in a very pragmatic way with ratios of teachers per student, or students per class, we suggest to use another kind of indicators in order to trace the potential long-term investment made by governments.
+Whilst it is tempting to look at education systems in a very pragmatic way with ratios of teachers per student, or number of students per class, we suggest to use another kind of indicators in order to trace the potential long-term investment made by governments.
 Indeed, we believe that education systems can favour entrepreneurship and, beyond, GDP growth at the country-level, depending on how supportive of students' self-confidence and how socially inclusive they are.
@@
 
-The regulatory framework, which includes administrative burdens, regulations and frameworks, as well as fiscal policy parameters.
+**The regulatory framework**, which includes administrative burdens, regulations and frameworks, as well as fiscal policy parameters.
 
-The market conditions, which include anti-trust laws, rules for competition, access to foreign markets, degree of public involvement and level of private demand.
+**The market conditions**, which include anti-trust laws, rules for competition, access to foreign markets, degree of public involvement and level of private demand.
 
-The access to finance, which includes access to debt financing, access to venture capital, and stock markets.
+**The access to finance**, which includes access to debt financing, access to venture capital, and stock markets.
 
-The creation and diffusion of knowledge, which include research and development activity, transfer of non-commercial knowledge, co-operation among firms, technology availability and take-up.
+**The creation and diffusion of knowledge**, which include research and development activity, transfer of non-commercial knowledge, co-operation among firms, technology availability and take-up.
 
-The entrepreneurial capabilities, which includes business and entrepreneurship education as well as immigration.
+**The entrepreneurial capabilities**, which includes business and entrepreneurship education as well as immigration.
 
-The entrepreneurship culture of a given area or population (The OECD refers partially to the Global Entrepreneurship Monitor or GEM data).
+**The entrepreneurship culture** of a population.
 

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Grilo and Thurik [@Grilo2005b] who looked into what determines entrepreneurship engagement levels throughout the European Union and the US pointed especially at the level of financial support available for entrepreneurs in the country and at administrative complexities.
+Grilo and Thurik [@Grilo2005b] who looked into what determines entrepreneurship engagement levels throughout the European Union and the US pointed especially at the level of financial support available for entrepreneurs in the country and also at administrative complexities.
 
@@
 Rather than trying to trace cultural features at large, as we mentioned earlier, we intend to focus specifically on one key cultural institution, that is the education system.
-Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996].
+Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996] which is key as "individuals who decide to start a new business exhibit more confidence than those who do not"  ???????
+Robin M.
+Hogarth and Natalia Karelaia 2011 Entrepreneurial success and failure MAIN BIB ?????????.
 Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012, there seem to be different amounts of entrepreneurial self-efficacy between countries.
+Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012, there seem to be different amounts of self-confidence and entrepreneurial self-efficacy between countries.
 By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur.
@@
 Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is much more rarely activitated in France, and only on an voluntary individual teacher's basis.
+
 Drawing from Inglehart research ?????????
@@
 We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.
-
 This assumption draws from Boyd and Vozikis's ???????

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Drawing from Inglehart research ?????????
-MAIN BIB 2000 ????????, we understand the period between 0 and 20 years of age to be a defining time in terms of personal values and personality construction, thus compulsory education, generally between 6 and 16 years of age, can prove of key importance in the building up of one's self-confidence.
+Our focus on the education systems stems partly from experience and from Inglehart research ?????????
+MAIN BIB 2000 ????????
+.
+Indeed, we understand the period between 0 and 20 years of age to be a defining time in terms of personal values and personality construction, thus compulsory education, generally between 6 and 16 years of age, can prove of key importance in the building up of one's self-confidence.
 We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-We will now present our quantitative methodology and the indicators we used in greater detail.
+As we attempt to measure the impact of education systems' support of students' self-confidence on the rate of entrepreneurship at the country-level, we expect to observe different effects depending if we consider entrepreneurial intentions only or we also look into actual entrepreneurial activities.
+Even in measuring the impact on activities, we could potentially observe different effects between nascent and established entrepreneurship.
+Therefore, we will consider the three measures of entrepreneursip separately:
+
+1 Entrepreneurial Intentions
+
+2 Nascent Entrepreneurship
+
+3 Established Entrepreneurship
+
+Having explained what lead us into this specific research design, we will now present our methodology for a quantitative analysis and the indicators that we used in greater detail.
 

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Ideally, since the literature suggests that self-confidence depends partly on one's integration within social networks [@OECD2009], we should ideally be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too :
+Ideally, since the literature suggests that self-confidence depends partly on one's integration within social networks [@OECD2009], we should be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too :
 
@@
 
-The lack of suitable data as well as the fact that OECD PISA tends to focus on different aspects of education systems for every triennal survey, lead us to give up on this.
+The lack of suitable data as well as the fact that OECD PISA tends to focus on different aspects of education systems for every triennal survey, lead us to give up on this for the time being.
 But we still think that should be included in a future research on that topic.

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Edited stargazer table

@@
 
-(Take this for the paper)
-
 Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the  dependent variables we selected as indicators of the entrepreneurship rate.
@@
 
-stargazer::stargazer(Z1, Z2, covariate.labels = labels, dep.var.labels = dlabels,
+stargazer::stargazer(Z1, Z2,
                      title = 'Linear Regression Estimates', notes = "Regression equation 1 is unimputed, regression equation 2 is imputed", digits = 2, type = 'latex')
@@
 
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
+```{r echo = FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
 

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Merged docs

@@
 date: "10 december 2014"
-output: html_document
+linestretch: 2 
+output: pdf_document
 ---
@@
 * * *
-```{r echo=FALSE, cache=TRUE, include=FALSE}
+
+```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
 
 # Set working directory
-setwd('~/Assign2Education/Proposal')
+setwd('~/Assign2Education/PresentationandPaper')
 
-# Install necessary packages
-library(plyr)
+# Library required packages
+library(ggvis)
+library(devtools)
+library(googleVis)
+library(countrycode)
 library(repmis)
-library(tidyr)
 library(reshape2)
-library(foreign)
+library(shiny)
+library(httpuv)
+library(ggplot2)
 
-# Install rempis from Christpher Gandrud's website
-devtools::install_github('christophergandrud/repmis')
-library(repmis)
+# Create a vector of packages used
+pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv', 'Zelig',
+          'stargazer', 'Amelia', 'ggplot2')
 
-# Load citation package
-pkgs <- c('repmis')
+# Create citations txt file
 repmis::LoadandCite(pkgs, file= 'RpackageCitations.bib')
+
+# Import WayofTeaching data
+wot <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")
 
@@
 
-#### Dependent Variables: Explaining the Country-level Rate of Entrepreneurship
+**Quantitative Analysis of the Impact of Education on Entrepreneurship**
 
-We have examined three dimensions of entrepreneurship to prepare for this stage of the project, established entrepreneurship in the country, nascent entrepreneurship (less than three months), and entrepreneurial intention.
-We will study each of these successively as we may well observe different effects.
+*Data Sources*
 
-To measure these three dimensions of entrepreneurship, we have used three [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) indicators:
+To complete a quantitative analysis of the impact of educational factors -- specifically the encouragement of creatitivity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship, we have drawn on publicly available data from the Global Entrepreneurship Monitor (GEM) National Expert Survey (NES) and Adult Population Survey (APS).
 
-- Established Business Ownership Rate (Percentage) 
-- Nascent Entrepreneurship Rate (Percentage)
-- Entrepreneurial intention Rate (Percentage)
+The Global Entrepreneurship Monitor project is an annual assessment of the entrepreneurial activity, aspirations, and attitudes of individuals across a wide range of countries.
+The countries covered have grown from a low of ten to covering 75% of world population and 89% of world GDP by 2013.
+The 2001-2010 multi-year APS data base, for example, contains over 1.3 million observations of a total of 85 countries.
+This data is often cited in academic research, including reports by the Organisation for Economic Co-operation and Development.
 
-#### Key Explanatory Variable: Degree of Self-confidence Reinforcement within the Education System
-
-As Inglehart has shown how personal values are shaped before the age of 20, we will try to show how compulsory education (from 6 to 16 years of age) shapes individuals, especially in terms of self-esteem.
-To do so, we decided to incorporate GEM indicators that relate to self- confidence.
-First, we included GEM survey data on the average "perceived capabilities" of an individual (18-64) in a given country to start a business.
-Second, we included additional GEM data on how the "fear of failure" could deter an average individual (18-64) in a country to become an entrepreneur.
-Both of these data sets indicate the average percentage for each characteristic at the country-level but they are solely describing a level of self-confidence in one's abilities to become an entrepreneur.
-We chose to use them as such even if they do not trace the specific causal chain between education systems and entrepreneurship that we intend to focus on.
-
-In order to trace specifically how supportive of one's self-confidence a given education system is, we chose to use one specific item of the GEM [National Experts Survey (NES)](http://www.gemconsortium.org/Data-Collection) as a proxy, namely D01.
-
-"In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative"
-
-Regarding this statement, the experts surveyed had to state whether it is:
-
-1 completely false  
-2 somewhat false  
-3 neither true nor false  
-4 somewhat true  
-5 completely true
-
-97 do not know  
-98 not applicable
-
-After searching through many potential data sources about education and finding no indicators suitable to trace our causal chain, we were forced to use that one item of a survey however low quality it might be.
-
-As a matter of fact, there are many reasons for which we should be concerned about that data and its quality.
-
-First, it was not always collected which makes any measure hard to follow through time, it is only since 2009 and 2011 that the NES was made compulsory.
-
-Second, the National Expert Surveys are very subjective data. For each entrepreneurial framework condition, that is:
+The NES is structured around nine entrepreneurial framework contitions evaluated by thirty-six experts in each surveyed country.
+These nine entrepreneurial framework conditions are included below (a minimum of four experts must be interviewed on each of the framework conditions).
 
@@
 
-Only four experts per framework condition are consulted in each country participating.
-
-Third, the collection of data could arguably be improved.
-Indeed, it is outsourced by GEM Coordination Team to national teams which seem to manage the time allowed for collection poorly ???METHODOLOGY NES REPORT HERE MAIN BIB ???
-.
-The national teams also tend to rely solely on their own personal networks.
-Which does not guarantee to get the best experts on each topic.
-
-Fourth, as a result of the flows above mentioned, we observe a lot of variation from year to year up to 0.73 on a scale from 1 to 5, that is up to 14.6% (UK 2007 / UK 2009).
-Which is far from what one would expect.
-Indeed, it seems very doubtful to say that the way of teaching in any country varies so much over time.
-Educational reforms are much more rare and one should on the contrary expect to see much more stability, almost a constant over a decade.
-
-#### Control Variables: Controlling for Classic Determinants of Entrepreneurship
-
-To control for the general state of the economy, we included annual GDP Growth from the World Bank [World Development Indicators](http://data.worldbank.org/data-catalog/world-development-indicators) as a control variable in our regression equations.
-In addition, we included a GEM indicator called "Perceived Opportunities." For each country, it is the average percentage of individuals who believe there are opportunities to start a business in their area.
-Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.
-
-In the future, we may revise this to include lagged GDP growth in recognition of the time taken for governments and individuals to react to the state of the economy, and are planning to include control variables from GEM.
-Specifically, we intend to control for the classic determinants of entrepreneurship -- economic and structural determinants.
-To do so, we will add the following nine key entrepreneurship conditions as defined in the GEM [National Experts Survey (NES)](http://www.gemconsortium.org/Data-Collection).
-
-1. Finance  
-2. Government policies  
-3. Government programs  
-4. Entrepreneurial Education and Training  
-5. Research and Development Transfer (R & D)  
-6. Commercial and professional infrastructure  
-7. Internal Market openness  
-8. Physical infrastructure and services  
-9. Cultural and social norms
-
-#### Regressions
-
-The following equations were used to determine the relationship between our dependent and explanatory variables:
-
-1. $PercentIntention = PercentPerceived(Perceived Capabilities) + Way of Teaching + PercentOpportunities(Perceived Opportunities)$
-
-2. $PercentNascent = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
-
-3. $PercentOwner = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$
-
-The variables *Percent Fear* and *Percent Opportunities* were included as an interaction term $PercentFear*PercentOpportunities$ because of the design of the survey.
-PercentFear is: "the Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business."
+The APS is a questionnaire distrubuted to a minimum of 2,000 adults in each participating country.
+The survey is created by a central GEM team, but the implementation is managed by national teams that compete for the role of implementing the survey.
+Experts are chosen based on experience and specialization and are expected to represent the entire country (including urban and rural areas).
 
@@
 
-#### Data Collection and Cleaning
+**Data Selection**
 
-To collect the data necessary to run these regression equations, we downloaded *.csv* data from GEM and used the WDI API to obtain the necessary annual GDP growth of OECD Countries.
+After reviewing the available data, we decided to select the following variables for our analysis.
 
-**Necessary R Packages**
+Source | Indicator 
+-------------|---------------
+APS | Rate of Entrepreneurship (Intention, Nascent, Established)
+NES | Way of Teaching
+APS | Perceived Capabilities
+APS | Fear of Failure / Perceived Opportunities
+APS | Perceived Opportunities
 
-The following packages were needed to complete the data collection portion of this assignment:
+The survey questions corresponding to these variables are as follows:
 
-- repmis  
-- tidyr  
-- reshape  
-- plyr  
-- WDI
+1. **Entrepreneurial Intention**: Percentage of 18-64 population (individuals involved in any stage of entrepreneurial activity excluded) who intend to start a business within three years.
 
-**GEM Data**
+2.
+**Nascent Entrepreneurship**: Percentage of 18-64 population who are currently a nascent entrepreneur, i.e., actively involved in setting up a business they will own or co-own; this business has not paid salaries, wages, or any other payments to the owners for more than three months.
 
-GEM data was embedded in an interactive database and was difficult to extract automatically without writing a programme.
-To simplify this process, we downloaded the necessary *.csv* files and saved them in our GitHub repository (to reduce complexity, we deleted the first three unnecessary rows before saving).
-We then linked to the RAW version of the files and added the code required to load them from *R*.
-The repmis package is required to load these documents from the repository.
+3.
+**Established Entrepreneur**: Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid salaries, wages, or any other payments to the owners for more than 42 months.
 
-Cleaning the GEM data required deleting unnecessary characters in the year columns, changing the years from columns to rows (changing the data from wide to long), and changing the column names to describe which data was being analysed.
-In the process of doing this we created new data sets for each of these survey questions, which were called C*dataset* (clean followed by the data set name).
-This was done for each of the six GEM data sets before merging these sets two at a time to create the data set *FinalGEM*.
+4. **Way of Teaching**: In my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative.
 
-For all 33 OECD countries we should have 13 observations, one per year from 2001 to 2013, for each variable.
-However, there are a few missing values, especially regarding the perceived opportunities for some countries, namely Estonia, Luxembourg and Slovak Republic.
+5. **Perceived Capabilities**: Percentage of 18-64 population who believe to have the required skills and knowledge to start a business
 
-**World Bank Data**
+6. **Fear of Failure**: Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
 
-As mentioned above, one of our control variables, annual GDP growth, was obtained using the WDI API from the World Bank.
-Using this API, we accessed GDP data from all the OECD countries directly from *R*.
-To clean this data, we used *plyr* to change the variable names then recoded the U.S.
-and South Korea country names to maintain consistency with the GEM data set and dropped an unnecessary column that was not included with the GEM data.
+7. **Perceived Opportunities**: Percentage of 18-64 population who see good opportunities to start a firm in the area where they live
 
-Finally, we merged the annual GDP growth data with the *FinalGEM* data set to create *CompleteDataset*.
-This is the data set used to run the regressions and generate the charts and figures outlined in this document.
-To reduce complexity in the environment we also included a command to remove unnecessary objects in the environment.
+The APS data represent the national-level average of values between 1 and 100 that were gathered as responses to surveys within each country.
+The NES data is calculated based on the average answer to a survey to the national experts.
+For each question, the experts surveyed had to state whether it is:
 
-<br>
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
+1. Completely false
+2. Somewhat false
+3. Neither true or false
+4. Somewhat true
+5. Completely true
 
-#### Import data from GEM Survey ####
+(97. Do not know)  
+(98. Not applicable)
 
-# Import GEM fear of failure data
-FearFail <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_FearFail.csv", header = TRUE, cache = FALSE)
+The process of importing, cleaning, and analyzing all of the data used in this project is fully documented and reproducable by referencing our GitHub repository.
 
-# Import GEM estblished entrepreneurship - current owner data
-CurrentOwner <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_CurrentOwner.csv", header = TRUE, cache = FALSE)
+**Analytical Framework**
 
-# Import GEM entrepreneurial intention data
-EntreIntention <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_EntreIntention.csv", header = TRUE, cache = FALSE)
+To understand the impact of educational factors -- specifically the encouragement of creatitivity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship we built our model as outlined in the table below.
 
-# Import GEM nascent entrepreneur data
-NascentEntre <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_NascentEntre.csv", header = TRUE, cache = FALSE)
+Variable | Indicator 
+-------------|---------------
+Y Dependent Variable | Rate of Entrepreneurship (Intention, Nascent, Established)
+X1 Explanatory Variable | Way of Teaching
+X2 Control Variable | Perceived Capabilities
+X3 Control Variable | Fear of Failure / Perceived Opportunities
+X4 Control Variable | Perceived Opportunities
 
-# Import GEM perceived capabilities data
-PerceivedCapabilities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEM_PerceivedCapabilities.csv", header = TRUE, cache = FALSE)
+..........(Describe why we use the rate of entrepreneurship indicators we chose)
 
-# Import GEM perceived opportunities data as a proxy for potential control variables
-PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE)
+Data on our explanatory variable, Way of Teaching, is available on the GEM website for the years 2001-2010.
+To illustrate the distribution of this data, we have created the following histogram.
+As shown in the histogram, the largest density of scores is approximately 2.3, which lies between the "somewhat false" and "neither true or false" categories.
+This is not a whole number because the scores given by each of the 4 experts surveyed for each frameork condition are averaged to create a national-level number.
+As discussed later in this paper, this presents some difficulties in drawing substantive conclusions from this data.
+Namely, a large number of indifferent responses complicate the process of determining the influence we would like to analyze.
 
-# Import 2010GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is
-SupportiveTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/GEMAvgIndicators.csv", header = TRUE, cache = FALSE)
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis', warning=FALSE}
 
-# Import GEM 2009 supportive teaching data
-setwd('~/Assign2Education/GEMData')
+# Library ggplot2
+library("ggplot2")
 
-GEM2001 <- read.spss('2001GEMNES.sav', to.data.frame = TRUE)
-GEM2002 <- read.spss('2002GEMNES.sav', to.data.frame = TRUE)
-GEM2003 <- read.spss('2003GEMNES.sav', to.data.frame = TRUE)
-GEM2004 <- read.spss('2004GEMNES.sav', to.data.frame = TRUE)
-GEM2005 <- read.spss('2005GEMNES.sav', to.data.frame = TRUE)
-GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
-GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
-GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
-GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
-GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)
-
-#### Clean data using tidy ####
-
-### Clean FearFail ###
-# Percentage of 18-64 population with positive perceived opportunities who indicate that fear of failure would prevent them from setting up a business.
-
-# Remove X's in FearFail year columns
-names(FearFail) <- gsub("X", "", names(FearFail))
-
-# Change years from columns to rows and create CFearFail
-CFearFail <- melt(data = FearFail,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010", "2011", "2012",
-                                   "2013"))
-
-# Rename columns
-CFearFail <- plyr::rename(x = CFearFail, 
-                                      replace = c("variable" = "Year",
-                                                  "value" = "PercentFear"))
-
-### Clean CurrentOwner ###
-# Percentage of 18-64 population who are currently owner-manager of an established business, i.e., owning and managing a running business that has paid sallaries, wages, or any other payments to the owners for more than 42 months
-
-# Remove X's in CurrentOwner year columns
-names(CurrentOwner) <- gsub("X", "", names(CurrentOwner))
-
-# Change years from columns to rows and create CCurrentOwner
-CCurrentOwner <- melt(data = CurrentOwner,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010", "2011", "2012",
-                                   "2013"))
-
-# Rename columns
-CCurrentOwner <- plyr::rename(x = CCurrentOwner, 
-                                      replace = c("variable" = "Year",
-                                                  "value" = "PercentOwner"))
-
-### Clean EntreIntention ###
-# Percentage of 18-64 population (individuals involved in any stage of entrepenerurial activity excluded) who intend to start a business within three years.
-
-# Remove X's in EntreIntention year columns
-names(EntreIntention) <- gsub("X", "", names(EntreIntention))
-
-# Change years from columns to rows and create CEntreIntention (No 2001 data available)
-CEntreIntention <- melt(data = EntreIntention,
-                  id.vars = c("Country"),
-                  measure.vars = c("2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010", "2011", "2012",
-                                   "2013"))
-
-# Rename columns
-CEntreIntention <- plyr::rename(x = CEntreIntention, 
-                                      replace = c("variable" = "Year",
-                                                  "value" = "PercentIntention"))
-
-### Clean NascentEntre ###
-# Percentage of 18-64 population who are currently a nascent entrepreneur, i.e., actively involved in setting up a business they will own or co-own; this business has not paid salaries, wages, or any other payments to the owners for more than three months.
-
-# Remove X's in NascentEntre year columns
-names(NascentEntre) <- gsub("X", "", names(NascentEntre))
-
-# Change years from columns to rows and create CNascentEntre
-CNascentEntre <- melt(data = NascentEntre,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010", "2011", "2012",
-                                   "2013"))
-
-# Rename columns
-CNascentEntre <- plyr::rename(x = CNascentEntre, 
-                                      replace = c("variable" = "Year",
-                                                  "value" = "PercentNascent"))
-
-### Clean PerceivedCapabilities ###
-# Percentage of 18-64 population who believe to have the required skills and knowledge to start a business
-
-# Remove X's in PerceivedCapabilities year columns
-names(PerceivedCapabilities) <- gsub("X", "", names(PerceivedCapabilities))
-
-# Change years from columns to rows and create CPreceivedCapabilities
-CPerceivedCapabilities<- melt(data = PerceivedCapabilities,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010", "2011", "2012",
-                                   "2013"))
-
-# Rename columns
-CPerceivedCapabilities <- plyr::rename(x = CPerceivedCapabilities, 
-                                      replace = c("variable" = "Year",
-                                                  "value" = "PercentPerceived"))
-
-### Clean PerceivedOpportunities ###
-# Percentage of 18-64 population who see good opportunities to start a firm in the area where they live
-
-# Remove X's in PerceivedOpportunities year columns
-names(PerceivedOpportunities) <- gsub("X", "", names(PerceivedOpportunities))
-
-# Change years from columns to rows and create CPreceivedOpportunities
-CPerceivedOpportunities<- melt(data = PerceivedOpportunities,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010", "2011", "2012",
-                                   "2013"))
-
-# Rename columns
-CPerceivedOpportunities <- plyr::rename(x = CPerceivedOpportunities, 
-                                      replace = c("variable" = "Year",
-                                                  "value" = "PercentOpportunities"))
-
-### Clean GEM NES Datasets
-# Draw out Country and D01 only
-Clean01 <- GEM2001[,c("country", "ki01d01")]
-Clean02 <- GEM2002[,c("country", "ki02d01")]
-Clean03 <- GEM2003[,c("country", "ki03d01")]
-Clean04 <- GEM2004[,c("ki04ctry", "ki04d01")]
-Clean05 <- GEM2005[,c("KI05ctry", "KI05D01")]
-Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
-Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
-Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
-Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
-Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]
-
-remove(GEM2001, GEM2002, GEM2003, GEM2004, GEM2005, GEM2006, GEM2007, GEM2008, GEM2009, GEM2010)
-
-# Edit column names for each dataframe
-
-Clean01 <- plyr::rename(x = Clean01, 
-                                      replace = c("ki01d01" = "Year01",
-                                                  "country" = "Country"))
-
-Clean02 <- plyr::rename(x = Clean02, 
-                                      replace = c("ki02d01" = "Year02",
-                                                  "country" = "Country"))
-
-Clean03 <- plyr::rename(x = Clean03, 
-                                      replace = c("ki03d01" = "Year03",
-                                                  "country" = "Country"))
-
-Clean04 <- plyr::rename(x = Clean04, 
-                                      replace = c("ki04d01" = "Year04",
-                                                  "ki04ctry" = "Country"))
-
-Clean05 <- plyr::rename(x = Clean05, 
-                                      replace = c("KI05D01" = "Year05",
-                                                  "KI05ctry" = "Country"))
-
-Clean06 <- plyr::rename(x = Clean06, 
-                                      replace = c("KI06D01_mean" = "Year06",
-                                                  "KI06CTRY" = "Country"))
-
-Clean07 <- plyr::rename(x = Clean07, 
-                                      replace = c("ki07d01_" = "Year07",
-                                                  "ki07ctry" = "Country"))
-
-Clean08 <- plyr::rename(x = Clean08, 
-                                      replace = c("NES08_D01_MEAN" = "Year08",
-                                                  "NES08COUNTRY" = "Country"))
-
-Clean09 <- plyr::rename(x = Clean09, 
-                                      replace = c("NES09_D01_MEAN" = "Year09",
-                                                  "NES09COUNTRY" = "Country"))
-
-Clean10 <- plyr::rename(x = Clean10, 
-                                      replace = c("NES10_D01_MEAN" = "Year10",
-                                                  "NES10CRNAME" = "Country"))
-
-#### Merge the data ####
-MergedGEM <- merge(CCurrentOwner, CEntreIntention,
-                   union("Country", "Year"),
-                   all = TRUE)
-
-MergedGem2 <- merge(CFearFail, CNascentEntre,
-                   union("Country", "Year"),
-                   all = TRUE)
-
-MergedGem3 <- merge(CPerceivedCapabilities, MergedGEM,
-                   union("Country", "Year"),
-                   all = TRUE)
-
-MergedGem4 <- merge(MergedGem2, MergedGem3,
-                   union("Country", "Year"),
-                   all = TRUE)
-
-FinalGEM <- merge(MergedGem4, CPerceivedOpportunities,
-                   union("Country", "Year"),
-                   all = TRUE)
-
-# Convert percent columns from character to numeric
-FinalGEM[,"PercentPerceived"] <- as.numeric(FinalGEM[,"PercentPerceived"])
-FinalGEM[,"PercentFear"] <- as.numeric(FinalGEM[,"PercentFear"])
-FinalGEM[,"PercentNascent"] <- as.numeric(FinalGEM[,"PercentNascent"])
-FinalGEM[,"PercentOwner"] <- as.numeric(FinalGEM[,"PercentOwner"])
-FinalGEM[,"PercentIntention"] <- as.numeric(FinalGEM[,"PercentIntention"])
-FinalGEM[,"PercentOpportunities"] <- as.numeric(FinalGEM[,"PercentOpportunities"])
-
-# Remove unncessary data from environment
-remove(CCurrentOwner, CEntreIntention, CFearFail, CNascentEntre, CPerceivedCapabilities, CPerceivedOpportunities, CurrentOwner, EntreIntention, FearFail, MergedGEM, MergedGem2, MergedGem3, MergedGem4, PerceivedCapabilities, PerceivedOpportunities, NascentEntre)
-
-CleanMerge <- cbind(names = c(rownames(Clean01), rownames(Clean02), rownames(Clean03),
-                              rownames(Clean04), rownames(Clean05), rownames(Clean06),
-                              rownames(Clean07), rownames(Clean08), rownames(Clean09),
-                              rownames(Clean10)),
-                    rbind.fill(list(Clean01, Clean02, Clean03, Clean04, Clean05, Clean06,
-                                    Clean07, Clean08, Clean09, Clean10)))
-
-# Recode countries
-CleanMerge$Country[CleanMerge$Country == "AUSTRALIA"] <- "Australia"
-CleanMerge$Country[CleanMerge$Country == "AUSTRIA"] <- "Austria"
-CleanMerge$Country[CleanMerge$Country == "BELGIUM"] <- "Belgium"
-CleanMerge$Country[CleanMerge$Country == "CANADA"] <- "Canada"
-CleanMerge$Country[CleanMerge$Country == "CHILE"] <- "Chile"
-CleanMerge$Country[CleanMerge$Country == "CZECH REPUBLIC"] <- "Czech Republic"
-CleanMerge$Country[CleanMerge$Country == "DENMARK"] <- "Denmark"
-CleanMerge$Country[CleanMerge$Country == "ESTONIA"] <- "Estonia"
-CleanMerge$Country[CleanMerge$Country == "FINLAND"] <- "Finland"
-CleanMerge$Country[CleanMerge$Country == "FRANCE"] <- "France"
-CleanMerge$Country[CleanMerge$Country == "GERMANY"] <- "Germany"
-CleanMerge$Country[CleanMerge$Country == "GREECE"] <- "Greece"
-CleanMerge$Country[CleanMerge$Country == "HUNGARY"] <- "Hungary"
-CleanMerge$Country[CleanMerge$Country == "ICELAND"] <- "Iceland"
-CleanMerge$Country[CleanMerge$Country == "IRELAND"] <- "Ireland"
-CleanMerge$Country[CleanMerge$Country == "ISRAEL"] <- "Israel"
-CleanMerge$Country[CleanMerge$Country == "ITALY"] <- "Italy"
-CleanMerge$Country[CleanMerge$Country == "JAPAN"] <- "Japan"
-CleanMerge$Country[CleanMerge$Country == "KOREA"] <- "South Korea"
-CleanMerge$Country[CleanMerge$Country == "LUXEMBURG"] <- "Luxemburg"
-CleanMerge$Country[CleanMerge$Country == "MEXICO"] <- "Mexico"
-CleanMerge$Country[CleanMerge$Country == "NETHERLANDS"] <- "Netherlands"
-CleanMerge$Country[CleanMerge$Country == "NEW ZEALAND"] <- "New Zealand"
-CleanMerge$Country[CleanMerge$Country == "NORWAY"] <- "Norway"
-CleanMerge$Country[CleanMerge$Country == "POLAND"] <- "Poland"
-CleanMerge$Country[CleanMerge$Country == "PORTUGAL"] <- "Portugal"
-CleanMerge$Country[CleanMerge$Country == "SLOVAK REPUBLIC"] <- "Slovak Republic"
-CleanMerge$Country[CleanMerge$Country == "SLOVENIA"] <- "SLOVENIA"
-CleanMerge$Country[CleanMerge$Country == "SPAIN"] <- "Spain"
-CleanMerge$Country[CleanMerge$Country == "SWEDEN"] <- "Sweden"
-CleanMerge$Country[CleanMerge$Country == "SWITZERLAND"] <- "Switzerland"
-CleanMerge$Country[CleanMerge$Country == "TURKEY"] <- "Turkey"
-CleanMerge$Country[CleanMerge$Country == "UNITED KINGDOM"] <- "United Kingdom"
-CleanMerge$Country[CleanMerge$Country == "UK"] <- "United Kingdom"
-CleanMerge$Country[CleanMerge$Country == "USA"] <- "United States"
-CleanMerge$Country[CleanMerge$Country == "UNITED STATES"] <- "United States"
-CleanMerge$Country[CleanMerge$Country == "Korea"] <- "South Korea"
-CleanMerge$Country[CleanMerge$Country == "US"] <- "United States"
-
-# Set columns to numeric
-CleanMerge[,"Year01"] <- as.numeric(CleanMerge[,"Year01"])
-CleanMerge[,"Year02"] <- as.numeric(CleanMerge[,"Year02"])
-CleanMerge[,"Year03"] <- as.numeric(CleanMerge[,"Year03"])
-CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year04"])
-CleanMerge[,"Year05"] <- as.numeric(CleanMerge[,"Year05"])
-CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year06"])
-CleanMerge[,"Year04"] <- as.numeric(CleanMerge[,"Year07"])
-CleanMerge[,"Year08"] <- as.numeric(CleanMerge[,"Year08"])
-CleanMerge[,"Year09"] <- as.numeric(CleanMerge[,"Year09"])
-CleanMerge[,"Year10"] <- as.numeric(CleanMerge[,"Year10"])
-
-# Change merged data from wide to long
-LongGEM<- melt(data = Merged9,
-                  id.vars = c("Country"),
-                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
-                                   "2007", "2008", "2009", "2010"))
-
-# Rename columns
-names(LongGEM) <- gsub("variable", "Year", names(LongGEM))
-names(LongGEM) <- gsub("value", "Support", names(LongGEM))
-
-# Create a vector with OECD countries
-myvars <- c('Australia', 'Austria', 'Belgium', 'Canada', 'Chile', 'Czech Republic', 'Denmark', 'Estonia', 'Finland', 'France', 'Germany', 'Greece', 'Hungary', 'Iceland', 'Ireland', 'Israel', 'Italy', 'Japan', 'Korea', 'Luxemburg', 'Mexico', 'Netherlands', 'New Zealand', 'Norway', 'Poland', 'Portugal', 'Slovak Republic', 'Slovenia', 'Spain', 'Sweden', 'Switzerland', 'Turkey', 'United Kingdom', 'United States')
-
-# Subset LongGEM with the countries we need
-subset_data <- subset(LongGEM, Country %in% myvars)
-
-# Delete unnecessary column
-subset_data$row.names <- NULL
-
-# Arrange subset_data by country and year
-GrandData <- arrange(subset_data, Country, Year)
-
-GrandData1 <- GrandData[order("Country",)]
-
-########### STUCK #############
-
-FinalData <- merge(FinalGEM, GrandData,
-                   union("Country", "Year"))
+# Create a histogram showing the distribution of Way of Teaching
+qplot(WayofTeaching, data = wot, geom = "histogram", binwidth = .10)
 
@@
 
-#### Data Analysis
+Starting with this explanatory variable, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).
+These three regression equations are as follows:
 
-To examine the relationship between these variables, we used least square estimation, the results of which can be found in the following table.
-The package *stargazer* was required to generate this table.
-As evidenced by the equation results, the individual variables selected are statistically significant, but the model only explains a relatively small degree of the variation in the dependent variable.
-For example, the adjusted $R^2$ of regression equation one is 0.29, the adjusted $R^2$ of regression equation two is 0.38, and the adjusted $R^2$ is 0.13.
-<br>
+1. $PercentEntreIntention = \beta_1WayofTeaching  + \beta_2PerceivedCabability + \beta_3PerceivedOpportunities$   
+  $+ \beta_4FearFailure + \beta_5FearFailure*PerceivedOpportunities$
 
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
+2. $PercentNascent = \beta_1WayofTeaching  + \beta_2PerceivedCabability + \beta_3PerceivedOpportunities$   
+  $+ \beta_4FearFailure + \beta_5FearFailure*PerceivedOpportunities$
 
-# Run linear regression R1
-R1 <- lm(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)
+3. $PercentOwner = \beta_1WayofTeaching  + \beta_2PerceivedCabability + \beta_3PerceivedOpportunities$   
+  $+ \beta_4FearFailure + \beta_5FearFailure*PerceivedOpportunities$
 
-# Obtain summary statistics of R1
-summary(R1)
-
-# Run linear regression R2
-R2 <- lm(PercentNascent ~ PercentPerceived + PercentFear*PercentOpportunities + Country, data = CompleteDataset)
-
-# Obtain summary statistics of R2
-summary(R2)
-
-# Run linear regression R3
-R3 <- lm(PercentOwner ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteDataset)
-
-# Obtain summary statistics of R3
-summary(R3)
-
-```
-
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
-
-# Library Stargazer for regression output tables
-library(stargazer)
-
-# Create regression output table
-labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
-            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')
-
-dlables <- c('National Level Average Percent Entrepreneurial Intention', 'National Level Nascent Entrepreneural Activity', 'National Level Average Percent Owning a Business')
-
-stargazer::stargazer(R1, R2, R3, covariate.labels = labels, dep.var.labels = dlables,
-                     title = 'Linear Regression Estimates', digits = 2, type = 'html')
-```
-<br>  
-National-level average of people perceiving opportunities but acknowledging fear of failure will prevent them from creating a business (FF)
-
-**Simulation Package and Cleaning**
-
-In addition to the output table, a simulation is helpful to visually illustrate the relationship the probability of obtaining a given value in the dependent variables conditional on change in the independent variable.
-We used the *Zelig* package to run a least square regression and generate a simulation of equation 1.
-Prior to running this regression, however, we ran the na.omit command to remove omitted variables from the equation.
-
-To examine the probabilities of achieving given outcomes, we generated three simulations for the first regression equation.  To demonstrate this method, we have included one simulation below.
-
-**Process**
-
-First, we estimated a least square equation with variation in the variable *PercentPerceived* of 20-100 percent.
-The ranges for variance in the independent variables was chosen by identifying the best range for capturing the largest degree of variance for the model.
-The first simulation is below.
-The y axis shows variation in *PercentIntention* conditional on change in *PercentPerceived* and the x axis shows variation in *PercentPerceived*.
-The results may be interpreted as showing that people who believe they have the knowledge required to start a business may or may not do so (with a high degree of variation), while people who do not believe they have this knowledge are consistently unlikely to start a business (there is little variation).
-
-```{r echo = FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
-
-# Library Zelig (can be buggy if loaded to early)
-library(Zelig)
-
-# Omit omitted data from simulation
-CompleteData_omit <- na.omit(CompleteDataset)
-
-# Run a least squares regression with Zelig
-Z1 <- zelig(PercentIntention ~ PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth, data = CompleteData_omit, model = "ls")
-```
-
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE }
-
-# Find appropriate range for PercentPerceived
-summary(CompleteData_omit$PercentPerceived)
-
-# Set range of PercentPerceived values in simulation
-x.out2 <- setx(Z1, PercentPerceived = 9:67)
-
-# Run simulation (default 1000 trials)
-simz2 <- sim(Z1, x = x.out2)
-
-# Adjust margins
-par(mar=c(2,2,2,2))
-
-# Plot simulation
-plot(simz2, xlab= 'PercentPerceived')
-
-```
-
-<br>
-
-#### Outlook
-
-Going forward, we are considering adding one of the six questions used by GEM to measure the importance of entrepreneurial education at the country level in its NES Survey.
-Item D01 states "in my country, teaching in primary and secondary education encourages creativity, self-sufficiency, and personal initiative." This could be a proxy to get a sense of how supportive of self esteem a given education system is.
-
-We may also want to quantify how individualistic or group-oriented an average student is by the end of compulsory education, as the literature holds social inclusion as an explanatory factor for self-esteem.
-We will use OECD PISA data on "the sense of belonging" for this.
-
-Next steps will also include looking more thoroughly into control variables and determining the most appropriate way to present our results.
-To do so we may need to extract data from various national NES reports and put together a table, as it does not seem to exist as such.
-
-```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
-
-library(stargazer)
-stargazer(CompleteDataset, type = 'html')
-
-```
-
-Estonia
-Luxemburg
-Slovak Republic
+The interaction term $\beta_5FearFailure*PerceivedOpportunities$ was added to the regression because the survey question regarding "Fear of Failure" was only proposed to survey respondents who indicated they do perceive opportunities to start a business.

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-Actually, what determines entrepreneurship at a country-level has been long searched already but although structural and environmental factors have been looked at extensively, less has been done regarding cultural or educational factors.
+Of course, what determines entrepreneurship at a country-level has been long searched already but although structural and environmental factors have been looked at extensively, less has been done regarding cultural or educational factors.
 Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ??????
@@
 
-Of course, we also looked into other studies connecting educational features and entrepreneurship.
+Eventually, this goes without saying, we also looked into other studies connecting educational features and entrepreneurship.
 As a matter of fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy ???????
@@
 
-Now, having explained how determinants of entrepreneurship have been looked into, having mentioned how education has been related to entrepreneurship so far, we need to assert here our very research design.
+**Quantitative Analysis of the Impact of Education on Entrepreneurship**
+
+*Research Design*
+
+At this stage, having explained how determinants of entrepreneurship have been looked into, having mentioned how education has been related to entrepreneurship so far, we need to assert here our very research design.
 What we expect to find out is to what extent the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries.
@@
 This entails providing feedback that will help the students maintain their level of motivation as well as their level of self-esteem.
-This also entails supporting students taking initiatives, encouraging creativity.
+This also includes supporting students taking initiatives and encouraging their creativity.
 
@@
 
-Having explained what lead us into this specific research design, we will now present our methodology for a quantitative analysis and the indicators that we used in greater detail.
-
-**Quantitative Analysis of the Impact of Education on Entrepreneurship**
+Having explained what lead us into this specific research design, we will now present our data sources in greater detail.
 

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Add map to draft

@@
 
+In addition to understanding the density of each recorded "Way of Teaching" indicator, it is also helpful to examine the differences in this indicator among OECD countries.
+To see this, we have created a figure showing the distribution of the average "Way of Teaching" value over the 2001-2010 period for the OECD countries included in the surveys.
+This figure is included below.
+
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+# Import GEM data frame
+WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")
+
+# Drop unnecessary column 1
+WayofTeaching$X <- NULL
+
+# Change data from long to wide format
+WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")
+
+# Delete variable name in Year columns
+names(WT) <- gsub("WayofTeaching.", "", names(WT))
+
+# Duplicate df for future use
+WT2 <- WT
+
+# Generate a new column with mean of all other columns
+WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
+                                          "2009", "2010")), na.rm = TRUE)
+
+# Drop year columns, leaving only mean column
+WT$'2001' <- NULL
+WT$'2002' <- NULL
+WT$'2003' <- NULL
+WT$'2004' <- NULL
+WT$'2005' <- NULL
+WT$'2006' <- NULL
+WT$'2007' <- NULL
+WT$'2008' <- NULL
+WT$'2009' <- NULL
+WT$'2010' <- NULL
+WT$'2011' <- NULL
+WT$'2012' <- NULL
+WT$'2013' <- NULL
+WT$row.names <- NULL
+
+# Create 
+WT[, 3] <- round(log(WT[, 3]), digits = 2)
+```
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+library(googleVis)
+
+# Plot
+WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
+                      colorvar = 'mean',
+                      options = list(
+                        colors = "['#ece7f2', '#2b8cbe']"
+))
+
+```
+
 Starting with this explanatory variable, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).
@@
 
+-------------------------
+
 Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the dependent variables we selected as indicators of the entrepreneurship rate.
 Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant and has a negative relationship with our explanatory variables.
+This relationship can be seen in the following regression output table.
 

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-### What we intend to do
+***Quantitative Analysis of the Impact of Education on Entrepreneurship***
 
-**Quantitative Analysis of the Impact of Education on Entrepreneurship**
+**Research Design**
 
-*Research Design*
+At this stage, having explained how determinants of entrepreneurship have been looked into, having mentioned how education has been related to entrepreneurship so far, we need to assert here our very research question which is:
 
-At this stage, having explained how determinants of entrepreneurship have been looked into, having mentioned how education has been related to entrepreneurship so far, we need to assert here our very research design.
-What we expect to find out is to what extent the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries.
+To what extent does the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries?
 
@@
 The support of students' self-confidence within education systems as we just defined it can also affect the students' entrepreneurial self-efficacy, that should be controled for.
-To do so, we will look at average perceived entrepreneurial capabilities and fear of failure in starting a business across the population at the country-level.
+To do so, we will look at the average perceived entrepreneurial capabilities and fear of failure in starting a business across the population at the country-level.
 
@@
 
-The lack of suitable data as well as the fact that OECD PISA tends to focus on different aspects of education systems for every triennal survey, lead us to give up on this for the time being.
+The lack of suitable data as well as the fact that OECD PISA (Programme for International Student Assessment) tends to focus on different aspects of education systems for every triennal survey, lead us to give up on this for the time being.
 But we still think that should be included in a future research on that topic.

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 
-..........(Describe why we use the rate of entrepreneurship indicators we chose)
-
 Data on our explanatory variable, Way of Teaching, is available on the GEM website for the years 2001-2010.
@@
 
-Starting with this explanatory variable, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).
+Starting with this explanatory variable, as mentioned earlier, we expected to observe different effects depending on the kind of entrepreneurship we looked at:
+
+1 Entrepreneurial Intentions
+
+2 Nascent Entrepreneurship
+
+3 Established Entrepreneurship
+
+Therefore, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).
 These three regression equations are as follows:

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Added tables and regression sims

@@
 
+image: ![Way of Teaching](https://raw.githubusercontent.com/SamDund/Assign2Education/master/PresentationandPaper/images/WoTmap.png)
+
 Starting with this explanatory variable, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).
@@
 Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the dependent variables we selected as indicators of the entrepreneurship rate.
-Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant and has a negative relationship with our explanatory variables.
+Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant when using "Nascent Entrepreur" or "Business Owner" as a dependent variable, has a negative coefficient in these regression equations.
 This relationship can be seen in the following regression output table.
-
-Overall, however, if we omit country-specific effects, we can demonstrate that the Way of Teaching and the Percent Perceived Good Opportunities are statistically significant in the model indicated below.
-
-<br>
-
-$NationalLevelAveragePercentOwningaBusiness = -6.82 + 1.03WayofTeaching + 0.10Percent Perceived Capability +$  
-$0.21Percent Fear Failure$ $+$ $0.12Percent Perceived Opportunities - 0.005Percent Fear Failure$ $*$ $Percent Perceived Opportunities$
-
-<br>
-
-We can show the relationship between the dependent and explanatory variables in the four simulations below.
-The R package Zelig allows us to set parameters for an explanatory variable and simulate 1000 trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).
-We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.
-A regression output table has also been included below.
-
-The simulations labeled "Unimputed" were created using only data collected from GEM.
-This simulation is not possible with missing data, so observations with missing data were omitted.
-In an attempt to increase the accuracy of this model, we used the R program Amelia to generate an imputed data frame.
-This program uses statistical inference to generate this data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).
-Simulations titled "Imputed" were calculated using this imputed data frame.
+This regression output was generated using a simple least square regression model.
 
@@
 ############ Running a regression with full df (including omitted variables)
-RG1 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
+RG1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
 
-RG2 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+RG2 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+
+RG3 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+```
+
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
+
+# Create vector of lables
+labels_1 <- c('Way of Teaching', 'Perceived Capabilities', 'Fear of Failure', 'Perceived Good Opportunities', 
+             'Fear of Failure x Perceived Good Opportunities')
+
+dlabels_1 <- c('Entrepreneurial Intention', 'Nascent Entrepreneur', 'Entrepreneurship Owner')
+
+# Regression output table with country-specific effects
+stargazer::stargazer(RG1, RG2, RG3,
+                     title = 'Linear Regression Estimates with Country-specific Effects',
+                     covariate.labels = labels_1, dep.var.labels = dlabels_1, digits = 2,
+                     font.size =  "scriptsize", type = 'latex', no.space = TRUE)
+
+```
+
+To more clearly demonstrate the relationship between the "Way of Teaching" and our dependent variables, we have omitted the country-specific effects and generated simulations to show demonstrate the outcome of 1000 trials of our regression equation.
+Before doing so, however, we ran another set of regressions to determine which equation we would like to examine more closely.
+A regression output table with these results has been included below.
+
+```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
+
+# Run three regression equations again (omitting country-specific effects)
+RG4 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
+
+RG5 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
+
+RG6 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
+
+```
+
+<br>
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
+
+# Regression output table with country-specific effects
+stargazer::stargazer(RG4, RG5, RG6,
+                     title = 'Linear Regression Estimates omitting Country-specific Effects',
+                     covariate.labels = labels_1, dep.var.labels = dlabels_1, digits = 2,
+                     font.size =  "scriptsize", type = 'latex', no.space = TRUE)
+
+```
+
+Given the positive relationship between the "Way of Teaching" and "Entrepreneurship Owner" we decided to use this equation for our simulations.
+Given the prevelence of omitted data in our data frame, we decided to attempt to increase the accuracy of this model by using the R program Amelia to generate an imputed data frame.
+This program uses statistical inference to generate imputed data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).
+Equation  titled "Imputed" were calculated using this imputed data frame.
+
+To generate the simulations, we decided to use the R package Zelig.
+This package allows us to set parameters for an explanatory variable and simulate trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).
+We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.
+A regression output table and our simulation results are included below.
+Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables."
+
+```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
 
@@
 ```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
+
+# Set new vector for dependent variable label
+dlabels_2 <- c('Entrepreneurship Owner')
+
+# Regression output table with country-specific effects
+stargazer::stargazer(Z1, Z2,
+                     title = 'Linear Regression Estimates omitting Country-specific Effects',
+                     covariate.labels = labels_1, dep.var.labels = dlabels_2, digits = 2,
+                     font.size =  "small", type = 'latex', no.space = TRUE,
+                     notes = "Regression equation 1 is unimputed, regression equation 2 is imputed")
+```
+
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
 library("Zelig")
@@
 ```
-
-```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
-library(stargazer)
-
-# Create regression output table
-labels <- c('Way of Teaching', 'National Level Perceived Capabilities', 'National Level Avg Fear of Failure',
-            'National Level Avg Perceived Good Opportunities', 
-            'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities',
-            '(Intercept)')
-
-dlabels <- c('National Level Average Percent Owning a Business')
-
-```
-
-<br>
-
-```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
-
-stargazer::stargazer(Z1, Z2,
-                     title = 'Linear Regression Estimates', notes = "Regression equation 1 is unimputed, regression equation 2 is imputed", digits = 2, type = 'latex')
-
-```
-
-```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
-
-# Import df of dependent and independent variables
-CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")
-
-# Run linear regression R1
-R1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)
-
-# Run linear regression R2
-R2 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)
-
-# Run linear regression R3
-R3 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)
-
-```
-
-```{r echo = FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
-
-# Library Stargazer for regression output tables
-library(stargazer)
-
-# Create regression output table
-labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
-            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')
-
-dlables <- c('National Level Average Percent Entrepreneurial Intention', 'National Level Nascent Entrepreneural Activity', 'National Level Average Percent Owning a Business')
-
-stargazer::stargazer(R1, R2, R3, covariate.labels = labels, dep.var.labels = dlables,
-                     title = 'Linear Regression Estimates', digits = 2, type = 'html')

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

@@
 The interaction term $\beta_5FearFailure*PerceivedOpportunities$ was added to the regression because the survey question regarding "Fear of Failure" was only proposed to survey respondents who indicated they do perceive opportunities to start a business.
+
+Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the dependent variables we selected as indicators of the entrepreneurship rate.
+Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant when using "Nascent Entrepreur" or "Business Owner" as a dependent variable, has a negative coefficient in these regression equations.
+This relationship can be seen in the following regression output table.
+This regression output was generated using a simple least square regression model.
+
+```{r echo = FALSE, cache= FALSE, include= FALSE}
+
+# Library Zelig (can be buggy if loaded too early)
+library(Zelig)
+
+# Library Amelia for imputed data
+library(Amelia)
+
+# Import df of dependent and independent variables
+CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")
+
+############ Running a regression with full df (including omitted variables)
+RG1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+
+RG2 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+
+RG3 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+```
+
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
+
+# Create vector of lables
+labels_1 <- c('Way of Teaching', 'Perceived Capabilities', 'Fear of Failure', 'Perceived Good Opportunities', 
+             'Fear of Failure x Perceived Good Opportunities')
+
+dlabels_1 <- c('Entrepreneurial Intention', 'Nascent Entrepreneur', 'Entrepreneurship Owner')
+
+# Regression output table with country-specific effects
+stargazer::stargazer(RG1, RG2, RG3,
+                     title = 'Linear Regression Estimates with Country-specific Effects',
+                     covariate.labels = labels_1, dep.var.labels = dlabels_1, digits = 2,
+                     font.size =  "scriptsize", type = 'latex', no.space = TRUE)
+
+```
+
+To more clearly demonstrate the relationship between the "Way of Teaching" and our dependent variables, we have omitted the country-specific effects and generated simulations to show demonstrate the outcome of 1000 trials of our regression equation.
+Before doing so, however, we ran another set of regressions to determine which equation we would like to examine more closely.
+A regression output table with these results has been included below.
+
+```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
+
+# Run three regression equations again (omitting country-specific effects)
+RG4 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
+
+RG5 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
+
+RG6 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
+
+```
+
+<br>
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
+
+# Regression output table with country-specific effects
+stargazer::stargazer(RG4, RG5, RG6,
+                     title = 'Linear Regression Estimates omitting Country-specific Effects',
+                     covariate.labels = labels_1, dep.var.labels = dlabels_1, digits = 2,
+                     font.size =  "scriptsize", type = 'latex', no.space = TRUE)
+
+```
+
+Given the positive relationship between the "Way of Teaching" and "Entrepreneurship Owner" we decided to use this equation for our simulations.
+Given the prevelence of omitted data in our data frame, we decided to attempt to increase the accuracy of this model by using the R program Amelia to generate an imputed data frame.
+This program uses statistical inference to generate imputed data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).
+Equation  titled "Imputed" were calculated using this imputed data frame.
+
+To generate the simulations, we decided to use the R package Zelig.
+This package allows us to set parameters for an explanatory variable and simulate trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).
+We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.
+A regression output table and our simulation results are included below.
+Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables."
+
+```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
+
+############ Running a regression omitting omitted variables
+
+# Generate a df omitting omitted variables
+CD_omitted <- na.omit(CD)
+
+# Run a least squares regression with Zelig
+Z1 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")
+
+############ Runnig a Zelig regression with imputed data and omitting remaining omitted variables
+
+# Import csv of df with imputed figures (created in Index_sources/Amelia_source)
+CI <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/gh-pages/GEMData/Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)
+
+# Omit variables that could not be imputed by Adelia (b/c of lack of data)
+CI_omitted <- na.omit(CI)
+
+# Regression equation with imputed values
+Z2 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")
+
+############ Set range of values for Z1 and Z2 using imputed and not imputed dfs
+
+####### Simulate Percent Perceived
+
+# Set range of PercentPerceived values in simulation (NOT IMPUTED)
+x.out1 <- setx(Z1, PercentPerceived = 9:67)
+
+# Run simulation (default 1000 trials) (NOT IMPUTED)
+simz1 <- sim(Z1, x = x.out1)
+
+# Set range of PercentPerceived values in siumlation (IMPUTED)
+x.out2 <- setx(Z2, PercentPerceived = 9:67)
+
+# Run simulation (default 1000 trials) (IMPUTED)
+simz2 <- sim(Z2, x = x.out2)
+
+####### Simulate Way of Teaching
+
+# Set range of WayofTeaching values in simulation (NOT IMPUTED)
+x.out3 <- setx(Z1, WayofTeaching = 1.353:3.278)
+
+# Run simulation (default 1000 trials) (NOT IMPUTED)
+simz3 <- sim(Z1, x = x.out3)
+
+# Set range of WayofTeaching values in simulation (IMPUTED)
+x.out4 <- setx(Z2, WayofTeaching = 1.128:3.312)
+
+# Run simulation (default 1000 trials) (IMPUTED)
+simz4 <- sim(Z2, x = x.out4)
+
+```
+
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
+
+# Set new vector for dependent variable label
+dlabels_2 <- c('Entrepreneurship Owner')
+
+# Regression output table with country-specific effects
+stargazer::stargazer(Z1, Z2,
+                     title = 'Linear Regression Estimates omitting Country-specific Effects',
+                     covariate.labels = labels_1, dep.var.labels = dlabels_2, digits = 2,
+                     font.size =  "small", type = 'latex', no.space = TRUE,
+                     notes = "Regression equation 1 is unimputed, regression equation 2 is imputed")
+```
+
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
+library("Zelig")
+
+# Set layout
+par(mfrow = c(2, 2))
+
+# Plot simz1 (unimputed)
+plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
+     main = "Unimputed (Equation 1)")
+
+# Plot simz2 (imputed)
+plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
+     main = "Imputed (Equation 2)")
+
+# Plot simz3 (unimputed)
+plot(simz3, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner',
+     main = "Unimputed (Equation 1)")
+
+# Plot simz4 (imputed)
+plot(simz4, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner',
+     main = "Imputed (Equation 2)")
+
+```
+
+**Results**
+
+**Limitations of the data**
+
+From the results and from the description of the data made earlier, one can easily foresee quite a few limitations to the consistency and effectiveness of the data we used for this research.
+Although they are obvious, one should still name them here.
+
+The GEM National Expert Survey however interesting and innovative for its extensive look into new sorts of data still allows for much improvement.
+It is essentially supposed to help control for the environmental determinants of entrepreneurship, which are here called the framework conditions.
+The major issue is not so much what it aims at revealing of the entrepreneurial context of each country but it has much more to do with methodology of data collection.
+Indeed, for each of these framework conditions, only four experts answered the survey, which makes the measure be very dependent on the individual respondent.
+This leads to highly variant data.
+
+Regarding the D01 indicator we used as a proxy for a way of teaching supportive of students' self-confidence, it is quite variant from year to year, which is not quite what we would expect.
+Indeed, as we look at the way of teaching and education features, these are generally

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Updated formatting

@@
 output: pdf_document
+linestretch: 1.5
+
 ---
@@
 
-The process of importing, cleaning, and analyzing all of the data used in this project is fully documented and reproducable by referencing our GitHub repository.
+Additional information on the GEM data used for this research can be seen in the descriptive statistics table included below.
+
+```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis', warning=FALSE}
+
+# Import df of dependent and independent variables
+CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")
+
+CD1 <- CD
+
+# Remove uncessesary column
+CD1$X <- NULL
+
+# Set Year as factor
+CD1[,"Year"] <- as.factor(CD1[,"Year"])
+
+# Rename column
+names(CD) <- gsub("PercentPerceived", "PerceivedCapability", names(CD))
+names(CD1) <- gsub("PercentPerceived", "PerceivedCapability", names(CD1))
+
+```
+
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis', warning=FALSE}
+
+# Generate descriptive statistics table
+stargazer(CD1, type = "latex")
+```
 
@@
 # Create a histogram showing the distribution of Way of Teaching
-qplot(WayofTeaching, data = wot, geom = "histogram", binwidth = .10)
+Q <- qplot(WayofTeaching, data = wot, geom = "histogram", binwidth = .05)
 
+Q + theme_bw()
 ```
@@
 
-# Import df of dependent and independent variables
-CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")
+############ Running a regression with full df (including omitted variables)
+RG1 <- lm(PercentIntention ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
 
-############ Running a regression with full df (including omitted variables)
-RG1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+RG2 <- lm(PercentNascent ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
 
-RG2 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
-
-RG3 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+RG3 <- lm(PercentOwner ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
 ```
@@
 # Run three regression equations again (omitting country-specific effects)
-RG4 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
+RG4 <- lm(PercentIntention ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
 
-RG5 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
+RG5 <- lm(PercentNascent ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
 
-RG6 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
+RG6 <- lm(PercentOwner ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
 
@@
 Given the positive relationship between the "Way of Teaching" and "Entrepreneurship Owner" we decided to use this equation for our simulations.
-Given the prevelence of omitted data in our data frame, we decided to attempt to increase the accuracy of this model by using the R program Amelia to generate an imputed data frame.
+In an effort to address data availability issues, we also decided to run a second model including imputed data generated by the R program Amelia to generate an imputed data frame.
 This program uses statistical inference to generate imputed data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).
@@
 This package allows us to set parameters for an explanatory variable and simulate trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).
-We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.
-A regression output table and our simulation results are included below.
-Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables."
+We chose to simulate values in our explanatory variable "Way of Teaching" and "Perceived Capabilities" for this analysis.
+One important aspect of the Zelig package is that observations with omitted variables will be omitted from the calculation.
+For this reason, there is some variation between the coefficients for the Zelig model and the model in the preceeding regression output chart.
+
+Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables." A regression output table and our simulation results are included below.
 
@@
 # Run a least squares regression with Zelig
-Z1 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")
+Z1 <- zelig(PercentOwner ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")
 
@@
 
+names(CI_omitted) <- gsub("PercentPerceived", "PerceivedCapability", names(CI_omitted))
+
 # Regression equation with imputed values
-Z2 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")
+Z2 <- zelig(PercentOwner ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")
 
@@
 
-# Set range of PercentPerceived values in simulation (NOT IMPUTED)
-x.out1 <- setx(Z1, PercentPerceived = 9:67)
+# Set range of PerceivedCapabilities values in simulation (NOT IMPUTED)
+x.out1 <- setx(Z1, PerceivedCapability = 9:67)
 
@@
 
-# Set range of PercentPerceived values in siumlation (IMPUTED)
-x.out2 <- setx(Z2, PercentPerceived = 9:67)
+# Set range of PerceivedCapability values in siumlation (IMPUTED)
+x.out2 <- setx(Z2, PerceivedCapability = 9:67)
 
@@
 stargazer::stargazer(Z1, Z2,
-                     title = 'Linear Regression Estimates omitting Country-specific Effects',
+                     title = 'Least Squares Regression for Continuous Dependent Variables',
                      covariate.labels = labels_1, dep.var.labels = dlabels_2, digits = 2,
-                     font.size =  "small", type = 'latex', no.space = TRUE,
+                     font.size =  "scriptsize", type = 'latex', no.space = TRUE,
                      notes = "Regression equation 1 is unimputed, regression equation 2 is imputed")
@@
 
-# Plot simz1 (unimputed)
-plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
-     main = "Unimputed (Equation 1)")
-
-# Plot simz2 (imputed)
-plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
-     main = "Imputed (Equation 2)")
-
 # Plot simz3 (unimputed)
@@
 
+# Plot simz1 (unimputed)
+plot(simz1, xlab = 'Percent Perceived Capabilities', ylab = 'Percent Entrepreneurship Owner',
+     main = "Unimputed (Equation 1)")
+
+# Plot simz2 (imputed)
+plot(simz2, xlab = 'Percent Perceived Capabilities', ylab = 'Percent Entrepreneurship Owner',
+     main = "Imputed (Equation 2)")
+
 ```
+
+As we can see from the regression output table, using the Amelia program to generate additional data expanded the observations analyzed from 172 to 318, and increased the statistical significance of our explantory variable.
+In addition, the positive slope of this equation is consistent with what we expected after our analysis of existing literature on this topic.
+In addition, this process reduced the variance in our simulation results, suggesting it improved the accuracy of this model.
+Despite this, we have several concerns regarding the reliability of existing GEM data (which will be discussed later in this paper), which makes us question the effectiveness of using this data to generate additional observations.
+
+Perceived opportunities
+
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+
+# Library required packages
+library(googleVis)
+library(countrycode)
+library(repmis)
+library("ggplot2")
+library("reshape2")
+
+# Import GEM data frame
+PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE, na.strings = "-")
+
+## Add country codes and place new column at beginning of the data frame
+# Create a vector of country codes
+D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")
+
+# Create a new column and insert the country code vector
+PerceivedOpportunities$new.col <- D2
+
+# Reorder columns so country code is first
+D3 <- PerceivedOpportunities[,c(15,1:14)]
+
+# Rename first column
+D4 <- plyr::rename(x = D3, 
+                   replace = c("new.col" = "iso2c"))
+
+# Remove X's in D4 year columns
+names(D4) <- gsub("X", "", names(D4))
+
+# Set columns as numeric
+D4[,"2001"] <- as.numeric(D4[,"2001"])
+D4[,"2002"] <- as.numeric(D4[,"2002"])
+D4[,"2003"] <- as.numeric(D4[,"2003"])
+D4[,"2004"] <- as.numeric(D4[,"2004"])
+D4[,"2005"] <- as.numeric(D4[,"2005"])
+D4[,"2006"] <- as.numeric(D4[,"2006"])
+D4[,"2007"] <- as.numeric(D4[,"2007"])
+D4[,"2008"] <- as.numeric(D4[,"2008"])
+D4[,"2009"] <- as.numeric(D4[,"2009"])
+D4[,"2010"] <- as.numeric(D4[,"2010"])
+D4[,"2011"] <- as.numeric(D4[,"2011"])
+D4[,"2012"] <- as.numeric(D4[,"2012"])
+D4[,"2013"] <- as.numeric(D4[,"2013"])
+
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
+
+# Subset Opp2
+Opp2 <- subset(D4, iso2c %in% myvars2)
+
+# Melt Opp2 df
+Opp3 <- melt(data = Opp2,
+                  id.vars = c("Country", "iso2c"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Edit column names
+names(Opp3) <- gsub("value", "PerceivedOpportunities", names(Opp3))
+names(Opp3) <- gsub("variable", "Year", names(Opp3))
+
+Opp3$iso2c <- NULL
+```
+
+```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+# Create plot
+G1 <- ggplot(Opp3,aes(x = Year, y = PerceivedOpportunities, colour = Country, group = Country)) + geom_line()
+
+G1 + ggtitle("Perceived Opportunities Over Time") + theme_bw()
+```

### 2014-12-12 PresentationandPaper/Draft1.Rmd
Added Latex to set single spacing in tables

@@
 
+\begin{singlespace}
 ```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis', warning=FALSE}
@@
 ```
+\end{singlespace}
 
@@
 X4 Control Variable | Perceived Opportunities
-
-..........(Describe why we use the rate of entrepreneurship indicators we chose)
 
@@
 Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant when using "Nascent Entrepreur" or "Business Owner" as a dependent variable, has a negative coefficient in these regression equations.
-This relationship can be seen in the following regression output table.
+This relationship can be seen in table 4 below.
 This regression output was generated using a simple least square regression model.
@@
 
+\begin{singlespace}
 ```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
@@
 Before doing so, however, we ran another set of regressions to determine which equation we would like to examine more closely.
-A regression output table with these results has been included below.
+The results can be seen in table 5 below.
 
@@
 
-<br>
+\begin{singlespace}
 ```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
@@
                      covariate.labels = labels_1, dep.var.labels = dlabels_2, digits = 2,
-                     font.size =  "scriptsize", type = 'latex', no.space = TRUE,
+                     font.size =  "small", type = 'latex', no.space = TRUE,
                      notes = "Regression equation 1 is unimputed, regression equation 2 is imputed")
 ```
+\end{singlespace}
 

### 2014-12-12 index.Rmd
Revised charts and removed content included in paper

@@
 CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")
+
+names(CD) <- gsub("PercentPerceived", "PerceivedCapability", names(CD))
 
@@
   layer_points(fill = ~factor(Country)) %>%
-  group_by(Country) %>%
-  layer_model_predictions(model = "lm")
+  group_by(Country)
 ```
@@
 CD_subset2$PercentNascent <- NULL
-CD_subset2$PercentPerceived <- NULL
+CD_subset2$PercentOpportunity <- NULL
 CD_subset2$PercentIntention <- NULL
@@
 
+names(CD_subset2) <- gsub("PercentPerceived", "PerceivedCapability", names(CD_subset2))
+
 # Create plot of PercentOpp and PercentOwner
 CD_subset2 %>% 
-  ggvis(x = ~PercentOpportunities, y = ~PercentOwner) %>% 
+  ggvis(x = ~PerceivedCapability, y = ~PercentOwner) %>% 
   layer_points(fill = ~factor(Country)) %>%
-  group_by(Country) %>%
-  layer_model_predictions(model = "lm")
+  group_by(Country)
 
 ```
-
-(Take this for the paper)
-
-Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the  dependent variables we selected as indicators of the entrepreneurship rate.
-Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant and has a negative relationship with our explanatory variables.
-
-Overall, however, if we omit country-specific effects, we can demonstrate that the Way of Teaching and the Percent Perceived Good Opportunities are statistically significant in the model indicated below.
-
-<br>
-
-$NationalLevelAveragePercentOwningaBusiness = -6.82 + 1.03WayofTeaching + 0.10Percent Perceived Capability +$  
-$0.21Percent Fear Failure$ $+$ $0.12Percent Perceived Opportunities - 0.005Percent Fear Failure$ $*$ $Percent Perceived Opportunities$
-
-<br>
-
-We can show the relationship between the dependent and explanatory variables in the four simulations below.
-The R package Zelig allows us to set parameters for an explanatory variable and simulate 1000 trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).
-We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.
-A regression output table has also been included below.
-
-The simulations labeled "Unimputed" were created using only data collected from GEM.
-This simulation is not possible with missing data, so observations with missing data were omitted.
-In an attempt to increase the accuracy of this model, we used the R program Amelia to generate an imputed data frame.
-This program uses statistical inference to generate this data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).
-Simulations titled "Imputed" were calculated using this imputed data frame.
-
-```{r echo = FALSE, cache= FALSE, include= FALSE}
-
-# Library Zelig (can be buggy if loaded too early)
-library(Zelig)
-
-# Library Amelia for imputed data
-library(Amelia)
-
-############ Running a regression with full df (including omitted variables)
-RG1 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
-
-RG2 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
-
-############ Running a regression omitting omitted variables
-
-# Generate a df omitting omitted variables
-CD_omitted <- na.omit(CD)
-
-# Run a least squares regression with Zelig
-Z1 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD_omitted, model = "ls")
-
-############ Runnig a Zelig regression with imputed data and omitting remaining omitted variables
-
-# Import csv of df with imputed figures (created in Index_sources/Amelia_source)
-CI <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/gh-pages/GEMData/Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)
-
-# Omit variables that could not be imputed by Adelia (b/c of lack of data)
-CI_omitted <- na.omit(CI)
-
-# Regression equation with imputed values
-Z2 <- zelig(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CI_omitted, model = "ls")
-
-############ Set range of values for Z1 and Z2 using imputed and not imputed dfs
-
-####### Simulate Percent Perceived
-
-# Set range of PercentPerceived values in simulation (NOT IMPUTED)
-x.out1 <- setx(Z1, PercentPerceived = 9:67)
-
-# Run simulation (default 1000 trials) (NOT IMPUTED)
-simz1 <- sim(Z1, x = x.out1)
-
-# Set range of PercentPerceived values in siumlation (IMPUTED)
-x.out2 <- setx(Z2, PercentPerceived = 9:67)
-
-# Run simulation (default 1000 trials) (IMPUTED)
-simz2 <- sim(Z2, x = x.out2)
-
-####### Simulate Way of Teaching
-
-# Set range of WayofTeaching values in simulation (NOT IMPUTED)
-x.out3 <- setx(Z1, WayofTeaching = 1.353:3.278)
-
-# Run simulation (default 1000 trials) (NOT IMPUTED)
-simz3 <- sim(Z1, x = x.out3)
-
-# Set range of WayofTeaching values in simulation (IMPUTED)
-x.out4 <- setx(Z2, WayofTeaching = 1.128:3.312)
-
-# Run simulation (default 1000 trials) (IMPUTED)
-simz4 <- sim(Z2, x = x.out4)
-
-```
-
-```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
-library("Zelig")
-
-# Set layout
-par(mfrow = c(2, 2))
-
-# Plot simz1 (unimputed)
-plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
-     main = "Unimputed (Equation 1)")
-
-# Plot simz2 (imputed)
-plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
-     main = "Imputed (Equation 2)")
-
-# Plot simz3 (unimputed)
-plot(simz3, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner',
-     main = "Unimputed (Equation 1)")
-
-# Plot simz4 (imputed)
-plot(simz4, xlab = 'Way of Teaching', ylab = 'Percent Entrepreneurship Owner',
-     main = "Imputed (Equation 2)")
-
-```
-
-```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
-library(stargazer)
-
-# Create regression output table
-labels <- c('Way of Teaching', 'National Level Perceived Capabilities', 'National Level Avg Fear of Failure',
-            'National Level Avg Perceived Good Opportunities', 
-            'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities',
-            '(Intercept)')
-
-dlabels <- c('National Level Average Percent Owning a Business')
-
-```
-
-<br>
-
-```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
-
-stargazer::stargazer(Z1, Z2, covariate.labels = labels, dep.var.labels = dlabels,
-                     title = 'Linear Regression Estimates', notes = "Regression equation 1 is unimputed, regression equation 2 is imputed", digits = 2, type = 'html')
-
-```
-
-<br>
 

### 2014-12-12 index.Rmd
Theme attempt

@@
 output: html_document
+theme: Cosmo
 ---
@@
 This will need to be addressed for future projects.
+
+### More information
+
+For more information about our project, including an academic paper on the topic, please see our [GitHub repository](https://github.com/SamDund/Assign2Education)

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Conclusion

@@
 This leads to highly variant data.
+Besides, the national teams hired by GEM Coordination Team were reported by GEM itself to manage time allocated for data collection rather poorly.
+That is, while they had five months at their disposal to approach and survey four experts for each framework condition, they happened on a regular basis to be in a hurry in July and therefore ended up relying on their personal connections to answer the surveys.
 
-Regarding the D01 indicator we used as a proxy for a way of teaching supportive of students' self-confidence, it is quite variant from year to year, which is not quite what we would expect.
-Indeed, as we look at the way of teaching and education features, these are generally
+Regarding the D01 indicator that we used as a proxy for a way of teaching supportive of students' self-confidence, it is quite variant from year to year, which is not quite what we would expect.
+Indeed, as we look at the way of teaching and education features, these are generally culture related and as such should be much less fluctuant.
+At most, they should vary due to reforms being implemented at national, federal or state level, but that does not take place every year, rather every four or five years, sometimes only once a decade or even less frequently.
+Thus this yearly change is very unlikely to be a faithful figuration of how supportive of students' self-confidence teaching is like in a given country.
+On top of that, we purposely selected one item among the six used to characterised potential entrepreneurial education.
+That one item cannot be compensated by others in our study, which probably worsened the effect.
+The scale between 0 and 5 makes the assessment even more approximate.
+As a result of all these flaws combined leads to some variations of up to 1 point for some countries, like for Denmark for instance.
+
+Now looking at GEM Adult Population Survey (APS), even if the data is directly collected by GEM from representatives samples of the population (around 2000 peole), once again we observe huge variation for indicators such as the perceived opportunities, which are unlikely to fluctuate that much in reality.
+That very indicator was used as a proxy for many potential control variables regarding economic outlook and other environmental determinants of entrepreneurship, and we do not expect the level of financing, the level of public programmes or the GDP growth for instance to vary that much from year to year.
+The subjective perception this indicator entails should have been compensated by the representativity of the sample and thus should not show so much variance.
+Once more, even if we are very doubtful about that data.
+
+Last but not least is the scarcity of the data.
+For the perceived capabilities, perceived opportunities and fear of failure, there are already a few missing data but this gets much worse regarding the way of teaching.
+For that key explanatory variable, many countries have only data for have the years we were looking into, those who had the most data were at least missing three years, and three countries (Estonia, Luxembourg and Slovak Republic) had no data available at all.
+
+Adding up all these limitations of the data we used, it does not come as a surprise that we could hardly get significant coefficients and could only observe general trends.
+
+**Conclusion**
+
+Education systems tend to be assessed in terms of numbers of students, ratios of teachers among other quantitative measures but what we tried to suggest here is that they could be looked at in quite a different way.
+As governments allocate public funds for education, they happen to make a long term investment, and, although this may not come as news, we intended here to propose a different rationale in doing so.
+Without denying the importance of all the classic determinants of entrepreneurship, we suggest that education systems could turn out to be one of those determinants that favour start up activites.
+
+From the research we attempted to conduct here, due to poor quality and inconsistent data, we cannot ascertain our point but we still firmly believe there could be something happening out there and this should be looked into more.
+Now that would mean collecting the adequate amount of data and computing a new kind of indicators that are not yet available.
+This surely is a prospect for future research.

### 2014-12-12 index.Rmd
Theme deleted
Minor edits

--- 2014-12-12 index.Rmd
@@
 
-2. Higher degree of individual self-esteem
+2. Higher degree of individual self-confidence
 
@@
 
-We have included our findings in a detailed paper available here.
+We have included our findings in a detailed paper available [here](https://github.com/SamDund/Assign2Education/tree/master/PresentationandPaper).
 In sum, however, the most statistically significant and important findings from our analysis are that there is some evidence of a postitive relationship between higher levels of self-confidence reinforcement in teaching (a higher "WayofTeaching" score) and the rate of people owning their own business.

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Spellcheck and minor edits

--- 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
@@
 author: "Sam Dundon and Thierry Racaud"
-date: "10 december 2014"
+date: "10 December 2014"
 linestretch: 2 
@@
 ---
-
-* * *
 
@@
 
-*Introduction to Collaborative Social Science Data Analysis*
-
-(The impact of self confidence on entrepreneurship.)
-
 ### Abstract
 
-### Why we chose to look into Education to explain Entrepreneurship - What has been done
+### Why we Chose to Look into Education to Explain Entrepreneurship - What Has Been Done
 
-Whilst it is tempting to look at education systems in a very pragmatic way with ratios of teachers per student, or number of students per class, we suggest to use another kind of indicators in order to trace the potential long-term investment made by governments.
+Whilst it is tempting to look at education systems in a very pragmatic way with ratios of teachers per student, or number of students per class, we suggest to use another kind of indicator in order to trace the potential long-term investment made by governments.
 Indeed, we believe that education systems can favour entrepreneurship and, beyond, GDP growth at the country-level, depending on how supportive of students' self-confidence and how socially inclusive they are.
-We see this process as manyfold but will only focus here on one of the potential causal relations.
+We see this process as many-fold but will only focus here on one of the potential causal relations.
 We want to understand specifically to want extent the support of individual self-confidence within education systems can affect the likelihood to become an entrepreneur, and thus impact the rate of entrepreneurship at the country level.
 
-In trying to explore what supports entrepreneurship at the country-level, one should start by refering to what research asserted for that matter.
-For this purpose, we refer here to the OECD reports available online here http://www.oecd.org/std/business-stats/48129925.pdf.
-Two main sorts of determinants or favourable conditions have been looked into, that is environmental factors and individual factors.
-Although we intend to focus more on individual factors, we
-want to mention here the environmental factors as they should be controled for. They actually divide into six broad categories:
+In trying to explore what supports entrepreneurship at the country-level, one should start by referring to what research asserted for that matter.
+For this purpose, we refer here to the Organisation for Economic Co-Operation and Development (OECD) list of indicator for entrepreneurial determinants available [here](http://www.oecd.org/std/business-stats/48129925.pdf).
+Two main sorts of determinants or favourable conditions, environmental factors and individual factors, have been identified and researched.
+Although we intend to focus more on individual factors, we want to mention here the environmental factors as they should be controlled for in our analysis.
+They have been divided into six broad categories by the OECD:
 
-**The regulatory framework**, which includes administrative burdens, regulations and frameworks, as well as fiscal policy parameters.
+**The regulatory framework**: Including administrative burdens, regulations and frameworks, as well as fiscal policy parameters.
 
-**The market conditions**, which include anti-trust laws, rules for competition, access to foreign markets, degree of public involvement and level of private demand.
+**The market conditions**: Including anti-trust laws, rules for competition, access to foreign markets, the degree of public involvement and level of private demand.
 
-**The access to finance**, which includes access to debt financing, access to venture capital, and stock markets.
+**The access to finance**: Including access to debt financing, access to venture capital, and stock markets.
 
-**The creation and diffusion of knowledge**, which include research and development activity, transfer of non-commercial knowledge, co-operation among firms, technology availability and take-up.
+**The creation and diffusion of knowledge**: Including research and development activity, the transfer of non-commercial knowledge, co-operation among firms, technology availability, and take-up.
 
-**The entrepreneurial capabilities**, which includes business and entrepreneurship education as well as immigration.
+**The entrepreneurial capabilities**: Including business and entrepreneurship education as well as immigration.
 
@@
 By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur.
-Here, the variable "perceived capabilites" has to be understood in a narrow sense, it refers only to the perceived capabilities to start a business.
+Here, the variable "perceived capabilities" has to be understood in a narrow sense, it refers only to the perceived capabilities to start a business.
 Seemingly the variable "fear of failure" only refers to the fear of failure as an obstacle in starting a business, despite the perceived good opportunities.
@@
 Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement.
-Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is much more rarely activitated in France, and only on an voluntary individual teacher's basis.
+Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is much more rarely activated in France, and only on an voluntary individual teacher's basis.
 
@@
 .
-One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions with students, can increase the rate of youth entrepreneurship but their perspective was still not directly in lign with our research design, they  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
+One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions with students, can increase the rate of youth entrepreneurship but their perspective was still not directly in line with our research design, they  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
 
@@
 
-The support of students' self-confidence within education systems as we just defined it can also affect the students' entrepreneurial self-efficacy, that should be controled for.
+The support of students' self-confidence within education systems as we just defined it can also affect the students' entrepreneurial self-efficacy, that should be controlled for.
 To do so, we will look at the average perceived entrepreneurial capabilities and fear of failure in starting a business across the population at the country-level.
@@
 
-The lack of suitable data as well as the fact that OECD PISA (Programme for International Student Assessment) tends to focus on different aspects of education systems for every triennal survey, lead us to give up on this for the time being.
+The lack of suitable data as well as the fact that OECD PISA (Programme for International Student Assessment) tends to focus on different aspects of education systems for every triennial survey, lead us to give up on this for the time being.
 But we still think that should be included in a future research on that topic.
@@
 Even in measuring the impact on activities, we could potentially observe different effects between nascent and established entrepreneurship.
-Therefore, we will consider the three measures of entrepreneursip separately:
+Therefore, we will consider the three measures of entrepreneurship separately:
 
@@
 
-To complete a quantitative analysis of the impact of educational factors -- specifically the encouragement of creatitivity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship, we have drawn on publicly available data from the Global Entrepreneurship Monitor (GEM) National Expert Survey (NES) and Adult Population Survey (APS).
+To complete a quantitative analysis of the impact of educational factors -- specifically the encouragement of creativity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship, we have drawn on publicly available data from the Global Entrepreneurship Monitor (GEM) National Expert Survey (NES) and Adult Population Survey (APS).
 
@@
 
-The NES is structured around nine entrepreneurial framework contitions evaluated by thirty-six experts in each surveyed country.
+The NES is structured around nine entrepreneurial framework conditions evaluated by thirty-six experts in each surveyed country.
 These nine entrepreneurial framework conditions are included below (a minimum of four experts must be interviewed on each of the framework conditions).
@@
 
-The APS is a questionnaire distrubuted to a minimum of 2,000 adults in each participating country.
+The APS is a questionnaire distributed to a minimum of 2,000 adults in each participating country.
 The survey is created by a central GEM team, but the implementation is managed by national teams that compete for the role of implementing the survey.
@@
 
-The process of importing, cleaning, and analyzing all of the data used in this project is fully documented and reproducable by referencing our GitHub repository.
+Additional information on the GEM data used for this research can be seen in the descriptive statistics table included below.
+
+```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis', warning=FALSE}
+
+# Import df of dependent and independent variables
+CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")
+
+CD1 <- CD
+
+# Remove uncessesary column
+CD1$X <- NULL
+
+# Set Year as factor
+CD1[,"Year"] <- as.factor(CD1[,"Year"])
+
+# Rename column
+names(CD) <- gsub("PercentPerceived", "PerceivedCapability", names(CD))
+names(CD1) <- gsub("PercentPerceived", "PerceivedCapability", names(CD1))
+
+```
+
+\begin{singlespace}
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis', warning=FALSE}
+
+# Generate descriptive statistics table
+stargazer(CD1, type = "latex")
+```
+\end{singlespace}
 
@@
 
-To understand the impact of educational factors -- specifically the encouragement of creatitivity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship we built our model as outlined in the table below.
+To understand the impact of educational factors -- specifically the encouragement of creativity, self-sufficiency, and personal initiative  -- on the country-level rate of entrepreneurship we built our model as outlined in the table below.
 
@@
 
+Therefore, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).
+These three regression equations are as follows:
+
 Data on our explanatory variable, Way of Teaching, is available on the GEM website for the years 2001-2010.
@@
 As shown in the histogram, the largest density of scores is approximately 2.3, which lies between the "somewhat false" and "neither true or false" categories.
-This is not a whole number because the scores given by each of the 4 experts surveyed for each frameork condition are averaged to create a national-level number.
+This is not a whole number because the scores given by each of the 4 experts surveyed for each framework condition are averaged to create a national-level number.
 As discussed later in this paper, this presents some difficulties in drawing substantive conclusions from this data.
@@
 
-# Library ggplot2
-library("ggplot2")
+# Create a histogram showing the distribution of Way of Teaching
+Q <- qplot(WayofTeaching, data = wot, geom = "histogram", binwidth = .05)
 
-# Create a histogram showing the distribution of Way of Teaching
-qplot(WayofTeaching, data = wot, geom = "histogram", binwidth = .10)
+Q + theme_bw()
+```
+
+In addition to understanding the density of each recorded "Way of Teaching" indicator, it is also helpful to examine the differences in this indicator among OECD countries.
+To see this, we have created a figure showing the distribution of the average "Way of Teaching" value over the 2001-2010 period for the OECD countries included in the surveys.
+This figure is included below.
+
+```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+# Import GEM data frame
+WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")
+
+# Drop unnecessary column 1
+WayofTeaching$X <- NULL
+
+# Change data from long to wide format
+WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")
+
+# Delete variable name in Year columns
+names(WT) <- gsub("WayofTeaching.", "", names(WT))
+
+# Duplicate df for future use
+WT2 <- WT
+
+# Generate a new column with mean of all other columns
+WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
+                                          "2009", "2010")), na.rm = TRUE)
+
+# Drop year columns, leaving only mean column
+WT$'2001' <- NULL
+WT$'2002' <- NULL
+WT$'2003' <- NULL
+WT$'2004' <- NULL
+WT$'2005' <- NULL
+WT$'2006' <- NULL
+WT$'2007' <- NULL
+WT$'2008' <- NULL
+WT$'2009' <- NULL
+WT$'2010' <- NULL
+WT$'2011' <- NULL
+WT$'2012' <- NULL
+WT$'2013' <- NULL
+WT$row.names <- NULL
+
+# Create 
+WT[, 3] <- round(log(WT[, 3]), digits = 2)
+```
+
+```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
+library(googleVis)
+
+# Plot
+WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
+                      colorvar = 'mean',
+                      options = list(
+                        colors = "['#ece7f2', '#2b8cbe']"
+))
 
@@
 
-Starting with this explanatory variable, as mentioned earlier, we expected to observe different effects depending on the kind of entrepreneurship we looked at:
+image: ![Way of Teaching](https://raw.githubusercontent.com/SamDund/Assign2Education/master/PresentationandPaper/images/WoTmap.png)
 
-1 Entrepreneurial Intentions
-
-2 Nascent Entrepreneurship
-
-3 Established Entrepreneurship
-
-Therefore, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).
+Starting with this explanatory variable, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).
 These three regression equations are as follows:
@@
 
+-------------------------
+
 Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the dependent variables we selected as indicators of the entrepreneurship rate.
-Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant when using "Nascent Entrepreur" or "Business Owner" as a dependent variable, has a negative coefficient in these regression equations.
-This relationship can be seen in the following regression output table.
+Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant when using "Nascent Entrepreneur" or "Business Owner" as a dependent variable, has a negative coefficient in these regression equations.
+This relationship can be seen in table 4 below.
 This regression output was generated using a simple least square regression model.
@@
 
-# Import df of dependent and independent variables
-CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")
+############ Running a regression with full df (including omitted variables)
+RG1 <- lm(PercentIntention ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
 
-############ Running a regression with full df (including omitted variables)
-RG1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+RG2 <- lm(PercentNascent ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
 
-RG2 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
-
-RG3 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+RG3 <- lm(PercentOwner ~ WayofTeaching + PerceivedCapability + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
 ```
 
+\begin{singlespace}
 ```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
@@
 ```
+\end{singlespace}
 
 Given the positive relationship between the "Way of Teaching" and "Entrepreneurship Owner" we decided to use this equation for our simulations.
-Given the prevelence of omitted data in our data frame, we decided to attempt to increase the accuracy of this model by using the R program Amelia to generate an imputed data frame.
+In an effort to address data availability issues, we also decided to run a second model including imputed data generated by the R program Amelia to generate an imputed data frame.
 This program uses statistical inference to generate imputed data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).
@@
 This package allows us to set parameters for an explanatory variable and simulate trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).
-We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.
-A regression output table and our simulation results are included below.
-Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables."
+We chose to simulate values in our explanatory variable "Way of Teaching" and "Perceived Capabilities" for this analysis.
+One important aspect of the Zelig package is that observations with omitted variables will be omitted from the calculation.
+For this reason, there is some variation between the coefficients for the Zelig model and the model in the preceding regression output chart.
+
+Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables." A regression output table and our simulation results are included below.
 
@@
 stargazer::stargazer(Z1, Z2,
-                     title = 'Linear Regression Estimates omitting Country-specific Effects',
+                     title = 'Least Squares Regression for Continuous Dependent Variables',
                      covariate.labels = labels_1, dep.var.labels = dlabels_2, digits = 2,
@@
 par(mfrow = c(2, 2))
-
-# Plot simz1 (unimputed)
-plot(simz1, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
-     main = "Unimputed (Equation 1)")
-
-# Plot simz2 (imputed)
-plot(simz2, xlab = 'Percent Perceived Opportunities', ylab = 'Percent Entrepreneurship Owner',
-     main = "Imputed (Equation 2)")
 
@@
 
+# Plot simz1 (unimputed)
+plot(simz1, xlab = 'Percent Perceived Capabilities', ylab = 'Percent Entrepreneurship Owner',
+     main = "Unimputed (Equation 1)")
+
+# Plot simz2 (imputed)
+plot(simz2, xlab = 'Percent Perceived Capabilities', ylab = 'Percent Entrepreneurship Owner',
+     main = "Imputed (Equation 2)")
+
+```
+
+As we can see from the regression output table, using the Amelia program to generate additional data expanded the observations analyzed from 172 to 318, and increased the statistical significance of our explanatory variable.
+In addition, the positive slope of this equation is consistent with what we expected after our analysis of existing literature on this topic.
+In addition, this process reduced the variance in our simulation results, suggesting it improved the accuracy of this model.
+Despite this, we have several concerns regarding the reliability of existing GEM data (which will be discussed later in this paper), which makes us question the effectiveness of using this data to generate additional observations.
+
+Perceived opportunities
+
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}
+
+# Library required packages
+library(googleVis)
+library(countrycode)
+library(repmis)
+library("ggplot2")
+library("reshape2")
+
+# Import GEM data frame
+PerceivedOpportunities <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/PerceivedOpportunities.csv", header = TRUE, cache = FALSE, na.strings = "-")
+
+## Add country codes and place new column at beginning of the data frame
+# Create a vector of country codes
+D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")
+
+# Create a new column and insert the country code vector
+PerceivedOpportunities$new.col <- D2
+
+# Reorder columns so country code is first
+D3 <- PerceivedOpportunities[,c(15,1:14)]
+
+# Rename first column
+D4 <- plyr::rename(x = D3, 
+                   replace = c("new.col" = "iso2c"))
+
+# Remove X's in D4 year columns
+names(D4) <- gsub("X", "", names(D4))
+
+# Set columns as numeric
+D4[,"2001"] <- as.numeric(D4[,"2001"])
+D4[,"2002"] <- as.numeric(D4[,"2002"])
+D4[,"2003"] <- as.numeric(D4[,"2003"])
+D4[,"2004"] <- as.numeric(D4[,"2004"])
+D4[,"2005"] <- as.numeric(D4[,"2005"])
+D4[,"2006"] <- as.numeric(D4[,"2006"])
+D4[,"2007"] <- as.numeric(D4[,"2007"])
+D4[,"2008"] <- as.numeric(D4[,"2008"])
+D4[,"2009"] <- as.numeric(D4[,"2009"])
+D4[,"2010"] <- as.numeric(D4[,"2010"])
+D4[,"2011"] <- as.numeric(D4[,"2011"])
+D4[,"2012"] <- as.numeric(D4[,"2012"])
+D4[,"2013"] <- as.numeric(D4[,"2013"])
+
+# Create country vector to subset
+myvars2 <- c('US','FR','DE','JP','GB')
+
+# Subset Opp2
+Opp2 <- subset(D4, iso2c %in% myvars2)
+
+# Melt Opp2 df
+Opp3 <- melt(data = Opp2,
+                  id.vars = c("Country", "iso2c"),
+                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
+                                   "2007", "2008", "2009", "2010"))
+
+# Edit column names
+names(Opp3) <- gsub("value", "PerceivedOpportunities", names(Opp3))
+names(Opp3) <- gsub("variable", "Year", names(Opp3))
+
+Opp3$iso2c <- NULL
+```
+
+```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
+
+# Create plot
+G1 <- ggplot(Opp3,aes(x = Year, y = PerceivedOpportunities, colour = Country, group = Country)) + geom_line()
+
+G1 + ggtitle("Perceived Opportunities Over Time") + theme_bw()
 ```

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
bib works

@@
 output: pdf_document
+bibliography: Main.bib
 ---
@@
 
-**The regulatory framework**: Including administrative burdens, regulations and frameworks, as well as fiscal policy parameters.
+- **The regulatory framework**: Including administrative burdens, regulations and frameworks, as well as fiscal policy parameters.
 
-**The market conditions**: Including anti-trust laws, rules for competition, access to foreign markets, the degree of public involvement and level of private demand.
+- **The market conditions**: Including anti-trust laws, rules for competition, access to foreign markets, the degree of public involvement and level of private demand.
 
-**The access to finance**: Including access to debt financing, access to venture capital, and stock markets.
+- **The access to finance**: Including access to debt financing, access to venture capital, and stock markets.
 
-**The creation and diffusion of knowledge**: Including research and development activity, the transfer of non-commercial knowledge, co-operation among firms, technology availability, and take-up.
+- **The creation and diffusion of knowledge**: Including research and development activity, the transfer of non-commercial knowledge, co-operation among firms, technology availability, and take-up.
 
-**The entrepreneurial capabilities**: Including business and entrepreneurship education as well as immigration.
+- **The entrepreneurial capabilities**: Including business and entrepreneurship education as well as immigration.
 
-**The entrepreneurship culture** of a population.
+- **The entrepreneurship culture** of a population.
 

### 2014-12-12 MiscData/Misc/MiscSims.Rmd
Re-arranged extra repository data

---
title: "Trial Simulations"
author: "Sam"
date: "November 14, 2014"
output: html_document
---

The second simulation was

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis' }

# Set range of PercentFear values in simulation
x.out <- setx(Z1, PercentFear = 20:100)

# Run simulation (default 1000 trials)
simz1 <- sim(Z1, x = x.out)

# Adjust margins
par(mar=c(2,3,2,2))

# Plot simulation
plot(simz1)

```

```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis' }

# Set range of PercentOpportunities values in simulation
x.out3 <- setx(Z1, PercentOpportunities = 20:100)

# Run simulation (default 1000 trials)
simz3 <- sim(Z1, x = x.out3)

# Adjust margins
par(mar=c(2,3,2,2))

# Plot simulation
plot(simz3)

```

### 2014-12-12 MiscData/PresentationandPaper/Draft1.Rmd
Re-arranged extra repository data

--- 2014-12-12 PresentationandPaper/Draft1.Rmd
@@
 
-In addition to understanding the density of each recorded "Way of Teaching" indicator, it is also helpful to examine the differences in this indicator among OECD countries.
-To see this, we have created a figure showing the distribution of the average "Way of Teaching" value over the 2001-2010 period for the OECD countries included in the surveys.
-This figure is included below.
-
-```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
-# Import GEM data frame
-WayofTeaching <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/WayofTeaching", header = TRUE, cache = FALSE, na.strings = "NA")
-
-# Drop unnecessary column 1
-WayofTeaching$X <- NULL
-
-# Change data from long to wide format
-WT <- reshape(WayofTeaching, idvar = c("iso2c", "Country"), timevar = "Year", direction = "wide")
-
-# Delete variable name in Year columns
-names(WT) <- gsub("WayofTeaching.", "", names(WT))
-
-# Duplicate df for future use
-WT2 <- WT
-
-# Generate a new column with mean of all other columns
-WT$mean <- rowMeans(subset(WT, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
-                                          "2009", "2010")), na.rm = TRUE)
-
-# Drop year columns, leaving only mean column
-WT$'2001' <- NULL
-WT$'2002' <- NULL
-WT$'2003' <- NULL
-WT$'2004' <- NULL
-WT$'2005' <- NULL
-WT$'2006' <- NULL
-WT$'2007' <- NULL
-WT$'2008' <- NULL
-WT$'2009' <- NULL
-WT$'2010' <- NULL
-WT$'2011' <- NULL
-WT$'2012' <- NULL
-WT$'2013' <- NULL
-WT$row.names <- NULL
-
-# Create 
-WT[, 3] <- round(log(WT[, 3]), digits = 2)
-```
-
-```{r echo = FALSE, cache= TRUE, include= TRUE, results= 'asis'}
-library(googleVis)
-
-# Plot
-WT_map <- gvisGeoChart(WT, locationvar = 'iso2c',
-                      colorvar = 'mean',
-                      options = list(
-                        colors = "['#ece7f2', '#2b8cbe']"
-))
-
-```
-
-image: ![Way of Teaching](https://raw.githubusercontent.com/SamDund/Assign2Education/master/PresentationandPaper/images/WoTmap.png)
-
 Starting with this explanatory variable, we built three regression equations to examine the impact of our explanatory variable on the rate of entrepreneurship (as measured by survey responses on the percentage of nascent entrepreneurs, established business owners, and respondents with the intention of becoming an entrepreneur).
@@
 
--------------------------
+Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the  dependent variables we selected as indicators of the entrepreneurship rate.
+Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant and has a negative relationship with our explanatory variables.
 
-Based on a review of academic literature and expectations from other data analysis, we expected to see a statistically significant positive relationship between self-confidence reinforcement in teaching and the dependent variables we selected as indicators of the entrepreneurship rate.
-Instead, we found that when controlling for country-specific effects, the Way of Teaching is not statistically significant when using "Nascent Entrepreur" or "Business Owner" as a dependent variable, has a negative coefficient in these regression equations.
-This relationship can be seen in the following regression output table.
-This regression output was generated using a simple least square regression model.
+Overall, however, if we omit country-specific effects, we can demonstrate that the Way of Teaching and the Percent Perceived Good Opportunities are statistically significant in the model indicated below.
+
+We can show the relationship between the dependent and explanatory variables in the four simulations below.
+The R package Zelig allows us to set parameters for an explanatory variable and simulate 1000 trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).
+We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.
+A regression output table has also been included below.
+
+The simulations labeled "Unimputed" were created using only data collected from GEM.
+This simulation is not possible with missing data, so observations with missing data were omitted.
+In an attempt to increase the accuracy of this model, we used the R program Amelia to generate an imputed data frame.
+This program uses statistical inference to generate this data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).
+Simulations titled "Imputed" were calculated using this imputed data frame.
 
@@
 ############ Running a regression with full df (including omitted variables)
-RG1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
+RG1 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
 
-RG2 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
-
-RG3 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
-```
-
-```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
-
-# Create vector of lables
-labels_1 <- c('Way of Teaching', 'Perceived Capabilities', 'Fear of Failure', 'Perceived Good Opportunities', 
-             'Fear of Failure x Perceived Good Opportunities')
-
-dlabels_1 <- c('Entrepreneurial Intention', 'Nascent Entrepreneur', 'Entrepreneurship Owner')
-
-# Regression output table with country-specific effects
-stargazer::stargazer(RG1, RG2, RG3,
-                     title = 'Linear Regression Estimates with Country-specific Effects',
-                     covariate.labels = labels_1, dep.var.labels = dlabels_1, digits = 2,
-                     font.size =  "scriptsize", type = 'latex', no.space = TRUE)
-
-```
-
-To more clearly demonstrate the relationship between the "Way of Teaching" and our dependent variables, we have omitted the country-specific effects and generated simulations to show demonstrate the outcome of 1000 trials of our regression equation.
-Before doing so, however, we ran another set of regressions to determine which equation we would like to examine more closely.
-A regression output table with these results has been included below.
-
-```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
-
-# Run three regression equations again (omitting country-specific effects)
-RG4 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
-
-RG5 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
-
-RG6 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities, data = CD)
-
-```
-
-<br>
-```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
-
-# Regression output table with country-specific effects
-stargazer::stargazer(RG4, RG5, RG6,
-                     title = 'Linear Regression Estimates omitting Country-specific Effects',
-                     covariate.labels = labels_1, dep.var.labels = dlabels_1, digits = 2,
-                     font.size =  "scriptsize", type = 'latex', no.space = TRUE)
-
-```
-
-Given the positive relationship between the "Way of Teaching" and "Entrepreneurship Owner" we decided to use this equation for our simulations.
-Given the prevelence of omitted data in our data frame, we decided to attempt to increase the accuracy of this model by using the R program Amelia to generate an imputed data frame.
-This program uses statistical inference to generate imputed data (more information on the Amelia package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Amelia/index.html)).
-Equation  titled "Imputed" were calculated using this imputed data frame.
-
-To generate the simulations, we decided to use the R package Zelig.
-This package allows us to set parameters for an explanatory variable and simulate trials of the above equation (more information on the Zelig package can be found on the program's [CRAN page](http://cran.r-project.org/web/packages/Zelig/index.html).
-We chose to simulate values in "Percent Perceived Capabilities" and "Way of Teaching" for this analysis.
-A regression output table and our simulation results are included below.
-Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables."
-
-```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
+RG2 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear*PercentOpportunities + PercentOpportunities + Country, data = CD)
 
@@
 ```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
-
-# Set new vector for dependent variable label
-dlabels_2 <- c('Entrepreneurship Owner')
-
-# Regression output table with country-specific effects
-stargazer::stargazer(Z1, Z2,
-                     title = 'Linear Regression Estimates omitting Country-specific Effects',
-                     covariate.labels = labels_1, dep.var.labels = dlabels_2, digits = 2,
-                     font.size =  "small", type = 'latex', no.space = TRUE,
-                     notes = "Regression equation 1 is unimputed, regression equation 2 is imputed")
-```
-
-```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
 library("Zelig")
@@
 ```
+
+```{r echo = FALSE, cache= FALSE, include= FALSE, results= 'asis'}
+library(stargazer)
+
+# Create regression output table
+labels <- c('Way of Teaching', 'National Level Perceived Capabilities', 'National Level Avg Fear of Failure',
+            'National Level Avg Perceived Good Opportunities', 
+            'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities',
+            '(Intercept)')
+
+dlabels <- c('National Level Average Percent Owning a Business')
+
+```
+
+<br>
+
+```{r echo = FALSE, cache= FALSE, include= TRUE, results= 'asis'}
+
+stargazer::stargazer(Z1, Z2, covariate.labels = labels, dep.var.labels = dlabels,
+                     title = 'Linear Regression Estimates', notes = "Regression equation 1 is unimputed, regression equation 2 is imputed", digits = 2, type = 'html')
+
+```
+
+```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis', warning=FALSE}
+
+# Run linear regression R1
+R1 <- lm(PercentIntention ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)
+
+# Run linear regression R2
+R2 <- lm(PercentNascent ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)
+
+# Run linear regression R3
+R3 <- lm(PercentOwner ~ WayofTeaching + PercentPerceived + PercentFear + PercentOpportunities + PercentFear*PercentOpportunities + Country, data = CD)
+
+```
+
+```{r echo = FALSE, cache=TRUE, include=TRUE, results='asis', warning=FALSE}
+
+# Library Stargazer for regression output tables
+library(stargazer)
+
+# Create regression output table
+labels <- c('National Level Avg Perceived Capabilities', 'National Level Avg Fear of Failure',
+            'Annual GDP Growth', 'National Level Avg Perceived Good Opportunities', 'National Level Avg Fear of Failure x National Level Avg Perceived Good Opportunities','(Intercept)')
+
+dlables <- c('National Level Average Percent Entrepreneurial Intention', 'National Level Nascent Entrepreneural Activity', 'National Level Average Percent Owning a Business')
+
+stargazer::stargazer(R1, R2, R3, covariate.labels = labels, dep.var.labels = dlables,
+                     title = 'Linear Regression Estimates', digits = 2)

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Main Bib

@@
 Of course, what determines entrepreneurship at a country-level has been long searched already but although structural and environmental factors have been looked at extensively, less has been done regarding cultural or educational factors.
-Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@Freytag2007] ??????
-2010 VERSION MAIN BIB ?????.
+Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@freytag2010entrepreneurship].
 Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done.
@@
 As they compared two Swedish regions similar in terms of structure and observed different outcomes, they too concluded that there might be a small cultural effect in attitudes toward start-up activities.
-In 2010, Freytag and Thurik ?????
-2010 VERSION MAINBIB ?????
-have also studied determinants of entrepreneurship in a cross-country setting and pointed at cultural features.
+In 2010, Freytag and Thurik [@freytag2010entrepreneurship] have also studied determinants of entrepreneurship in a cross-country setting and pointed at cultural features.
 Their results showed that "country specific (cultural) variables seem to explain the preference for entrepreneurship" and self-employment.
@@
 Rather than trying to trace cultural features at large, as we mentioned earlier, we intend to focus specifically on one key cultural institution, that is the education system.
-Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996] which is key as "individuals who decide to start a new business exhibit more confidence than those who do not"  ???????
-Robin M.
-Hogarth and Natalia Karelaia 2011 Entrepreneurial success and failure MAIN BIB ?????????.
+Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996] which is key as "individuals who decide to start a new business exhibit more confidence than those who do not" [@hogarth2012entrepreneurial].
 Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].
@@
 
-Our focus on the education systems stems partly from experience and from Inglehart research ?????????
-MAIN BIB 2000 ????????
-.
+Our focus on the education systems stems partly from experience and from Inglehart research [@inglehart2000modernization] .
 Indeed, we understand the period between 0 and 20 years of age to be a defining time in terms of personal values and personality construction, thus compulsory education, generally between 6 and 16 years of age, can prove of key importance in the building up of one's self-confidence.
 We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.
-This assumption draws from Boyd and Vozikis's ???????
-MAIN BIB ????????
-stating how entrepreneurial intentions are at least partially the result of thought processes, which "underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour".
+This assumption draws from Boyd and Vozikis's [@boyd1994influence] stating how entrepreneurial intentions are at least partially the result of thought processes, which "underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour".
 Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours".
-To assert this, they rely on Fishbein and Ajzen 1975 ??????
-MAIN BIB ????????
-who illustrate the relation between beliefs and behaviour as follows:
+To assert this, they rely on Fishbein and Ajzen [@fishbein1975belief] who illustrate the relation between beliefs and behaviour as follows:
 
@@
 There could even be an incidence of the intention to perform a certain behaviour on the actual performance of that behaviour, which could lead to look into skills, abilities and willpower.
-It is almost like "individuals would be predisposed to entrepreneurial intentions based upon a combination of both personal and contextual factors" ?????
-Boyd and Vosikis MAIN BIB ?????
-but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality for "self-efficacy will moderate the relationship between the development of entrepreneurial intentions and the likelihood that these intentions will result in entrepreneurial actions or behaviour".
+It is almost like "individuals would be predisposed to entrepreneurial intentions based upon a combination of both personal and contextual factors" [@boyd1994influence] but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality for "self-efficacy will moderate the relationship between the development of entrepreneurial intentions and the likelihood that these intentions will result in entrepreneurial actions or behaviour".
 Therefore, we will have to control for this entrepreneurial self-efficacy as we research potential effects of positive reinforcement.
@@
 Eventually, this goes without saying, we also looked into other studies connecting educational features and entrepreneurship.
-As a matter of fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy ???????
-Boyd and Vosikis MAIN BIB ???????????
-.
+As a matter of fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy [@boyd1994influence].
 One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions with students, can increase the rate of youth entrepreneurship but their perspective was still not directly in line with our research design, they  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
-
-????????????????????????????????????????????????????????????????????????????????????????????
-
-The cross-cultural perspective on teaching and learning proposed by Watkins [@Watkins2010] shall help us compare countries.
-
-Cheng and Wong’s study about school effectiveness in East Asia [@Cheng2006] will also help.
-
-Eventually, to put all these into perspective, along with Gartner [@Gartner1990] we will have a closer look at entrepreneurship’s underlying meanings in research and, with Acs, Desai and Klapper [@Acs2008], we will ask ourselves what “entrepreneurship” data really shows.
-
-?????????????????????????????????????????????????????????????????????????????????????????????
 

### 2014-12-12 index.Rmd
Organization of repository

@@
 # Create a vector of packages used
-pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv', 'Zelig',
-          'stargazer', 'Amelia')
+pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv')
 

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
minor edit

@@
 author: "Sam Dundon and Thierry Racaud"
-date: "10 December 2014"
+date: "12 December 2014"
 linestretch: 2 
@@
 
-Whilst it is tempting to look at education systems in a very pragmatic way with ratios of teachers per student, or number of students per class, we suggest to use another kind of indicator in order to trace the potential long-term investment made by governments.
+While it is tempting to look at education systems in a very pragmatic way with ratios of teachers per student, or number of students per class, we suggest to use another kind of indicator in order to trace the potential long-term investment made by governments.
 Indeed, we believe that education systems can favour entrepreneurship and, beyond, GDP growth at the country-level, depending on how supportive of students' self-confidence and how socially inclusive they are.
@@
 
-Grilo and Thurik [@Grilo2005b] who looked into what determines entrepreneurship engagement levels throughout the European Union and the US pointed especially at the level of financial support available for entrepreneurs in the country and also at administrative complexities.
-
-Of course, what determines entrepreneurship at a country-level has been long searched already but although structural and environmental factors have been looked at extensively, less has been done regarding cultural or educational factors.
-Yet, “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@freytag2010entrepreneurship].
+This framework and studies such as that by Grilo and Thurik [@Grilo2005b], who looked into what determines entrepreneurship engagement levels throughout the European Union and the U.S., provides a helpful starting point for our analysis.
+However, rather than focusing on the structural and environmental factors driving the rate of entrepreneurship at a country-level -- which as been researched extensively already -- we have chosen to examine cultural and educational factors.
+We reached this decision following research indicating that “the relative stability of differences in entrepreneurship across countries suggests that factors other than economic ones are at play” [@freytag2010entrepreneurship].
 Even if “in recent years research has increasingly devoted itself to the subject” [@OECD2009], a lot still needs to be done.
 
-Over a hundred years have passed since Max Weber tried to explain how religious-ethical motivations affect entrepreneurship [@weberprotestant], and today religion may be less effective in justifying why some are more likely to start businesses than others.
-Still, that was a founding stone and it is now widely admitted that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” [@OECD2009].
+Research on these factors began as early as a hundred years ago, when Max Weber attempted to explain how religious-ethical motivations affect entrepreneurship [@weberprotestant].
+Today, religion may be less effective in justifying why some are more likely to start businesses than others, but this effort served as a founding stone and it is now widely recognized that “cultural features influence attitudes towards start-ups and that these attitudes, in turn, have an impact on start-up activities” [@OECD2009].
 
-More recently, Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid a stepping stone by investigating the relationship between structural factors, mainly economic, and cultural factors.
+More recently, Davidsson, along with Delmar at first (1992), then alone (1995), then with Wiklund [@davidsson1997values], at his turn, laid subsequent stepping stones by investigating the relationship between structural factors, mainly economic, and cultural factors.
 As they compared two Swedish regions similar in terms of structure and observed different outcomes, they too concluded that there might be a small cultural effect in attitudes toward start-up activities.
@@
 
-Rather than trying to trace cultural features at large, as we mentioned earlier, we intend to focus specifically on one key cultural institution, that is the education system.
-Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996] which is key as "individuals who decide to start a new business exhibit more confidence than those who do not" [@hogarth2012entrepreneurial].
+Rather than trying to trace cultural features at large, as we mentioned earlier, we intend to focus specifically on one key cultural institution, the education system.
+Indeed, like many in the education literature tend to assert, we believe that school personnel have an affect on students' self-confidence [@Scott1996], which is key as "individuals who decide to start a new business exhibit more confidence than those who do not" [@hogarth2012entrepreneurial].
 Now in entrepreneurship literature, "self-confidence was found to depend almost exclusively on the individual features of the respective person and his or her integration in social networks " [@OECD2009].
 
-Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012, there seem to be different amounts of self-confidence and entrepreneurial self-efficacy between countries.
+Still, if we look at the following data from the [Global Entrepreneurship Monitor (GEM)](http://www.gemconsortium.org) Adult Population Survey (APS) from 2012, there seem to be different degrees of self-confidence and entrepreneurial self-efficacy between countries.
 By a country's entrepreneurial self-efficacy we mean the belief that the average individual of that country holds about his or her abilities to succeed as an entrepreneur.
-Here, the variable "perceived capabilities" has to be understood in a narrow sense, it refers only to the perceived capabilities to start a business.
-Seemingly the variable "fear of failure" only refers to the fear of failure as an obstacle in starting a business, despite the perceived good opportunities.
+Here, the variable "Perceived Capabilities" should be understood in a narrow sense, it refers only to the perceived capabilities to start a business.
+Seemingly the variable "Fear of Failure" only refers to the "Fear of Failure" as an obstacle in starting a business, despite the "Perceived Opportunities."
 
@@
 
-1 Beliefs  
-2 Attitudes  
-3 Intentions  
-4 Behaviour
+\begin{singlespace}
 
-There could even be an incidence of the intention to perform a certain behaviour on the actual performance of that behaviour, which could lead to look into skills, abilities and willpower.
-It is almost like "individuals would be predisposed to entrepreneurial intentions based upon a combination of both personal and contextual factors" [@boyd1994influence] but Boyd and Vosikis building upon social psychology research introduce the concept of self-efficacy in Bird's model of entrepreneurial intentionality for "self-efficacy will moderate the relationship between the development of entrepreneurial intentions and the likelihood that these intentions will result in entrepreneurial actions or behaviour".
-Therefore, we will have to control for this entrepreneurial self-efficacy as we research potential effects of positive reinforcement.
+1. Beliefs
 
-Eventually, this goes without saying, we also looked into other studies connecting educational features and entrepreneurship.
-As a matter of fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy [@boyd1994influence].
-One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions with students, can increase the rate of youth entrepreneurship but their perspective was still not directly in line with our research design, they  asserted that a more business-like environment in K-12 education was the key, which was favoured by voucher programmes.
+2. Attitudes
+
+3. Intentions
+
+4. Behaviour  
+\end{singlespace}
+
+There could even be an incidence of the intention to perform a certain behaviour on the actual performance of that behaviour, which could make research into skills, abilities and willpower an important step in understanding entrepreneurship rates.
+This sentiment was echoed by Boyd, who stated "individuals would be predisposed to entrepreneurial intentions based upon a combination of both personal and contextual factors" [@boyd1994influence].
+This has been further stregthened in research by Boyd and Vosikis, building upon social psychology research, as they introduced the concept of self-efficacy in Bird's model of entrepreneurial intentionality, saying "self-efficacy will moderate the relationship between the development of entrepreneurial intentions and the likelihood that these intentions will result in entrepreneurial actions or behaviour." Therefore, we will need to control for this entrepreneurial self-efficacy as we research the potential effects of positive reinforcement.
+
+We also looked into other studies connecting educational features and entrepreneurship.
+In fact, most of the research tends to focus specifically on entrepreneurial education, whatever its form, as it is expected partly to support the entrepreneurial self-efficacy [@boyd1994influence].
+One slightly different and interesting perspective is that of King and Sobel [@Kerry2008], who have already tried to show how school choice, and thus a different kind of interactions with students, can increase the rate of youth entrepreneurship.
+However, their perspective was still not directly in line with our research design, as they  asserted that a more business-like environment -- favoured by voucher programs -- in K-12 education was the key answer to their research question.
 
@@
 
-At this stage, having explained how determinants of entrepreneurship have been looked into, having mentioned how education has been related to entrepreneurship so far, we need to assert here our very research question which is:
+At this stage, having explained how the determinants of entrepreneurship have been researched and having mentioned how education has been related to entrepreneurship so far, we need to assert here our research question:
 
-To what extent does the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries?
+*To what extent does the support of students' self-confidence within the education system impacts the rate of entrepreneurship across OECD countries?*
 
@@
 
----> Education system reinforcing self-confidence
+1. An education system reinforcing self-confidence
 
----> Higher degree of individual self-confidence
+2. Higher degree of individual self-confidence
 
----> Higher probability an individual will become an entrepreneur
+3. Higher probability an individual will become an entrepreneur
 
----> higher rate of entrepreneurship at a country-level.
+4. Higher rate of entrepreneurship at a country-level
 
@@
 # Import csv of df with imputed figures (created in Index_sources/Amelia_source)
-CI <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/gh-pages/GEMData/Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)
+CI <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/gh-pages/MiscData/GEMData/Cimputed5.csv", header = TRUE, sep = ",", na.strings = NA)
 

### 2014-12-12 PresentationandPaper/Draft1.Rmd

@@
 ```
+
+### Abstract
+
+The process of allocating public funds for education is an opportunity to make calculated long-term investments in a nation's populace.
+The rationale for decisions made during this process, however, is often difficult to understand.
+That is, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors - not just structural and economic factors - in determining individual and societal tendencies to start a business, these factors are often not included in the decision-making process.
+Actually, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.
+We believe that education systems can favour entrepreneurship and, beyond, GDP growth at the country-level, depending on how supportive of students' self-confidence and how socially inclusive they are.
+We see this process as many-fold but we only focus here on one of the potential causal relations.
+We want to understand specifically to want extent the support of individual self-confidence within education systems can affect the likelihood to become an entrepreneur, and thus impact the rate of entrepreneurship at the country level.
+We use the Global Entrepreneurship Monitor data, both the Adult Population Survey (APS) and the National Expert Survey (NES) to characterise the features of education systems across OECD countries from 2001 until 2010.
+We control for the average entrepreneurial self-efficacy across the population as well as for the perceived opportunities to start a business.
+Due to scarce data, due to some flaws in the collection, we cannot ascertain here that the causal chain we look into actually takes place but we firmly believe that is a need for another type of indicators to deepen the research in that direction.

### 2014-12-12 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Final commit

@@
 ### Abstract
+
+\begin{singlespace}
+
+The process of allocating public funds for education is an opportunity to make calculated long-term investments in a nation's populace.
+The rationale for decisions made during this process, however, is often difficult to understand.
+That is, while many claims have been made in entrepreneurship literature regarding the importance of cultural and educational factors - not just structural and economic factors - in determining individual and societal tendencies to start a business, these factors are often not included in the decision-making process.
+Actually, only a few empirical studies have been carried out on this topic and most of them focused on which attitudes were favourable to starting a business, while almost none explored what determined these dispositions.
+
+We believe that education systems can favour entrepreneurship and, beyond, GDP growth at the country-level, depending on how supportive of students' self-confidence and how socially inclusive they are.
+We see this process as many-fold but we only focus here on one of the potential causal relations.
+We want to understand specifically to want extent the support of individual self-confidence within education systems can affect the likelihood to become an entrepreneur, and thus impact the rate of entrepreneurship at the country level.
+
+We use the Global Entrepreneurship Monitor data, both the Adult Population Survey (APS) and the National Expert Survey (NES) to characterise the features of education systems across OECD countries from 2001 until 2010.
+We control for the average entrepreneurial self-efficacy across the population as well as for the perceived opportunities to start a business.
+Due to scarce data, due to some flaws in the collection, we cannot ascertain here that the causal chain we look into actually takes place but we firmly believe that is a need for another type of indicators to deepen the research in that direction.
+
+\end{singlespace}
 
@@
 The support of students' self-confidence within education systems as we just defined it can also affect the students' entrepreneurial self-efficacy, that should be controlled for.
-To do so, we will look at the average perceived entrepreneurial capabilities and fear of failure in starting a business across the population at the country-level.
+To do so, we will look at the average perceived entrepreneurial capabilities and "Fear of Failure" in starting a business across the population at the country-level.
 
@@
 
-Regarding potential control variables, we should normally consider including at least the main environmental determinants of entrepreneurship but the lack of consistency in the data at hand for our explanatory variables made us use a summary of those as a proxy.
+Regarding potential control variables, we should normally consider including at least the main environmental determinants of entrepreneurship, but the lack of consistency in the data at hand for our explanatory variables made us use a summary of those as a proxy.
 We chose to use the level of good opportunities to start a business perceived on average across the population of the given country.
@@
 
-*Data Sources*
+**Data Sources**
 
@@
 Experts are chosen based on experience and specialization and are expected to represent the entire country (including urban and rural areas).
-
-<br>
 
@@
 
-Additional information on the GEM data used for this research can be seen in the descriptive statistics table included below.
+Additional information on the GEM data used for this research can be seen in the descriptive statistics table  below.
 
@@
 
+# This map will not display in a static Latex document.  Instead, we have included a screanshot of the map as it appears in an html file.
+
 ```
 
-image: ![Way of Teaching](https://raw.githubusercontent.com/SamDund/Assign2Education/master/PresentationandPaper/images/WoTmap.png)
+![Way of Teaching](https://raw.githubusercontent.com/SamDund/Assign2Education/master/PresentationandPaper/images/WoTmap.png)
 
@@
 The interaction term $\beta_5FearFailure*PerceivedOpportunities$ was added to the regression because the survey question regarding "Fear of Failure" was only proposed to survey respondents who indicated they do perceive opportunities to start a business.
-
--------------------------
 
@@
 
-Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables." A regression output table and our simulation results are included below.
+Given our data characteristics and the available models in the Zelig package, we used a "Least Squares Regression for Continuous Dependent Variables." A regression output table and our simulation results are below.
 
@@
 In addition, this process reduced the variance in our simulation results, suggesting it improved the accuracy of this model.
-Despite this, we have several concerns regarding the reliability of existing GEM data (which will be discussed later in this paper), which makes us question the effectiveness of using this data to generate additional observations.
+Despite this, we have several concerns regarding the reliability of existing GEM data (which will be discussed in the next section), which makes us question the effectiveness of using this data to generate additional observations.
 
-Perceived opportunities
+**Limitations of the data**
+
+From the results and from the description of the data made earlier, one can easily foresee quite a few limitations to the consistency and effectiveness of the data we used for this research.
+Although they are obvious, one should still name them here.
+
+The GEM National Expert Survey however interesting and innovative for its extensive look into new sorts of data still allows for much improvement.
+It is essentially supposed to help control for the environmental determinants of entrepreneurship, which are here called the framework conditions.
+The major issue is not so much what it aims at revealing of the entrepreneurial context of each country but it has much more to do with methodology of data collection.
+Indeed, for each of these framework conditions, only four experts answered the survey, which makes the measure be very dependent on the individual respondent.
+This leads to highly variant data.
+Besides, the national teams hired by GEM Coordination Team were reported by GEM itself to manage time allocated for data collection rather poorly.
+That is, while they had five months at their disposal to approach and survey four experts for each framework condition, they happened on a regular basis to be in a hurry in July and therefore ended up relying on their personal connections to answer the surveys [@OECDProject].
+
+Regarding the "Way of Teaching" variable that we used as a proxy for a way of teaching supportive of students' self-confidence, it is quite variant from year to year, which is not quite what we would expect.
+Indeed, as we look at the way of teaching and education features, these are generally culture related and as such should be much less fluctuant.
+At most, they should vary due to reforms being implemented at national, federal or state level, but that does not take place every year, rather every four or five years or even less frequently.
+Thus this yearly change is very unlikely to be an accurate indicator of how supportive of students' self-confidence teaching is like in a given country.
+On top of that, we purposely selected one item among the six used to characterise potential entrepreneurial education (Way of Teaching).
+Isolating that one item from the other 5 factors may have lessened the indicator's reliability.
+In addition, the scale between 0 and 5 makes the assessment even more approximate.
+As a result of all these flaws combined leads to some variations of up to 1 point for some countries, including Denmark.
+
+Now looking at GEM Adult Population Survey (APS), even if the data is directly collected by GEM from representatives samples of the population (around 2000 peole), once again we observe huge variation for indicators such as the "Perceived Opportunities," which are unlikely to fluctuate that much in reality.
+That very indicator was used as a proxy for many potential control variables regarding economic outlook and other environmental determinants of entrepreneurship, and we do not expect the level of financing, the level of public programmes or the GDP growth for instance to vary that much from year to year.
+The subjective perception this indicator entails should have been balanced by the representativity of the sample and thus should not show so much variance.
+Once more, even if we are very doubtful about that data.
+
+A final issue has been the scarcity of the data.
+For the "Perceived Capability", "Perceived Oportunities" and "Fear of Failure" indicators, there are already several missing observations.
+However, for our explanatory variable, "Way of Teaching," there is considerably more missing obersvations.
+In fact, many countries have only data a few of the years we were looking into.
+Those who had the most data were at least missing three years, and three countries (Estonia, Luxembourg and Slovak Republic) had no data available at all.
+We have included a chart of "Perceived Opportunties" below to illustrate how this data has been inconsistent over time.
 
@@
 
-**Results**
-
-**Limitations of the data**
-
-From the results and from the description of the data made earlier, one can easily foresee quite a few limitations to the consistency and effectiveness of the data we used for this research.
-Although they are obvious, one should still name them here.
-
-The GEM National Expert Survey however interesting and innovative for its extensive look into new sorts of data still allows for much improvement.
-It is essentially supposed to help control for the environmental determinants of entrepreneurship, which are here called the framework conditions.
-The major issue is not so much what it aims at revealing of the entrepreneurial context of each country but it has much more to do with methodology of data collection.
-Indeed, for each of these framework conditions, only four experts answered the survey, which makes the measure be very dependent on the individual respondent.
-This leads to highly variant data.
-Besides, the national teams hired by GEM Coordination Team were reported by GEM itself to manage time allocated for data collection rather poorly.
-That is, while they had five months at their disposal to approach and survey four experts for each framework condition, they happened on a regular basis to be in a hurry in July and therefore ended up relying on their personal connections to answer the surveys.
-
-Regarding the D01 indicator that we used as a proxy for a way of teaching supportive of students' self-confidence, it is quite variant from year to year, which is not quite what we would expect.
-Indeed, as we look at the way of teaching and education features, these are generally culture related and as such should be much less fluctuant.
-At most, they should vary due to reforms being implemented at national, federal or state level, but that does not take place every year, rather every four or five years, sometimes only once a decade or even less frequently.
-Thus this yearly change is very unlikely to be a faithful figuration of how supportive of students' self-confidence teaching is like in a given country.
-On top of that, we purposely selected one item among the six used to characterised potential entrepreneurial education.
-That one item cannot be compensated by others in our study, which probably worsened the effect.
-The scale between 0 and 5 makes the assessment even more approximate.
-As a result of all these flaws combined leads to some variations of up to 1 point for some countries, like for Denmark for instance.
-
-Now looking at GEM Adult Population Survey (APS), even if the data is directly collected by GEM from representatives samples of the population (around 2000 peole), once again we observe huge variation for indicators such as the perceived opportunities, which are unlikely to fluctuate that much in reality.
-That very indicator was used as a proxy for many potential control variables regarding economic outlook and other environmental determinants of entrepreneurship, and we do not expect the level of financing, the level of public programmes or the GDP growth for instance to vary that much from year to year.
-The subjective perception this indicator entails should have been compensated by the representativity of the sample and thus should not show so much variance.
-Once more, even if we are very doubtful about that data.
-
-Last but not least is the scarcity of the data.
-For the perceived capabilities, perceived opportunities and fear of failure, there are already a few missing data but this gets much worse regarding the way of teaching.
-For that key explanatory variable, many countries have only data for have the years we were looking into, those who had the most data were at least missing three years, and three countries (Estonia, Luxembourg and Slovak Republic) had no data available at all.
-
-Adding up all these limitations of the data we used, it does not come as a surprise that we could hardly get significant coefficients and could only observe general trends.
+Considering these data limitations, it does not come as a surprise that we struggled to obtain significant parameters and could only observe general trends.
 
@@
 
-Education systems tend to be assessed in terms of numbers of students, ratios of teachers among other quantitative measures but what we tried to suggest here is that they could be looked at in quite a different way.
+Education systems tend to be assessed in terms of numbers of students, ratios of teachers among other quantitative measures, but what we tried to suggest here is that they could be looked at in quite a different way.
 As governments allocate public funds for education, they happen to make a long term investment, and, although this may not come as news, we intended here to propose a different rationale in doing so.
@@
 
-From the research we attempted to conduct here, due to poor quality and inconsistent data, we cannot ascertain our point but we still firmly believe there could be something happening out there and this should be looked into more.
-Now that would mean collecting the adequate amount of data and computing a new kind of indicators that are not yet available.
+From the research we attempted to conduct here, due to poor quality and inconsistent data, we cannot ascertain our point, but still firmly believe there is an under recognized impact of education on entrepreneurship and this should be more thoroughly explored.
+This would require additional collection and analysis of data and the creation of new kinds of indicators that are not yet available.
 This surely is a prospect for future research.
+
+**References**

### 2014-12-12 index.Rmd
final commit

@@
 This can be seen in the chart below.
-As we can see, however, when we add a trendline for each country the relationship becomes less certain.
-For example, in the case of the United States and the United Kingdom, the country-specific trend line has a decreasing slope.
+For example, in the case of the United States and the United Kingdom, the country-specific trend appears to have a decreasing slope.
 We believe this may be due to inconsistency in the survey and that a larger data set would allow us to more accurately describe the relationship between these variables.
